
@STRING{ACTA = "Acta Informatica"}
@STRING{AIAAJ = "AIAA Journal"}
@STRING{AJP = "American Journal of Physics"}
@STRING{ARFM = "Annual Review of Fluid Mechanics"}
@STRING{CACM = "Communications of the ACM"}
@STRING{CAMCOS = "Comm. App. Math. and Comp. Sci."}
@STRING{CMP = "Comm. Math. Phys."}
@STRING{COMBST = "Combustion Science and Technology"}
@STRING{COMP-SURVEY = "ACM Computing Surveys"}
@STRING{COMPLANG = "Computer Languages"}
@STRING{COMPUTER = "IEEE Computer"}
@STRING{CPAM = "Comm. Pure and Appl. Math."},
@STRING{IEEEASSP = "IEEE Transactions on Acoustics, Speech, 
	and Signal Processing"}
@STRING{IEEETC = "IEEE Transactions on Computers"}
@STRING{IEEETSE = "IEEE Transactions on Software Engineering"}
@STRING{IEEES = "IEEE Software"}
@STRING{IJSC = "International Journal on Supercomputing"}
@STRING{IJNMF = "Int. J. Numer. Meth. Fl."}
@STRING{JACM = "Journal of the ACM"}
@STRING{JAS = "J. Aero. Sci."}
@STRING{JCP = "J. Comput. Phys."}
@STRING{JCSS = "Journal of Computer and System Sciences"}
@STRING{JFM = "J. Fluid Mech."}
@STRING{JOTA = "Journal of Optimization Theory and Applications"}
@STRING{JPDC = "Journal of Parallel and Distributed Computing"}
@STRING{JCHEMPHYS = "J. Chem. Phys."}
@STRING{LBL = "Lawrence Berkeley Laboratory"}
@STRING{NM = "Numerische Mathematique"}
@STRING{PES = "Polymer Engineering and Science"}
@STRING{PECS = "Progress in Energy and Combustion Science"}
@STRING{PF = "Phys. Fluids"}
@STRING{SIAMJC = "SIAM Journal on Computing"}
@STRING{SIAMJNA = "SIAM J. Numer. Anal."}
@STRING{SIAMJSSC = "SIAM Journal on Scientific and Statistical Computing"}
@STRING{SIAMJSC = "SIAM J. Sci. Comput."}
@STRING{SIAMJAM = "SIAM Journal on Applied Mathematics "}
@STRING{SIGPLANNOTICES = "ACM SIGPLAN Notices"}
@STRING{SPE = "Software Practice \& Experience"}
@STRING{SPET = "SPE Transactions"}
@STRING{TOMS = "ACM Transactions on Mathematical Software"}
@STRING{TOPLAS = "ACM Transactions on Programming Languages and Systems"}
@STRING{TUGBOAT = "{\sc TUGboat}: The Communications of the {\TeX}
	Users Group"}

#===============================================================================
# CROSSREFERENCES
#===============================================================================

#-------------------------------------------------------------------------------
# Chombo
#-------------------------------------------------------------------------------

@TechReport{Chombo,
  crossref =     {ChomboDesign}
}

#-------------------------------------------------------------------------------
# Runtimes
#-------------------------------------------------------------------------------

@InProceedings{Legion2012,
  crossref =     {Bauer2012}
}

@InProceedings{StarPU2010,
  crossref =     {Augonnet2010}
}

#===============================================================================

    ###
   #   #
   #   #
   #####
   #   #
   #   #
   #   #


@TechReport{exascale,
  author =       {Advanced Scientific Computing Advisory Committee Subcommittee},
  title =        {The opportunities and challenges of exascale computing},
  institution =  {DOE},
  year =         {2010},
  OPTkey =       {},
  OPTtype =      {},
  OPTnumber =    {},
  OPTaddress =   {},
  OPTmonth =     {},
  OPTnote =      {},
  OPTannote =    {}
}

 "", , , 14:105-119, doi: DOI: 10.2140/camcos.2019.14.105

@ARTICLE{Lo2019,
author = {Boris Lo and Phillip  Colella},
title  = {An Adaptive Local Discrete Convolution Method for the Numerical Solution of Maxwell's Equations},
journal = {Communications in Applied Mathematics and Computational Science}, 
date = {April 26, 2019},
volume = {14},
pages = {105-119},
doi  = {DOI: 10.2140/camcos.2019.14.105}
}

@MISC{eigenweb,
  author = {Ga\"{e}l Guennebaud and Beno\^{i}t Jacob and others},
  title = {Eigen v3},
  howpublished = {http://eigen.tuxfamily.org},
  year = {2010}
 }
 
@article {Abid1999,
	author = {Abid, M. and Wu, M. S. and Liu, J. B. and Ronney, P. D. and Ueki, M. and Maruta, K. and Kobayashi, H. and Niioka, T. and VanZandt, D. M.},
	title = {Experimental and Numerical Study of Flame Ball {IR} and {UV} Emissions},
	journal = {Combust. Flame},
	year = {1999},
	volume = {116},
	number = {},
	pages = {348--359},
	month = {},
	note = {}
	}

@article{Abgrall2001,
author = {Abgrall, R. and Karni, S.},
title = {Computations of compressible multifluids},
journal = JCP,
volume = {169},
number = {2},
pages = {594 -- 623},
year = {2001},
issn = {0021-9991},
OPTdoi = {https://doi.org/10.1006/jcph.2000.6685},
OPTurl = {http://www.sciencedirect.com/science/article/pii/S0021999100966853}
}

@article{Abgrall2006,
author = {Abgrall, R.},
title = {Residual distribution schemes: current status and future trends},
journal = {Comput. Fluids},
volume = {35},
number = {},
pages = {641 -- 669},
year = {2006},
OPTdoi = {10.1016/j.compfluid.2005.01.007},
}

@article{Adams1996,
author = {Adams, N.A. and Shariff, K.},
title = {A high-resolution hybrid compact-{ENO} scheme for shock-turbulence interaction problems},
journal = JCP,
volume = {127},
number = {},
pages = {27--51},
year = {1996},
}

@inbook{Aftosmis2000,
author = {M. Aftosmis and M. Berger and G. Adomavicius},
title = {A parallel multilevel method for adaptively refined {C}artesian grids with embedded boundaries},
booktitle = {38th Aerospace Sciences Meeting and Exhibit},
year = {2000},
doi = {10.2514/6.2000-808},
}

@TechReport{AIAA-VnV1998,
  author =       {AIAA},
  title =        {Guide for the Verification and Validation of Computational Fluid Dynamics Simulations},
  institution =  {AIAA},
  year =         1998,
  number =       {G-077-1998}}

@article {Aldama1991,
author = {Aldama, A. A. and Harleman, D. R. F.},
title = {The approximation of nonlinearities in the filtered {N}avier-{S}tokes equations},
journal = {Adv. Water Resources},
year = {1991},
volume = {14},
number = {1},
pages = {15--30},
month = {July},
note = {}
}

@article {Alexander1967,
author = {Alexander, J. D.},
title = {Dual mode magnus rotor bomblet},
journal = {Proceedings of Conference on Dynamics and Aerodynamics of Bomblets, Air Force Armament Laboratory Report No. AFATL-TR-67-195},
year = {1967},
volume = {1},
number = {},
pages = {389-418},
month = {October},
note = {}
}

@article {Allmaras2012,
author = {Allmaras, S. R. and Johnson, F. T. and Spalart, P. R.},
title = {Modification and Clarifications for the Implementation of the Spalart-Allmaras Turbulence Model},
journal = {Seventh International Conference on Computational Fluid Dynamics},
year = {2012},
volume = {ICCFD7-1902},
number = {},
pages = {},
month = {July},
note = {}
}


@article {AlzuetaBilbao1998,
author = {Alzueta, M. U. and Bilbao, R. and Millera, A. and Glarborg, P. and {\O}stberg, M. and Dam-Johansen, K.},
title = {Low Temperature Gas Reburning. {NO}$_x$ Reduction Potential and Effects of Mixing},
journal = {Energy Fuels},
year = {1998},
volume = {12},
number = {},
pages = {329-338},
month = {},
note = {}
}

@article{Asbai2021,
author = {Asbai-Ghoudan, R. and {Ruiz de Galarreta}, S. and Rodriguez-Florez, N.},
title = {Analytical model for the prediction of permeability of triply periodic minimal surfaces},
journal = {Journal of the Mechanical Behavior of Biomedical Materials},
volume = {124},
pages = {104804},
year = {2021},
issn = {1751-6161},
doi = {https://doi.org/10.1016/j.jmbbm.2021.104804}
}

@book {Annual2002,
author = {Energy Information Administration},
title = {Annual Energy Review 2002},
year = {2003},
publisher = {U.\ S.\ Department of Energy},
edition = {},
address = {Washington},
note = {GPO Stock No\ 061-003-01134-9}
}

@unpublished {ANAG,
 author = {Colella, P.},
 title = {Chombo - Software for Adaptive Solutions of Partial Differential Equations},
 note = {https://seesar.lbl.gov/anag},
 month = {},
 year = {2000}
}


@Misc{5how,
  title =     {5th International Workshop on High Order {CFD} Methods},
  OPThowpublished = {},
  month =     {Jan},
  year =      {2018},
  note =      {https://how5.cenaero.be/},
  OPTannote =    {}
}

 
https://how5.cenaero.be/
@article {Angioletti2005, 
author = {Angioletti, M. and E. Nino and G. Ruocco}, 
title = {CFD turbulent modeling of jet impingement and its validation by PIV and mass transfer measurements}, 
journal = {Int. J. Thermal Sci.}, 
year = {1992}, 
volume = {96}, 
number = {}, 
pages = {1388--1392}, 
month = {}, 
note = {} 
}

@book{Anderson1989,
  title={Hypersonic and High Temperature Gas Dynamics},
  author={Anderson, J. D.},
  year={1989},
  publisher={McGraw-Hill},
  address={New York}
}

@BOOK{Anderson1990,
    AUTHOR={J. D. Anderson},
    TITLE={Modern Compressible Flow with Historical Perspective},
    PUBLISHER={McGraw-Hill},
    ADDRESS={New York},
    OPTEDITION = {2nd edition},
    YEAR={1990}   }


@article {Anderson1999, 
author = {J. L. Anderson and S. L. Anderson}, 
title = {A Monte Carlo Implementation of the Nonlinear Filtering Problem to Produce Ensemble Assimilations and Forecasts}, 
journal = {American Meteorological Society}, 
year = {1999}, 
volume = {127}, 
number = {}, 
pages = {2741--2758}, 
month = {December}, 
note = {} 
}

@techreport{Anderson2000,
author = {Anderson, J.D.},
title = {Hypersonic and high temperature gas dynamics},
institution = {AIAA},
year = {2000},
}

@article {Anderson2001, 
author = {Anderson, J. L.}, 
title = {An ensemble adjustment Kalman filter for data assimilation}, 
journal = {Mon. Wea. Rev.}, 
year = {2001}, 
volume = {129}, 
number = {}, 
pages = {2884-2903}, 
month = {}, 
note = {} 
}

@article {Anderson2003, 
author = {Anderson, J. L.}, 
title = {A local least squares framework for ensemble filtering}, 
journal = {Mon. Wea. Rev.}, 
year = {2003}, 
volume = {131}, 
number = {}, 
pages = {634-642}, 
month = {}, 
note = {} 
}

@article {Anderson2007, 
author = {Anderson, J. L.}, 
title = {An adaptive covariance inflation error correction algorithm for ensemble fitlers}, 
journal = {Tellus}, 
year = {2007}, 
volume = {59A}, 
number = {}, 
pages = {520-526}, 
month = {}, 
note = {} 
}

@article {Anderson2009, 
author = {Anderson, J. L. and Hoar, T. and Raeder, K. and Liu, H. and Collins, N. and Torn, R. and Avellano, A.}, 
title = {The Data Assimilation Research Testbed: A community Facility}, 
journal = {Bulletin of the American Meteorological Society}, 
year = {2009}, 
volume = {90}, 
number = {}, 
pages = {1283-1296}, 
month = {}, 
note = {} 
}

@article{Anderson2015,
author = {Anderson, R. W. and Dobrev, V. A. and Kolev, Tz. V. and Rieben, R. N.},
title = {Monotonicity in high-order curvilinear finite element arbitrary {L}agrangian–{E}ulerian remap},
journal = {Int. J. Numer. Meth. Fl.},
volume = {77},
number = {5},
pages = {249-273},
keywords = {shock hydrodynamics, multi-material hydrodynamics, monotonicity, ALE methods, finite element methods, high-order methods},
doi = {https://doi.org/10.1002/fld.3965},
year = {2015}
}

@article{Anderson2017,
title = {High-order local maximum principle preserving ({MPP}) discontinuous Galerkin finite element method for the transport equation},
journal = JCP,
volume = {334},
pages = {102 - 124},
year = {2017},
issn = {0021-9991},
doi = {https://doi.org/10.1016/j.jcp.2016.12.031},
author = {R. Anderson and V. Dobrev and Tz. Kolev and D. Kuzmin and M. {Quezada de Luna} and R. Rieben and V. Tomov}
}

@article {Apodaca2014, 
author = {Apodaca, K. and Zupanski, M. and DeMaria, M. and Knaff, J. A. and Grasso, L. D.}, 
title = {Development of a hybrid variational-ensemble assimilation technique for observed lightning tested in a mesoscale model}, 
journal = {Nonlinear Process Geophys.}, 
year = {2014}, 
volume = {21}, 
pages = {1027--1041}
}

@ARTICLE {Antepara2015,
author = {Antepara, O. and Lehmkuhl, O. and Borrell, R. and Chiva, J. and Oliva, A.},
title = {Parallel adaptive mesh refinement for large-eddy simulations of turbulent flows},
journal = {Comput. Fluids},
year = {2010},
volume = {110},
pages = {48--60}
}


@article {Anthes1973, 
author = {Anthes, R. A.}, 
title = {Data Assimilation and Initialization of Hurricane Prediction Models}, 
journal = {Journal of the Atmospheric Sciences}, 
year = {1973}, 
volume = {31}, 
number = {}, 
pages = {702-719}, 
month = {April}, 
note = {} 
}

@ARTICLE{Wilke1950,
    AUTHOR = {Wilke, C. R.},
    TITLE = {A Viscosity Equation for Gas Mixtures},
    JOURNAL = JCHEMPHYS,
    YEAR = {1950},
    VOLUME = {18},
    PAGES = {517--519}  }

@BOOK{Gardiner1984,
  AUTHOR = 	 {W. C. Gardiner, Jr.},
  ALTEDITOR = 	 {},
  TITLE = 	 {Combustion Chemistry},
  PUBLISHER = 	 {Springer-Verlag New York Inc.},
  YEAR = 	 {1984},
  OPTVOLUME = 	 {},
  OPTNUMBER = 	 {},
  OPTSERIES = 	 {},
  ADDRESS = 	 {Boca Raton},
  OPTEDITION = 	 {},
  OPTMONTH = 	 {},
  OPTNOTE = 	 {},
  OPTANNOTE = 	 {}
}

@Misc{Arduino,
  key =          {Arduino},
  note =         {\url{https://www.arduino.cc/}}
}

@article {Arnold1992, 
author = {Arnold, A. and Lange, B. and Bouch\'e, T. and Heitzmann, T. and Schiff, G. and Ketterle, W. and Monkhouse, P. and Wolfrum, J.}, 
title = {Absolute Temperature Fields in Flames by {2D-LIF} of {OH} using Excimer lasers and {CARS} Spectroscopy}, 
journal = {Ber. Bunsenges. Phys. Chem.}, 
year = {1992}, 
volume = {96}, 
number = {}, 
pages = {1388--1392}, 
month = {}, 
note = {} 
}

@article {Arulampalam2002, 
author = {Arulampalam, S. and Maskell, S. and Gordon, N. and Clapp, T.}, 
title = {A tutorial on particle filters for online nonlinear/nongaussian {B}ayesia tracking}, 
journal = {IEEE Trans. Sig. Proc.}, 
year = {2002}, 
volume = {50}, 
number = {}, 
pages = {174--188}, 
month = {}, 
note = {} 
}

@article {Arrhenius1889,
author = {Arrhenius, S.},
title = {{\" U}ber die Reaktionsgeschwindigkeit bei der Inversion von Rohrzucker durch S{\" a}uren},
journal = {Z. Physik. Chem.},
volume = {4},
pages = {226},
year = {1889}
}

@TechReport{ASCAC2010,
  author =       {Ashby, S. and Beckman, P. and Chen, J. Colella, P. and Collins, B. and Crawford, D. and Dongarra, J. and Kothe, D. and Lusk, R. and Messina, P. and Mezzacappa, T. and Moin, P. and Norman, M. and Rosner, R. and Sarkar, V. and Siegel, A. Streitz, F. and White, A. and Wright, M.},
  title =        {Summary Report of the Advanced Scientific Computing Advisory Committee(ASCAC) Subcommittee},
  institution =  {U.S. Department of Energy},
  year =         {2010},
  OPTkey =       {},
  OPTtype =      {},
  OPTnumber =    {},
  OPTaddress =   {},
  OPTmonth =     {},
  OPTnote =      {},
  OPTannote =    {}
}

@Book{Asch2016,
  author =    {Asch, M. and Bocquet, M. and Nodet, M.},
  title =        {DATA ASSIMILATION: METHODS, ALGORITHMS, AND APPLICATIONS},
  publisher =    {{SIAM}},
  year =         {2016}
}

@article{Ascher1997,
title = "Implicit-explicit {R}unge-{K}utta methods for time-dependent partial differential equations",
author = "Ascher, U. M. and Ruuth, S. J. and Spiteri, R. J.",
journal = "Applied Numerical Mathematics",
volume = "25",
number = "2",
pages = "151 - 167",
year = "1997",
note = "Special Issue on Time Integration",
issn = "0168-9274"
}

@article{AshurstShepherd:1997,
  author = {W. T. Ashurst and I. G. Shepherd},
 title = {Flame fron curvature distributions in a turbulent premixed flame
zone},
 journal = {Combust. Sci. Tech.},
 Vol = 124,
 Pages = {115-144},
 year = 1997
}

@article{attal2015a,
  title={Development and validation of a chemical reaction solver coupled to the {FLASH} code for combustion applications},
  author={Attal, N. and Ramaprabhu, P. and Hossain, J. and Karkhanis, V. and Uddin, M. and Gord, J. R. and Roy, S.},
  journal={Comput. Fluids},
  volume={107},
  pages={59--76},
  year={2015},
  issn = {0045-7930},
  publisher={Elsevier}
}

@Article{attal2015b,
author={Attal, N. and Ramaprabhu, P.},
title={Numerical investigation of a single-mode chemically reacting Richtmyer-Meshkov instability},
journal={Shock Waves},
year={2015},
volume={25},
number={4},
pages={307--328},
issn={1432-2153},
OPTdoi={10.1007/s00193-015-0571-6},
OPTurl={http://dx.doi.org/10.1007/s00193-015-0571-6}
}

@TechReport{Augonnet2010,
  author =       {Augonnet, C. and Thibault, S. and Namyst, R.},
  title =        {{S}tar{PU}: a Runtime System for Scheduling Tasks over Accelerator-Based Multicore Machines},
  institution =  {INRIA},
  year =         2010,
  number =       {RR-7240},
  note =         {\url{https://hal.inria.fr/inria-00467677}}
}

@article{Augonnet2011,
 author = {Augonnet, C. and Thibault, S. and Namyst, R. and Wacrenier, P.},
 title = {{StarPU}: A Unified Platform for Task Scheduling on Heterogeneous Multicore Architectures},
 journal = {Concurr. Comput. : Pract. Exper.},
 issue_date = {February 2011},
 volume = {23},
 number = {2},
 month = {February},
 year = {2011},
 issn = {1532-0626},
 pages = {187--198},
 numpages = {12},
 url = {http://dx.doi.org/10.1002/cpe.1631},
 doi = {10.1002/cpe.1631},
 acmid = {1951454},
 publisher = {John Wiley and Sons Ltd.},
 address = {Chichester, UK},
}

@article {Aung1997,
author = {Aung, K. T. and Hassan, M. I. and Faeth, G. M.},
title = {Flame Stretch Interactions of Laminar Premixed Hydrogen/Air Flames at Normal Temperature and Pressure},
journal = {Combust. Flame},
year = {1997},
volume = {109},
number = {},
pages = {1--24},
month = {},
note = {}
}

@article {Aung1998,
author = {Aung, K. T. and Hassan, M. I. and Faeth, G. M.},
title = {Effects of Pressure and Nitrogen Dilution on Flame/Stretch Interactions of Laminar Premixed {H}$_2$/{O}$_2$/{N}$_2$ Flames},
journal = {Combust. Flame},
year = {1998},
volume = {112},
number = {},
pages = {1--15},
month = {},
note = {}
}

@unpublished {aviation,
 author = {ATA},
 title = {Fort Worth-based American Airlines and 14 other carriers sign on for alternative aviation fuel},
 note = {{\ttfamily http://www.pegasusnews.com}},
 month = {},
 year = {2009}
}

   ####
   #   #
   #   #
   ####
   #   #
   #   #
   ####



@Article{Balci2012,
  author =       {Balci, N. and Mazzucato, A. and Restrepo, J. and Sell, G.},
  title =        {Ensemble Dynamics and Bred Vectors},
  journal =      {Monthly Weather Review},
  year =         {2012},
  OPTkey =       {},
  OPTvolume =    {},
  OPTnumber =    {},
  OPTpages =     {},
  OPTmonth =     {},
  OPTnote =      {},
  annote =    {https://doi.org/10.1175/MWR-D-10-05054.1}
}

@techreport {Brdar2000,
author = {Brdar, R. D. and Jones, R. M.},
title = {{GE IGCC Technology and Experience with Advanced Gas Turbines}},
institution = {GE Power Systems},
year = {2000},
type = {Technical Report},
number = {GER-4207},
address = {Schenectady},
month = oct,
note = {}
}

@techreport {Zhang2023,
author = {Simon Zhang and D. T. Graves and D. F. Martin},
title = {Chombo 4 Performance Report},
institution = {LBNL},
month = oct,
year = {2023},
type = {Technical Report},
number = {LBNL-2001551},
note = {}
}
@techreport {Balakumar2003,
author = {Balakumar, P.},
title = {Transition in a supersonic boundary-layer due to roughness and acoustic disturbances},
institution = {AIAA},
year = {2003},
type = {Technical Report},
note = {}
}

@article{Balci2012,
author = {Balci, N. and Mazzucato, A. and Restrepo, J. and Sell, G.},
title = {Ensemble Dynamics and Bred Vectors},
journal = {Monthly Weather Review},
volume = {140},
number = {7},
pages = {2308-2334},
year = {2012},
}

@article{Bannister2017,
  title={A review of operational methods of variational and ensemble‐variational data assimilation},
  author={Bannister, R. N.},
  journal={Royal Meteorological Society},
  volume={143},
  number={},
  pages={607--633},
  year={2017},
  month={},
}


@article{Barad2005,
  title={A fourth-order accurate local refinement method for {P}oisson's equation},
  author={Barad, M. and Colella, P.},
  journal=JCP,
  volume={209},
  number={1},
  pages={1--18},
  year={2005},
  month={},
  publisher={Elsevier},
  issn = {0021-9991},
  doi={https://doi.org/10.1016/j.jcp.2005.02.027}
}

@techreport {Bardina1983,
author = {Bardina, J. and Ferziger, J. H. and Reynolds, W. C.},
title = {Improved turbulence models based on large eddy simulation of homogeneous, incompressible, turbulent flows},
institution = {Stanford University},
year = {1983},
type = {Technical Report, Thermosciences Division, Dept. Mechanical Engineering},
number = {TF-19},
address = {},
month = {},
note = {}
}

@unpublished {Barlow,
author = {Barlow, R. S.},
title = {Turbulent Nonpremixed Flame Workshop},
note = {http://www.ca.sandia.gov/tdf/Workshop/Submodels.html},
month = {},
year = {}
}

@article {Barenblatt1962,
author = {Barenblatt, G. I. and Zeldovich, Y. B. and Istratov, A. G.},
title = {On diffusional-thermal stability of a laminar flame (in {R}ussian)},
journal = {Zhurnal Prikladnoi Mekhaniki i Tekhnicheskoi Fiziki},
year = {1962},
volume = {4},
number = {},
pages = {21--26},
month = {},
note = {}
}

@techreport {Barth1990,
author = {Barth, T.J. and Frederickson, P.O.},
title = {High-order solution of the {E}uler equations on unstructured grids using quadratic reconstruction},
institution = {AIAA},
year = {1990},
type = {Paper},
number = {AIAA-90-0013},
address = {},
month = {},
note = {}
}

@techreport {Barth1993,
author = {Barth, T.},
title = {Recent developments on high order k-exact reconstruction on unstructured meshes},
institution = {31st Aerospace Sciences Meet and Exhibit, Reno},
year = {1993},
type = {Paper},
number = {AIAA-93-0668},
pages = {1--15},
month = {},
note = {}
}

@article {Bassi1997,
author = {Bassi, F and Rebay, S},
title = {A high-order accurate discontinuous finite element method for the numerical solution of the compressible {N}avier–{S}tokes equations},
journal = {J. Comput. Phys.},
year = {1997},
volume = {131},
number = {},
pages = {267--279},
month = {},
note = {},
OPTdoi = {10.1006/jcph.1996.5572},
}

@article {Baukal1996,
author = {Baukal, C. and B. Gebhart},
title = {A review of semi-analytical solutions for flame impingement heat transfer},
journal = {Int. J. Thermal Sci},
year = {1996},
volume = {39},
number = {},
pages = {2989--3002},
month = {},
note = {}
}

@article {BaumPoinsot1994,
author = {Baum, M. and Poinsot, T. J. and Haworth, D. C. and Darabiha, N.},
title = {Direct numerical simulation of {H}$_2$/{O}$_2$/{N}$_2$ flames with complex chemistry in two-dimensional turbulent flows},
journal = {J. Fluid Mech.},
volume = 281,
pages = {1--32},
year = 1994
}

@inproceedings{Bauer2012,
 author = {Bauer, M. and Treichler, S. and Slaughter, E. and Aiken, A.},
 title = {Legion: Expressing Locality and Independence with Logical Regions},
 booktitle = {Proceedings of the International Conference on High Performance Computing, Networking, Storage and Analysis},
 series = {SC '12},
 year = {2012},
 isbn = {978-1-4673-0804-5},
 location = {Salt Lake City, Utah},
 pages = {66:1--66:11},
 articleno = {66},
 numpages = {11},
 url = {http://dl.acm.org/citation.cfm?id=2388996.2389086},
 acmid = {2389086},
 publisher = {IEEE Computer Society Press},
 address = {Los Alamitos, CA, USA},
}

@Book{Batchelor1970,
  author =    {Batchelor, G. K.},
  ALTeditor =    {},
  title =        {Introduction to Fluid Dynamics},
  publisher =    {Cambridge University Press},
  year =         {1970},
  OPTkey =       {},
  OPTvolume =    {},
  OPTnumber =    {},
  OPTseries =    {},
  OPTaddress =   {},
  OPTedition =   {},
  OPTmonth =     {},
  note =      {pp. 193e195},
  OPTannote =    {}
}

@article{BedatCheng:1995,
author = {Bedat, B. and Cheng, R. K.},
title = {Experimental study of premixed flames in intense isotropic turbulence},
journal = {Combust. flame},
volume = 100,
year = 1995,
pages = {485--494}
}

@article {Beer1988,
author = {Be\'er, J. M.},
title = {Stationary Combustion: the Industrial Leimotiv},
journal = {Proc. Combust. Inst.},
year = {1988},
volume = {22},
number = {},
pages = {1--16},
month = {},
note = {Plenary lecture}
}

@article {Beer2000,
author = {Be\'er, J. M.},
title = {Combustion technology developments in power generation in response to environmental challenges},
journal = {Prog. Energy Combust. Sci.},
year = {2000},
volume = {26},
number = {},
pages = {301--307},
month = {},
note = {}
}

@article {Behara2010a,
author = {Behara, S. and Mittal, S.},
title = {Flow past a circular cylinder at low Reynolds number: Oblique vortex shedding},
journal = PF,
year = {2010},
volume = {22},
number = {},
pages = {},
month = {May},
note = {}
}

@article {Behara2010b,
author = {Behara, S. and Mittal, S.},
title = {Wake transition in flow past a circular cylinder},
journal = PF,
year = {2010},
volume = {22},
number = {},
pages = {},
month = {Nov},
note = {}
}

@techreport {Bell1983,
author = {Bell, B. F.},
title = {Design and fabrication of a Darrieus/Savonius hybrid vertical-axis wind turbine},
institution = {United States Department of Energy},
year = {1983},
type = {Technical Report},
number = {DOE/R1/24255--T1/NH-81-004},
address = {},
month = {September},
note = {}
}

@article{Bell2006c, 
 author = {Bell, J. B. and Cheng, R. K. and Day, M. S. and Shepherd, I. G.},
 title = {Numerical Simulation of {L}ewis Number Effects on Lean Premixed Turbulent Flames}, 
 journal = {Proc. Combust. Inst.}, 
 year = {2007},
 volume = {31},
 note = {},
 pages = {1309--1317}
}

@inproceedings {Bell2006a,
	author = {Bell, J. B. and Day, M. S. and Grcar, J. F. and Lijewski, M. J.},
	title = {A Computational Study of Equivalence Ratio Effects in Turbulent, Premixed Methane-Air Flames},
	booktitle = {Proceedings European Conference on Computational Fluid Dynamics},
	year = {2006},
	editor = {Wesseling, P. and Onate, E. and Periaux, J.},
	pages = {},
	organization = {European Community on Computational Methods in Applied Sciences (ECCOMAS)},
	publisher = {TU Delft},
	address = {},
	month = {},
	note = {CD-ROM ISBN 90-9020970-0}
	}

@article {BellBrown2000,
author = {J. B. Bell and N. J. Brown and M. S. Day and M. Frenklach and J. F. Grcar and S. R. Tonse},
title = {The dependence of chemistry on the inlet equivalence ratio in vortex-flame interactions},
journal = {Proc. Combust. Inst.},
year = {2000},
volume = {28},
pages = {1933--1939}
}

@inproceedings {BellDay2001,
booktitle = {Numerical Methods for Fluid Dynamics {VII}},
author = {Bell, J. B. and Day, M. S. and Almgren, A. S. and Lijewski, M. J. and Rendleman, C. A.},
year = {2001},
editor = {Baines, M. J.},
pages = {207--213},
organization = {ICFD},
address = {Oxford and Reading Universities},
month = mar,
note = {Also appears as \cite {BellDay2002b}.}
}

@article {BellDay2002, 
author = {Bell, J. B. and Day, M. S. and Grcar, J. F. and Bessler, W. G. and Schultz, C. and Glarborg, P. and Jensen, A. D.},
title = {Detailed modeling and laser-induced fluorescence imaging of nitric oxide in a {NH}$_3$-seeded non-premixed methane/air flame},
journal = {Proc. Combust. Inst.}, 
year = {2002}, 
volume = {29}, 
pages = {2195--2202}
}

@article {BellDay2002b,
author = {Bell, J. B. and Day, M. S. and Almgren, A. S. and Lijewski, M. J. and Rendleman, C. A.},
title = {A Parallel Adaptive Projection Method for Low {M}ach Number Flows},
journal = {Int. J. Numer. Meth. Fluids},
year = {2002},
volume = {40},
pages = {209--216}
}

@Article{BellDay2002c,
author = {Bell, J. B. and Day, M. S. and Grcar, J. F.},
title = {Numerical simulation of premixed turbulent methane combustion},
journal = {Proc. Combust. Inst.},
year = {2002},
volume = {29},
pages = {1987--1993}
}

@article {BellDay2010,
author = {Bell, J. B. and Day, M. S. and Gao, X. and Lijewski, M. J.},
title = {Simulation of Nitrogen Emissions in a Low Swirl Burner},
journal = {J. Phys.: Conf. Ser.},
year = {2010},
volume = {},
number = {},
pages = {},
month = {July},
note = {}
}

@Article{BellEtal2005,
author = {Bell, J. B. and Day, M. S. and Grcar, J. F. and Lijewski, M. J.},
title = {Stochastic Algorithms for the Analysis of Numerical Flame Simulations},
journal = {J. Comput. Phys.},
year = {2005},
volume = {202},
issue = {1},
pages = {262--280}
}

@Article{BellEtal2005b,
author = {Bell, J. B. and Day, M. S. and Grcar, J. F. and Lijewski, M. J.},
title = {Active Control for Statistically Stationary Turbulent Premixed Flame Simulations},
journal = {Comm.\ App.\ Math.\ Comput.\ Sci.},
year = {2005},
volume = {1},
number = {1},
month = nov,
pages = {29--52}
}

@article{BellEtal2005c, 
 author = {Bell, J. B. and Day,  M. S. and Grcar, J. F. and Lijewski, M.
J. and Driscoll, J. F. and Filatyev, S. F.},
 title = {Numerical Simulation of a Laboratory-Scale Turbulent Slot Flame},
 journal = {Proc. Combust. Inst.}, 
 volume = {31},
 year = {2007},
 note = {},
 pages = {1299--1307}
 }

@inproceedings {BellEtal2005d, 
 author = {Bell, J. B. and Day, M. S. and Grcar, J. F. and Lijewski, M. J.},
 title = {Equivalence Ratio Effects in Turbulent, Premixed Methane-Air Flames},
booktitle = {Proceedings of the European Conference on Computational Fluid Dynamics},
year = {2006},
pages = {432:1-19},
editor = {P. Wessleing and E Onate and J P\'eriaux},
organization = {},
publisher = {},
address = {Egmond Aan Zee, The Netherlands},
note = {5--8 September}
}

@article {Bell2005c,
author = {Bell, J. B. and Day, M. S. and Shepherd, I. G. and Johnson, M. 
and Cheng, R. K. and Grcar, J. F. and Beckner, V. E. and Lijewski, M. J.},
title = {Numerical Simulation of a Laboratory-Scale Turbulent {V}-Flame},
journal = {Proc. Natl. Acad. Sci. USA},
year = {2005},
volume = {102},
number = {29},
pages = {10006--10011},
month = {},
note = {}
}

@article {Bell2007,
author = {Bell, J. B. and Day, M. S. and Grcar, J. F. and Driscoll, J. F. and Lijewski, M. J. and Filatyev, S. A.},
title = {Numerical Simulation of a Laboratory-Scale Turbulent slot Flame},
journal = {Proc. Combust. Inst},
year = {2007},
volume = {31},
number = {},
pages = {1299-1307},
month = {},
note = {}
}


@Misc{Bell2011,
  OPTkey =       {},
  author =    {Bell, J.},
  title =     {Combustion Simulation on Next Generation Architectures},
  howpublished = {Presentation in Los Alamos National Laboratory},
  month =     {May},
  year =      {2011},
  note =      {https://ccse.lbl.gov/people/jbb/Talks/LANL_2011.pdf},
  OPTannote =    {}
}

@book {BellEtal2006,
author = {Bell, J. B. and Day, M. S. and Almgren, A. S.  and Lijewski, M. J. and Rendleman, C. A. and
Cheng, R. K. and Shepherd, I. G.},
title = {Simulation of Lean Premixed Turbulent Combustion},
publisher = {Institute of Physics Publishing},
year = {2006},
volume = {46},
series = {Journal of Physics Conference Series: SciDAC 2006 (W.\ Tang, Ed.)},
address = {Denver, CO},
edition = {},
month = {}
}

@book {BellEtal2008,
author = {Bell, J. B. and Cheng, R. K. and Day, M. S. and Beckner, V. E. and Lijewski, M. J.},
title = {Simulation of Lean Premixed Turbulent Combustion},
publisher = {Institute of Physics Publishing},
year = {2006},
volume = {46},
series = {Journal of Physics Conference Series: SciDAC 2006 (W.\ Tang, Ed.)},
address = {Denver, CO},
edition = {},
month = {}
}

@article {Bell2007a,
author = {Bell, J. B. and Cheng, R. K. and Day, M. S. and Shepherd, I. G.},
title = {Numerical simulation of {L}ewis number effects on lean premixed turbulent flames},
journal = {Proc. Combust. Inst.},
year = {2007},
volume = {31},
number = {},
pages = {1309--1317},
month = {},
note = {}
}

@book {BellEtal2010,
author = {Bell, J. B. and Day, M. S. and Gao, X. and Lijewski, M. J.},
title = {Simulation of Nitrogen Emissions in a Low Swirl Burner},
publisher = {Institute of Physics Publishing},
year = {2010},
volume = {46},
series = {Journal of Physics Conference Series: SciDAC 2010},
address = {Chattanooga, Tennessee},
edition = {},
month = {July}
}

@patent {Bench1971,
  title = {Spherical Free Fall Apparatus},
  author = {Bench, T. E.},
  number = {3604352},
  type = {Patent},
  location = {US},
 year = {1971},
 month = {US Patent 3604352, 09},
}

@ARTICLE{bergerColella1989,
    AUTHOR = {Berger, M. J. and Colella, P.},
    TITLE = {Local Adaptive Mesh Refinement for Shock Hydrodynamics},
    JOURNAL=JCP,
    YEAR = {1989},
    NUMBER = {1},
    MONTH = {May},
    VOLUME={82},
    PAGES={64--84}
}

@article{Berger1984,
title = {Adaptive mesh refinement for hyperbolic partial differential equations},
author = {Berger, M. J. and Oliger, J.},
journal = JCP,
volume = {53},
number = {3},
pages = {484--512},
year = {1984},
issn = {0021-9991},
OPTdoi = {https://doi.org/10.1016/0021-9991(84)90073-1},
OPTurl = {http://www.sciencedirect.com/science/article/pii/0021999184900731},
}

@Article{Berger1987,
  author =       {Berger, M. J.},
  title =        {On Conservation at Grid Interfaces},
  journal =      SIAMJNA,
  year =         {1987},
  volume =       {24},
  number =       {5},
  pages =        {967--984}
}

@article{Berger1990,
title = {Stable boundary condition for {C}artesian grid calculations},
author = {Berger, M. J. and Leveque, R.J.},
journal = {Computer System in Engineering},
volume = {1},
number = {},
pages = {305--311},
year = {1990},
}

@InProceedings{Berger2012,
  author =       {Berger, M. J. and Aftosmis, M. J.},
  title =        {Progress Towards a {C}artesian Cut-Cell Method for Viscous Compressible Flow},
  booktitle =    {50th AIAA Aerospace Sciences Meeting},
  year =         2012,
  number =       {AIAA 2012-1301},
  organization = {AIAA}
}

@InProceedings{Berger2017,
  author =       {Berger, M. J. and Aftosmis, M. J.},
  title =        {An ODE-based Wall Model for Turbulent Flow Simulations},
  booktitle =    {55th AIAA Aerospace Sciences Meeting},
  year =         2017,
  number =       {AIAA 2017-0528},
  organization = {AIAA}
}

        
@InProceedings{Bertolacci2015,
  author =       {Bertolacci, I. and Olschanowsky, C. and Harshbarger, B. and Chamberlain, B. and Wonnacott D. and Strout, M.},
  title =        {Parameterized Diamond Tiling for Stencil Computations with Chapel parallel iterators},
  booktitle =    {Supercomputing (ICS)},
  year =         {2015},
}

@Article{Bertolacci2019,
  author =       {Bertolacci, I. J. and Strout, M. M. and Riley, J. and Guzik, S. M. and Davis, E. C. and Olschanowsky, C.},
  title =        {Using the Loop Chain Abstraction to Schedule Across Loops in Existing Code},
  journal =      {International Journal of High Performance Computing and Networking},
  year =         2019,
  key =          13,
  pages =        {86--104}
}

@article{Bhatnagar:1954,
  author =       {Bhatnagar, P. L. and Gross, E. P. and Krook, M.},
  title =        {A model for collision processes in gases .1. Small amplitude processes in charged and neutral one-component systems.},
  journal =      {Physical Review},
  year =         1954,
  volume =       94
}

@article {Biasi2005,
author = {Biasi, V. de},
title = {Targeting turbine research needs to burn syngas and hydrogen fuels},
journal = {Gas Turbine World},
year = {2005},
volume = {},
number = {},
pages = {28--30},
month = {March-April},
note = {}
}

@article{Billet2005,
title = {Improvement of convective concentration fluxes in a one step reactive flow solver},
author = {Billet, G.},
journal = JCP,
volume = {204},
number = {1},
pages = {319--352},
year = {2005},
note = {},
issn = {0021-9991},
OPTdoi = {http://dx.doi.org/10.1016/j.jcp.2004.10.016},
OPTurl = {http://www.sciencedirect.com/science/article/pii/S002199910400419X}

}

@article{Billet2008,
author = {Billet, G. and Giovangigli, V. and de Gassowski, G.},
title = {Impact of volume viscosity on a shock--hydrogen-bubble interaction},
journal = {Combust. Theory Model.},
volume = {12},
number = {2},
pages = {221-248},
year = {2008},
OPTdoi = {10.1080/13647830701545875}
}

@article {Bishop2001,
author = {Bishop, C. and Etherton, J. and Majmudar, S. J.},
title = {Adaptive sampling with the ensemble transform Kalman filter. Part I: Theoretical aspect},
journal = {Mon. Wea. Rev.},
year = {2001},
volume = {129},
number = {},
pages = {420--430},
month = {},
note = {}
}

@article {Biswas1994,
author = {Biswas, R and Devine, KD and Flaherty, J},
title = {Parallel, adaptive finite element methods for conservation laws},
journal = {Appl. Numer. Math},
year = {1994},
volume = {14},
number = {},
pages = {255--283},
month = {},
note = {},
OPTdoi = {10.1016/0168-9274(94)90029-9}
}

@article {Board1992,
author = {Board, D.S.},
title = {Final report of the second defense science board task force on the national aero-space plane},
journal = {NASP},
year = {1992},
volume = {},
number = {},
pages = {94-00052},
month = {},
note = {}
}

@Article{Bocquet2010,
  author =       {M. Bocquet and C. A. Pires and L. Wu},
  title =        {Beyond Gaussian statistical modeling in geophysical data assimilation},
  journal =      {Mon. Wea},
  year =         {2010},
  OPTkey =       {},
  volume =    {138},
  OPTnumber =    {},
  pages =     {2997–3023},
  OPTmonth =     {},
  OPTnote =      {},
  OPTannote =    {}
}

@Patent{Boehler1966,
 author = {Boehler, G. D. and Foshag, W. F.},
 title = {Wing Rotors},
 number = {US 3262656},
 type = {Patent},
 location = {US},
 year = {1966},
 month = {US Patent 3262656, 07},
 day = {26},
 yearfiled = {1964},
}

@article {Bremer2004,
author = {Bremer, P.-T. and Edelsbrunner, H. and Hamann, B. and Pascucci, V.},
title = {A topological hierarchy for functions on triangulated surfaces},
journal = {IEEE Transactions on Visualization and Computer Graphics},
year = {2004},
volume = {10},
number = {4},
pages = {385-396},
month = {July-August},
note = {}
}

@book {Bremer2006,
author = {Bremer, P.-T. and V. Pascucci, V.},
editor = {},
title = {A Practical Approach to Two-dimensional Scalar Topology},
booktitle = {Topology-Based Methods In Visualization},
publisher = {Springer Verlag},
year = {2007},
volume = {},
number = {},
series = {Mathematics and Visualization},
address = {Berlin},
month = {},
pages = {151--169}
} 

@inproceedings {Bremer2009,
title={A Topological Framework for the Interactive Exploration of Large Scale Turbulent Combustion},
booktitle = {Proceedings of the 5th IEEE International Conference on e-Science},
author = {Bremer, P.-T. and Weber G. and Tierny, J. and Pascucci, V. and Day, M. and Bell, J.},
year = {2009},
editor = {},
pages = {247--254},
address = {},
note = {}
}

@article{Brent1971,
author={Brent, R. P.},
title={An algorithm with guaranteed convergence for finding a zero of a function},
journal={The Computer Journal},
volume={14},
number={4},
pages={422-425},
year={1971},
month={January}
}

@article{Brown1990,
author = {Brown, Peter N. and Saad, Youcef},
title = {Hybrid Krylov Methods for Nonlinear Systems of Equations},
journal = {SIAM J. Sci. and Stat. Comput.},
year = {1990},
volume = {11},
number = {3},
pages = {450–-481}
}

@inproceedings {Bull2014,
title={Simulation of the Compressible Taylor Green Vortex using High-Order Flux Reconstruction Schemes},
booktitle = {7th AIAA Theoretical Fluid Mechanics Conference},
author = {Bull, J. R. and Jameson, A.},
number = {AIAA 2014-3210},
organization = {AIAA Aviation Forum},
year = {2014},
note = {}
}

@article {Chen2009,
author = {Chen, J.H. and Choudhary, A. and de Supinski, B. and DeVries, M. and Hawkes, E.R. and Klasky, S. and Liao, W. K. and Ma, K. L. and Mellor-Crummey, J. and Podhorszki, N. and Sankaran, R. and Shende, S. and Yoo, C.S.},
title = {Terascale direct numerical simulations of turbulent combustion using S3D},
journal = {Comput. Sci. Disc.},
year = {2009},
volume = {2},
number = {1},
pages = {},
month = {Jan},
note = {}
}

@inbook{Chong2008global,
publisher = {John Wiley and Sons, Ltd},
isbn = {9781118033340},
title = {Global Search Algorithms},
booktitle = {An Introduction to Optimization},
chapter = {14},
pages = {267-295},
doi = {https://doi.org/10.1002/9781118033340.ch14},
url = {https://onlinelibrary.wiley.com/doi/abs/10.1002/9781118033340.ch14},
eprint = {https://onlinelibrary.wiley.com/doi/pdf/10.1002/9781118033340.ch14},
year = {2008},
keywords = {global search algorithms, Nelder-Mead simplex algorithm, simulated annealing, particle swarm optimization, genetic algorithms},
abstract = {Summary This chapter contains sections titled: Introduction The Nelder-Mead Simplex Algorithm Simulated Annealing Particle Swarm Optimization Genetic Algorithms}
}

@inbook{Chong2008linear,
publisher = {John Wiley and Sons, Ltd},
isbn = {9781118033340},
title = {Solving Linear Equations},
booktitle = {An Introduction to Optimization},
chapter = {12},
pages = {211-245},
doi = {https://doi.org/10.1002/9781118033340.ch12},
url = {https://onlinelibrary.wiley.com/doi/abs/10.1002/9781118033340.ch12},
eprint = {https://onlinelibrary.wiley.com/doi/pdf/10.1002/9781118033340.ch12},
year = {2008},
keywords = {Linear equations, least-squares analysis, recursive least-squares algorithm, linear equation, Kaczmarz's algorithm},
abstract = {Summary This chapter contains sections titled: Least-Squares Analysis The Recursive Least-Squares Algorithm Solution to a Linear Equation with Minimum Norm Kaczmarz's Algorithm Solving Linear Equations in General}
}

@inbook{Chong2008newton,
publisher = {John Wiley and Sons, Ltd},
isbn = {9781118033340},
title = {Newton's Method},
booktitle = {An Introduction to Optimization},
chapter = {9},
pages = {155-167},
doi = {https://doi.org/10.1002/9781118033340.ch9},
url = {https://onlinelibrary.wiley.com/doi/abs/10.1002/9781118033340.ch9},
eprint = {https://onlinelibrary.wiley.com/doi/pdf/10.1002/9781118033340.ch9},
year = {2008},
keywords = {Newton's method, Levenberg-Marquardt modification, nonlinear least squares, Newton-Raphson method, quadratic approximation},
abstract = {Summary This chapter contains sections titled: Introduction Analysis of Newton's Method Levenberg-Marquardt Modification Newton's Method for Nonlinear Least Squares}
}

@article {Colella1984,
author = {Colella, P. and Woodward, P.},
title = {The piecewise parabolic method for gas-dynamical simulations},
journal=JCP,
year = {1984},
volume = {54},
number = {},
pages = {174--201},
note = {}
}

@article {Colella1990,
author = {Colella, P.},
title = {Multidimensional Upwind Methods for Hyperbolic Conservation Laws},
journal=JCP,
year = {1990},
volume = {87},
number = {1},
pages = {171--200},
note = {}
}

@article{Colella1999,
author = {Colella, P.  and Trebotich, D. P.},
title = {Numerical simulation of incompressible viscous flow in deforming domains},
journal = {Proceedings of the National Academy of Sciences},
volume = {96},
number = {10},
pages = {5378-5381},
year = {1999},
doi = {10.1073/pnas.96.10.5378}}

@article{Colella2008,
author={Colella, P. and Sekora, M.},
title={A limiter for {PPM} that preserves accuracy at smooth extrema},
journal=JCP,
volume={227},
number={15},
year={2008},
month={},
pages={7069--7076}
}

@article {Cooper1998,
author = {Cooper, C. S. and Ravikrishna, R. V. and Laurendeau, N. M.},
title = {Comparisons of Laser-Saturated, Laser-Induced, and Planar Laser-Induced Fluorescence Measurements of Nitric Oxide in a Lean Direct-Injection Spray Flame},
journal = {Applied Optics},
year = {1998},
volume = {37},
number = {21},
pages = {4823--4833},
month = jul,
note = {}
}

@article {Curtiss1952,
author = {Curtiss, C. F. and Hirschfelder, J. O.},
title = {Integration of Stiff Equations},
journal = {Proc. Natl. Acad. Sci. USA},
year = {1952},
volume = {38},
number = {},
pages = {235--243},
month = {},
note = {}
}

@techreport {Bell2003,
author = {Bell, J. B. and Day, M. S. and Shepherd, I. G. and Johnson, M. and Cheng, R. K. and Beckner, V. E. and Lijewski, M. J. and Grcar, J. F.},
title = {Numerical Simulation of a Laboratory-Scale Turbulent {V}-flame},
institution = {Lawrence Berkeley National Laboratory},
year = {2003},
type = {Technical Report},
number = {LBNL-54198},
address = {},
month = {},
note = {}
}


@article {BennettMcEnally2000,
author = {B. A. V. Bennett and C. S. Mc{E}nally and L. D. Pfefferle and M. D. Smooke},
title = {Computational and experimental study of axisymmetric coflow partially premixed methane/air flames},
journal = {Combust. Flame},
volume = {123},
pages = {522--546},
year = {2000}
}

@article {BennettMcEnally2001,
author = {B. A. V. Bennett and C. S. Mc{E}nally and L. D. Pfefferle and M. D. Smooke and M. B. Colket},
title = {Computational and experimental study of axisymmetric coflow partially premixed ethylene/air flames},
journal = {Combust. Flame},
volume = {127},
pages = {2004--2022},
year = {2001}
}

@article {BennettSmooke1999,
author = {B. A. V. Bennett and M. D. Smooke},
title = {A comparison of the structures of lean and rich axisymmetric laminar Bunsen flames: application of local rectangular refinement solution-adaptive gridding},
journal = {Combust. Theory Model.},
volume = 3,
pages = {657--687},
year = {1999}
}

@article {BesslerHildenbrand2001, 
author = {Bessler, W. G. and Hildenbrand, F. and Schulz, C.}, 
title = {Two-Line Laser-Induced Fluorescence Imaging of Vibrational Temperatures in a {NO}-Seeded Flame}, 
journal = {Applied Optics}, 
year = {2001}, 
volume = {40}, 
number = {}, 
pages = {748--756}, 
month = {}, 
note = {} 
}

@article {BesslerSchulz2002, 
author = {Bessler, W. G. and Schulz, C. and Lee, T. and Shin, D.-I. and Hofmann, M. and Jeffries, J. B. and Wolfrum, J. and Hanson, R. K.}, 
title = {Quantitative {NO-LIF} imaging in high-pressure flames}, 
journal = {Appl. Phys. B}, 
year = {2002}, 
volume = {75}, 
number = {}, 
pages = {97--102},
month = {}, 
note = {} 
}

@article {Bilger1976,
author = {Bilger, R. W.},
title = {Turbulent Jet Diffusion Flames},
journal = {Prog. Energy Combust. Sci.},
year = {1976},
volume = {1},
number = {2--3},
pages = {87--109},
month = {},
note = {}
}

@article {Bilger1988,
author = {Bilger, R. W.},
title = {The structure of turbulent non-Premixed Flames},
journal = {Proc. Combust. Inst.}, 
year = {1988},
volume = {22},
number = {},
pages = {475--488},
month = {},
note = {}
}

@book {Bird2002,
author = {Bird, R. B. and Stewart, W. E. and Lightfoot, E. N.},
title = {Transport Phenomena},
year = {2002},
publisher = {John Wiley \& Sons, Inc.},
edition = {second},
address = {New York}
}

@article {BLE1998,
    AUTHOR = {Gerrit Burgers and Peter Jan van Leeuwen and Geir Evensen},
     TITLE = {Analysis Scheme in the Ensemble Kalman Filter},
   JOURNAL = {Mon. Wea. Rev.},
    VOLUME = {126},
      YEAR = {1998},
     PAGES = {1719-1724},
}

@article {Bockle2000, 
author = {B\"ockle, S. and Kazenwadel, J. and Kunzelmann, T. and Schulz, C.}, 
title = {Laser-diagnostic multi-species imaging in strongly swirling natural gas flames},
journal = {Appl. Phys. B}, 
year = {2000}, 
volume = {71}, 
number = {}, 
pages = {741--746},
month = {}, 
note = {} 
}


@InProceedings{Boger2000,
  author =       {M. Boger and D. Veynante},
  title =        {Large Eddy Simulation of a Turbulent Premixed V-
Shaped Flame},
  OPTcrossref =  {},
  OPTkey =       {},
  booktitle = {Advances in Turbulence},
  year =      {2000},
  OPTeditor =    {},
  OPTvolume =    {},
  OPTnumber =    {},
  OPTseries =    {},
  OPTpages =     {},
  month =     {June},
  address =   {Barcelona, Spain},
  organization = {European Turbulence Conference },
  OPTpublisher = {},
  note =      {8a:2000 : Barcelona, Catalunya},
  OPTannote =    {}
}



@article{Boeing2016,
AUTHOR = {Boeing, G.},
TITLE = {Visual Analysis of Nonlinear Dynamical Systems: Chaos, Fractals, Self-Similarity and the Limits of Prediction},
JOURNAL = {Systems},
VOLUME = {4},
YEAR = {2016},
volume = {4},
NUMBER = {37}
}

@article {Bongers2003,
author = {Bongers, H. and de Goey, L. P. H.},
title = {The effect of simplified transport modeling on the burning velocity of laminar premixed flames},
journal = {Combust. Sci. Technol.},
year = {2003},
volume = {175},
number = {},
pages = {1915--1928},
month = {},
note = {}}

@article {Booker1999,
author = {Booker, A. J. and Dennis Jr., J. E. and Frank, P. D. and Serafini, D. B. and Torczon, V. and Trosset, M. W.},
title = {A Rigorous Framework for Optimization of Expensive Functions by Surrogates},
journal = {Structural and Multidisciplinary Optimization},
year = {1999},
volume = {17},
number = {1},
pages = {1--13},
month = {},
note = {}
}

@incollection {Borghi1984,
author = {Borghi1984},
title = {On the structure of turbulent premixed flames},
booktitle = {Recent Advances in Aeronautical Science},
year = {1984},
volume = {},
number = {},
series = {},
type = {},
edition = {},
editor = {Bruno, C. and Casci, C.},
pages = {},
organization = {},
publisher = {Pergamon},
address = {},
note = {}
}

@article {Borkar1999,
author = {Borkar, V. S. and Mundra, S. M.},
title = {Bayesian parameter estimation and adaptive control of Markov processes with time-averaged cost},
journal = {Applicationes Mathematicae},
year = {1999},
volume = {25},
number = {4},
pages = {339--358},
month = {},
note = {}
}

@article {Bose2010,
author = {Bose, S. T. and Moin, P. and You, D.},
title = {Grid-independent large-eddy simulation using explicit filtering},
journal = PF,
year = {2010},
volume = {22},
number = {10},
pages = {},
month = {},
note = {}
}

@TechReport{Bose2011,
author =       {Bose, S. T. and Moin, P. and Ham, F.},
title =        {Explicitly filtered large eddy simulation on unstructured grids},
institution =  {Center for Turbulence Research},
year =         {2011},
type = {Annual Research Briefs 2011}
}

@article {Bose2018,
author = {Bose, S. T. and Park, G. I.},
title = {Wall-modeled large-eddy simulation for complex turbulent flows},
journal = {Annual Review of Fluid Mechanics},
year = {2018},
volume = {50},
number = {},
pages = {535--561},
month = {},
note = {}
}

@inproceedings{Bosilca2011,
author = {Bosilca, G. and Bouteiller, A. and Danalis, A. and Herault, T. and Lemariner, P. and Dongarra, J.},
title = {{DAGuE}: A Generic Distributed {DAG} Engine for High Performance Computing},
journal = {Proceedings of the Workshops of the 25th IEEE International Symposium on Parallel and Distributed Processing (IPDPS 2011 Workshops)},
year = {2011},
month = {00-2011},
pages = {1151-1158},
publisher = {IEEE},
address = {Anchorage, Alaska, USA}
}

@article {Boudreau1979,
author = {Boudreau, A.H.},
title = {Artificial induced boundary-layer transition on blunt-slender cones at hypersonic speeds},
journal = {Journal of Spacecraft and Rockets}, 
year = {1979}, 
volume = {16},
number = {4},
pages = {245--251},
}

@unpublished {BowmanHanson,
 author = {Bowman et al., C. T.},
 title = {{GRI}-{M}ech 2.11},
 note = {Available at \url{http://www.me.berkeley.edu/gri_mech}},
 month = {},
 year = {}
}

{C. T. Bowman and R. K. Hanson and D. F. Davidson and W. C. Gardiner and Jr. and V. Lissianski and G. P. Smith and D. M. Golden and M. Frenklach and M. Goldenberg}

@article {Bowman1992,
author = {Bowman, C. T.},
title = {Control of combustion-generated nitrogen oxide emissions: technology driven by regulation},
journal = {Proc. Combust. Inst.}, 
year = {1992}, 
volume = {24}, 
pages = {859--878},
}

@article {Braack2004,
author = {Braack, M. and Ern, A.},
title = {Coupling multimodelling with local mesh refinement for the numerical computation of laminar flames},
journal = {Combust.\ Theory Model.},
year = {2004},
volume = {8},
number = {},
pages = {771--788},
month = {},
note = {}
}

@article {Bradley1992,
author = {Bradley, D.},
title = {How Fast Can We Burn?},
journal = {Proc. Combust. Inst.},
year = {1992},
volume = {24},
pages = {247--262}
}

@article {Bradley1996,
author = {Bradley, D. and Gaskell, P. H. and Gu, X. J.},
title = {Burning Velocities, {M}arkstein Lengths, and Flame Quenching for Spherical Methane-Air Flames: A Computational Study},
journal = {Combust. Flame},
year = {1996},
volume = {104},
number = {},
pages = {176--198},
month = {},
note = {}
}

@article {Bradley2002,
author = {Bradley, D.},
title = {Problems of predicting turbulent burning rates},
journal = {Combust. Theory Model.},
year = {2000},
volume = {6},
number = {},
pages = {361--382},
month = {},
note = {}
}

@article {Bradley2003,
author = {Bradley, D. and Haq, M. Z. and Hicks, R. A. and Kitagawa, T. and Lawes, M. and Sheppard, C. G. W. and Woolley, R.},
title = {Turbulent burning velocity, burned gas distribution, and associated flame surface definition},
journal = {Combust. Flame},
year = {2003},
volume = {133},
number = {},
pages = {415--430},
month = {},
note = {}
}

@InProceedings{Brady2020,
  author = {Brady, P. T. and Livescu, D.},
  title = {Stable, High-Order and Conservative Cut-Cell Methods},
  booktitle = {2020 AIAA SciTech Forum},
  year = {2020},
  OPTnumber = {},
  organization = {AIAA SciTech Forum},
  OPTnote = {\url{}}
}

@article {BrailovskySivashinsky1997,
	author = {Brailovsky, I. and Sivashinsky, G.},
	title = {On Stationary and Travelling Flame Balls},
	journal = {Combust. Flame},
	year = {1997},
	volume = {110},
	number = {},
	pages = {524--529},
	month = {},
	note = {}
	}

@article {Branch1982,
author = {Branch, M. C. and Kee, R. J. and Miller, J. A.},
title = {A Theoretical Investigation of Mixing Effects in the Selective Reduction of Nitric Oxide by Ammonia},
journal = {Combust. Sci. Technol.},
year = {1982},
volume = {29},
number = {},
pages = {147--165},
month = {},
note = {}
}


@article{BregeonGordonWilliams:1978,
   author = {Bregeon, B. and Gordon, A. S. and Williams, F. A.},
  journal = {Combust. Flame},
  title = {Near-limit downward propagation of hydrogen and methane flames in oxygen\slash nitrog
en mixtures},
  volume = 33,
  pages = {33--45},
  year = 1978
}


@article {Breitung2005,
author = {Breitung et al., W.},
title = {Integral large scale experiments on hydrogen combustion for
severe accident code validation-{HYCOM}},
journal = {Nuclear Engineering and Design},
year = {2005},
volume = {253},
pages = {253--270}
}

{W. Breitung and S. Dorofeev and A. Kotchourko and R. Redlinger and W. Scholtyssek and A. Bentaib and J.-P. L'Heriteau and P. Pailhories and J. Eyink and M. Movahed and K.-G. Petzold and M. Heitsch and V. Alekseev and A. Denkevits and M. Kuznetsov and A. Efimenko and M. V. Okun and T. Huld and D. Baraldi}

@article {BroadwellLutz1998,
author = {Broadwell, J. E. and Lutz, J. E.},
title = {A turbulent jet chemical reaction model: {NO}$_x$ production in jet flames},
journal = {Combust. Flame},
year = {1998},
volume = {114},
number = {},
pages = {319-335},
month = {},
note = {}
}

@article {Brouwer1996,
author = {Brouwer, J. and Heap, M. P. and Pershing, D. W. and Smith, P. J.},
title = {A model for prediction of selective noncatalytic reduction of nitrogen oxides by ammonia, urea, and cyanuric acid with mixing limitations in the presence of {CO}},
journal = {Proc. Combust. Inst.},
year = {1996},
volume = {},
number = {},
pages = {2117--2124},
month = {},
note = {}
}

@article {Brown2005,
author = {N. J. Brown and K. L. Revzan},
title = {Comparative Sensittivity Analysis of Transport Properties and Reaction Rate Coefficients},
journal = {Int. J. Chem. Kinet.},
year = {2005},
volume = {37},
number = {},
pages = {538--553},
month = {},
note = {}
}

@article {Brune2015,
author = {Brune, P. and Knepley, M. and Smith, B. and Tu, X.},
title = {Composing scalable nonlinear algebraic solvers},
journal = {SIAM Review},
year = {2015},
volume = {57},
number = {4},
pages = {535--565},
month = {},
note = {}
}

@article {Brunk1962,
author = {Brunk, J. E. and Davidson, W. L. and Rakestraw, R. W.},
title = {The dynamics of spinning bodies at large angle of attack},
journal = {AFOSR/DRA-62-3},
year = {1962},
volume = {III},
number = {},
pages = {},
month = {June},
note = {}
}

@TechReport{Brunk1963,
  author = {Brunk, J. E.},
  title =  {The dynamics and aerodynamics of self-sustained large angle of attack body spinning motions},
  institution =  {Air Force Office of Scientific Research},
  year = {1963},
  type = {Technical Report},
  number = {AFOSR-4596},
  address = {},
  month = {February},
  note = {} 
}

@article {Brunk1967,
author = {Brunk, J. E.},
title = {Aerodynamics and flight mechanics of high performance autorotating glide-type bomblets},
journal = {Proceedings of Conference on Dynamics and Aerodynamics of Bomblets, Vol. 1. Technical Report AFATL-TR-67-195},
year = {1967},
volume = {1},
number = {},
pages = {},
month = {},
note = {}
}

@article {Brunk1968,
author = {Brunk, James E.},
title = {Aerodynamics and flight mechanics of magnus-rotor bomblets, volume {III}. Special aerodynamic studies},
journal = {Air Force Armament Laboratory Technical Report NO. AFATL-TR-68-73},
year = {1961},
volume = {},
number = {},
pages = {},
month = {},
note = {}
}

@TechReport{Brunk1970a,
  author = {Brunk, J. E.},
  title =  {Aerodynamic dispersion techniques},
  institution =  {Air Force Armament Laboratory},
  year = {1970},
  type = {Technical Report},
  number = {AFATL-TR-70-123},
  address = {},
  month = {November},
  note = {} 
}

@TechReport{Brunk1970b,
  author = {Brunk, J. E.},
  title =  {User's manual: extended capability magnus rotor and ballistic body 6-dof trajectory program},
  institution =  {Air Force Armament Laboratory},
  year = {1970},
  type = {Technical Report},
  number = {AFATL-TR-70-40},
  address = {},
  month = {May},
  note = {} 
}

@article {Brunk1975,
author = {Brunk, James E. and Billingsley, James P.},
title = {Autorotating magnus-rotor aero-design handbook},
journal = {AEDC-TR-75-24},
year = {1975},
volume = {},
number = {},
pages = {},
month = {July},
note = {}
}

@article {Brunk2015,
author = {Brunk, James E.},
title = {All about aerodynamics from a business card},
journal = {},
year = {2015},
volume = {},
number = {},
pages = {},
month = {September},
note = {published online at Research Gate}
}

@article {BuckmasterWeeratunga1984,
author = {Buckmaster, J. and Weeratunga, S.},
title = {},
journal = {Combust. Sci. Technol.},
year = {1984},
volume = {35},
number = {},
pages = {287--296},
month = {},
note = {}
}

@article {BuckmasterJoulin1990,
author = {Buckmaster, J. and Joulin, G. and Ronney, P.},
title = {The Structure and Stability of Nonadiabatic Flame Balls},
journal = {Combust. Flame},
year = {1990},
volume = {79},
number = {},
pages = {381--392},
month = {},
note = {}
}

@article {BuckmasterJoulin1991,
author = {Buckmaster, J. and Joulin, G. and Ronney, P.},
title = {The Structure and Stability of Nonadiabatic Flame Balls: {II}. Effects of Far-Field Losses},
journal = {Combust. Flame},
year = {1991},
volume = {84},
number = {},
pages = {411--422},
month = {},
note = {}
}

@article {BuckmasterSmooke1993,
author = {Buckmaster, J. and Smooke, M. and Giovangigli, V.},
title = {Analytical and Numerical Modeling of Flame-Balls in Hydrogen-Air Mixtutes},
journal = {Combust. Flame},
year = {1993},
volume = {94},
number = {},
pages = {113--124},
month = {},
note = {}
}

@article {BuckmasterRonney1998,
author = {Buckmaster, J. and Ronney, P.},
title = {Flame-ball drift in the presence of a total diffusive heat flux},
journal = {Proc. Combust. Inst.},
year = {1998},
volume = {27},
number = {},
pages = {2603--2610},
month = {},
note = {}
}

@article {Bucy2012,
author = {Bucy, H. and Baumgardner, M. and Marchese, A. J.},
title = {Chemical and Physical Properties of Algal Methyl Ester Biodiesel Containing Varying Levels of Methyl Eicosapentaenoate and Methyl Docosahexaenoate},
journal = {Algal Research},
year = {2012},
volume = {},
number = {},
pages = {},
month = {},
note = {DOI:  10.1016/j.algal.2012.02.001}
}


@article {Burke1928,
author = {Burke, S. P. and Schumann, T. E. W.},
title = {Diffusion Flames},
journal = {Ind. Engin. Chem.},
year = {1928},
volume = {20},
number = {10},
pages = {998--1004},
month = {},
note = {}
}

@article {Bush1970,
author = {Bush, W. B. and Fendell, F. E.},
title = {Asymptotic Analysis of Laminar Flame Propagation for General {L}ewis Numbers},
journal = {Combustion Science and Technology},
year = {1970},
volume = {1},
number = {},
pages = {421--428},
month = {},
note = {}
}

@techreport {Bustamante1969,
author = {Bustamante, A. C. and Stone, G. W.},
title = {The autorotation characteristics of various shapes in subsonic and hypersonic flows},
institution = {Sandia Corporation},
year = {1969},
type = {},
number = {SC-RR-69-159},
month = {April},
}

    ###
   #   #
   #
   #
   #
   #   #
    ###

@book {Caines1988,
author = {Caines, P. E.},
title = {Linear Stochastic Systems},
year = {1988},
publisher = {John Wiley},
edition = {},
address = {New York}
}

@book {BigCheese,
author = {G. Golub and C. Van Loan},
title = {Matrix Computations},
year = {1993},
publisher = {John Hopkins University Press},
address = {London}
}

@article {Calvo2001,
author = {Calvo, M.P. and Novo, J.},
title = {{Linearly implicit {R}unge-{K}utta methods for advection-reaction-diffusion equations}},
journal = {Applied Numerical Mathematics},
year = {2001},
volume = {37},
number = {},
pages = {535--549},
month = {},
note = {}
}


@article {Candel1990,
author = {Candel, S. M. and Poinsot, T. J.},
title = {Flame Stretch and the Balance Equation for the Flame Area},
journal = {Combustion Science and Technology},
year = {1990},
volume = {70},
number = {},
pages = {1--15},
month = {},
note = {}
}

@inproceedings {Carati2000,
title = {Time filtering in large-eddy simulations},
booktitle = {Proceedings for the Summer Program},
author = {Carati, D. and Wray, A.},
year = {2000},
editor = {},
pages = {263--270},
organization = {Center for Turbulence Research},
address = {},
month = {},
note = {}
}

@article {Carme2001,
author = {Carme, S. and Pham, D. T. and Verron, J.},
title = {Improving the singular evolutive extended Kalman filter for strongly nonlinear models for use in ocean data assimilation},
journal = {Inverse Problems},
year = {2001},
volume = {17},
number = {5},
pages = {1535--1559},
month = {},
note = {}
}

@article {Catris2000,
author = {Catris, S. and Aupoix, B.},
title = {Density corrections for turbulence models},
journal = {Aerosp. Sci. Technol.},
year = {2000},
volume = {4},
number = {},
pages = {1--11},
month = {January},
note = {}
}


@TechReport {CFD++,
author =  {Chakravarthy, Sukumar and Peroomian, Oshin and Goldberg, Uriel and Palaniswamy, Sampath},
title = {The CFD++ computational fluid dynamics software suite},
institution = {AIAA and SAE, World Aviation Conference, Anaheim,CA,USA.},
year = {1998} 
}

@article {Carrassi2009,
author = {Carrassi, A. and Vannitsem, S. and Zupanski, D},
title = {{The maximum likelihood ensemble filter performances in chaotic systems}},
journal = {Tellus A: Dynmanic Meteorology and Oceanography},
year = {2009},
volume = {61},
number = {5},
pages = {587--600},
month = {},
note = {}
}

@book{Cengel2018,
place = {New York, NY},
title = {Fluid mechanics: fundamentals and applications},
publisher = {McGraw-Hill Education},
author = {{\c C}Çengel, Yunus A. and Cimbala, John M.},
year = {2018}
}

@article {Cha2000,
author = {Cha, C. M. and Kramlich, J. C.},
title = {Modeling Finite-Rate Mixing Effects in Reburning Using a Simple Mixing Model},
journal = {Combust. Flame},
year = {2000},
volume = {122},
number = {},
pages = {151--164},
month = {},
note = {}
}

@article {Chakraborty2004,
author = {Chakraborty, N. and Cant, S.},
title = {Unsteady effects of strain rate and curvature on turbulent premixed flames in an inflow outflow configuration},
journal = {Combust. Flame},
year = {2004},
volume = {137},
number = {},
pages = {129--147},
month = {},
note = {}
}

@article {ChakrabortyCant2005,
author = {Chakraborty, N. and Cant, S.},
title = {Influence of Lewis number on curvature effects in turbulent premixed flame propagation in the thin reaction zones regime},
journal = {Phys.\ Fluids},
year = {2005},
volume = {17},
number = {},
pages = {105105},
month = {},
note = {}
}

@article {Chakraborty2005,
author = {Chakraborty, P. and Balachandar, S. and Adrian, R. J.},
title = {On the relationships between local vortex identification schemes},
journal = {J. Fluid Mech.},
year = {2005},
volume = {535},
pages = {189--214}
}


@article {Chakraborty2008,
author = {Chakraborty, N. and Hawkes, E. R. and Chen, J. H. and Cant, S.},
title = {The effects of strain rate and curvature on surface density function transport in turbulent premixed methane-air and hydrogen-air flames: A comparative study},
journal = {Combust. Flame},
year = {2008},
volume = {154},
number = {},
pages = {1427--1444},
month = {},
note = {}
}


@article {Chakraborty2008b,
author = {Chakraborty, N. and Klein M.},
title = {A priori direct numerical simulation assessment of algebraic flame surface density models for turbulent premixed flames in the context of large eddy simulation},
journal = PF,
year = {2008},
volume = {20},
number = {},
pages = {},
month = {},
note = {}
}
@article {Chakraborty2009,
author = {Chakraborty, N. and Cant, S.},
title = {Effects of Lewis number on turbulent scalar transport and its modelling in turbulent premixed flames},
journal = {Combust. Flame},
year = {2009},
volume = {156},
number = {},
pages = {259--280},
month = {},
note = {}
}

@article {Chang1992, 
author = {Chang, A. Y. and DiRosa, M. D. and Hanson, R. K.}, 
title = {Temperature dependence of collision broadening and shift in the {NO} {A} $\leftarrow$ {X} (0,0) band in the presence of argon and nitrogen}, 
journal = {J. Quant. Spectrosc. Radiat. Transfer}, 
year = {1992}, 
volume = {47}, 
number = {},
pages = {375--390}, 
month = {}, 
note = {} 
}

@article {Charlston2001,
author = {Charleston-Goch, D. and Chadwick, B. L. and Morrison, R. J. S. and Campisi, A. and Thomsen, D. D. and Laurendeau, N. M.},
title = {{Laser-Induced Flourescence Measurements amd Modeling of Nitric Oxide in Premixed Flames of $\rm CO + H+2 + CH_4$ and Air at High Pressures}},
journal = {Combust. Flame},
year = {2001},
volume = {125},
number = {},
pages = {729--743},
month = {},
note = {}
}

@article {Charlette2002,
author = {Charlette, F. and Meneveau, C. and Veynante, D.},
title = {A power-law flame wrinkling model for {LES} of premixed turbulent combustion {P}art {I}: non-dynamic formulation and initial tests},
journal = {Combust. Flame},
year = {2002},
volume = {131},
number = {},
pages = {159--180},
month = {},
note = {}
}

@book{Chase1998,
  title={{NIST}-{JANAF} Thermochemical Tables},
  author={Chase, M. W.},
  series={J. Phys. Chem. Ref. Data},
  edition={4},
  year={1998},
  volume={9},
  publisher={American Inst. of Physics}
}

@book {ChenChen1995,
author = {Chen, G. and Chen, G. and Hsu, S.-H.},
title = {Linear Stochastic Control Systems},
year = {1995},
publisher = {CRC Press},
edition = {},
address = {Boca Raton}
}

@article{ChenDoolen:1998,
  author =       {Chen, S. and Doolen, G. D.},
  title =        {Lattice {B}oltzmann method for fluid flows},
  journal =      {Annu. Rev. Fluid Mech.},
  volume=        30,
  pages =        {329--364},
  year =         1998
}

@article {ChenIm1998,
author = {Chen, J. H. and Im, H.},
title = {Correlation of flame speed with stretch in turbulent premixed methane/air flames},
journal = {Proc. Combust. Inst.},
year = {1998},
volume = {27},
number = {},
pages = {819--826},
month = {},
note = {}
}

@article {Chen2002,
author = {Chen, Y.-C. and Kalt, P. A. M. and Bilger, R. W. and Swaminathan, N.},
title = {Effects of mean flow divergence on turbulent scalar flux and local flame structure in premixed turbulent combustion},
journal = {Proc. Combust. Inst.},
year = {2002},
volume = {},
number = {},
pages = {1863--1871},
month = {},
note = {}
}

@article {Cheng1991,
author = {Cheng, R. K. and Shepherd, I. G.},
title = {The Influence of Burner Geometry on Premixed Turbulent Flame Propagation},
journal = {Combust. Flame},
year = {1991},
volume = {85},
number = {},
pages = {7--26},
month = {},
note = {}
}

@article{Cheng2008,
author = {R. K. Cheng and D. Littlejohn},
title = {Effects of Combustor Geometry on the Flowfields and Flame Properties of a Low-Swirl Injector},
journal = {Journal of Engineering for Gas Turbines and Power,},
volume = {in press (2008)},
year = {2008},
note = {also ASME GT2007-27512},
}

@TechReport{Cheng2009,
  author = {Cheng, R. K.},
  title =  {Low-Swirl Burner for Fuel-Flexible Gas Turbines in Near-Zero Emissions Clean Coal Power Plants},
  institution =  {Lawrence Berkeley National Laboratory},
  year = {2009},
  note = {} 
}

@InBook{Cheng2009a,
  author =    {R. K. Cheng},
  ALTeditor =    {T. Lieuwen and V. Yang and R. Yetter},
  title =        {Turbulent Combustion Properties of Premixed Syngases},
  chapter =      {5},
  publisher =    {CRC Press},
  year =         {2009},
  address =   {Boca Raton, Florida},
  pages =     {129-168},
}

@article{Cheng2009b,
author = {R. K. Cheng and D. Littlejohn and P. A. Strakey and T. Sidwell},
title = {Laboratory investigation of a low-swirl injector with {H}$_2$ and {CH}$_4$ at gas turbine conditions},
journal = {Proc. Combust. Inst.},
volume = {32},
year = {2009},
pages = {3001--3009},
note = {},
}

@article{Cheng2014,
author = {Cheng, W. and Samtaney, R.},
title = {Power-law versus log-law in wall-bounded turbulence: A large-eddy simulation perspective},
journal = PF,
volume = {26},
number = {},
year = {2014},
pages = {011703-1--011703-7},
note = {},
}

@article{Cheng2015,
author = {Cheng, W. and Pullin, D. I. and Samtaney, R.},
title = {Large-eddy simulation of separation and reattachment of a flat plate turbulent boundary layer},
journal = JFM,
volume = {785},
number = {},
year = {2015},
pages = {78--108},
note = {},
}

@article{Cheng2017,
author = {Cheng, W. and Pullin, D. I. and Samtaney, R. and Zhang, W. and Gao, W.},
title = {Large-eddy simulation of flow over a cylinder with $Re_D$ from $3.9 \times 10^3$ to $8.5 \times 10^5$: a skin-friction perspective},
journal = JFM,
volume = {820},
number = {},
year = {2017},
pages = {121--158},
note = {},
}
@article{Cheng2018,
author = {Cheng, W. and Pullin, D. I. and Samtaney, R.},
title = {Large-eddy simulation of flow over a grooved cylinder up to transcritical Reynolds numbers},
journal = JFM,
volume = {835},
number = {},
year = {2018},
pages = {327--362},
note = {},
}

@article {Chiesa2005,
author = {P. Chiesa and G. Lozza and L. Mazzocchi},
title = {Using Hydrogen Gas as Turbine Fuel},
journal = {J. Eng. Gas Turbines Power},
year = {2005},
volume = {127},
number = {},
pages = {73--80},
month = {},
note = {}
}
@ARTICLE{SBCL:2005,
    AUTHOR = {P. Schwartz and M. Barad and P. Colella and T. Ligocki},
    TITLE = {A {C}artesian Grid Embedded Boundary Method for the Heat Equation and Poisson's Equation in Three Dimensions},
    JOURNAL= JCP,
    VOLUME={211},
    NUMBER={2},
    MONTH=January,
    YEAR={2006},
    PAGES={531-550}
}

@ARTICLE{CGKM:2005,
    AUTHOR = {P. Colella and D. T. Graves and B. Keen and D. Modiano},
    TITLE = {A {C}artesian Grid Embedded Boundary Method for Hyperbolic Conservation Laws},
    JOURNAL= JCP,
    VOLUME={211},
    NUMBER={1},
    MONTH=January,
    YEAR={2006},
    PAGES={347-366}
}

@TechReport{ChomboDesign,
  author =       {M. Adams and P. Colella and D. T. Graves and J. N. Johnson and H. S. Johansen and N. D. Keen and T. J. Ligocki and
D. F. Martin and P. W. McCorquodale and D. Modiano and P. O. Schwartz and T. D. Sternberg and B. {Van Straalen}},
  title =        {{C}hombo Software Package for {AMR} Applications---Design Document},
  institution =  {Lawrence Berkeley National Laboratory},
  year =         2015,
  number =       {LBNL-6616E}
}

@TechReport{ChomboDesignEB,
  author =       {P. Colella and D. T. Graves and T. J. Ligocki and G. Miller and D. Modiano and P. Schwartz and B. V. Straalen and J. Pillod and D. Trebotich and M. Barad},
  title =        {{EBChombo software package for {C}artesian grid, embedded
boundary application}},
  institution =  {Lawrence Berkeley National Laboratory},
  year =         2014,
  number =       {LBNL-6615E}
}

@Manual{ChomboDesign3,
  title =        {{Chombo Software Package for AMR Applications - Design Document}},
  author =       {P. Colella and D. T. Graves and N.D. Keen and T. J. Ligocki and
D. F. Martin and P.W. McCorquodale and D. Modiano and P.O. Schwartz and T.D. Sternberg and B. Van Straalen},
  organization = {Lawrence Berkeley National Laboratory},
  year =         {2009},
  note =         {{\ttfamily https://seesar.lbl.gov/anag/chombo/ChomboDesign-3.0.pdf}},
}

@article{Chorin1968,
  doi = {10.1090/s0025-5718-1968-0242392-2},
  year = {1968},
  publisher = {American Mathematical Society ({AMS})},
  volume = {22},
  number = {104},
  pages = {745--745},
  author = {Chorin, A. J.},
  title = {Numerical solution of the {N}avier-{S}tokes equations},
  journal = {Mathematics of Computation}
}

@article{BCG1989,
  doi = {10.1016/0021-9991(89)90151-4},
  year = {1989},
  month = dec,
  publisher = {Elsevier {BV}},
  volume = {85},
  number = {2},
  pages = {257--283},
  author = {Bell, J. B. and Colella, P. and Glaz, H. M.},
  title = {A second-order projection method for the incompressible {N}avier-{S}tokes equations},
  journal = JCP
}

@article {Chorin2009,
author = {Chorin, A. J. and Tu, X.},
title = {Implicit sampling for particle filters},
journal = {Proceedings of the National Academy of Sciences},
year = {2009},
volume = {106},
number = {41},
pages = {17249-17254},
month = {},
note = {}
}

@incollection {Chorin2013, 
AUTHOR = {Chorin, A. and Morzfeld, M. and Tu, X.},
   TITLE    = "A survey of implicit
    particle filters for data assimilation",
   BOOKTITLE    = "State Space Models --- Application in Economics and Finance",
   SERIES   = "Statistics and Econometrics for Finance",
   VOLUME   = "1",
   PUBLISHER    = "Springer",
   YEAR     = "2013",
   PAGES    = "63-88",
}
@article {Chorin2013b,
author = {Chorin, A. and Morzfeld, M. and Tu, X.},
title = {Implicit sampling, with application to data assimilation},
journal = {Chinese Annals of Mathematics. Series B},
year = {2013},
volume = {34},
number = {1},
pages = {89--98},
month = {},
note = {}
}

@article {Chorin2016, 
 AUTHOR = {Chorin, A. and Lu, F. and Miller, R. and
              Morzfeld, M. and Tu, X.},
     TITLE = {Sampling, feasibility, and priors in data assimilation},
   JOURNAL = {Discrete Contin. Dyn. Syst.},
  FJOURNAL = {Discrete and Continuous Dynamical Systems. Series A},
    VOLUME = {36},
      YEAR = {2016},
    NUMBER = {8},
     PAGES = {4227--4246},
}

@TechReport{Choudhari2005,
author = {Choudhari, M. and Fischer, P.},
title = {Roughness-induced transient growth},
institution = {35th AIAA Fluid Dynamics Conference},
year = {2005},
type = {AIAA},
}

@TechReport{Christopher2016,
author = {Christopher, J. C. and Gao, X. and Guzik, S. M.},
title = {Anisotropic Patch-Based Adaptive Mesh Refinement for Finite-Volume Methods},
institution = {54th AIAA Aerospace Sciences Meeting},
year = {2016},
type = {AIAA},
number = {2016-0605}
}

@inproceedings{Christopher2019,
  title = {Space-Time Adaptivity with Multigrid Reduction in Time for the Compressible {N}avier-{S}tokes Equations},
  booktitle = {19th Copper Mountain Conference On Multigrid Methods},
  author = {Christopher, J. and Gao, X. and Guzik, S. M. and Falgout, R. D. and Schroder, J. B.},
  year = {2019},
  note = {LLNL-CONF-765114}
}

@inproceedings{Christopher2020,
   author = {J. Christopher and X. Gao and S.Guzik and R. D. Falgout and J. B. Schroder},
   title = {Parallel In Time for a Fully Space-Time Adaptive Mesh Refinement Algorithm},
   booktitle = {Proceedings of the AIAA SciTech Forum},
   year = {Jan., 2020},
   location = {Orlando, FL, USA},
   publisher = {AIAA}
}

@inproceedings{Christopher2021,
   author = {J. Christopher and X. Gao and S.Guzik},
   title = {High-Order Implicit-Explicit Additive {R}unge-{K}utta Schemes for Numerical Combustion with Adaptive Mesh Refinement},
   year = {2021},
   note = {Accepted for publication},
   publisher = {Int. J. Numer. Meth. Fl.}
}

@article {Chung2006,
author = {Chung, M.},
title = {{C}artesian cut cell approach for simulating incompressible flows with rigid bodies of arbitrary shape},
journal = {Comput. Fluids},
year = {2006},
volume = {35},
number = {},
pages = {606--623},
month = {},
note = {}
}

@article {Chung2009,
author = {Chung, D. and Pullin, D. I.},
title = {Large-eddy simulation and wall modelling of turbulent channel flow},
journal = JFM,
year = {2009},
volume = {631},
number = {},
pages = {281--309},
month = {},
note = {}
}

@article {Chung2010,
author = {Chung, D. and Pullin, D. I.},
title = {Direct numerical simulation and large-eddy simulation of stationary buoyancy-driven turbulence},
journal = JFM,
year = {2010},
volume = {643},
number = {},
pages = {279--308},
month = {},
note = {}
}

@article {ChungLaw1984,
author = {Chung, S. H. and Law, C. K.},
title = {{B}urke-{S}chumann Flame with Streamwise and Preferential Diffusion},
journal = {Combust. Sci. Technol.},
year = {1984},
volume = {37},
number = {},
pages = {21--46},
month = {},
note = {}
}

@article {ChungLaw1984b,
author = {Chung, S. H. and Law, C. K.},
title = {An Invariant Derivation of Flame Stretch},
journal = {Combust. Flame},
year = {1984},
volume = {55},
number = {},
pages = {123--125},
month = {},
note = {}
}

@techreport {Clark1977,
author = {Clark, R. A. and Ferziger, J. H. and Reynolds, W. C.},
title = {Evaluation of Subgrid-Scale Turbulence Models Using a Fully Simulated Turbulent Flow},
institution = {NASA},
year = {1977},
type = {Technical Report},
number = {NASA-CR-152642},
address = {},
month = {March},
note = {} 
}

@article {Clark1979,
author = {Clark, R. A. and Ferziger, J. H. and Reynolds, W. C.},
title = {Evaluation of subgrid-scale models using an accurately simulated turbulent flow},
journal = JFM,
year = {1979},
volume = {91},
number = {},
pages = {1--16},
month = {},
note = {}
}

@techreport {Clarke1986,
author = {Clarke, D. and Salas, M. and Hassan, H.},
title = {Euler calculations for multi-element airfoils using {C}artesian grids},
institution = {AIAA},
year = {1986},
type = {Paper},
number = {J. 24},
address = {},
pages = {1128-1135},
month = {},
note = {} 
}

@article {Clavin1983,
author = {Clavin, P. and Joulin, G.},
title = {Premixed flames in large scale and high intensity turbulent flow},
journal = {J. Physique--Lettres},
year = {1983},
volume = {44},
number = {},
pages = {L1--L12},
month = {},
note = {}
}

@article {Clavin2000,
author = {Clavin, P.},
title = {},
journal = {Proc. Combust. Inst.},
volume = 28,
year = 2000,
pages = {569}
}

@article {Chorin2012,
title = "Interpolation and Iteration for
    Nonlinear Filters",
journal = "M2AN Math. Model. Numer. Anal.  ",
volume = "46",
pages = "535-543",
year = "2012",
author = " A. Chorin and X. Tu",
} 

@article {ChungLaw1988,
author = {Chung, S. H. and Law, C. K.},
title = {An Integral Analysis of the Structure and Propagation of Stretched Premixed Flames},
journal = {Combust. Flame},
year = {1988},
volume = {72},
number = {3},
pages = {325--336},
month = jun,
note = {}
}

@article {Cockburn1989,
author = {Cockburn, B and Shu, C-W},
title = {TVB {R}unge–{K}utta local projection discontinuous {G}alerkin finite element method for conservation laws II: general framework},
journal = {Math. Comput.},
year = {1989},
volume = {52},
number = {},
pages = {411--435},
month = {},
note = {}
}

@article {Cockburn1998,
author = {Cockburn, B and Shu, C-W},
title = {The {R}unge–{K}utta discontinuous {G}alerkin finite element method for conservation laws V: multidimensional systems},
journal = {J. Comput. Phys.},
year = {1998},
volume = {141},
number = {},
pages = {199--224},
month = {},
note = {},
OPTdoi = {10.1006/jcph.1998.5892},
}

@article {Cocks2015,
author = {Cocks, P. A. T. and Soteriou, M. and Sankaran, V.},
title = {Impact of numerics on the predictive capabilities of reacting flow LES},
journal = {Combust. and Flame},
year = {2015},
volume = {162},
number = {},
pages = {3394--3411},
month = {},
note = {}
}

@ARTICLE{Coelho2009,
 author =  {Coelho, P. J.},
 title =   {Approximate solutions of the filtered radiative transfer equation in large eddy
simulations of turbulent reactive flows},
 journal ={Combust. Flame},
 volume =  {156},
 year =    {2009},
 pages =   {1099--1110}
}

@article {CoffeeHeimerl1981,
author = {T. P. Coffee and J. M. Heimerl},
title = {Transport algorithms for premixed laminar steady-state flames},
journal = {Combust. Flame},
volume = {43},
pages = {273},
year = {1981}
}

@article {Coirier1996,
author = {Coirier, W. and Powell, K.},
title = {Solution-adaptive {C}artesian cell approach for viscous and inviscid flows},
journal = {AIAA J.},
volume = {34},
number = {5},
pages = {938-945},
year = {1996}
}

@article {Colburn2011,
author = {Colburn, C. H. and Cessna, J. B. and Bewley, T. R.},
title = {State estimation in wall-bounded flow systems part 3. {T}he ensemble {K}almam filter},
journal = {J. Fluid Mech.},
volume = {682},
pages = {289--303},
year = {2011}
}

@article{Colella2006,
        author = {Colella, P. and Graves, D.T. and Keen, B.J. and Modiano, D.},
        title = {A {C}artesian grid embedded boundary method for hyperbolic conservation laws},
        journal = JCP,
        year = 2006,
        volume = 211,
        pages = {347--366}}
        
@ARTICLE{Colella2011,
 author =  {P. Colella and M. R. Dorr and J. A. F.  Hittinger and D. F. Martin},
 title =   {High-order finite-volume methods in mapped coordinates},
 journal = JCP,
 volume =  {230},
 year =    {2011},
 pages =   {2952--2976}
}

@ARTICLE{Colin2000,
  author={Colin, O. and Ducros, F. and Veynante, D. and Poinsot, T.},
  title={A thickened flame model for large eddy simulations of turbulent premixed combustion},
  journal = {Phys. Fluids},
  volume = {12},
  number = {7},
  pages= {1843--1863},
  year= {2000}
} 

@Misc{Comer2019,
  author =       {Comer, A. and Ihme, M. and Li, C. and Menon, S. and Oefeline, J. and Rankin, B. and Sankaran, V. and Sankaran, V.},
  title =        {Proceedings of the Third Model Validation for Propulsion ({MVP} 3) Workshop},
  month =        {January},
  year =         {2019},
  note =         {{AIAA} SciTech Forum}
}

@article{ComteBellot1971,
author={Comte-Bellot, G. and Corrsin, S.},
title={Simple {E}ulerian time correlation of full and narrow-band velocity signals in grid-generated, 'isotropic' turbulence},
journal={J. Fluid Mech.},
volume={48},
number={},
year={1971},
month={},
pages={273--337}
}

@ARTICLE{Copalle1983,
  author={Copalle, A. and Vervisch, P.},
  title={The total emissivities of high temperature flames},
  journal = {Combust. Flame},
  volume = {49},
  number = {},
  pages= {101--108},
  year= {1983}
} 

@article {Cook1961,
author = {Cook, Martin L.},
title = {Magnus force and moments on a quasi-cylindrical rotating body with the axis of rotation perpendicular to the airstream},
journal = {AERO 1006},
year = {1961},
month = {August},
note = {David W. Taylor Model Basin Report, (Confidential?)}
}

@article{Corpetti2009,
author = {Corpetti, T. and H{\'e}as, P. and M{\'e}min, E. and Papadakis, N.},
title = {Pressure image assimilation for atmospheric motion estimation},
journal = {Tellus A},
year = {2009},
volume = {61},
number = {},
pages = {160--178},
month = {},
note = {}
}


@article{Correa1992,
AUTHOR = "S.M. Correa",
TITLE = "A Review of NOx Formation Under Gas-Turbine Combustion Conditions",
JOURNAL = "Combust. Sci. Technol." ,
VOLUME ="87",
PAGES = "329-362",
YEAR = "1992"
}

@article{Correia2013,
author = {Correia, A. W. and Peters, J. L. and Levy, J. I. and Melly, S. and Dominici, F.},
title = {Residential exposure to aircraft noise and hospital admissions for cardiovascular diseases: multi-airport retrospective study},
journal = {Br. Med. J.},
year = {2013},
volume = {347},
number = {7928},
pages = {},
month = {October},
note = {}
}

@article {Costa2003,
author = {Costa, F. de S. and Cardoso, J. and Villela, T. E. A.},
title = {{Effects of Wet $\rm CO$ Oxidation on the Operation of Engines and Power Generators}},
journal = {J. of the Braz. Soc. of Mech. Sci. \& Eng.},
year = {2003},
volume = {25},
number = {4},
pages = {341--346},
month = October--December,
note = {}
}

@article{Crockett2010,
        author = {Crockett, R. K. and Colella, P. and Graves, D. T.},
        title = {A {C}artesian grid embedded boundary method for solving the {P}oisson and heat equations with discontinuous coefficients in three dimensions},
        journal = jcp,
        year = 2010,
        volume = 230,
        number = 7,
        pages = {2451--2469}}

@Manual{CUDAPGv82017,
  title =        {CUDA C Programming Guide},
  organization = {Nvidia},
  edition =      {8.0},
  note =         {\url{http://docs.nvidia.com/cuda/cuda-c-programming-guide/index.html}}
}

@Manual{CUDAPGv9-2018,
  title =        {CUDA C Programming Guide},
  organization = {Nvidia},
  edition =      {9.2},
  note =         {\url{https://docs.nvidia.com/cuda/cuda-c-programming-guide/index.html}}
}
@Manual{CUDAPGv2019,
  title =        {CUDA C Programming Guide},
  organization = {Nvidia},
  edition =      {10.1},
  note =         {\url{"https://docs.nvidia.com/cuda/pdf/CUDA_C_Programming_Guide.pdf}}
}
@article {Curran2002,
author = {Curran, H.J. and Gaffuri,P. and Pitz, W.J. and Westbrook, C. J.},
title = {A comprehensive modeling study of iso-octane oxidation},
journal = {Combust. Flame},
volume ={129},
pages = {253--280},
year = {2002}
}

@article {Curran1998,
author = {Curran, H.J. and Gaffuri,P. and Pitz, W.J. and Westbrook, C. J.},
title = {A Comprehensive Modeling Study of n-Heptane Oxidation},
journal = {Combust. Flame},
volume ={114},
pages = {149--177},
year = {1998}
}

   ####
   #   #
   #   #
   #   #
   #   #
   #   #
   ####

@article {Dakhoul1986a,
author = {Dakhoul, Y.M. and Bedford, K.W.},
title = {Improved averaging method for turbulent flow simulation. Part I: Theoretical development and application to Burgers transport equation},
journal = {International Journal for Numerical Methods in Fluids 6.2},
year = {1986},
volume = {},
number = {},
pages = {49--64},
month = {},
note = {}
}

@article {Dakhoul1986b,
author = {Dakhoul, Y.M. and Bedford, K.W.},
title = {Improved averaging method for turbulent flow simulation. Part {II}: Calculations and verification},
journal = {International Journal for Numerical Methods in Fluids 6.2},
year = {1986},
volume = {},
number = {},
pages = {65--82},
month = {},
note = {}
}

@article {Damkohler1940,
author = {Damk\"ohler, G.},
title = {},
journal = {A. Electrochem.},
year = {1940},
volume = {46},
number = {},
pages = {601},
month = {},
note = {}
}

@article {Damen2006,
author = {Damen, K. and Troost, M. van and Faaij, A. and Tuckenburg, W.},
title = {{A comparison of electricity and hydrogen production systems with $\rm CO_2$ capture and storage. Part A: Review and selection of promising conversion and capture technologies}},
journal = {Prog. Energy Combust. Sci.},
year = {2006},
volume = {32},
number = {},
pages = {215--246},
month = {},
note = {}
}

@article {Daou2002,
author = {Daou, J. and Dold, J. and Matalon, M.},
title = {The thick flame asymptotic limit and {D}amk\"ohler's hypothesis},
journal = {Combust. Theory Model.},
year = {2002},
volume = {6},
number = {},
pages = {141--153},
month = {},
note = {}
}

@article {Darabiha1996,
author = {Darabiha, N. and Candel, S. M. and Marble, F. E.},
title = {The Effect of Strain Rate on a Premixed Laminar Flame},
journal = {Combust. Flame},
year = {1996},
volume = {64},
number = {},
pages = {203--217},
month = {},
note = {}
}

@Article{Day2000,
  author =       {Day, M. S. and Bell, J. B.},
  title =        {Numerical simulation of laminar reacting flows with complex chemistry},
  journal =      {Combust. Theory Model.},
  year =         {2000},
  volume =    {4},
  pages =     {535-556}
}

@book {DayEtal2009,
author = {Day, M. S. and Bell, J. B. and Cheng, R. K. and Tachibana, S. and Beckner, V. E. and Lijewski, M. J.},
title = {Cellular burning in lean premixed turbulent hydrogen-air flames: coupling experimental and computational analysis at the laboratory scale},
publisher = {Institute of Physics Publishing},
year = {2009},
volume = {180},
series = {Journal of Physics Conference Series: SciDAC 2009 (W.\ Tang, Ed.)},
address = {San Diego, CA},
pages = {012031},
edition = {},
month = {}
}

@article {Day2011a,
author = {Day, M. S. and Bell, J. B. and Gao, X. and Glarborg, P.},
title = {Numerical Simulation of Nitrogen Oxide Formation in Lean Premixed Turbulent H2/O2/N2 Flames},
journal = {Proc. Combust. Inst.},
year = {2011},
volume = {33},
number = {1},
pages = {1591--1599},
month = {},
note = {}
}
@article {Day2011b,
author = {Day, M. S. and Gao, X. and Bell, J. B.} ,
title = {Properties of Lean Turbulent Methane-Air Flames with Significant Hydrogen Addition},
journal = {Proc. Combust. Inst.},
year = {2011},
volume = {33},
number = {1},
pages = {1601--1608},
month = {},
note = {}
}

@techreport {Demaree,
author = {James E. Demaree},
title = {Reevaluation of burner characteristics for fire resistance tests},
institution = {U.S. Department of Transportation, Federal Aviation Administration},
year = {1977},
type = {Technical Report},
number = {FAA-RD-76-213},
address = {},
month = {},
note = {} 
} 

@article{DongEtal2005,
author = {Dong, Y. and Holley, A. T. and Andac, M. G. and Egolfopoulos, F. N. and Davis,
S. G. and Middha, P. and Wang, H},
title = {Extinction of premixed {H}2/air flames: Chemical kinetics and molecular diffusion
effects},
journal = {Combus. Flame},
volume = 142, 
number = 4,
year = 2005,
pages = {374--387}
}

@article{DavisEtal2005,
author = {Davis, S. G. and Joshi, A. V. and Wang, H. and Egolfopoulos, F. N.},
title = {An optimized kinetic model for {$H_2/CO$} combustions},
journal = {Proc. Combust. Inst.},
volume = 30,
year = 2005,
pages = {1283-1292}
}

@article {Day1972,
author = {Day, M. J. and Dixon-Lewis, G. and Thoomson, K.},
title = {Flame Structure and Flame Reaction Kinetics. {VI}. Structure, Mechanism and Properties of Rich Hydrogen + Nitrogen + Oxygen Flames},
journal = {Proc. Roy. Soc. London Ser. A},
year = {1972},
volume = {330},
number = {},
pages = {199--218},
month = {},
note = {issue 1581}
}

@article {Day2009,
author = {Day, M. S. and Bell, J. B. and Bremer, Peer-Timo and Pascucci, V. and Beckner, V. and Lijewski, M.}, 
title = {Turbulence effects on cellular burning structures in lean premixed hydrogen flames}, 
journal = {Combust. Flame}, 
year = {2009}, 
volume = {156}, 
number = {}, 
pages = {1035--1045}, 
month = {}, 
note = {} 
}
@article {DayBell2000, 
author = {Day, M. S. and Bell, J. B.}, 
title = {Numerical simulation of laminar reacting flows with complex chemistry}, 
journal = {Combust. Theory Model.}, 
year = {2000}, 
volume = {4}, 
number = {}, 
pages = {535--556}, 
month = {}, 
note = {} 
}

@article {deCharentenay2002,
author = {de Charentenay, J. and Ern, A.},
title = {Multicomponent transport impact on turbulent premixed H2/O2 flames},
journal = {Combust.\ Theory Model.},
year = {2002},
volume = {6},
number = {},
pages = {439--462},
month = {},
note = {}
}

@book{DeBoor,
author    = {De Boor, Carl},
title     = {A practical guide to splines; rev. ed.},
publisher = {Springer},
address   = {Berlin},
series    = {Applied mathematical sciences},
year      = {2001}
}

@article {Dee2009,
author = {Dee, D. P. and Uppala, S.},
title = {Variational bias correction of satellite radiance data in the ERA-Interim reanalysis},
journal = {Q. J. R. Meteorol Soc.},
year = {2009},
volume = {135},
number = {},
pages = {1830--1841},
month = {},
note = {}
}

@article {Deng2012,
author = {Deng, X and Mao, M and Tu, G and Zhang, H and Zhang, Y},
title = {High-order and high accurate CFD models and their applications for complex grid problems},
journal = JCP,
year = {2012},
volume = {11},
number = {4},
pages = {1081--1102},
month = {April},
note = {}
}

@article {Derber1998,
author = {Derber, J. C. and Wu, W.-S.},
title = {The use of {TOVS} cloud-cleared radiances in the {NCEP} {SSI} analysis system},
journal = {Mon. Wea. Rev.},
year = {1998},
volume = {126},
number = {},
pages = {2287--2299},
month = {},
note = {}
}

@article {DeshairesJoulin1984,
author = {Deshaires, B. and Joulin G.},
title = {},
journal = {Combust. Sci. Technol.},
year = {1984},
volume = {37},
number = {},
pages = {99--116},
month = {},
note = {}
}

@Article{Devendran2017,
  author =       {Devendran, D. and Graves, D. T. and Johansen, H. and Ligocki, T.},
  title =        {A fourth-order {C}artesian grid embedded boundary method for {P}oisson's equation},
  journal =      {Comm. App. Math. and Comp. Sci.},
  year =         2017,
  volume =       12,
  number =       1,
  pages =        {51--79}
}

@article {Deshaires1990,
author = {Deshaires, B. and Cambray, P.},
title = {The Velocity of a Premixed Flame as a Function of the Flame Stretch: An Eperimental Study},
journal = {Combust. Flame},
year = {1990},
volume = {82},
number = {},
pages = {361--375},
month = {},
note = {}
}

@PhdThesis{Diez2018,
  author =       {Diez, R.},
  title =        {Machine learning for RANS turbulence modelling of variable property flows},
  school =       {Delft University of Technology},
  year =         {2018},
  OPTkey =       {},
  OPTtype =      {},
  OPTaddress =   {},
  OPTmonth =     {},
  OPTnote =      {},
  OPTannote =    {}
}

@article {Dikpati2012,
author = {Dikpati, M. and Anderson, J. L.},
title = {{EVALUATING POTENTIAL FOR DATA ASSIMILATION IN A FLUX-TRANSPORT DYNAMO MODEL BY ASSESSING SENSITIVITY AND RESPONSE TO MERIDIONAL FLOW VARIATION}},
journal = {The Astrophysical Journal},
year = {2012},
volume = {756},
number = {1},
pages = {20},
month = {},
note = {doi:10.1088/0004-637X/756/1/20}
}


@article {DiRosa1994a, 
author = {DiRosa, M. D. and Hanson, R. K.},
title = {Collision-Broadening and -Shift of {NO} $\gamma(0,0)$ Absorption Lines by {H}$_2${O}, {O}$_2$, and {NO} at 295{K}},
journal = {J. Mol. Spectrosc.}, 
year = {1994},
volume = {164}, 
number = {}, 
pages = {97--117}, 
month = {}, 
note = 
{} 
}

@article {DiRosa1994b, 
author = {DiRosa, M. D. and Hanson, R. K.},
title = {Collision broadening and shift of {NO} $\gamma(0,0)$ absorption lines by {O}$_2$ and {H}$_2${O} at high temperature}, 
journal = {J. Quant. Spectrosc. Radiat. Transfer},
year = {1994}, 
volume = {52}, 
number = {}, 
pages = {515--529},
month = {}, 
note = {} 
}

@inproceedings {DiSarli2005,
booktitle = {International Conference on Hydrogen Safety},
author = {Di Sarli, V. and Di Benedetto, A.},
year = {2005},
editor = {},
pages = {},
organization = {ICHS},
address = {Pisa, Italy},
month = sep,
note = {Study of hydrogen enriched premixed flames}
}

@article {DixonLewis1973,
author = {Dixon-Lewis, G. and Isles, G. L. and Walmsley, R.},
title = {Flame Structure and Flame Reaction Kinetics. {VIII}. Structure, Properties and Mechanism of a Rich Hydrogen + Nitrogen + Oxygen Flame at Low Pressure},
journal = {Proc. Roy. Soc. London Ser. A},
year = {1973},
volume = {331},
number = {},
pages = {571--584},
month = {},
note = {}
}

@article {Dowdy1990,
author = {Dowdy, D. R. and Smith, D. B. and Taylor, S. C. and Williams, A.},
title = {The use of expanding spherical flames to determine burning velocities and stretch effects in hydrogen/air mixtures},
journal = {Proc. Combust. Inst.},
year = {1990},
volume = {23},
number = {},
pages = {325--332},
month = {},
note = {}
}

@ARTICLE{dosSantos2008,
author = {dos Santos, R. and Lecanu, M. and Ducruix, S. and Gicquel, O. and Iacona, E. and Veynante, D.},
title = {Coupled large eddy simulations of turbulent combustion and radiative heat transfer},
journal = {Combust. Flame},
volume = 152, 
number = 3,
year = 2008,
pages = {387--400}
}
@article{Domingo2005,
title = "{DNS} of a premixed turbulent {V} flame and {LES} of a ducted flame using a {FSD-PDF} subgrid scale closure with {FPI}-tabulated chemistry ",
journal = "Combust. Flame ",
volume = "143",
number = "4",
pages = "566-586",
year = "2005",
issn = "0010-2180",
author = "Pascale Domingo and Luc Vervisch and Sandra Payet and Raphael Hauguel",
keywords = "Direct numerical simulation",
keywords = "Large eddy simulation",
keywords = "Premixed combustion",
keywords = "Tabulated detailed chemistry "
}

@article{Domingo2008,
title = "Large-eddy simulation of a lifted methane jet flame in a vitiated coflow ",
journal = "Combust. Flame ",
volume = "152",
number = "3",
pages = "415-32",
year = "2008",
note = "",
issn = "0010-2180",
author = "Domingo, P. and Vervisch, L. and Veynante, D.",
keywords = "Large-eddy simulation",
keywords = "Detailed chemistry tabulation",
keywords = "Autoignition",
keywords = "Partially premixed turbulent combustion "
}

@Book{Doucet2001,
  author =    {Doucet, A. and de Freitas, N. and Gordon, N.},
  title =        {Sequential {M}onte {C}arlo Methods in Practice},
  publisher =    {Springer, New York},
  year =         {2001}
}

@article{Galpin2008,
title = "Large-eddy simulation of a fuel-lean premixed turbulent swirl-burner",
journal = "Combust. Flame",
volume = "155",
pages = "247-66",
year = "2008",
note = "",
issn = "0010-2180",
author = "J\'{e}remy Galpin and Alexandre Naudin and Luc Vervisch and Christian Angelberger and Olivier Colin and Pascale Domingo",
keywords = "Large-eddy simulation",
keywords = "Premixed turbulent combustion",
keywords = "Swirling flame "
}

@article {DrakeBlint1989,
author = {Drake, M. C. and Blint, R. J.},
title = {Thermal {NO}$_x$ in Stretched Laminar Opposed-Flow Diffusion Flames with {CO}/{H}$_2$/{N}$_2$ Fuel},
journal = {Combust. Flame},
year = {1989},
volume = {76},
number = {},
pages = {151--167},
month = {},
note = {}
}

@article {DrakeBlint1991,
author = {Drake, M. C. and Blint, R. J.},
title = {Relative Importance of Nitric Oxide Formation Mechanisms in Laminar Opposed-flow Diffusion Flames},
journal = {Combust. Flame},
year = {1991},
volume = {83},
number = {},
pages = {185--203},
month = {},
note = {}
}

@article {Dreier1992, 
author = {Dreier, T. and Dreizler, A. and
Wolfrum, J.}, 
title = {The Application of a {R}aman-shifted tunable {K}r{F} Eximer Laser for laser-induced fluorescence Combustion Diagnostics}, 
journal = {Appl. Phys. B}, 
year = {1992}, 
volume = {55}, 
number = {}, 
pages = {381--387}, 
month = {}, 
note = {} 
}

@article {Driscoll1994,
author = {Driscoll, J. F. and Sutkus, D. J. and Roberts, W. L. and Post, M. E. and Goss, L. P.},
title = {The Strain Exerted by a Vortex on a Flame -- Determined From Velocity Field Images},
journal = {Combust. Sci. Technol.},
year = {1996},
volume = {96},
pages = {213--229}
}

@article {Driscoll2008,
author = {Driscoll, J. F.},
title = {Turbulent premixed combustion: Flamelet structure and its effect on turbulent burning velocities},
journal = {Prog. Energy Combust. Sci.},
year = {2008},
volume = {34},
number = {},
pages = {91--134},
month = {},
note = {}
}

@article {Duan2010,
author = {Duan, J. and Fischer, P. and Iliescu, T. and {\"O}zg{\"o}kmen, T. M.},
title = {Bridging the Boussinesq and primitive equations through spatio-temporal filtering},
journal = {Applied Mathematics Letters},
year = {2010},
volume = {23},
number = {},
pages = {453--456},
month = {},
note = {}
}

@article {Duan2010a,
author = {Duan, Le. and Wang, Xiaowen and Zhong, Xiaolin},
title = {A high-order cut-cell method for numerical simulation of hypersonic boundary-layer instability with surface roughness},
journal = JCP,
year = {2010},
volume = {229},
number = {19},
pages = {7207-7237},
month = {June},
note = {}
}

@article {Duraisamy2019,
author = {Duraisamy, K. and Iaccarino, G. and Xiao, H.},
title = {Turbulence Modeling in the Age of Data},
journal = {Annual Review of Fluid Mechanics},
year = {2019},
volume = {51},
number = {},
pages = {357--377},
month = {},
note = {}
}

@article {Durbin1995,
author = {Durbin, P.},
title = {Separated flow computations with the $K$-$\epsilon$-$\bar{\nu^2}$ model},
journal = {AIAA Journal},
year = {1995},
volume = {33},
number = {},
pages = {659--664},
month = {},
note = {}
}

@article {Dryer1972,
author = {Dryer, F. L. and Glassman, I.},
title = {High-temperature oxidation of {CO} and {CH}$_4$},
journal = {Proc. Combust. Inst.},
year = {1972},
volume = {14},
number = {},
pages = {987--1003},
month = {},
note = {}
}

@misc{DRM19,
  author =    {Kazakov, A. and Frenklach, M.},
  title =     {Reduced Reaction Sets based on GRI-Mech 1.2},
  howpublished = {http://www.me.berkeley.edu/drm/},
  month =     {},
  year =      {},
  note =      {University of California at Berkeley}
  }
  
@Article{Dubey2009,
  author =       {Dubey, A. and Antypas, K. and Ganapathy, M.K. and Reid, L.B. and Riley, K. and Sheeler, D. and Siegel, A. and Weide K.},
  title =        {Extensible component based architecture for FLASH, {A} massively parallel, multiphysics simulation code},
  journal =      {Parallel Comput.},
  year =         {2009},
  volume =    {35},
  pages =     {512-522}
}

   #####
   #
   #
   ###
   #
   #
   #####

@Article{Ebtehaj2014,
  author =       {Ebtehaj, A. M. and Zupanski, M. and Lerman, G. and Foufoula-Georgiou, E.},
  title =        {Variational Data Assimilation via Sparse Regularization},
  journal =      {Tellus A},
  year =         {2014},
  volume =    {66}
}

@book {Eckbreth1996,
author = {Eckbreth, A. C.},
editor = {},
title = {Laser diagnostics for combustion temperature and species},
publisher = {Gordon and Breach Publishers},
year = {1996},
volume = {},
series = {},
address = {Amsterdam},
edition = {second},
month = {},
note = {}
}

@incollection {Eddings1994,
author = {Eddings, E. G. and Smith, P. J. and Heap, M. P. and Pershing, D. W. and Sarofim, A. F.},
title = {The use of models to predict the effect of fuel switch on {NO}$_x$ emissions},
booktitle = {Coal-Blending and Switching of Low-Sulfur Western Coals},
editor = {Bryers, R. W. and Harding, N. S.},
publisher = {ASME for The Engineering Foundation},
year = {1994},
pages = {169--184},
note = {Papers presented at The Engineering Foundation Conference on Coal-Blending and Switching of Low-Sulfur Western Coals, Snowbird, Utah, September 26--October 1, 1993}
}

@inproceedings {Edelsbrunner2003,
author = {Edelsbrunner, H. and Harer, J. and Natarajan, V. and Pascucci, V.},
title = {Morse complexes for piecewise linear 3-manifolds},
booktitle = {Proceedings of the 19th ACM Symposium on Computational Geometry},
year = {2003},
editor = {},
pages = {361--370},
organization = {},
publisher = {},
address = {},
month = {June},
}

@unpublished {Edson2019,
author = {Edson and Bunder and Mattner and Roberts},
title = {Lyapunov exponents of the {K}uramoto-{S}ivashinsky {PDE}},
note = {{https://arxiv.org/pdf/1902.09651.pdf}},
month = {Febuary},
year = {2019}
}

@article {Egolfopoulos1990,
	author = {Egolfopoulos, F. N. and Law, C. K.},
	title = {{An Experimental and Computational Study of the Burning Rates of Ultra-Lean to Moderately-Rich H$_2$/O$_2$2/N$_2$ Laminar Flames with Pressure Variations}},
	journal = {Proc. Combust. Inst.},
	year = {1990},
	volume = {23},
	number = {},
	pages = {333--340},
	month = {},
	note = {}
	}

@article {Egolfopoulos1994,
author = {Egolfopoulos, F.},
title = {Dynamics and structure of unsteady, strained, laminar premixed flames},
volume = {25},
year = {1994},
journal = {Proc. Combust. Inst.},
pages = {1365--1373},
}

@article {Ekaterinaris2005,
author = {Ekaterinaris, JA},
title = {High-order accurate, low numerical diffusion methods for aerodynamics},
volume = {41},
year = {2005},
journal = {Prog. Aerosp. Sci.},
pages = {192--300},
}

@book {Ern1994,
author = {Ern, A. and Giovangigli, V.},
editor = {},
title = {Multicomponent Transport Algorithms},
publisher = {Springer-Verlag},
year = {1994},
volume = {m24},
series = {Lecture Notes in Physics},
address = {Berlin},
edition = {},
month = {},
note = {}
}

@article {Ern1995,
author = {Ern, A. and Douglas, C. C. and Smooke, M. D.},
title = {Detailed chemistry modeling of laminar diffusion flames on parallel computers},
journal = {Int. J. Sup. App.},
year = {1995},
volume = {9},
number = {},
pages = {167--186},
month = {},
note = {}
}

@article {Ern1996,
author = {Ern, A. and Giovangigli, V.},
title = {The structure of transport linear systems in dilute isotropic gas mixtures},
journal = {Phys.\ rev.\ {E}},
year = {1996},
volume = {53},
number = {},
pages = {485--492},
month = {},
note = {}
}

@article {Ern1998,
author = {Ern, A. and Giovangigli, V.},
title = {Thermal diffusion effects in hydrogen-air and methane-air flames},
journal = {Combust.\ Theory Model.},
year = {1998},
volume = {2},
number = {},
pages = {349--372},
month = {},
note = {}
}

@article {Ern1999,
author = {Ern, A. and Giovangigli, V.},
title = {Impact of detailed multicomponent transport on planar and counterflow hydrogen\slash air and methane\slash air flames},
journal = {Combust.\ Sci.\ Technol.},
year = {1999},
volume = {149},
number = {},
pages = {157--181},
month = {},
note = {}
}

@techreport {ErnGiovangigli2004,
author = {Ern, A. and Giovangigli, V.},
title = {{EGLIB: A General-Purpose Fortran Library for Multicomponent Transport Property Evaluations}},
institution = {},
year = {2004},
type = {},
number = {},
address = {},
month = {},
note = {Version 3.4}
}

@article {EchekkiChen2003,
author = {Echekki, T. and Chen, J. H.},
title = {Direct numerical simulation of autoignition in non-homogeneous hydrogen-air mixtures},
journal = {Combust. Flame},
year = {2003},
volume = {134},
number = {},
pages = {169--191},
month = {},
note = {}
}
@book {echekki2011,
author = {Echekki, T. and Mastorakos, E.},
title = {Turbulent Combustion Modeling},
publisher = {Institute of Physics Publishing},
year = {2011},
volume = {},
series = {},
address = {},
edition = {},
month = {}
}

@article {Escoda1983,
author = {Escoda, M. C. and Long, M. B.},
title = {{Rayleigh Scattering Measurements of the Gas Concentration Field in Turbulent Jets}},
journal = {AIAA Journal},
year = {1983},
volume = {21},
number = {1},
pages = {81--84},
month = jan,
note = {}
}

@article {Evensen1994a,
author = {Evensen, G.},
title = {Inverse methods and data assimilation in nonlinear ocean models},
journal = {Physica D},
year = {1994},
volume = {77},
number = {},
pages = {108--129},
month = {},
note = {}
}

@article {Evensen1994b,
author = {Evensen, G.},
title = {Sequential data assimilation with a nonlinear quasi-geostrophic model using Monte Carlo methods to forcast error statistics},
journal = {Journal of Geophysical Research},
year = {1994},
volume = {99},
number = {},
pages = {10143--10162},
month = {},
note = {}
}

@article {Evensen2003,
author = {Evensen, G.},
title = {The ensemble Kalman filter: Theoretical formulation and practical implementation},
journal = {Ocean Dyn},
year = {2003},
volume = {53},
number = {},
pages = {343--367},
month = {},
note = {}
}

@article{Evensen2004,
author={Evensen, G.},
title={Sampling strategies and square root analysis schemes for the EnKF},
journal={Ocean Dynamics},
year={2004},
volume={54},
number={6},
pages={539--560},
}

@Book{Evensen2007,
  author =    {Evensen, G.},
  title =        {Data assimilation: the ensemble Kalman filter},
  publisher =    {Springer},
  year =         {2007}
}

@article {Fadlun2000,
author = {Fadlun, E. and Verzicoo, R. and Orlandi, R. and  Mohd-Yusof, J.},
title = { Combined immersed-boundary finite-difference methods for three-dimensional complex flow simulations},
journal = {J. Comput. Phys.},
year = {2000},
volume = {161},
number = {},
pages = {35--60},
note = {}
}


@article {Favre1983,
author = {Favre, A.},
title = {Turbulence: Space-time statistical properties and behavior in supersonice flows},
journal = PF,
year = {1983},
volume = {26},
number = {10},
pages = {2851--2863},
month = oct,
note = {}
}

@article {Fedkiw1999,
author = {Fedkiw, R.P. and Aslam, T.D. and Xu, S.},
title = {The ghost fluid method for deflagration and detonation discontinuities},
journal = JCP,
year = {1999},
volume = {154},
number = {2},
pages = {393--427},
month = {},
note = {}
}

@article {Fenimore1972,
author = {Fenimore, C. P.},
title = {Formation of Nitric Oxide from Fuel Nitrogen in Ethylene Flames},
journal = {Combust. Flame},
year = {1972},
volume = {19},
number = {},
pages = {289--296},
month = {},
note = {}
}

@techreport {FAA,
author = {James E. Demaree},
title = {Reevaluation of burner characteristics for fire resistance tests},
institution = {U.S. Department of Transportation, Federal Aviation Administration},
year = {1977},
type = {Technical Report},
number = {FAA-RD-76-213},
address = {},
month = {},
note = {} 
} 

@techreport {FAA2012,
author = {USFAA},
title = {14 CFR Part 25, Airworthiness standatds: Transport category airplanes},
year = {2012},
type = {Technical Report},
number = {Appendix F, Part I},
address = {},
month = {},
note = {} 
} 

@article {Fedkiw1996,
author  = {Fedkiw, Ronald P. and Merriman, Barry and Osher, Stanley},
title   = {High Accuracy Numerical Methods for Thermally Perfect Gas Flows with Chemistry},
year    = {1997},
journal = JCP,
volume  = {132},
pages   = {175-90}
}

@article {Ferioli2006,
	author = {Ferioli, F. and Buckley, S. G.},
	title = {Measurements of hydrocarbons using laser-induced breakdown spectroscopy},
	journal = {Combust. Flame},
	year = {2006},
	volume = {144},
	number = {3},
	pages = {435--447},
	month = feb,
	note = {}
	}

@article {Fielding1998,
author = {Fielding, J. and Schaffer, A. M. and Long, M. B.},
title = {Three-scalar imaging in turbulent non-premixed flames of methane},
journal = {Proc. Combust. Inst.},
year = {1998},
volume = {27},
number = {},
pages = {1007--1014},
month = {},
note = {}
}

@article{Fdasilva2000,
author = {Figueria da Silva, L. F. and Deshaies, B.},
title = {Stabilization of an oblique detonation wave by a wedge: a parametric numerical study},
journal = {Combust. and Flame},
volume = {121},
number = {1},
pages = {152--166},
year = {2000},
issn = {0010-2180},
OPTdoi = {https://doi.org/10.1016/S0010-2180(99)00141-8},
OPTurl = {http://www.sciencedirect.com/science/article/pii/S0010218099001418}
}

@article {Filatyev2004,
author = {Filatyev, S. A. and Driscoll, J. F. and Carter, C. D. and Donbar, J. M.},
title = {Measured properties of turbulent premixed flames for model assessment, including burning velocities, stretch rates, and surface densities},
journal = {Combust. Flame},
year = {2004},
volume = {141},
number = {},
pages = {1--21},
month = {},
note = {}
}

@article {Filatyev2005,
author = {Filatyev, S. A. and Driscoll, J. F. and Carter, C. D. and Donbar, J. M.},
title = {A database of turbulent premixed flame properties for model assessment, including burning velocities, stretch rates, and surface densities},
journal = {Combust. Flame},
year = {2005},
volume = {141},
number = {},
pages = {1--21},
month = {},
note = {}
}

@article {Fiorina2010,
author = {Fiorina, B. and Vicquelin, R. and Auzillon, P. and Gicquel, O. and Veynante, D.},
title = {A filtered tabulated chemistry model for {LES} of premixed combustion},
journal = {Combust. Flame},
year = {2010},
volume = {157},
number = {3},
pages = {465--475},
month = {},
note = {}
}




@article {Fiveland1991,
author = {Fiveland, W. A. and Jamaluddin, A. S.},
title = {Three-dimensional spectral radiative heat transfer by the discrete-ordinates method},
journal = {J. Thermophys. Heat Transfer},
year = {1991},
volume = {5},
number = {3},
pages = {335--339},
month = {},
note = {}
}

@article {Fiveland1988,
author = {Fiveland, W. A.},
title = {Three-dimensional radiative heat transfer solutions by the discrete-ordinates method},
journal = {J. Thermophys. Heat Transfer},
year = {1988},
volume = {2},
number = {4},
pages = {309},
month = {},
note = {}
}

@article {Flatau1964,
author = {Flatau, A.},
title = {An investigation of the rotational and aerodynamic characteristics of high aspect ratio rotors},
journal = {CRDL TM 1-4},
year = {1964},
volume = {},
number = {},
pages = {},
month = {},
note = {Edgewood Arsenals, Md.}
}

@Patent{Flatau1976,
 author = {Flatau, A},
 title = {Radio Controlled Wing Rotor Bomblet},
 number = {US 3954057},
 type = {Patent},
 location = {US},
 year = {1976},
 month = {US Patent 3954057, 05},
 day = {4},
}

@article {Fletcher1968,
author = {Fletcher, C. A. J.},
title = {Wind tunnel tests on an axisymmetric, lifting bomblet with body mounted, rectangular fins},
journal = {Technical Note HSA 141, AD 855 048},
year = {1968},
volume = {},
number = {},
pages = {},
month = {},
note = {Australian Defence Scientific Service, Weapons Research Establishment}
}

@article {Fletcher2006,
author = {Fletcher, S. J. and Zupanski, M.},
title = {A hybrid multivariate Normal and lognormal distribution for data assimilation},
journal = {Atmospheric Science Letters},
year = {2006},
volume = {7},
pages = {43--46}
}

@article {Fok2008,
author = {Fok, Pak-Wing and Rosales, Rodolfo R.},
title = {Multirate integration of axisymmetric step-flow equations},
journal = {J. Comp. Phys.},
Year = {2008},
Eprint = {arXiv:0810.2517}
}

@techreport {Foshag1969,
author = {Foshag, W. F. and Boehler, G. D.},
title = {Review and preliminary evaluation of lifting horizontal-axis rotating-wing aeronautical systems},
institution = {USAAVLABS},
year = {1969},
type = {Technical Report},
number = {USAAVLABS TR 69-13},
address = {},
month = {March},
note = {}
}

@article {Frank1991,
author = {Frank, J, H. and Lyons, K. M. and Long, M. B.},
title = {Technique for Three-Dimensional
Measurements of the Time Development of Turbulent Flames},
journal = {Optics Letters},
year = {1991},
volume = {16},
number = {12},
pages = {958--960},
month = jun,
note = {}
}

@article{Freret2019,
author = {Freret, L. and Ivan, L. and Sterck, H. and Groth, C. P.},
title = {High-Order Finite-Volume Method with Block-Based AMR for Magnetohydrodynamics Flows},
year = {2019},
issue_date = {April 2019},
publisher = {Plenum Press},
address = {USA},
volume = {79},
number = {1},
issn = {0885-7474},
url = {https://doi.org/10.1007/s10915-018-0844-1},
doi = {10.1007/s10915-018-0844-1},
journal = {J. Sci. Comput.},
month = {apr},
pages = {176–208},
numpages = {33},
keywords = {Ideal magnetohydrodynamics (MHD) flows, High-order finite volume scheme, Anisotropic block-based adaptive mesh refinement}
}

@techreport {FrenklachWang1995,
author = {M. Frenklach and H. Wang and M. Goldenberg and G. P. Smith and D. M. Golden and C. T. Bowman and R. K. Hanson and W. C. Gardiner and V. Lissianski},
title = {{GRI-Mech}---An Optimized Detailed Chemical Reaction Mechanism for Methane Combustion},
institution = {Gas Research Institute},
number = {GRI-95/0058},
year = {1995},
note = {\url{http://www.me.berkeley.edu/gri_mech/}}
}

@article {Fryxell2000,
author = {Fryxell, B. and Olson, K. and Ricker, P. and Timmes, F. X. and Zingale, M. and Lamb, D. Q. and MacNeice, P. and Rosner, R. and Truran, J. W. and Tufo, H.},
title = {{FLASH}: An Adaptive Mesh Hydrodynamics Code for Modeling Astrophysical Thermonuclear Flashes},
journal = {Astrophys. J. Suppl. S.},
year = {2000},
volume = {131},
pages = {273--334}
}

@article {Fu1972,
author = {Fu, T.},
title = {Heat radiation from fires of aviation fuels},
journal = {Fire Technology},
year = {1972},
volume = {},
pages = {54--67}
}

@article{Fugger2018a,
author = {Fugger, C. A. and Yi, T. and Sykes, J. and Caswell, A. W. and Rankin, B. A. and Miller, J. D. and Gord, J. R.},
title = {The Structure and Dynamics of a Bluff-Body Stabilized Premixed Reacting Flow},
journal = {2018 AIAA Aerospace Sciences Meeting},
year = {2018},
volume = {},
pages = {},
number = {2018-1190},
}

@article{Fugger2018b,
author = {Fugger, C. A. and Caswell, A. W. and Rankin, B. A. and Gord, J. R.},
title = {Structure and Dynamics of {CH}$_{2}${O}, {OH}, and  the Velocity Field of a Confined Bluff-body Premixed Flame, using Simultaneous {PLIF} and {PIV} at 10 k{H}z},
journal = {37th Proc. Comb. Inst.},
year = {2018},
volume = {},
pages = {},
number = {},
}

@article {Fugger2019,
author = {Fugger, C. and Paxton, B. and Gord, J. R. and Rankin, B. A. and Caswell, A. W.},
title = {Measurements and Analysis of Flow-Flame Interactions in Bluff-Body-Stabilized Turbulent Premixed Propane-Air Flames},
journal = {AIAA SciTech Forum},
year = {2019},
volume = {},
pages = {10.2514/6.2019-0733}
}

@article {Fukutani1990,
author = {Fukutani, S. and Kunioshi, N. and Jinno, Hiroshi},
title = {Mechanism of combustion reactions in hydrogen-air premixed flames},
journal = {Bull. Chem. Soc. Jpn.},
year = {1990},
volume = {63},
pages = {2191--2198}
}

@article {Fukutani1991,
author = {Fukutani, S. and Kunioshi, N. and Jinno, Hiroshi},
title = {Combustion reactions in methane-air premixed flames},
journal = {Bull. Chem. Soc. Jpn.},
year = {1991},
volume = {64},
pages = {1623--1631}
}

@article{Fureby2017,
author = {Fureby,C.},
title = {A Comparative Study of Large Eddy Simulation ({LES}) Combustion Models applied to the Volvo Validation Rig },
journal = {AIAA SciTech Forum} ,
year = {2017},
volume = {},
number = {},
pages = {10.2514/6.2017-1575},
month = {},
note = {}
}

@article{Furtado2008,
author = {Furtado, H. C. M. and Campos Velho, H. F. and Macau, E. E. N.},
title = {Data assimilation: Particle filter and artificial neural networks},
journal = {Journal of Physics: Conference Series} ,
year = {2008},
volume = {135},
number = {1},
pages = {012073},
month = {},
note = {doi:10.1088/1742-6596/135/1/012073}
}


    ###
   #   #
   #
   #  ##
   #   #
   #   #
    ###

@techreport {Gaitonde1999,
author = {Gaitonde, D.V. and Visbal, M.R.},
title = {Further development of a {N}avier–{S}tokes solution procedure based on higher-order formulas},
institution = {AIAA},
year = {1999},
month = {},
number = {1999-0557},
note = {}
}

@article {Gao2006a,
author = {Gao, X. and Groth, C. P. T.},
title = {A Parallel Adaptive Mesh Refinement Algorithm for Predicting Turbulent Non-Premixed Combusting Flows},
journal = {Int. J. Comut. Fluid Dyn.},
year = {2006},
volume = {20},
number = {5},
pages = {349--357},
month = {},
note = {}
}

@TechReport{Gao2006b,
author = {Gao, X. and Groth, C. P. T.},
title = {Parallel Adaptive Mesh Refinement Scheme for Turbulent Non-Premixed Combusting Flow Prediction},
institution = {44th AIAA Aerospace Sciences Meeting},
year = {2006},
type = {AIAA},
number = {2006-1448}
}

@TechReport{Gao2008a,
author = {Gao, X. and Groth, C. P. T.},
title = {Parallel Adaptive Mesh Refinement Scheme for Three-Dimensional Turbulent Non-Premixed Combustion},
institution = {46th AIAA Aerospace Sciences Meeting},
year = {2008},
type = {AIAA},
number = {2008-1017}
}

@PhdThesis{Gao2008b,
  author =       {Gao, X.},
  title =        {A parallel solution-adaptive method for turbulent non-premixed combusting flows},
  school =       {University of Toronto},
  year =         2008
}

@inproceedings {Gao2009,
author = {Gao, X. and Day, M. S. and Bell, J. B.},
title = {Characterization of Freely Propagating Hydrogen Flames},
booktitle = {Fall Technical Meeting of the Western States Section of the Combustion Institute},
year = {2009},
editor = {},
pages = {},
organization = {},
publisher = {},
address = {},
month = {},
note = {}
}

@article {Gao2010,
author = {Gao, X. and C. P. T. Groth},
title = {A parallel solution-adaptive method for three-dimensional turbulent non-premixed combusting flows},
journal=JCP,
year = {2010},
volume = {229},
number = {},
pages = {3250--3275},
month = {},
note = {}
}

@article {Gao2011,
author = {Gao, X. and Northrup, S. and Groth, C.P.T.},
title = {Parallel Solution-Adaptive Method for Two-Dimensional Non-Premixed Combusting Flows},
journal = {Progress in Computational Fluid Dynamics, An International Journal},
year = {2011},
volume = {11},
number = {2},
pages = {76--95},
month = {},
note = {}
}

@Misc{Gao2014a,
  author =    {Gao, X. and Liu, J.},
  title =     {Data Assimilation for Computational Fluid Dynamics Modeling of Combustion },
  month =     {May},
  year =      {2014},
  note =      {26th International Conference on Parallel Computational Fluid Dynamics}
}

@TechReport{Gao2014b,
  author =       {Gao, X. and Guzik, S. M. J. and Colella, P.},
  title =        {A Fourth-Order Boundary Treatment for Viscous Fluxes on {C}artesian Grid Finite-Volume Methods},
  institution =  {52nd AIAA Aerospace Sciences Meeting},
  year =         {2014},
  type =         {AIAA},
  number =       {2014-1277}
}

@inproceedings {Gao2015a,
author = {Gao, X. and Wang, Y. and Overton, N. and May, I.},
title = {Estimation of Flame Speed Model Parameter Using Ensemble {K}alman Filter Algorithm},
booktitle = {Fall Meeting of the Western States Section of the Combustion Institute},
year = {2015},
editor = {},
pages = {},
organization = {},
publisher = {},
address = {},
month = {October},
note = {WSSCI 2015-134IE-0013}
}

@TechReport{Gao2015b,
  author =       {Gao, X. and Guzik, S. M. J.},
  title =        {A Fourth-Order Scheme for the Compressible {N}avier-{S}tokes Equations},
  institution =  {53rd AIAA Aerospace Sciences Meeting},
  year =         {2015},
  type =         {AIAA},
  number =       {2015-0298}
}

@Article{Gao2016a,
  author =       {Gao, X. and Owen, L. D. and Guzik, S. M. J.},
  title =        {A Parallel Adaptive Numerical Method with Generalized Curvilinear Coordinate Transformation for Compressible {N}avier-{S}tokes Equations},
  journal =      {Int. J. Numer. Meth. Fluids},
  year =         2016,
  volume =       82,
  pages =        {664--688}
}

@TechReport{Gao2016b,
author = {Gao, X. and Owen, L. D. and Guzik, S. M.},
title = {A High-Order Finite-Volume Method for Combustion},
institution = {54th AIAA Aerospace Sciences Meeting},
year = {2016},
type = {AIAA},
number = {2016-1808}
}

@InProceedings{Gao2016c,
  author =       {Gao, X. and Wang, Y. and Overton, N. and May, I. and Tu, X.},
  title =        {Data Assimilated Computational Fluid Dynamics Algorithm for Combustion},
  booktitle =    {54th AIAA Aerospace Sciences Meeting},
  year =         2016,
  number =       {AIAA 2016-1810},
  organization = {AIAA SciTech Forum},
  note =         {\url{https://doi.org/10.2514/6.2016-1810}}
}

@article {Gao2017DAa,
author = {Gao, X. and Wang, Y. and Overton, N. and Zupanski, M. and Tu, X.},
title = {Data-assimilated computational fluid dynamics modeling of convection-diffusion-reaction problems},
journal = {Journal of Computational Science},
year = {2017},
volume = {21},
number = {},
pages = {38--59},
month = {},
note = {}
}

@Article{Gao2019,
  author =       {Gao, W. and Zhang, W. and Cheng, W. and Samtaney, R.},
  title =        {Wall-modelled large-eddy simulation of turbulent flow past airfoils},
  journal =      {J. Fluid Mech.},
  year =         2019,
  volume =       873,
  pages =        {174--410}
}

@inproceedings {Garai2016,
author = {Garai, A. and Diosady, L. T. and Madavan, N. K. and Murman, S. M.},
title = {DNS of low-pressure turbine cascade flows with elevated inflow turbulence using a discontinuous-Galerkin spectral-element method},
booktitle = {Proceedings of ASME Turbo Expo 2016: Turbomachinery Technical Conference and Exposition},
year = {2016},
editor = {},
pages = {},
organization = {},
publisher = {ASME},
address = {},
month = {June},
}

@article {Gibou2005,
author = {Gibou, F. and Fedkiw, R.P.},
title = {A fourth order accurate discretization for the Laplace and heat equations on arbitrary domain with applications to the Stefan problem},
journal = JCP,
year = {2005},
volume = {202},
number = {},
pages = {577--601},
month = {},
note = {}
}

@article{Gicquel2000,
title = "Laminar premixed hydrogen/air counterflow flame simulations using flame prolongation of {ILDM} with differential diffusion",
journal = "Proc Combust Inst",
volume = "28",
number = "2",
pages = "1901-1908",
year = "2000",
note = "",
issn = "1540-7489",
author = "Olivier Gicquel and Nasser Darabiha and Dominique Th\'{e}venin",
}

@article {Groth2014,
author = {Herna\'{n}dez-P\'{e}rez and Groth, C. and G\"{u}lder, \"{O}.},
title = {Large-eddy simulation of lean hydrogenemethane turbulent premixed flames in the methane dominated regime},
journal = {Int. J. Hydrogen Energy},
year = {2014},
volume = {39},
number = {},
pages = {7147--7157},
month = {},
note = {}
}

@article {Gallagher2019,
author = {Gallagher, T. P. and Sankaran, V.},
title = {Affordable Explicitly Filtered Large-Eddy Simulation for Reacting Flows},
journal = {AIAA JOURNAL},
year = {2019},
volume = {57},
number = {2},
pages = {10.2514/1.J057213},
month = {},
note = {}
}

@article {Gardiner1977,
author = {Gardiner, Jr., W. C.},
title = {The pC, pR, pM, and pS method of formulating the results of computer modeling studies of chemical reactions},
journal = {The Journal of Computational Chemistry},
year = {1977},
volume = {81},
number = {},
pages = {2367--2371},
month = {},
note = {}
}

@article {Gaspari1999,
author = {Gaspari, G. and Cohn, S. E.},
title = {Construction of correlation functions in two and three dimensions},
journal = {Q. J. R. Meteorol. Soc.},
year = {1999},
volume = {125},
number = {},
pages = {723--757},
month = {},
note = {}
}


@inproceedings {QAMR:1989,
    AUTHOR = {J.B. Bell and P. Colella and J.A. Trangenstein and M. Welcome},
    TITLE = {Adaptive Mesh Refinement on Moving Quadrilateral Grids},
   booktitle = {Proceedings of the {AIAA} 9th Computational Fluid Dynamics Conference},
   address   = {Buffalo, N.Y.},
   month     = {June},
   year      = 1989,
	pages={471--479},
}

@phdthesis {Garland1999,
author = {Garland, M.},
title = {Quadric-based polygonal surface simplification},
school = {Carnegie Mellon University},
year = {1999},
address = {},
month = {}
}

@article {Gauducheau1998,
author = {Gauducheau, J. L. and Benet, B. and Serby, G.},
title = {A numerical study of lean CH$_4$/H$_2$/air premixed flames
at high pressure},
journal = {Combust. Sci. and Tech.},
year = {1998},
volume = {137},
number = {},
pages = {81--99},
month = {},
note = {}
}

@incollection {Gullbrand2002,
author = {Gullbrand, J. and Chow, F.-K.},
title = {Investigation of numerical errors, subfilter-scale
models, and subgrid-scale models in turbulent
channel flow simulations},
year = {2002},
editor = {},
pages = {},
organization = {},
publisher = {Center for Turbulence Research},
address = {Stanford University},
month = {},
}

@article {Gebman1967,
author = {Gebman, J. R.},
title = {A description of the rotational characteristics of high aspect ratio modified rectangular rotors},
journal = {Proceedings of Conference on Dynamics and Aerodynamics of Bomblets, Technical Report AFATL-TR-67-195},
year = {1967},
volume = {1},
}

@Book{Gelb1974,
  author =    {Gelb, A.},
  ALTeditor =    {},
  title =        {Applied optimal estimation},
  publisher =    {MIT Press, Cambridge, MA},
  year =         {1974},
  OPTkey =       {},
  OPTvolume =    {},
  OPTnumber =    {},
  OPTseries =    {},
  OPTaddress =   {},
  OPTedition =   {},
  OPTmonth =     {},
  OPTnote =      {},
  OPTannote =    {}
}

@phdthesis{Genin2009,
  title={Study of compressible turbulent flows in supersonic environment by large-eddy simulation},
  author={Genin, F. M.},
  year={2009},
  school={Georgia Institute of Technology}
}

@Article{Germano1986a,
  author =       {Germano, M.},
  title =        {Differential filters for the large eddy numerical simulation of turbulent flows},
  journal =      PF,
  year =         {1986},
  volume =    {29},
  number =    {6},
  pages =     {1755--1756},
  month =     {June}
}

@Article{Germano1986b,
  author =       {Germano, M.},
  title =        {Differential filters of elliptic type},
  journal =      PF,
  year =         {1986},
  volume =    {29},
  number =    {6},
  pages =     {1757},
  month =     {June}
}

@Article{Germano1991,
  author =       {Germano, M. and Piomelli, U. and Moin, P. and Cabot, W.},
  title =        {A dynamic subgrid-scale eddy viscosity model},
  journal =      {Phys. Fluids A},
  year =         {1991},
  OPTkey =       {},
  volume =    {3},
  number =    {7},
  pages =     {1760--1765},
  OPTmonth =     {},
  OPTnote =      {},
  OPTannote =    {}
}

@article {Gerlinger2003,
author = {Gerlinger, W. and Schneider, K. and F\"ohlich, J. and Bockhorn, H.},
title = {Numerical simulations on the stability of spherical flame structures},
journal = {Combust. Flame},
year = {2003},
volume = {132},
number = {},
pages = {247--271},
month = {},
note = {}
}

@article{Ghanem2010,
author  = {Ghanem, A. and Muller, A. and Nahle, C. P. and Kocurek, J. and Werner N. and Hammerstingle, C. and Schild, H. H., and Schwab, J. O. and Mellert, F. and Fimmers, R. and Nickenig, G. and Thomas, D.},
title   = {Risk and fate of cerebral embolism after transfemoral aortic valve implantation: a prospective pilot study with diffusion-weighted magnetic resonance imaging},
journal = {Journal of American College of Cardiology},
volume  = {55},
number  = {},
year    = {2010},
month   = {},
pages   = {1427--1432}
}

@article{Ghia1982,
author = {Ghia, U. and Ghia, K. N. and Shin, C. T.},
title = {High-{Re} solutions for incompressible flow using the {N}avier-{S}tokes equations and a multigrid method},
journal = JCP,
volume = {48},
number = {3},
pages = {387--411},
year = {1982},
issn = {0021-9991},
OPTdoi = {https://doi.org/10.1016/0021-9991(82)90058-4},
OPTurl = {http://www.sciencedirect.com/science/article/pii/0021999182900584},
}

@Article{Ghosal1995,
  author =       {Ghosal, S. and Lund, T. and Moin, P. and Akselvoll, K.},
  title =        {A dynamic localization model for large-eddy simulation of turbulent flows},
  journal =      {J. Fluid Mech.},
  year =         {1995},
  volume =    {286},
  number =    {},
  pages =     {229--255},
  month =     {March}
}

@article {Giles2006,
author = {Giles, D. E. and Som, S. and Aggarwal, S. K.},
title = {{$\rm NO_x$} emmission characteristics of counterflow syngas diffusion flames with airstream dilution},
journal = {Fuel},
year = {2006},
volume = {85},
number = {12--13},
pages = {1729--1742},
month = sep,
note = {}
}

@Book{Gill1981,
  author =    {Gill, O. E. and Murray, W. and Wright, M. H.},
  ALTeditor =    {},
  title =        {Practical Optimization},
  publisher =    {Academic Press},
  year =         {1981},
  OPTkey =       {},
  OPTvolume =    {},
  OPTnumber =    {},
  OPTseries =    {},
  OPTaddress =   {},
  OPTedition =   {},
  OPTmonth =     {},
  OPTnote =      {},
  OPTannote =    {}
}

@article {Gillespie1976,
author = {D. T. Gillespie},
title = {Stochastic simulation of chemical processes},
journal = {J. Comput. Phys.},
volume = {22},
year = {1976},
pages = {403}
}

@article {Gillespie1977,
author = {D. T. Gillespie},
title = {Exact stochastic simulation of coupled chemical reactions},
journal = {J. Phys. Chem.},
volume = {81},
year = {1977},
pages = {2340--2361}
}

@article {Gilmanov2005,
author = {Gilmanov, A. and Sotiropoulos, F.},
title = {A hybrid {C}artesian/immersed boundary method for simulating flows with 3D, geometrically complex, moving bodies},
journal = {J. Comput. Phys.},
volume = {207},
year = {2005},
pages = {457--492}
}

@article {Giovangigli1987,
author = {Giovangigli, V. and Smooke, M. D.},
title = {Extinction Limits of Strained Premixed Laminar Flames with Complex Chemistry},
journal = {Combust. Sci. Technol.},
year = {1987},
volume = {53},
number = {},
pages = {23--49},
month = {},
note = {}
}

@article {Giovangigli1992,
author = {Giovangigli, V. and Smooke, M. D.},
title = {Application of Continuation Techniques to Plane Premixed Laminar Flames},
journal = {Combust. Sci. Technol.},
year = {1992},
volume = {87},
number = {},
pages = {241--256},
month = {},
note = {}
}

@book {Giovangigli1999,
author = {Giovangigli, V.},
title = {Multicomponent Flow Modeling},
year = {1999},
publisher = {Birkh\"auser},
edition = {},
address = {Boston}
}

@incollection {Givi1994,
author = {P. Givi},
title = {Spectral and random vortex methods in turbulent reacting flow},
booktitle = {Turbulent Reacting Flows},
editor = {P. A. Libby and F. A. Williams},
publisher = {Academic Press},
pages = {475--572},
year = {1994}
}

@misc {Glarborg2004,
author = {Glarborg, P.},
title = {},
howpublished = {Private communication},
month = {},
year = {2004},
note = {}
}

@article{Glarborg2007,
AUTHOR = "P. Glarborg",
!TITLE = "{}",
JOURNAL = "Proc. Combust. Inst." ,
VOLUME ="31",
PAGES = "77-98",
YEAR = "2007" }

@article {GlarborgMiller1986,
author = {Glarborg, P. and Miller, J. A. and Kee, R. J.},
title = {Kinetic Modeling and Sensitivity Analysis of Nitrogen Oxide Formation in Well-Stirred Reactors},
journal = {Combust. Flame}, 
year = {1986},
volume = {65},
number = {},
pages = {177--202},
month = {},
note = {}
}

@techreport {GlarborgKee1986,
author = {Glarborg, P. and Kee, R. J. and Grcar, J. F. and Miller, J. A},
title = {{PSR}: A Fortran Program for Modeling Well-Stirred Reactors},
institution = {Sandia National Laboratories},
year = {1986},
type = {Technical Report},
number = {SAND86-8209},
address = {},
month = {},
note = {}
}

@article {GlarborgAlzueta1998, 
author = {Glarborg, P. and Alzueta, M. U. and Dam-Johansen, K. and Miller, J. A.}, 
title = {Kinetic Modelling of Hydrocarbon/Nitric Oxide Interactions in a Flow Reactor},
journal = {Combust. Flame}, 
year = {1998}, 
volume = {115}, 
number = {},
pages = {1--27}, 
month = {}, 
note = {} 
}

@article {GlarborgKristensen2000,
author = {Glarborg, P. and Kristensen, P. G. and Dam-Johansen, K. and Alzueta, M. U. and Millera, A. and Bilbao, R.},
title = {Nitric Oxide Reduction by Non-hydrocarbon Fuels. {I}mplications for Reburning with Gasification Gases},
journal = {Energy Fuels},
year = {2000},
volume = {14},
number = {},
pages = {828--838},
month = {},
note = {}
}

@article {GlarborgJensen2003,
author = {Glarborg, P. and Jensen, A. and Johnsson, J. E.},
title = {Fuel Nitrogen Conversion in Solid Fuel Fired Systems},
journal = {Prog. Energy Combust. Sci.},
volume = {29},
pages = {89--113},
year = {2003}
}

@book {Glassman1996,
author = {Glassman, I.},
title = {Combustion},
year = {1996},
publisher = {Academic Press},
edition = {third},
address = {}
}

@article {Godunov1959,
author = {Godunov, SK},
title = {A finite-difference method for the numerical computation of discontinuous solutions of the equations of fluid dynamics},
journal = {Mat. Sb.},
year = {1959},
volume = {47},
number = {},
pages = {271},
month = {},
note = {}
}

@article {Goey1997,
author = {de Goey, L. P. H. and ten Thije Boonkkamp, J. H. M.},
title = {A Mass-Based Definition of Flame Stretch for Flames with Fine Thickness},
journal = {Combustion Science and Technology},
year = {1997},
volume = {122},
number = {},
pages = {399--405},
month = {},
note = {}
}

@article {GoeyMallens1997,
author = {de Goey, L. P. H. and Mallens, R. M. M. and ten Thije Boonkkamp, J. H. M.},
title = {An Evaluation of Different Contributions to Flame Stretch for Stationary Premixed Flames},
journal = {Combust. Flame},
year = {1997},
volume = {110},
number = {},
pages = {54--66},
month = {},
note = {}
}

@article {Goey1999,
author = {de Goey, L. P. H. and ten Thije Boonkkamp, J. H. M.},
title = {A Flamelet Description of Premixed Laminar Flames and the Relation with Flame Stretch},
journal = {Combust. Flame},
year = {1999},
volume = {119},
number = {},
pages = {253--271},
month = {},
note = {}
}

@book {Goldberg1989,
author = {Goldberg, D. E.},
title = {Genetic Algorithms in Search Optimization and Machine Learning},
year = {1989},
publisher = {Addison-Wesley},
edition = {},
address = {}
}


@TECHREPORT{GordonMcbride:1994,
    AUTHOR = {S. Gordon and B. J. McBride},
    TITLE = {Computer program for calculation of complex chemical equilibrium 
             compositions, rocket performance, incident and reflective shocks, and Chapman-Jouget detonations},
    INSTITUTION = {NASA},
    TYPE={Reference Publication},
    NUMBER={1311},
    YEAR = {1994}    }

@article {GordonSmith1958,
author = {Gordon, A. S. and Smith, S. R. and McNesby, J. R.},
title = {},
journal = {Combust. Sci. Technol.},
year = {1958},
volume = {7},
pages = {317},
}

@article {Gordon1994,
author = {Gordon, A. S. and Li, S. C. and Libby, P. A. and Williams, F. A.},
title = {Influence of Initial Velocity Distributions on the Height of Methane-Air Nonpremixed Flames},
journal = {Combust. Sci. Technol.},
year = {1994},
volume = {100},
number = {},
pages = {395--399},
month = {},
note = {}
}

@TECHREPORT{Gordon1994b,
    AUTHOR = {Gordon, S. and McBride, B. J.},
    TITLE = {Computer Program for Calculation of Complex Chemical Equilibrium Compositions and Applications {I}. Analysis},
    INSTITUTION = {NASA},
    TYPE={Reference Publication},
    NUMBER={1311},
    YEAR = {1994}
    }

@article {Gordon1999,
author = {Gordon, A. S. and Li, S. C. and Williams, F. A.},
title = {Visible Flame Heights of Laminar Coflow Diffusion Flames},
journal = {Combust. Sci. Technol.},
year = {1999},
volume = {141},
number = {},
pages = {1--18},
month = {},
note = {}
}

@book {Gottlieb1977,
place={Philadelphia},
publisher={SIAM},
author = {Gottlieb, D and Orszag, SA},
title = {Numerical analysis of spectral method: theory},
year = {1977},
note = {}
}

@article {Gran1998,
author = {Gran, I. R. and Echekki, T. and Chen, J. H.},
title = {Negative flame speed in an unsteady 2-d premixed flame: a computational study},
journal = {Proc. Combust. Inst.},
year = {1998},
volume = {27},
number = {},
pages = {323--329},
month = {},
note = {}
}


@article {Graves2013,
author = {Graves, D. T. and Colella, P. and Modiano, D. and Johnson, J. and Sjogreen, B. and and Gao, X.},
title = {A {C}artesian Grid Embedded Boundary Method for the Compressible {N}avier {S}tokes Equations},
journal = {Comm. App. Math. Comp. Sci.},
year = {2013},
volume = {8},
number = {1},
pages = {99--122},
month = {},
note = {}
}


@InProceedings{GaoZhang2016
,
  author =       {Gao, W. and Zhang, W. and Samtaney,R.},
  title =        {Wall modeling in complex geometry and application to large-eddy simulation of turbulent flow over an airfoil},
  OPTcrossref =  {},
  OPTkey =       {},
  booktitle = {20th Australasian Fluid Mechanics Conference
},
  year =      {2016},
  OPTeditor =    {},
  OPTvolume =    {},
  OPTnumber =    {},
  OPTseries =    {},
  OPTpages =     {},
  month =     {December},
  address =   {Perth, Australia},
  OPTorganization = {},
  OPTpublisher = {},
  OPTnote =      {},
  OPTannote =    {}
}

@article {Grcar2004,
author = {Grcar, J. F. and Glarborg, P. and Bell, J. B. and Day, M. S. and Loren, A. and Jensen, A. D.},
title = {Effects of Mixing on Ammonia Oxidation in Combustion Environments at Intermediate Temperatures},
journal = {Proc. Combust. Inst.},
year = {2004},
volume = {30},
number = {},
pages = {1193--1200},
month = {}
}

@article {Grcar2006,
author = {Grcar, J. F. and Day, M. S. and Bell, J. B.},
title = {A Taxonomy of Integral Reaction Path Analysis},
journal = {Combust. Theory Model.},
year = {2006},
volume = {10},
number = {4},
pages = {559--580},
month = aug,
note = {}
}
 

@inproceedings {Grcar2007a,
	author = {Grcar, J. F. and Day, M. S. and Bell, J. B.},
	title = {Diagnostics for the Combustion Science Workbench},
	booktitle = {Proceedings of the 5$^{\rm th}$ US Combustion Meeting
(CD-ROM)},
	year = {2007},
	editor = {},
	pages = {},
	organization = {},
	publisher = {Western States Section of the Combustion Institute},
	address = {},
	month = mar,
	note = {Paper D09}
	}

@techreport {Grcar2007b,
author = {Grcar, J. F.},
title = {An Explicit {R}unge-{K}utta Iteration for Diffusion in the Low
Mach Number Combustion Code},
institution = {Lawrence Berkeley National Laboratory},
year = {2007},
type = {Technical Report},
number = {LBNL-63375},
address = {Berkeley},
month = {},
note = {}
}

@article {Grcar2008a,
author = {Grcar, J. F. and Bell, J. B. and Day, M. S.},
title = {The {S}oret Effect in Naturally Propagating, Premixed, Lean, Hydrogen-Air Flames},
journal = {Proc. Combust. Inst.},
year = {2008},
volume = {32},
number = {},
pages = {},
month = {},
note = {Accepted for oral presentation.  Also appears as technical report LBNL-XXXXX.}
}

@article {Greenberg1980,
author = {J. B. Greenberg},
title = {On the Prediction of Thermal Diffusion Effects in Laminar One-Dimensional Flames},
journal = {Combust. Sci. Technol.},
year = {1980},
volume = {24},
number = {1},
pages = {83--88},
month = {},
note = {}
}

@article {Greene1988,
author = {Greene, J.M. and Kim, J.},
title = {The steady states of {K}uramoto-{S}ivashinsky equation},
journal = {Phys. D},
year = {1988},
volume = {33},
number = {},
pages = {99--120},
month = {},
note = {}
}

@article {Gronskis2013,
author = {Gronskis, A. and Heitz, D. and M{\'emin}, E.},
title = {Inflow and initial conditions for direct numerical simulation based on adjoint data assimilation},
journal = JCP,
year = {2013},
volume = {242},
number = {},
pages = {480--497},
month = {},
note = {}
}

@article {GrootOijen2002,
author = {Groot, G. R. A. and Oijen, J. A. van and de Goey, L. P. H. and Seshadri, K. and Peters, N.},
title = {The effects of strain and curvature on the mass burning rate of premixed laminar flames},
journal = {Combust. Theory Model.},
year = {2002},
volume = {6},
number = {},
pages = {675--695},
month = {},
note = {}
}

@article {Gross1954,
author = {Gross, Donald S.},
title = {Wind Tunnel Tests of Rotating Bodies, 5th Series},
journal = {University of Maryland Wind Tunnel Report No. 116},
year = {1954},
month = {May},
}

@article {Gulder2002,
author = {G\"{u}lder, \"{O}. L. and Smallwood, G.J. and Wong, R. and Snelling, D. R. and Smith, R. and Deschamps, B. M. and Sautet, J.-C.},
title = {Flame Front Surface Characteristics in Turbulent Premixed 
Propane/Air Combustion},
journal = {Combust. Flame},
year = {2002},
volume = {120},
number = {},
pages = {407--416},
month = {},
note = {}
}
@article {Gulder2007,
author = {G\"{u}lder, \"{O}. L. and Smallwood, G.J.},
title = {Flame Surface Densities in Premixed Combustion at 
Medium to High Turbulence Intensities},
journal = {Combust. Flame},
year = {2007},
volume = {179},
number = {},
pages = {191--206},
month = {},
note = {}
}
@article {Gulder2007b,
author = {G\"{u}lder, \"{O}. L.},
title = {Contribution of Small Scale Turbulence to Burning Velocity of Flamelets 
in the Thin Reaction Zone Regime},
journal = {Proc. Combust. Inst.},
year = {2007},
volume = {31},
number = {},
pages = {1369--1375},
month = {},
note = {}
}

@article {Gu2000,
author = {Gu, X. J. and Haq, M. Z. and Lawes, M. and Woolley, R.},
title = {Laminar Burning Velocity and {M}arkstein Lengths of Methane-Air Mixtures},
journal = {Combust. Flame},
year = {2000},
volume = {121},
number = {},
pages = {41--58},
month = {},
note = {}
}

@book{Gurvich1989,
place={New York},
edition={4},
title={Thermodynamic properties of individual substances},
volume={1 and 2},
publisher={Hemisphere.},
author={Gurvich, L. V. and Veyts, I. V. and Alcock, C. B.},
year={1989}
}

@MastersThesis{Guzik2003,
  author =       {Guzik, S. M.},
  title =        {Venting Optimization of a Pulse Detonation Engine},
  school =       {Laval University},
  year =         2003
}

@InProceedings{Guzik2008a,
  author =       {Guzik, S. M. and Groth, C. P. T.},
  title =        {A High-Order Residual-Distribution Scheme with Variation-Bounded Nonlinear Stabilization},
  booktitle =    {46th AIAA Aerospace Sciences Meeting},
  year =         2008,
  number =       {AIAA 2008-777},
  organization = {AIAA},
  note =         {\url{https://doi.org/10.2514/6.2008-777}}
}

@article{Guzik2008b,
author = {Guzik, S. M. and Groth, C. P. T.},
title = {Comparison of Solution Accuracy of Multidimensional Residual Distribution and Godunov-Type Finite-Volume Methods},
journal = {Int. J. Comut. Fluid Dyn.},
year = {2008},
volume = {22},
number = {1-2},
pages = {61--83},
}

@PhdThesis{Guzik2010,
  author =       {Guzik, S. M. J.},
  title =        {Accurate residual-distribution schemes for accelerated parallel architectures},
  school =       {University of Toronto},
  year =         2010
}

@InProceedings{Guzik2012,
  author =       {Guzik, S. M. and McCorquodale, P. and Colella, P.},
  title =        {A Freestream-Preserving High-Order Finite-Volume Method for Mapped Grids with Adaptive-Mesh Refinement},
  booktitle =    {50th AIAA Aerospace Sciences Meeting},
  year =         2012,
  number =       {AIAA 2012-0574},
  organization = {AIAA},
  note =         {\url{https://doi.org/10.2514/6.2012-574}}
}

@InProceedings {Guzik2009,
  author =       {Guzik, S. M. and Groth, C. P. T.},
  title =        {Heterogeneous Parallelism of High-Order Residual Distribution Schemes Using Central and Graphics Processing Units},
  booktitle =    {Proceedings of the 21st International Conference on Parallel Computational Fluid Dynamics},
  year =         {2009},
  pages =        {267--271}
}

@InProceedings{Guzik2013,
  author =       {Guzik, S. M. J. and Gao, X. and Weisgraber, T. and Alder, B. and Colella, P.},
  title =        {An Adaptive Mesh Refinement Strategy with Conservative Space-Time Coupling for the Lattice-Boltzmann Method},
  booktitle =    {51st AIAA Aerospace Sciences Meeting},
  year =         2013,
  number =       {AIAA 2013-0866},
  organization = {AIAA},
  note =         {\url{https://doi.org/10.2514/6.2013-866}}
}

@article {Guzik2014,
author = {Guzik, S. M. and Weisgraber, T. H. and Colella, P. and Alder, B. J.},
title = {Interpolation Methods and the Accuracy of Lattice-Boltzmann Mesh Refinement},
journal = {J. Comput. Phys.},
year = {2014},
volume = {259},
number = {},
pages = {461--487},
month = {},
note = {}
}

@article {Guzik2015,
author = {Guzik, S. M. and Gao, X. and Owen, L. D. and McCorquodale, P. and Colella, P.},
title = {A Freestream-Preserving Fourth-Order Finite-Volume Method in Mapped Coordinates with Adaptive-Mesh Refinement},
journal = {Comput. Fluids},
year = {2015},
volume = {123},
number = {},
pages = {202--217},
month = {},
note = {}
}

@article{Guzik2016,
  author =       {Guzik, S. M. and Gao, X. and Olschanowsky, C.},
  title =        {A high-performance finite-volume algorithm for solving partial differential equations governing compressible viscous flows on structured grids},
  journal =      {Comput. Math Appl.},
  year =         {2016},
  volume =       {72},
  pages =        {2098--2118} 
}

@InProceedings{Guzik2018,
  author =       {Guzik, S. M. and Riley, J.},
  title =        {Adaptive Mesh Refinement on Parallel Heterogeneous ({CPU}/{GPU}) Architectures},
  booktitle =    {2018 AIAA Aerospace Sciences Meeting},
  year =         2018,
  number =       {AIAA 2018-1831},
  OPTorganization = {AIAA},
  note =         {\url{https://doi.org/10.2514/6.2018-1831}}
}

@article {Gyulassy2006,
author = {Gyulassy, A. and Natarajan, V. and Pascucci, V. and Bremer, P.-T. and Hamann, B.},
title = {A topological approach to simplification of three-dimensional scalar functions},
journal = {IEEE Trans.\ Vis.\ Comp.\ Graph.},
year = {2006},
volume = {12},
number = {4},
pages = {474--484},
month = {},
note = {}
}

@article {Gyulassy2007, 
author = {Gyulassy, A. and Natarajan, V. and Hamann, B. and Duchaineau, M. and Pascucci, V. and Bringa E. and Higginbotham, A.},
title = {Topologically clean distance fields}, 
journal = {IEEE Trans.\ Vis.\ Comp. Graph.},
year = {2007}, 
volume = {13}, 
number = {6}, 
pages = {1432--1439}
}


   #   #
   #   #
   #   #
   #####
   #   #
   #   #
   #   #

@article {Haller2005,
author = {Haller, G.},
title = {An objective definition of a vortex},
journal = {J. Fluid Mech.},
year = {2005},
volume = {525},
number = {},
pages = {1--26},
month = {},
note = {}
}
 
@article {Hamalainen1995,
author = {H\"{a}m\"{a}l\"{a}inen, J. P. and Aho, M. J.},
title = {Effect of fuel composition on the conversion of volatile solid fuel-{N} to {N}$_2${O} and {NO}},
journal = {Fuel},
year = {1995},
volume = {74},
number = {12},
pages = {1922--1924},
month = {},
note = {}
}

@article {Hamill2001,
author = {Hamill, T. and Whitaker, J. S. and Snyder, C.},
title = {Distance-dependent filtering of background error covariance estimates in an ensemble Kalman filter},
journal = {Mon Wea. Rev.},
year = {2001},
volume = {129},
number = {},
pages = {2776--2790},
month = {},
note = {}
}

@article {Han1999,
author = {Han, D. and Mungal, M. G. and Zamansky, V. M. and Tyson, T. J.},
title = {Prediction of {NO}$_x$ Control by Basic and Advanced Gas Reburning Using the Two-Stage {L}agrangian Model},
journal = {Combust. Flame},
year = {1999},
volume = {119},
number = {},
pages = {483--493},
month = {},
note = {}
}

@article{Hanson1990,
author = {Hanson, R. K. and Seitzman, J. M. and Paul, P. H.},
title ={Planar Laser-Fluorescence Imaging of Combustion Gases},
journal = {Appl. Phys. B},
volume = 50,
year = 1990,
pages = {441--454}
}

@article {Han2003,
author = {Han, X. and Wei, X. and Schnell, U. and Hein, K.},
title = {Detailed modeling of hybrid reburn/{SNCR} processes for {NO}$_x$ reduction in coal-fired furnaces},
journal = {Combust. Flame},
year = {2003},
volume = {132},
number = {},
pages = {374--386},
month = {},
note = {}
}

@article {Hansell2013,
author = {Hansell, A. L. and Blangiardo, M. and Fortunato, L. and Floud, S. and Hoogh, K. and Fecht, D. and Ghosh, R. E. and Laszlo, H. E. and Pearson, C. and Beale, L. and Beevers, S. and Gulliver, J. and Best, N. and Richardson, S. and Elliott, P.},
title = {Aircraft noise and cardiovascular disease near Heathrow airport in London: small area study},
journal = {Br. Med. J.},
year = {2013},
volume = {347},
number = {7928},
pages = {},
month = {October},
note = {}
}

@article {Harris2006,
author = {Harris, P. G. and Stowe, R. A. and Ripley, R. C. and Guzik, S. M.},
title = {Pulse Detonation Engine as a Ramjet Replacement},
journal = {J. Propul. Power},
year = {2006},
volume = {22},
number = {2},
pages = {462--437},
month = {},
note = {}
}

@article {Harten1987,
author = {Harten, A. and Engquist, B. and Osher, S. and Chakravarthy, S.},
title = {Uniformly high order essentially non-oscillatory schemes III},
journal = {J. Comput. Phys.},
year = {1987},
volume = {71},
number = {},
pages = {231--303},
month = {},
note = {}
}

@article {Hartmann2008,
author = {Hartmann, D. and Meinke, M. and Schröder, W.},
title = {An adaptive multilevel multigrid formulation for {C}artesian hierarchical grid methods},
journal = {Comput. Fluids},
year = {2008},
volume = {37},
number = {},
pages = {1103--1125},
month = {},
note = {}
}

@article {Hasegawa1998,
author = {Hasegawa, T. and Sato, M.},
title = {Study of Ammonia Removal from Coal-Gasified Fuel},
journal = {Combust. Flame},
year = {1998},
volume = {114},
number = {},
pages = {246--258},
month = {},
note = {}
}

@techreport {Hasselbrink1996,
author = {Hasselbrink, E. F. and Mungal, M. G.},
title = {An analysis of the time-averaged properties of the far field of the transverse jet},
institution = {AIAA},
year = {1996},
type = {Paper},
number = {AIAA 96-0201},
address = {},
month = {},
note = {}
}

@article{Hatoum2017,
author = {Hatoum, H. and Moore, B. L. and Maureira, P. and Dollery, J. and Crestanello, J. A.  and Dasi, L. P.},
title = {Aortic sinus flow stasis and likely in valve-in-valve transcatheter aortic valve implantation},
journal = {Journal of thoracic and cardiovascular surgery},
volume = {154},
number = {},
pages = {32--43},
year = {2017},
}

@article{Hatoum2018a,
author  = {Hatoum, H. and Moore, B. L. and Dasi, L. P.},
title   = {On the Significance of Systolic Flow Waveform on Aortic Valve Energy Loss},
journal = {Annals of Biomedical Engineering},
volume  = {46},
number  = {},
year    = {2018},
month   = {},
pages   = {2102--2111}
}

@article{Hatoum2018b,
author = {Hatoum, H. and Dollery, J. and Lilly, S. M. and Crestanello, J. and Dasi, L. P.},
title = {Impact of patient-specific morphologies on sinus flow stasis in transcatheter aortic valce replacement: An in vitro study},
journal = {Journal of thoracic and cardiovascular surgery},
volume = {},
number = {},
pages = {},
year = {2018},
}

@article{Hatoum2018c,
author = {Hatoum, H. and Dollery, J. and Lilly, S. M. and Crestanello, J. and Dasi, L. P.},
title = {Implantation Depth and Rotational Orientation Effect on Valve-in-Valve Hemodynamics and Sinus Flow},
journal = {The Annals of Thoracic Surgery},
volume = {},
number = {},
pages = {},
year = {2018},
}

@article{Hatoum2019a,
author  = {Hatoum, H. and Dasi, L. P.},
title   = {Spatiotemporal Complexity of the Aortic Sinux Vortex as a Function of Leaflet Calcification},
journal = {Annals of Biomedical Engineering},
volume  = {47},
number  = {4},
year    = {2019},
month   = {},
pages   = {1116--1128}
}

@article{Hatoum2019b,
author  = {Hatoum, H. and Mo, X.-M.},
title   = {Modeling of the Instantaneous Transvalvular Pressure Gradient in Aortic Stenosis},
journal = {Annals of Biomedical Engineering},
volume  = {47},
number  = {8},
year    = {2019},
month   = {},
pages   = {1748--1763}
}

@article{Hatoum2019c,
author = {Hatoum, H. and Maureira, P. and Lilly, S. M. and Crestanello, J. A.  and Dasi, L. P.},
title = {Leaflet Laceration to Improve Neosinus and Sinus Flow After Valve-in-Vale},
journal = {Circulation: Cardiovascular Interventions},
volume = {12},
number = {},
pages = {},
year = {2019},
}

@article{Hatoum2019d,
author = {Hatoum, H. and Maureira, P. and Lilly, S. M. and Crestanello, J. A.  and Dasi, L. P.},
title = {Impact of Leaflet Laceration on Transcatheter Aortic Valve-in-Valve Washout},
journal = {JACC: Cardiovascular Interventions},
volume = {},
number = {},
pages = {},
year = {2019},
}

@article {Hauer1955,
author = {Hauer, Herbert J. and Kelly, Howard R.},
title = {The subsonic aerodynamic characteristics of spinning cone-cylinders and ogive-cylinders at large angles of attack},
journal = {NAVORD Report 3529},
year = {1955},
month = {July},
}

@article {Hawkes2004,
author = {Hawkes, E.R. and Chen, J. H.},
title = {Direct numerical simulation of hydrogen-enriched lean premixed methane-air flames},
journal = {Combust. Flame},
volume = {138},
pages = {242--258},
year = {2004}
}

@article {Hawkes2005, 
author = {Hawkes, E.R. and Chen, J. H.}, 
title = {Evaluation of models for flame stretch due to curvature in the thin reaction zones regime},
journal = {Proc. Combust. Inst.}, 
year = {2005}, 
volume = {30},
number = {}, 
pages = {647--655}, 
month = {}, 
note = {} 
}


@Misc{Hawkes2007,
  OPTkey =       {},
  author =    {Hawkes, E.R. and Chen, J. H. and Gruber, A. and Lu, Tianfeng},
  title =     {DNS of premixed flames},
  howpublished = {Presentation in Sandia National Laboratories},
  OPTmonth =     {},
  year =      {2007},
  note =      {http://energy.lbl.gov/aet/combustion/workshop/Mainz/Hawkes.pdf},
  OPTannote =    {}
}

@article {Haworth1992,
author = {Haworth, D. C. and Poinsot, T. J.},
title = {Numerical simulations of {L}ewis number effects in turbulent premixed flames},
journal = {J. Fluid Mech.},
volume = {244},
pages = {405--436},
year = {1992}
}

@article {Haworth2000,
author = {Haworth, D. C. and Blint, R. J. and Cuenot, B. and Poinsot, T. J.},
title = {Numerical simulation of turbulent propane-air combustion with nonhomogeneous reactants},
journal = {Combust. Flame},
volume ={121},
pages = {395--417},
year = {2000}
}

@article {HaworthBlint2000,
author = {D. C. Haworth and R. J. Blint and B. Cuenot and T. J. Poinsot},
title = {Numerical simulation of turbulent propane-air combustion with nonhomogeneous reactants},
journal = {Combust. Flame},
volume = {121},
pages = {395--417},
year = {2000}
}

@article {Hawthorne1949,
author = {Hawthorne, W. R. and Weddell, D. S. and Hottel, H. C.},
title = {},
journal = {Proc. Combust. Inst.},
year = {1949},
volume = {3},
number = {},
pages = {266},
month = {},
note = {Proceedngs of the Symposium on Combustion and Flame, and Explosion Phenomena, September 7--11, 1948.}
}

@article {Hayase2015,
author = {Hayase, T.},
title = {Numerical simulation of real-world flows},
journal = {Fluid Dynamics Research},
year = {2015},
volume = {47},
number = {5},
pages = {051201},
month = {},
note = {doi:10.1088/0169-5983/47/5/051201}
}

@article {Hedenquist1994,
author = {Hedenquist, J. W. and Lowenstern, J. B.},
title = {The role of magmas in the formation of hydrothermal ore depositis},
journal = {Nature},
year = {1994},
volume = {370},
number = {},
pages = {519--527},
month = {18 August},
note = {}
}

@article {Heinz1983,
author = {Heinz, D. L. and Jeanloz, R.},
title = {{Inhomogeneity parameter of a homogeneous Earth}},
journal = {Nature},
year = {1983},
volume = {301},
number = {},
pages = {138--139},
month = {13 January},
note = {}
}

@article {Hendricks2011,
author = {Hendricks, R.C. and Bushnell and D.M. and Shouse, D.T.},
title = {{ Aviation Fueling: A Cleaner, Greener Approach}},
journal = { International Journal of Rotating Machinery},
year = {2011},
volume = {},
number = {},
pages = {},
month = {13 January},
note = {Article ID 782969, 13 pages, 2011. doi:10.1155/2011/782969}
}

@inproceedings {Henshaw1996,
author = {Henshaw, W. D.},
title = {Overture: An object-oriented system for solving {PDE}s in moving geometries on overlapping grids.},
booktitle = {First AFOSR Conference on Dynamic Motion CFD},
year = {1996},
volume = {10},
pages = {281-290},
editor = {Sakell, L. and Knight, D. D.},
organization = {},
publisher = {},
address = {},
note = {}
}

@Book{Henshaw1996b,
author = {Henshaw, W. D.},
title = {Automatic grid generation},
publisher = {Acta Numerica},
note = {5:121-148},
year = {1996}
}

@Article{Henshaw2003,
  author =       {Henshaw, W. D. and Schwendeman, D. W.},
  title =        {An adaptive numerical scheme for high-speed reactive flow on overlapping grids},
  journal =      {J. Comput. Phys.},
  year =         {2003},
  volume =    {191},
  pages =     {420-447}
}

@Article{Henshaw2006,
  author =       {Henshaw, W. D. and Schwendeman, D. W.},
  title =        {Moving overlapping grids with adaptive mesh refinement for high-speed reactive and non-reactive flow},
  journal =      {J. Comput. Phys.},
  year =         {2006},
  volume =    {216},
  pages =     {744-779}
}

@article {Hewson2002,
author = {Hewson, J. C. and Kerstein, A. R.},
title = {Local extinction and reignition in nonpremixed turbulent {$\rm CO$ / $\rm H_2$ / $\rm N_2$} jet flames},
journal = {Combust. Sci. and Tech.},
year = {2002},
volume = {174},
number = {},
pages = {35--66},
month = {},
note = {}
}

@article {Hilbert2004,
author = {Hilbert, R. and Tap, F. and El-Rabii, H. and Th\'evenin, D.},
title = {Impact of detailed chemistry and transport models on turbulent combustion simulations},
journal = {Prog. Energy Combust. Sci.},
year = {2004},
volume = {},
number = {},
pages = {61--117},
month = {},
note = {}
}

@article {Hildenbrand2000, 
author = {Hildenbrand, F. and Schulz, C. and Wolfrum, J. and Keller, F. and Wagner, E.}, 
title = {Laser diagnostic analysis of {NO} formation in a direct injection diesel engine with pump-line-nozzle and common rail injection systems},
journal = {Proc. Combust. Inst.}, 
year = {2000}, 
volume = {28},
number = {}, 
pages = {1137--1144}, 
month = {}, 
note = {} 
}

@techreport{Hilditch1997,
  title={A projection method for low Mach number fast chemistry reacting flow},
  author={J. Hilditch and P. Colella},
  institution = {AIAA},
  year={1997},
  month={January},
  type={Paper},
  number={AIAA 97-0263}
}

@inproceedings {Hilka1995,
author = {Hilka, M. and Veynante, D. and Baum, M. and Poinsot, T. J.},
title = {Simulations of flame-vortex interactions using detailed
and reduced chemical kinetics},
booktitle = {Symposium on Turbulent Shear Flows},
year = {1995},
volume = {10},
pages = {19.19-24},
editor = {},
organization = {},
publisher = {},
address = {Pennsylvania State University},
note = {}
}

@article {Hill2006,
author = {Hill, D. J. and Pantano, C. and Pullin, D. I.},
title = {Large-eddy simulation and multi-scale modelling of a {R}ichtmyer-{M}eshkov instability with reshock},
journal = JFM,
year = {2006},
volume = {557},
number = {},
pages = {29--61},
month = {},
note = {}
}

@article{hindmarsh2005sundials,
  title={{SUNDIALS}: Suite of nonlinear and differential/algebraic equation solvers},
  author={Hindmarsh, Alan C and Brown, Peter N and Grant, Keith E and Lee, Steven L and Serban, Radu and Shumaker, Dan E and Woodward, Carol S},
  journal={ACM Transactions on Mathematical Software (TOMS)},
  volume={31},
  number={3},
  pages={363--396},
  year={2005},
  publisher={ACM}
}

@Book{Hinze1975,
author = {Hinze, J. O.},
title = {Turbulence},
publisher = {McGraw-Hill},
edition = {2},
year = {1975}
}

@article {Hohlfeld1993, 
author = {Hohlfeld, R. G. and King, J. I. F. and Drueding, T. W. and Sandri, G. v. H.}, 
title = {Solution of Convolution Integral Equations by the Method of Differential Inversion},
journal = {SIAM J. Appl. Math.}, 
year = {1993}, 
volume = {53},
number = {1}, 
pages = {154--167}, 
month = feb, 
note = {} 
}

@article{Holgate2018,
  title={A Review of Embedded Large Eddy Simulation for Internal Flows},
  author={J. Holgate and A. Skillen and T. Craft and A. Revell},
  journal={Arch. Comput. Method. E.},
  year={2018},
  pages={1-18}
}

@article{Hottel1996,
	author = {Hottel, H. C.},
	title = {{Warren Kendall Lewis, August 21, 1882 -- March 9, 1975}},
	journal = {Biographical Memoirs},
	year = {1996},
	volume = {70},
	number = {},
	pages = {},
	month = {},
	note = {Available from the world wide web pages of the National Academy
of Sciences}
}

@article{Houim2011,
title = {A low-dissipation and time-accurate method for compressible multi-component flow with variable specific heat ratios},
author = {Houim, R. W. and Kuo, K. K.},
journal = JCP,
volume = {230},
number = {23},
pages = {8527--8553},
year = {2011},
issn = {0021-9991},
OPTdoi = {htts://doi.org/10.1016/j.jcp.2011.07.031},
OPTurl = {http://www.sciencedirect.com/science/article/pii/S0021999111004621}
}

@InBook{Houser2013,
  ALTauthor =    {Houser, P. R.},
  ALTeditor =    {Tiefenbacher, J.},
  title =        {Approaches to Disaster Management - Examining the Implications of Hazards, Emergencies and Disasters},
  chapter =      {4},
  publisher =    {InTech},
  year =         {2013},
  OPTkey =       {},
  OPTvolume =    {},
  OPTnumber =    {},
  OPTseries =    {},
  OPTtype =      {},
  OPTaddress =   {},
  OPTedition =   {},
  OPTmonth =     {},
  OPTpages =     {},
  note =      {http://www.intechopen.com/books/approaches-to-disaster-management-examining-the-implications-of-hazards-emergencies-and-disasters/improved-disaster-management-using-data-assimilation},
  OPTannote =    {}
}

@article{Houtekamer1998,
author = {Houtekamer, P. L. and Mitchell, H. L.},
title = {Data Assimilation using an ensemble Kalman filter technique},
journal = {Mon. Wea. Rev.},
year = {1998},
volume = {126},
number = {},
pages = {796--811},
month = {},
note = {}
}

@article{Houtekamer2001,
author = {Houtekamer, P. L. and Mitchell, H. L.},
title = {A Sequential Ensemble Kalman Filter for Atmospheric Data Assimilation},
journal = {American Meteorological Society},
year = {2001},
volume = {129},
number = {},
pages = {123--137},
month = {},
note = {}
}

@inproceedings{Hoque2017,
 author = {Hoque, R. and Herault, T. and Bosilca, G. and Dongarra, J.},
 title = {Dynamic Task Discovery in PaRSEC: A Data-flow Task-based Runtime},
 booktitle = {Proceedings of the 8th Workshop on Latest Advances in Scalable Algorithms for Large-Scale Systems},
 series = {ScalA '17},
 year = {2017},
 isbn = {978-1-4503-5125-6},
 location = {Denver, Colorado},
 pages = {6:1--6:8},
 articleno = {6},
 numpages = {8},
 url = {http://doi.acm.org/10.1145/3148226.3148233},
 doi = {10.1145/3148226.3148233},
 acmid = {3148233},
 publisher = {ACM},
 address = {New York, NY, USA}
}

@article{Hu2006,
author = {Hu, X. and Khoo, B. and Adams, N. and Huang, F.},
title = {A conservative interface method for compressible flows},
journal = {J. Comput. Phys.},
year = {2006},
volume = {219},
number = {},
pages = {553--578},
month = {},
note = {}
}

@article{Huang1998,
author = {Huang, Z. and Bechtold, J. K. and Matalon, M.},
title = {Weakly stretched premixed flames in oscillating flows},
journal = {Combust. Theory Model.},
year = {1998},
volume = {2},
number = {},
pages = {115--133},
month = {},
note = {}
}

@techreport{Hughes2003,
author = {Hughes, J. F.},
title = {Differential Geometry of Implicit Surfaces in 3-Space - {A} Primer},
institution = {Department of Computer Sciences, Brown University},
year = {2003},
type = {Technical Report},
number = {CS-03-05},
address = {},
month = {},
note = {}
}

@article{Hughes2001,
author = {Hughes, K. J. and Tur\'anyi, T. and Clague, A. and Pilling, M. J.},
title = {Development and testing of a comprehensive chemical mechanism for the oxidation of methane},
journal = {Int. J. Chem. Kinet.},
year = {2001},
volume = {33},
number = {},
pages = {513--538},
month = {},
note = {version 1.5, \url {http://www.chem.leeds.ac.uk/Combustion/methane.htm}}
}

@article {Hult2007,
author = {Hult, J. and Gashi, S. and Chakraborty, N. and Klein, M. and Jenkins, K. W. and Cant, S. and Kaminski, C. F.},
title = {Measurement of flame surface density for turbulent premixed flames using PLIF and DNS},
journal = {Proc. Combust. Inst.}, 
year = {2007},
volume = {31},
pages = {1319--1326}
}

@TechReport{Hurst2020,
  author =       {Hurst, C. and Gao, X.},
  title =        {Increasing the Finite Limit of Predictability in Turbulence by Data Assimilation},
  institution =  {AIAA},
  year =         {2020},
  OPTkey =       {},
  OPTtype =      {},
  OPTnumber =    {},
  OPTaddress =   {},
  OPTmonth =     {},
  OPTnote =      {},
  OPTannote =    {}
}

@article {Hussain1991,
author = {Hussain, F. and Kambe, T. and Kuwahara, K. and Orszag, S.},
title = {Challenges in turbulence research (Report of discussions, Tokyo, September 1989)},
journal = {Fluid Dynamics Research}, 
year = {1991},
volume = {7},
pages = {51--63}
}

@techreport {Huth1998,
author = {Huth, M. and Gaio, G. and Heilos, A. and Vortmeyer, N. and Schetter, B. and Karg, J.},
title = {Experiences in Development and Operation of Siemens IGCC Gas Turbines Using Gasification Products form Coal and Refinery Residues},
institution = {Gasification Technologies Council},
year = {1998},
type = {{Gasification Technologies Conference Paper}},
number = {},
address = {Arlington},
month = {},
note = {Available from the world wide web: \url {http://www.gasification.org/Presentations/1998.htm}.}
}

@article{Huttunen2018,
author = {Huttunen, J.M.J amd Kaipio, J.P. and Haario, H},
title = {Approximation error approach in spatiotemporally chaotic models with application to {K}uramoto-{S}ivashinsky equation},
journal = {Computational Statistics and Data Analysis},
year = {2018},
volume = {123},
number = {},
pages = {13--31},
month = {},
note = {}
}

@article{Hyman1986a,
author = {Hyman, J.M. and Nicolaenko, B.},
title = {The {K}uramoto-{S}ivashinsky equations, a bridge between {PDE}s and dynamical systems},
journal = {Phys. D},
year = {1986},
volume = {18},
number = {},
pages = {113--126},
month = {},
note = {}
}

@article{Hyman1986b,
author = {Hyman, J.M. and Nicolaenko, B.},
title = {Order and complexity in the {K}uramoto-{S}ivashinsky model of turbulent
interfaces},
journal = {Phys. D},
year = {1986},
volume = {23},
number = {},
pages = {265--292},
month = {},
note = {}
}

@unpublished {HfromCoalProgram,
 author = {{U}.\ {S}.\ {D}ept.\ of {E}nergy{,} {O}ffice of {F}ossil {E}nergy},
 title = {Hydrogen from Coal Program: Research, Development and Demonstration Plan},
 month = {Sept.},
 note = {Available at \url{http://fossil.energy.gov/programs/fuels/publications/programplans/2009_Draft_H2fromCoal_Sept30_web.pdf}},
 year = {2009}
}
@unpublished {ISTecHPC,
 author = {HPC},
 title = {ISTeC Cray High Performance Computing (HPC) System},
 month = {1},
 note = {{http://istec.colostate.edu/}},
 year = {2011}
}

   ###
    #
    #
    #
    #
    #
   ###

@article {Iijima1986,
author = {Iijima, T. and Takeno, T.},
title = {Effects of Temperature and Pressure on Burning Velocity},
journal = {Combust. Flame},
year = {1986},
volume = {65},
number = {},
pages = {35--43},
month = {},
note = {}
}

@article {Ilbas2006,
author = {Ilbas, M. and Crayford, A. P. and Yilmaz, I. and Bowen, P .J. and Syred, N.},
title = {Laminar burning velocities of hydrogen-air and hydrogen-methane-air mixtures: An
experimental study},
journal = {Int. J. of Hydrogen Energy},
year = {2006},
volume = {31},
number = {12},
pages = {1768--1779},
month = {},
note = {}
}
@article {Im1997,
author = {Im, H. G. and Lund, S. and Ferziger, J.H.},
title = {Large eddy simulation of turbulent front propagation with dynamic subgrid models},
journal = PF,
year = {1997},
volume = {9},
number = {12},
pages = {3826--3833},
month = {},
note = {}
}

@article {Im2006,
author = {Im, H. G.},
title = {Effects of hydrogen addition on the Markstein length and flammability limit of stretched methane/air premixed flames},
journal = {Combust. Sci. Tech.},
year = {2006},
volume = {178},
number = {},
pages = {1585--1661},
month = {},
note = {}
}

@article {ImChen2002,
author = {Im, H. G. and Chen, J. H.},
title = {Preferential Diffusion Effects on the Burning Rate of Interacting Turbulent Premixed Hydrogen-Air Flames},
journal = {Combust. Flame},
year = {2002},
volume = {131},
number = {},
pages = {246--258},
month = {},
note = {}
}

@article {Inge1996,
author = {Gran, I. R. and Magnussen, B. F.},
title = {A numerical study of a bluff-body stabilized diffusion flame. Part 1. Influence of turbulence modeling and boundary conditions.},
journal = {Comb. Sci. Tech.},
year = {1996},
volume = {119},
number = {},
pages = {171--190},
month = {},
note = {}
}

@book {Incropera2007,
author = {Incropera, F. and Dewitt, D. },
title = {Fundamentals of Heat and Mass Transfer},
year = {2007},
publisher = {Wiley},
edition = {sixth},
address = {}
}

@article {Inge1996a,
author = {Gran, I. R. and Magnussen, B. F.},
title = {A numerical study of a bluff-body stabilized diffusion flame. Part 2. Influence of combustion modeling and finite-rate chemistry.},
journal = {Comb. Sci. Tech.},
year = {1996},
volume = {119},
number = {},
pages = {191--217},
month = {},
note = {}
}

@Manual{intel_XeonE5v2,
  title =        {Intel Xeon Processor E5-1600/E5-2600/E5-4600 v2 Product Families},
  organization = {Intel},
  month =        {March},
  year =         2014,
  note =         {\url{http://www.intel.com/content/www/us/en/processors/xeon/xeon-e5-v2-datasheet-vol-1.html}}
}

@article {Ishizuka1982,
author = {Ishizuka, S. and Miyasaka, K. and Law, C. K.},
title = {Effects of Heat Loss, Preferential Diffusion, and Flame Stretch on Flame-Front Instability and Extinction of Propane/Air Mixtures},
journal = {Combust. Flame},
year = {1982},
volume = {45},
number = {},
pages = {293--308},
month = {},
note = {}
}

@article {Ishizuka1986,
author = {Ishizuka, S. and Sakai, Y.},
title = {Structure and tip-opening of laminar diffusion flames},
journal = {Proc. Combust. Inst.}, 
year = {1986},
volume = {21},
pages = {1821--1828}
}

@article {Ivan2014,
author = {Ivan, L. and Groth, C.},
title = {High-order solution-adaptive central essentially non-oscillatory ({CENO}) method for viscous flows},
journal = {J. Comput. Phys.},
year = {2014},
volume = {257},
number = {A},
pages = {830--862},
month = {},
note = {}
}

@article{Ivan2015,
title = {High-order central {ENO} finite-volume scheme for hyperbolic conservation laws on three-dimensional cubed-sphere grids},
journal = JCP,
volume = {282},
pages = {157 - 182},
year = {2015},
issn = {0021-9991},
doi = {https://doi.org/10.1016/j.jcp.2014.11.002},
author = {L. Ivan and H. {De Sterck} and A. Susanto and C.P.T. Groth}
}

@article {Iversen1968,
author = {Iversen, J. D.},
title = {The magnus rotor as an aerodynamic decelerator},
journal = {AIAA 2nd Aerodynamic Deceleration Systems Conference},
year = {1968},
month = {September},
note = {NO. 68-962}
}

@TechReport{Jackson1989,
  author =       {Jackson, T. L. and Grosch, C. E.},
  title =        {Absolute/convective instabilities and the convective Mach number in a compressible mixing layer},
  institution =  {NASA},
  year =         {1989}
}
@article {Jackson2003,
author = {Jackson, G. S. and Sai, R. and Plaia, J. M. and Boggs, C. M. and Kiger, K. T.},
title = {Influence of {H}${}_2$ on the response of lean premixed {CH}${}_4$ flames to high strained flows},
journal = {Combust. Flame},
year = {2003},
volume = {132},
number = {3},
pages = {503--511},
month = {},
note = {Erratum 135(3):363, 2003}
}

@article {Jackson2003erratum,
author = {Jackson, G. S. and Sai, R. and Plaia, J. M. and Boggs, C. M. and Kiger, K. T.},
title = {Erratum to ``Influence of {H}${}_2$ on the response of lean premixed {CH}${}_4$ flames to high strained flows''},
journal = {Combust. Flame},
year = {2003},
volume = {135},
number = {3},
pages = {363},
month = {},
note = {}
}

@article {Jackson2007,
author = {Jackson, J. D. and Launder, B.},
title = {Osborne Reynolds and the Publication of His Papers on Turbulent Flow},
journal = {Annu. Rev. Fluid Mech.},
year = {2007},
volume = {39},
number = {},
pages = {19--35},
month = {January},
note = {}
}

@techreport {Jacobson1973,
author = {Jacobson, I. D.},
title = {Magnus characteristics of arbitrary rotating bodies},
institution = {NATO AGARD},
year = {1973},
type = {Technical Report},
number = {AGARD-AG-171},
address = {},
month = {November},
}

@Article{Janjic2014,
  author =       {Janji$\acute{c}$, T. and McLaughlin, D. and Cohn, E. S. and Verlaan, M.},
  title =        {Conservation of Mass and Preservation of Positivity with Ensemble-Type Kalman Filter Algorithms},
  journal =      {American Meteorological Society},
  year =         {2014},
  volume =    {142},
  pages =     {755--773},
  month =     {February}
}

@Book{Jazwinski1970,
  author =    {Jazwinski, A. H.},
  title =        {Stochastic Processes and Filtering Theory},
  publisher =    {Academic Press},
  year =         {1970},
  address =   {New York}
}

@article {Jensen2007,
author = {Jensen, K. and J. Ripoll and A. Wray and D. Joseph and M. El-Hafi},
title = {On various modeling approaches to radiative heat transfer in pool fires},
journal = {Combust. Flame},
year = {2007},
volume = {148},
number = {},
pages = {263--279},
month = {},
note = {}
}


@article {Jeong1995,
author = {Jeong, J. and Hussain, F.},
title = {On the identification of a vortex},
journal = {J. Fluid Mech.},
year = {1995},
volume = {285},
number = {},
pages = {69--94},
month = {},
note = {}
}

@article {Jiang1996,
author = {Jiang, G. and Shu, C.-W.},
title = {Efficient implementation of weighted {ENO} schemes},
journal = {J. Comput, Phys.},
year = {1996},
volume = {126},
number = {},
pages = {202--228},
month = {},
note = {}
}

@article {Jirka2004,
author = {Jirka, G.},
title = {Integral model for turbulent buoyant jets in unbounded stratified flows. part I: single round jet},
journal = {Environmental Fluid Mechanics},
year = {2004},
volume = {4},
number = {},
pages = {1--56},
month = {},
note = {}
}

@article {Johansen1998,
author = {Johansen, H. and Colella, P.},
title = {A {C}artesian grid embedded boundary method for {P}oisson’s equation on irregular domains},
journal = JCP,
volume = {147},
pages = {60--85},
year = {1998}
}

@article {Johnsson1994,
author = {J. E. Johnsson},
title = {{Formation and Reduction of Nitrogen Oxides in Fluidized-Bed Combustion}},
journal = {Fuel},
volume = {73},
pages = {1398--1415},
year = {1994}
}

@article {Kadowaki2005,
author = {Kadowaki, S. and Hasegawa, T.},
title = {Numerical simulation of dynamics of premixed flames: flame instability and vortex-flame interaction},
journal = {Prog. Energy Combust. Sci.},
year = {2005},
volume = {31},
number = {},
pages = {193--241},
month = {},
note = {}
}

@article{Kadioglu2008,
title = {A fourth-order auxiliary variable projection method for zero-Mach number gas dynamics},
journal = {Journal of Computational Physics},
volume = {227},
number = {3},
pages = {2012-2043},
year = {2008},
issn = {0021-9991},
doi = {https://doi.org/10.1016/j.jcp.2007.10.008},
author = {Kadioglu, S. and Klein, R. and Minion, M.}
}

@article {Kalman1960,
	author = {Kalman, R.},
	title = {A new approach to linear filtering and prediction problems},
	journal = {Trans. ASME, Ser. D, J. Basic Eng.},
	year = {1960},
	volume = {82},
	number = {},
	pages = {35--45},
	month = {},
	note = {}
	}

@article {Kalman1961,
	author = {Kalman, R. and Bucy, R.},
	title = {New results in linear filtering and prediction problems},
	journal = {Trans. ASME, Ser. D, J. Basic Eng.},
	year = {1961},
	volume = {83},
	number = {},
	pages = {95--109},
	month = {},
	note = {}
	}

@inproceedings {Kalnay2002,
author = {Kalnay, E. and Corazza, M. and Cai, M.},
title = {Are Bred Vectors The Same As Lyapunov Vectors?},
booktitle = {Symposium on Observations, Data Assimilation, and Probabilistic Prediction},
year = {2002},
editor = {},
pages = {6820},
organization = {American Meteorological Society},
publisher = {},
address = {},
month = {},
note = {}
}


@book{Kalnay2003,
author={Kalnay, E.},
title={Atmospheric modeling, data assimilation and predictabilty},
publisher={Cambridge University Press},
year={2003},
edition =   {1st}
}
@book{Kalnay2012,
author={Kalnay, E.},
title={Atmospheric modeling, data assimilation and predictabilty},
publisher={Cambridge University Press},
year={2012},
edition =   {7th}
}


@conference{Kalnay2003b,
	Author = {Kalnay, E. and Peña, M. and Yang, S.-C. and Cai, M.},
	title = {Breeding and predictability in coupled Lorenz models},
	year = {2003},
        publisher = {ECMWF}
}

@article{Kamkar2011,
author = {Kamkar, S. J. and Wissink, A. M. and Sankaran, V. and Jameson, A.},
title = {Feature-driven {C}artesian adaptive mesh refinement for vortex-dominated flows},
journal = JCP,
year = {2011},
volume = {230},
pages = {6271--6298}
}

@article {KaganSivashinsky1997,
	author = {Kagan, L. and Sivashinsky, G.},
	title = {Self-fragmentation of nonadiabatic cellular flames},
	journal = {Combust. Flame},
	year = {1997},
	volume = {108},
	number = {},
	pages = {220--226},
	month = {},
	note = {}
	}

@article {KaganMinaev2004,
	author = {Kagan, L. and Minaev, S. and Sivashinsky, G.},
	title = {On self-drifting flame balls},
	journal = {Math. Comput. Simulation},
	year = {2004},
	volume = {65},
	number = {},
	pages = {511-520},
	month = {},
	note = {}
        }



@article {Karim1996,
	author = {Karim, G. A. and Wierzba, I. and Al-Alousi, Y.},
	title = {Methane-Hydrogen mixtures as fuels},
	journal = {Int. J. Hydrogen Energy},
	year = {1996},
	volume = {21},
	number = {},
	pages = {625--631},
	month = {},
	note = {}
	}

@article{Karni1996,
  title={Hybrid multifluid algorithms},
  author={Karni, S.},
  journal=SIAMJSC,
  volume={17},
  number={5},
  pages={1019--1039},
  year={1996},
  publisher={SIAM}
}

@article {Kato2012,
author = {Kato, H. and Obayashi, S.},
title = {Approach for uncertainty of turbulence modeling based on data assimilation technique},
journal = {Computers and Fluids},
volume = {85},
year = {2012},
pages = {2--7}
}

@article {Kato2015,
author = {Kato, H. and Yoshizawa, A. and Ueno, G. and Obayashi, S.},
title = {A data assimilation methodology for reconstructing turbulent flows around aircraft},
journal = JCP,
volume = {283},
year = {2015},
pages = {559--581}
}

@techreport {Katoh2006 ,
author = {Katoh, A. and Kitagawa, K. and Gupta, A. K.},
title = {Examination of methane-hydrogen mixture flame using isotope shift/PLIF spectroscopy},
institution = {AIAA},
year = {2006},
type = {Paper},
number = {20191-4344},
address = {},
month = {},
note = {}
}

@article {Kawai2012,
author = {Kawai, S. and Larsson, J.},
title = {Wall-modeling in large eddy simulation: {L}ength scales, grid resolution, and accuracy},
journal = {Phys. Fluids},
volume = {24},
year = {2012},
pages = {015105}
}

@unpublished {Kazakov,
author = {Kazakov, A. and Frenklach, M.},
title = {Reduced Reaction Sets based on {GRI-M}ech 1.2},
note = {\url{http://www.me.berkeley.edu/drm/}}
}

@techreport {KeeDixonLewis1986,
author = {Kee, R. J. and Dixon-Lewis, G. and Warnatz, J. and Coltrin, M. E. and Miller, J. A.},
title = {A {FORTRAN} Computer Code Package for the Evaluation of Gas-phase Multicomponent Transport Properties},
institution = {Sandia National Laboratories},
year = {1986},
type = {Technical Report},
number = {SAND86-8246},
address = {Livermore},
month = {},
note = {}
}

@article {KeeMiller1988,
author = {Kee, R. J. and Miller, J. A. and Evans, G. H. and Dixon-Lewis, G.},
title = {A computational model of the structure and extinction of strained, opposed flow premixed methane-air flames},
volume = {22},
year = {1988},
pages = {1479--1494},
journal = {Proc. Combust. Inst.}
}

@techreport {KeeGrcar1985,
author = {Kee, R. J. and Grcar, J. F. and Smooke, M. D. and Miller, J. A.},
title = {{PREMIX}: A Fortran Program for Modeling Steady, Laminar, One-Dimensional Premixed Flames},
institution = {Sandia National Laboratories},
year = {1983},
type = {Technical Report},
number = {SAND85-8240},
address = {Livermore},
month = {},
note = {}
}

@techreport {KeeRupley1996,
author = {Kee, R. J. and Ruply, R. M. and Meeks, E. and Miller, J. A.},
title = {CHEMKIN-{III}: A {FORTRAN} Chemical Kinetics Package for the Analysis of Gas-phase Chemical and Plasma Kinetics},
institution = {Sandia National Laboratories},
year = {1996},
type = {Technical Report},
number = {SAND96-8216},
address = {Livermore},
month = {},
note = {}
}

@techreport{KeeRupley2000,
  title={CHEMKIN Collection, Release 3.6, Reaction Design},
  author={Kee, R. J. and Rupley, F. M. and Miller, J. A. and Coltrin, M. E. and Grcar, J. F. and Meeks, E. and Moffat, H. K. and Lutz, A. E. and Dixon-Lewis, G. and Smooke, M. D. and others},
  institution = {Sandia National Laboratories},
  number = {SAND96-8216},
  year={2000}
}

@techreport {KeeWarnatz1983,
author = {Kee, R. J. and Warnatz, J. and Miller, J. A.},
title = {A {FORTRAN} Computer Code Package for the Evaluation of Gas-phase Viscosities, Conductivities, and Diffusion Coefficients},
institution = {Sandia National Laboratories},
year = {1983},
type = {Technical Report},
number = {SAND83-8209},
address = {},
month = {},
note = {}
}

@article {Kelman1997a,
author = {Kelman, J. B. and Masri, A. R.},
title = {Quantitative technique for imaging mixture fraction, temperature, and the hydroxyl radical in turbulent diffusion flames},
journal = {Applied Optics}, 
year = {1997},
volume = {36},
number = {},
pages = {3506--3514},
month = {},
note = {}
}

@article {Kelman1997b,
author = {Kelman, J. B. and Masri, A. R.},
title = {{Simultaneous Imaging of Temperature and OH Number Density in Turbulent Diffusion Flames}},
journal = {Combustion Science and Technology},
year = {1997},
volume = {122},
number = {1--6},
pages = {1--32},
month = {},
note = {}
}

@article {Kennedy2003,
author = {Kennedy, C. and Carpenter, M.},
title = {{Additive {R}unge-{K}utta schemes for convection-diffusion-reaction equations}},
journal = {Applied Numerical Mathematics},
year = {2003},
volume = {44},
number = {},
pages = {139--181},
month = {},
note = {}
}

@article {Kido1994,
author = {Kido, H. and Huang, S. and Tanoue, K. and Nitta, T.},
title = {{Improvement of lean hydrocarbon mixtures combustion performance by hydrogen addition and its mechanisms}},
journal = {Int. Symposium COMODIA},
year = {1994},
volume = {},
number = {},
pages = {119--124},
month = {},
note = {}
}

@techreport {Kido2003,
author = {Kido, H. and Nakahara, M. and Nakashima, K.},
title = {A study on premixed turbulent combustion of hydrogen including hydrocarbon},
institution = {AIAA},
year = {2003},
type = {Paper},
number = {AIAA-2003-4638},
address = {},
month = {},
note = {}
}

@article {Kikuchi2015,
author = {Kikuchi, R. and Misaka, T. and Obayashi, S.},
title = {Assessment of probability density function based on POD reduced-order model for ensemble-based data assimilation},
journal = {Fluid Dynamics Research},
year = {2015},
volume = {47},
number = {5},
pages = {051403},
month = {},
note = {doi:10.1088/0169-5983/47/5/051403}
}

@article {Kim2001,
author = {Kim, C.-S.},
title = {An immersed-boundary finite volume method for simulations of flow in complex geometeries},
journal = {J. Comput. Phys.},
year = {2001},
volume = {171},
number = {},
pages = {132--150},
month = {},
note = {}
}

@article {Kimball-Linne1986,
author = {Kimball-Linne, M. A. and Hanson, R. K.},
title = {Combustion-Driven Flow Reactor Studies of Thermal De{NO}$_x$ Reaction Kinetics},
journal = {Combust. Flame},
year = {1986},
volume = {64},
number = {},
pages = {337--351},
month = {},
note = {}
}

@article {Kirkpatrick2003,
author = {Kirkpatick, M. and Armfield, S. and Kent, J.},
title = {A representation of curved boundaries for the solution of the {N}avier-{S}tokes equations on a staggered three dimensional {C}artesian grid},
journal=JCP,
year = {2003},
volume = {184},
pages = {1--36}
}

@article {Kittel1971,
author = {Kittel, C.},
title = {Postulational Basis of the Law of Increase of Entropy},
journal = {Proc. Natl. Acad. Sci. USA},
year = {1971},
volume = {68},
number = {11},
pages = {2746--2747},
month = nov
}

@article{Khalili2019,
author = {Khalili, M. Ehsan and Larsson, Martin and Müller, Bernhard},
title = {High-order ghost-point immersed boundary method for viscous compressible flows based on summation-by-parts operators},
journal = IJNMF,
volume = {89},
number = {7},
pages = {256-282},
doi = {https://doi.org/10.1002/fld.4696},
year = {2019}
}

@article {Kjaergaard1996,
author = {Kj{\ae}rgaad, K. and Glarborg, P. and Dam-Johansen, K.},
title = {Pressure Effects on the Thermal De-{NO}$_x$ Process},
journal = {Proc. Combust. Inst.},
year = {1996},
volume = {26},
number = {},
pages = {2067--2074},
month = {},
note = {}
}

@article {Klockner2009,
author = {Klockner, A and Warburton, T and Bridge, J and Hesthaven, JS},
title = {Nodal discontinuous Galerkin methods on graphics processors},
journal = JCP,
year = {2009},
volume = {228},
number = {},
pages = {7863--7882},
month = {},
OPTdoi = {10.1016/j.jcp.2009.06.041}
}

@book {Kohse-Hoinghaus2002,
	editor = {Kohse-H{\"o}inghaus, K. and Jeffries, J. B.},
	title = {Applied Combustion Diagnostics},
	publisher = {Taylor and Francis},
	year = {2002},
	volume = {},
	series = {},
	address = {New York},
	edition = {},
	month = {},
	note = {}
	}

@Manual{Kokkos_web,
  title =        {Kokkos C++ Performance Portability Programming EcoSystem: The Programming Model---Parallel Execution and Memory Abstraction},
  organization = {Sandia National Laboratories},
  note =         {\url{https://github.com/kokkos/kokkos}}
}

@Manual{Kokkos_webdoc,
  title =        {Kokkos: The C++ Performance Portability Programming Model},
  organization = {Sandia National Laboratories},
  note =         {\url{https://github.com/kokkos/kokkos/wiki}}
}

@article{Kolla2016,
author = {Kolla, H and Zhao, X and Chen, J. H. and Swaminathan, N.},
title = {Velocity and Reactive Scalar Dissipation Spectra in Turbulent Premixed Flames},
journal = {Combustion Science and Technology},
volume = {188},
number = {9},
pages = {1424-1439},
year  = {2016},
publisher = {Taylor & Francis},
doi = {10.1080/00102202.2016.1197211},
URL = {https://doi.org/10.1080/00102202.2016.1197211}
}

@article{Kolmogorov1941,
author = {Kolmogorov, A. N.},
title = {The local structure of turbulence in incompressible viscous fluid for very large Reynolds numbers},
journal = {Dokl. Akad. Nauk SSSR},
volume = {30},
number = {4},
pages = {299--303},
year  = {1941}
}

@article{Konigstein2015,
author = {Konigstein, M. and Bes-Assa, E. and Banai, S. and Shacham, Y. and Abramoitz, Y. and Steinvil, A. and Leshem Rubinow, E. and Havakuk, O. and Halkin, A. and Keren, G. and Finkelstein, A. and Arbel, Y.},
title = {Periprocedural bleeding, acute kidney injury, and long-term mortality after transcatheter aortic valve implantation},
journal = {Can J Cardiol},
volume = {31},
number = {},
pages = {56-62},
year = {2015},
}

@article {Korn1998,
author = {Korn, E. L. and Graubard, B. I.},
title = {Scattterplots with Survey Data},
journal = {The American Statistician},
year = {1998},
volume = {52},
number = {1},
pages = {58--69},
month = feb,
note = {}
}

@article {Kosovic2002,
author = {Kosovic, B. and Pullin, D. I. and Samtaney, R.},
title = {Subgrid-scale modeling for large-eddy simulations of compressible turbulence},
journal = PF,
year = {2002},
volume = {14},
number = {4},
pages = {1511--1522},
month = {April}
}

@techreport{Knight1998,
author = {Knight, D. and Zhou, G. and Okong'o, N. and Shukla, V.},
title = {Compressible large eddy simulation using unstructured grids},
institution = {AIAA},
year = {1998},
month = {January},
type = {Paper},
number = {98-0535}
}

@article{Kravchenko1999,
title = "B-Spline Method and Zonal Grids for Simulations of Complex Turbulent Flows",
journal = JCP,
volume = "151",
number = "2",
pages = "757 - 789",
year = "1999",
author = "Kravchenko, A. G. and Moin, P. and Shariff, K."
}

@TechReport{Kreuder2013,
author = {Kreuder, J. J. and Kirkpatrick, A. T. and Gao, X},
title = {Computation of Heat Transfer from an Impinging Flame Jet to a Plane Surface},
institution = {51st AIAA Aerospace Sciences Meeting},
year = {2013},
type = {AIAA},
number = {2013-0605}
}

@inproceedings {Krieger2013,
author = {Krieger, C. and Strout, M. M. and Olschanowsky, C. and Stone, A. and Guzik, S. M. and Gao, X. and Bertolli, C. and Kelly, P. H. J. and Mudalige, G. and Straalen, B. V. and Williams, S.},
title = {Loop Chaining: A Programming Abstraction for Balancing Locality and Parallelism},
booktitle = {18th International Workshop on High-Level Parallel Programming Models and Supportive Environments},
year = {2013},
editor = {},
pages = {},
organization = {},
publisher = {},
address = {},
month = {May},
note = {}
}

@article {Kristensen1996,
author = {Kristensen, P. G. and Glarborg, P. and Dam-Johansen, K.},
title = {Nitrogen Chemistry During Burnout in Fuel-Staged Combustion},
journal = {Combust. Flame},
year = {1996},
volume = {107},
number = {},
pages = {211--222},
month = {},
note = {}
}

@article {Krutiev1976,
author = {Krutiev, V. A. and Gorbanenko, A. D.},
title = {},
journal = {Teploenergetika},
year = {1976},
volume = {23},
number = {},
pages = {72},
month = {},
note = {}
}

@article {Kumar2009,
author = {Kumar, A. and Mazumder, S.},
title = {Coupled solution of the species conservation equations using unstructured finite-volume method},
journal = {Int. J. Numer. Methods Fluids},
year = {2010},
volume = {64},
number = {4},
pages = {409--442},
month = {},
note = {}
}

@article {Kundu1998,
author = {Kundu, K. and P. Penko and S. Yang},
title = {Simplified Jet-A/Air combustion mechanisms for calculation of NOx emissions},
journal = {AIAA paper 98-3986},
year = {1998},
volume = {},
number = {},
pages = {},
month = {},
note = {}
}

@article {Kulhavy1993,
author = {Kulhav{\'y}, R.},
title = {Implementation of Bayesian Parameter Estimation in Adaptive Control and Signal Processing},
journal = {Journal of the Royal Statistical Society. Series D (The Statistician)},
year = {1993},
volume = {42},
number = {4},
pages = {471--482},
month = {},
note = {}
}


@book {Kuo1986,
author = {Kuo, K.K.},
title = {Principles of Combustion},
year = {1986},
publisher = {John Wiley \& Sons},
edition = {},
address = {New York}
}

@article {Kuramoto1978,
author = {Kuramoto, Y.},
title = {Diffusion-Induced Chaos in Reaction Systems},
journal = {Supplement of the Progress of Theoretical Physics},
year = {1978},
volume = {},
number = {64},
pages = {346--367},
month = {},
note = {}
}

@book {Kushner1971,
author = {Kushner, H.},
title = {Introduction to Stochastic Control},
year = {1971},
publisher = {Holt, Rinehart and Winston},
edition = {},
address = {New York}
}

   #
   #
   #
   #
   #
   #
   #####

@Book{Lahoz2010,
  author =    {Lahoz, W. and Khattatov, B. and Menard, R.},
  ALTeditor =    {},
  title =        {Data Assimilation: Making Sense of Obervations},
  publisher =    {Springer},
  year =         {2010},
  OPTkey =       {},
  OPTvolume =    {},
  OPTnumber =    {},
  OPTseries =    {},
  address =   {New York},
  OPTedition =   {},
  OPTmonth =     {},
  OPTnote =      {},
  OPTannote =    {}
}


@Book{Lambert1991,
  author =    {Lambert, J. D.},
  ALTeditor =    {},
  title =        {Numerical Methods for Ordinary Differential Systems},
  publisher =    {John Wiley \& Sons},
  year =         {1991},
  OPTkey =       {},
  OPTvolume =    {},
  OPTnumber =    {},
  OPTseries =    {},
  address =   {New York},
  OPTedition =   {},
  OPTmonth =     {},
  OPTnote =      {},
  OPTannote =    {}
}

@article {Laney2007, 
author = {Laney, D. and Bremer, P.-T. and Mascarenhas, A. and Miller, P. and Pascucci, V.},
title = {Understanding the structure of the turbulent mixing layer in hydrodynamic instabilities}, 
journal = {IEEE Trans.\ Vis.\ Comp. Graph.},
year = {2006}, 
volume = {13}, 
number = {1}, 
pages = {1053--1060},
month = {}, 
note = {} 
}

@article {Laux1992, 
author = {Laux, C. O. and Kruger, C. H.},
title = {Arrays of radiative transition probabilities for the {N}$_2$ first and second positive, {NO} beta and gamma, {N}$_2^+$ first negative, and {O}$_2$ {S}chumann-{R}unge band systems}, 
journal = {J. Quant. Spectrosc. Radiat. Transfer},
year = {1992}, 
volume = {48}, 
number = {}, 
pages = {9--24},
month = {}, 
note = {} 
}

@article {Lavante1983,
author = {von Lavante, E. and Strehlow, R. A.},
title = {The Mechanism of Lean Limit Flame Extinction},
journal = {Combust. Flame},
year = {1983},
volume = {49},
number = {},
pages = {123--140},
month = {},
note = {}
}

@article {Laverdant2003,
author = {Laverdant, A. and Th\'evenin, D.},
title = {Interaction of a Gaussian acoustic wave with a turbulent premixed flame},
journal = {Combust. Flame},
year = {2003},
volume = {134},
number = {},
pages = {11-19},
month = {},
note = {}
}

@article{Law1988,
author = {Law, C. K.},
title = {Dynamics of stretched flames},
volume = {22},
year = {1988},
pages = {1381--1402},
journal = {Proc. Combust. Inst.},
note = {}
}

@article {Law2000,
author = {Law, C. K. and Sung, C. J.},
title = {Structure, aerodynamics, and geometry of premixed flamelets},
journal = {Prog. Energy Combust. Sci.},
year = {2000},
volume = {26},
number = {},
pages = {459--505},
month = {},
note = {}
}

@article {Law2004,
author = {Law, C. K. and Kwon, O.C.},
title = {Effects of hydrocarbon substitution on atmospheric hydrogen-air flame propagation},
journal = {Int. J. of Hydrogen Energy},
year = {2004},
volume = {29},
number = {},
pages = {867--879},
month = {},
note = {}
}

@article {Lawn2004a,
author = {Lawn, C. J. and Evesque, S. and Polifke, W.},
title = {A model for the thermoacoustic response of a premixed swirl burner, part {I}: acoustic aspects},
journal = {Combust. Sci. Technol.},
year = {2004},
volume = {176},
number = {8},
pages = {1331--1358},
month = {},
note = {}
}

@article {Lawn2004b,
author = {Lawn, C. J. and Polifke, W.},
title = {A model for the thermoacoustic response of a premixed swirl burner, part {II}: the flame response},
journal = {Combust. Sci. Technol.},
year = {2004},
volume = {176},
number = {8},
pages = {1359--1390},
month = {},
note = {}
}

@article {Lafay2008,
author = {Lafay, Y. and Renou, B. and Cabot, G. and Boukhalfa, M.},
title = {Experimental and numerical investigation of the effect of H2 enrichment on laminar methane-air flame thickness},
journal = {Combust. Flame},
year = {2008},
volume = {153},
number = {4},
pages = {540--561},
month = {},
note = {}
}

@Book{Layton2012,
  author =    {Layton, W. J. and Rebholz, L. G.},
  ALTeditor =    {Morel, J.-M. and Teissier, B.},
  title =        {Approximate Deconvolution Models of Turbulence: Analysis, Phenomenology and Numerical Analysis},
  publisher =    {Springer},
  year =         {2012},
  series =    {Lecture Notes in Mathematics},
  address =   {New York}
}

@article {Lee2003,
author = {Lee, L. and LeVeque, R.},
title = {An immersed interface method for incompressible {N}avier–{S}tokes equations},
journal = {SIAM Journal of Scientific Computing},
year = {2003},
volume = {25},
number = {},
pages = {832--856},
month = {},
note = {}
}

@article {Leith1974,
author = {Leith, C. E.},
title = {Theoretical skill of {M}onte {C}arlo forecasts},
journal = {Mon. Wea. Rev.},
year = {1974},
volume = {102},
number = {},
pages = {409--418},
month = {},
note = {}
}

@article {Lele1992,
author = {Lele, SK},
title = {Compact finite difference schemes with spectral-like resolution},
journal = {J. Comput. Phys.},
year = {1992},
volume = {103},
number = {},
pages = {16--42},
month = {},
note = {}
}

@article {LeMaitre2004,
author = {Le Ma\^{\i}tre, O. P. and Knio, O. M. and Najm, H. N. and Ghanem, R. G.},
title = {Uncertainty propagation using {W}iener-{H}aar expansions},
journal = {J. Comput. Phys.},
year = {2004},
volume = {197},
number = {1},
pages = {28--57},
month = {},
note = {}
}

@article {Leonard1974,
author = {Leonard, A.},
title = {Energy Cascade in Large-Eddy Simulations of Turbulent Fluid Flows},
journal = {Avances in Geophysics},
year = {1974},
volume = {18},
number = {},
pages = {237--248},
month = {},
note = {}
}

@article {Li1992,
author = {Li, S. C. and Libby, P. A. and Williams, F. A.},
title = {},
journal = {Proc. Combust. Inst.},
year = {1992},
volume = {24},
number = {},
pages = {1503--1512},
month = {},
note = {}
}


@article {Li1994,
author = {Li, C. and Kailasanath, K. and Oran, E. S.},
title = {Detonation structures behind oblique shocks},
journal = PF,
year = {1994},
volume = {6},
number = {4},
pages = {1600--1611},
month = {},
note = {},
OPTdoi = {10.1063/1.868273},
OPTURL = { https://doi.org/10.1063/1.868273}
}

@article {Li1995,
author = {Li, C. and Kailasanath, K. and Oran, E. S. and Landsberg, A. M. and Boris, J. P.},
title = {Dynamics of oblique detonations in ram accelerators},
journal = {Shock Waves},
year = {1995},
volume = {5},
number = {},
pages = {97--101},
month = {},
note = {}
}

@TechReport{Li1992,
  author =       {Li, C. and Kailasanath, K. and Oran},
  title =        {Numerical Studies for the RAM Accelerator},
  institution =  {Naval Research Laboratory},
  year =         {1992}
}


@article {Li1996,
author = {Li, C. and Kailasanath, K. and Oran, E. S.},
title = {Stability of projectiles in thermally choked ram accelerators,},
journal = {Journal of Propulsion and Power},
year = {1996},
volume = {12},
number = {4},
pages = {807--816},
month = {},
note = {}
}

@article {Li2013,
author = {Li, J. and Tu, X.},
title = {A nonoverlapping domain decomposition method for
incompressible {S}tokes equations with continuous pressures},
journal = {SIAM J. Numer. Anal.},
year = {2013},
volume = {51},
number = {2},
pages = {1235--1253},
month = {},
note = {}
}

@article{Ligocki2008,
	Author = {Ligocki, T. and Schwartz, P. and Percelay, J. and Colella, P.},
    title = {Embedded Boundary Grid Generation using the Divergence Theorem, Implicit Functions, and Constructive Solid Geometry},
	Journal = {Journal of Physics: Conference Series},
	Volume = {125},
	Year = {2008}}
        
@article {Libby1982,
author = {Libby, P. A. and Williams, F. A.},
title = {Structure of Laminar Flamelets in Premixed Turbulent Flames},
journal = {Combust. Flame},
year = {1982},
volume = {44},
number = {},
pages = {287--303},
month = {},
note = {}
}

@article {Libby1987,
author = {Libby, P. A. and Williams, F. A.},
title = {Premixed Laminar Flames with General Rates of Strain},
journal = {Combustion Science and Technology},
year = {1987},
volume = {54},
number = {},
pages = {237--273},
month = {},
note = {}
}

@article{Liberman2010,
title = {Deflagration-to-detonation transition in highly reactive combustible mixtures},
journal = {Acta Astronautica},
volume = {67},
number = {7},
pages = {688 - 701},
year = {2010},
issn = {0094-5765},
doi = {https://doi.org/10.1016/j.actaastro.2010.05.024},
url = {http://www.sciencedirect.com/science/article/pii/S0094576510001906},
author = {M.A. Liberman and M.F. Ivanov and A.D. Kiverin and M.S. Kuznetsov and A.A. Chukalovsky and T.V. Rakhimova},
}

@article {Liberman2011A,
author = {Liberman, M. A. and Kiverin, A. D. and Ivanov, M. F.},
title = {On detonation initiation by a temperature gradient for a detailed chemical reaction models},
journal = {Physics Letters A},
year = {2011},
volume = {375},
number = {17},
issn = {0375-9601},
pages = {1803 - 1808},
doi = {https://doi.org/10.1016/j.physleta.2011.03.026},
url = {http://www.sciencedirect.com/science/article/pii/S0375960111003410},
month = {April},
note = {}
}

@inproceedings {Lilly1967,
author = {Lilly, D. K.},
title = {The Representation of Small-Scale Turbulence in Numerical Simulation Experiments},
booktitle = {Proceedings of IBM Scientific Computing Symposium on Environmental Sciences},
year = {1967},
editor = {},
pages = {195--210},
organization = {},
publisher = {},
address = {},
month = {},
note = {}
}

@article {Lipatnikov2002,
author = {Lipatnikov, A. N. and Chomiak, J.},
title = {Turbulent flame speed and thickness: phenomenology, evaluation, and application in multi-dimensional simulations},
journal = {Prog. Energy Combust. Sci.},
year = {2002},
volume = {28},
number = {},
pages = {1--74},
month = {},
note = {}
}

@article {Lipatnikov2005,
author = {Lipatnikov, A. N. and Chomiak, J.},
title = {Molecular transport effects on turbulent flame propagation and structure},
journal = {Prog. Energy Combust. Sci.},
year = {2005},
volume = {31},
number = {},
pages = {1--73},
month = {},
note = {}
}



@article{Littlejohn2007,
author = {D. Littlejohn and R. K. Cheng},
title = {Fuel Effects on a Low-swirl Injector for Lean Premixed Gas Turbines},
journal = {Proc.\ Combust.\ Inst.},
volume = {31},
pages = {3155--3162},
year = {2007},
}


@article {Liu1991,
author = {Liu, Y. and Lenze, B. and Leuckel, W.},
title = {Investigation on the laminar and turbulent burning velocities of premixed lean and rich flames of methane-hydrogen-air mixtures},
journal = {Progress in Astronautics and Aeronautics},
year = {1991},
volume = {131},
number = {},
pages = {259-274},
month = {},
note = {Dyn. Deflagrations React. Syst.: Flames}
}

@article {Liu2006,
author = {Liu, Y and Vinokur, M and Wang, ZJ},
title = {Discontinuous spectral difference method for conservation laws on unstructured grids},
journal = {J. Comput. Phys.},
year = {2006},
volume = {216},
number = {},
pages = {780--801},
month = {},
OPTdoi = {10.1016/j.jcp.2006.01.024}
}

@article {Liu2012,
author = {Liu, W. and Tu, X. and Zhang, M.},
title = {{P}oisson-{N}ernst-{P}lanck systems for ion flow with density
functional theory for hard-sphere potential: {I}-{V} relations and critical potentials. {P}art {II}: {N}umerics},
journal = { J. Dynam. Differential Equations},
year = {2012},
volume = {24},
number = {4},
pages = {985--1004},
month = {},
note = {}
}

@article {Löhner2008,
author = {Löhner, R. and Cebral, J. and Camelli, F. and Appanaboyina, A. and Baum, J. and Mestreau, E. and Soto, O.},
title = {Adaptive embedded and immersed unstructured grid techniques},
journal = {Comput. Methods Appl. Mech. Eng.},
year = {2008},
volume = {197},
number = {},
pages = {2173--2197},
month = {},
note = {}
}

@book{Lomax2001,
author={Lomax, H. and Pulliam, T. H. and Zingg, D. W.},
title={Fundamentals of Computational Fluid Dynamics},
series={Scientific Computation},
year={2001},
publisher={Springer-Verlag Berlin Heidelberg},
edition={1}
}

@article {Lombardini2011,
author = {Lombardini, M. and Hill, D. J. and Pullin, D. I. and Meiron, D. I.},
title = {Atwood ratio dependence of {R}ichtmyer-{M}eshkov flows under reshock conditions using large-eddy simulations},
journal = {JFM},
year = {2011},
volume = {670},
number = {},
pages = {439--480},
month = {},
note = {}
}

@article {Long1983,
author = {Long, M. B. and Fourguette, D. C. and Escoda, M. C. and Layne, C. B.},
title = {{Instantaneous Ramanography of a turbulent diffusion flame}},
journal = {Optics Letters},
year = {1983},
volume = {8},
number = {5},
pages = {244--246},
month = may,
note = {}
}

@article {Loptien1960,
author = {Loptien, George W.},
title = {An investigation of cone-cylinder bodies in the steady state spin mode and magnus force effects on a cone-cylinder body},
journal = {WADD TN 60-76},
year = {1960},
month = {August},
note = {Wright Air Development Division}
}

@article {Lorenz1963,
author = {Lorenz, E. N.},
title = {Deterministic nonperiodic flow},
journal = {J. Atmos. Sci.},
year = {1963},
volume = {20},
number = {},
pages = {130-141},
}

@article {Lorenc1986,
author = {Lorenz, A. C.},
title = {Analysis methods for numerical weather prediction},
journal = {Q. J. R. Meteorol. Soc.},
year = {1986},
volume = {112},
number = {},
pages = {1177--1194},
}

@article {Lorenc2003,
author = {Lorenz, A. C.},
title = {The potential of the ensemble Kalman filter for NWP -- a comparison with 4D-Var},
journal = {Q. J. R. Meteorol. Soc.},
year = {2003},
volume = {129},
number = {},
pages = {3183--3203},
}

@article {Louis2001,
author = {Louis, J. J. J. and Kok, J. B. W. and Klein, S. A.},
title = {Modeling and Measurements of a 16-kW Turbulent Nonadiabatic Syngas Diffusion Flame in a Cooled Cylindrical Combustion Chamber},
journal = {Combust. Flame},
year = {2001},
volume = {125},
number = {1--2},
pages = {1012-1031},
month = {},
note = {}
}


@article {Lozinski1994,
author = {Lozinski, D. and Buckmaster, J. and Ronney P.},
title = {Absolute Flamability Limits and Flame Balls},
journal = {Combust. Flame},
year = {1994},
volume = {97},
number = {},
pages = {301--316},
month = {},
note = {}
}

@article {Lu2015,
author = {Lu, F. and Morzfeld, M. and Tu, X. and Chorin, A.},
title = {Limitations of polynomial chaos expansions in the {B}ayesian solution of inverse problems},
journal = {J.  Comput. Phys.},
year = {2015},
volume = {282},
number = {},
pages = {138--147},
month = {},
note = {}
}

@Book{Luenberger1984,
  author =    {Luenberger, D. L.},
  title =        {Linear and Non-linear Programming},
  publisher =    {Addison-Wesley},
  year =         {1984},
  edition =   {2nd Ed.}
}

@article {Lugt1983, 
author = {Lugt, H. J.}, 
title = {Autorotation}, 
journal = {Annual Review of Fluid Mechanics}, 
year = {1983}, 
volume = {15}, 
number = {}, 
pages = {123-147}, 
month = {}, 
note = {} 
}

@article {Lund2003, 
author = {Lund, T. S.}, 
title = {The Use of Explicit Filters in Large Eddy Simulation}, 
journal = {Computers and Mathematics with Application}, 
year = {2003}, 
volume = {46}, 
number = {4}, 
pages = {603-616}, 
month = {August}, 
note = {} 
}

@article {Lundgren1982, 
author = {Lundgren, T. S.}, 
title = {Strained spiral vortex model for turbulent fine structure}, 
journal = {Phys. Fluids}, 
year = {1982}, 
volume = {25}, 
number = {12}, 
pages = {2193-2203}, 
month = {December}, 
note = {} 
}

@techreport {Lundgren2003,
author = {Lundgren, T. S.},
title = {Linearly forced isotropic turbulence},
year = {2003},
type = {Annual Research Briefs},
institution = {Center for Turbulence Research},
number = {},
address = {},
month = {},
note = {} 
}

@article {Luo2014,
author = {Luo, X. and Lorentzen, R. J. and Stordal, A. S. and N{\ae}vdal, G.},
title = {Toward an enhanced Bayesian estimation framework for multiphase flow soft-sensing},
journal = {Inverse Problems},
year = {2014},
volume = {30},
number = {11},
pages = {114012},
month = {},
note = {}
}


@techreport {Lutz1988,
author = {Lutz, A. E. and Kee, R. J. and Miller, J. A.},
title = {{SENKIN}: A Fortran Program for Predicting Homogeneous Gas Phase Chemical Kinetics with Sensitivity Analysis},
institution = {Sandia National Laboratories},
year = {1988},
type = {Sandia Report},
number = {SAND87-8248},
address = {Livermore, California},
month = {},
note = {}
}

@article {Lyon1987,
author = {Lyon, R. K.},
title = {Thermal De{NO}$_x$: Controlling nitrogen oxides emissions by a noncatalytic process},
journal = {Environ. Sci. Technol.},
year = {1987},
volume = {21},
number = {3},
pages = {231--236},
month = {},
note = {}
}

@article {Lyon1990,
author = {Lyon, R. K. and Cole, J. A.},
title = {A Reexamination of the Rapre{NO}$_x$ Process},
journal = {Combust. Flame},
year = {1990},
volume = {82},
number = {},
pages = {435--443},
month = {},
note = {}
}
   #     #
   ##   ##
   # # # #
   #  #  #
   #     #
   #     #
   #     #

@article{Ma2017,
title = {An entropy-stable hybrid scheme for simulations of transcritical real-fluid flows},
author = {Ma, P. C. and Lv, Y. and Ihme, M.},
journal = JCP,
volume = {340},
pages = {330--357},
year = {2017},
issn = {0021-9991},
OPTdoi = {https://doi.org/10.1016/j.jcp.2017.03.022},
OPTurl = {http://www.sciencedirect.com/science/article/pii/S0021999117302176},
keywords = {Real fluid, Spurious pressure oscillations, Double-flux model, Entropy stable, Hybrid scheme}
}

@article {Magnussen2005,
author = {Magnussen, B. F.},
title = {The eddy dissipation concept},
journal = {ECCOMAS Thematic Conference on Computational Combustion},
year = {2005},
volume = {},
number = {},
pages = {},
}

@article {Mahesh1998,
author = {Mahesh, K.},
title = {A family of high order finite difference schemes with good spectral resolution},
journal = JCP,
year = {1998},
volume = {145},
number = {},
pages = {332--358},
}

@article {MajdaSethian1985,
author = {Majda, A. and Sethian, J. A.},
title = {The derivation and numerical solution of the equations for zero {M}ach number combustion},
journal = {Combust. Sci. Technol.},
volume = {42},
pages = {185--205},
year = {1985}
}

@article {Majumdar2001,
author = {Majumdar, S. and Iaccarino, G. and Durbin, P.},
title = {RANS solver with adaptive structured boundary non-conforming grids},
journal = {Annual Res. Briefs, Cent. Turb. Res.},
volume = {},
pages = {353--364},
year = {2001}
}

@article {Mallens1995,
author = {Mallens, R. M. M. and Lange, H. C. de and Ven, C. H. J. van de and de Goey, L. P. H.},
title = {Modeling of confined and unconfined laminar premixed flames on slit and tube burners},
journal = {Combust. Sci. Technol.},
volume = {107},
pages = {387--401},
year = 1995
}

@article {Mallens1997,
author = {Mallens, R. M. M. and Loijenga, B. O. and de Goey, L. P. H. and Sonnemans, P. J. M.},
title = {Numerical and Experimental Study of Lean {M}- and {V}-shaped flames},
journal = {Combust. Sci. Technol.},
year = {1997},
volume = {122},
number = {},
pages = {331-344},
month = {},
note = {}
}

@article {Malmstrom1997,
author = {Malmstrom, T. G. and Kirkpatrick, A. T. and Christensen, B. and Knappmiller, K. D.},
title = {Centerline velocity decay measurements in low-velocity axisymmetric jets},
journal = {J. Fluid Mech.},
year = {1997},
volume = {246},
pages = {363--377}
}

@article {Mandel2008,
author = {Mandel, J. and Bennethum, L. S. and Beezley, J. D. and Coen J. I. and Douglas C. D. and Kim, M. and Vodacek A.},
title = {A wildland fire model with data assimilation},
journal = {Mathematics and Computers in Simulation},
year = {2008},
volume = {79},
pages = {584--606}
}

@inproceedings {Manneville1984,
author = {Manneville, P.},
title = {Lyapunov exponents for the {K}uramoto-{S}ivashinsky equations},
booktitle = {Proc. Conf. on Turbulence},
year = {1984},
editor = {},
pages = {},
organization = {Lecture Notes in Physics},
publisher = {Springer-Verlag},
address = {},
month = {},
note = {}
}


@Book{Mansour1979,
  ALTauthor =    {Mansour, N.N. and Moin, P. and Reynolds, W.C. and Ferziger, J.H.},
  ALTeditor =    {Durst, F. and Launder, B.E. and Schmidt, F.W. and Whitelaw, J.H.},
  title =        {Improved Methods for Large Eddy Simulations of Turbulence},
  publisher =    {Springer, Berlin, Heidelberg},
  year =         {1979},
  OPTkey =       {},
  OPTvolume =    {},
  OPTnumber =    {},
  OPTseries =    {},
  OPTaddress =   {},
  OPTedition =   {},
  OPTmonth =     {},
  OPTnote =      {},
  OPTannote =    {}
}

@article {Mantel1999,
author = {Mantel, T. and Samaniego, J.-M.},
title = {Fundamental mechanisms in premixed turbulent flame propagation via flame-vortex interactions {P}art {II}: {N}umerical simulation},
journal = {Combust. Flame},
year = {1999},
volume = {118},
pages = {557--582}
}

@techreport {Marano2003,
author = {Marano, J.},
title = {{GASIFICATION And Supporting Technologies}},
institution = {U.S. Department of Energy National Energy Technology Laboratory and Energy Information Administration},
year = {2003},
type = {{Refinery Technology Profiles}},
number = {},
address = {},
month = jun,
note = {}
}

@article {Margolin2009,
author = {Margolin, L. G.},
title = {Finite-scale equations for compressible fluid flow},
journal = {Phil. Trans. R. Soc. A},
year = {2009},
volume = {367},
pages = {2861--2871}
}

@book {Markowsky2003,
author = {Markowsky et al., J. J.},
title = {Review of {DOE}'s {V}ision 21 {R}esearch and {D}evelopment {P}rogram -- {P}hase 1},
year = {2003},
publisher = {National Academy of Sciences National Research Council},
edition = {},
address = {Washington, DC},
note = {See also \url {http://www.fossil.energy.gov/programs/powersystems/vision21/}}
}

@article {Markstein1949,
author = {Markstein, G. H.},
title = {Cell Structure of Propane Flames Burning in Tubes},
journal = {J. Chem. Phys.},
year = {1949},
volume = {17},
number = {4},
pages = {428--429},
month = apr,
note = {}
}

@article {Markstein1951,
author = {Markstein, G. H.},
title = {Experimental and theoretical study of flame front stability},
journal = {J. Aero. Sci.},
year = {1951},
volume = {18},
number = {},
pages = {199},
month = {},
note = {}
}

@book {Markstein1964,
editor = {Markstein, G. H.},
title = {Nonsteady Flame Propagation},
year = {1964},
publisher = {Pergamon Press},
edition = {},
address = {Oxford}
}

@article {Martin1990, 
author = {R. J. Martin and N. J. Brown}, 
title = {Nitrous oxide formation and destruction in lean, premixed combustion},
journal = {Combust. Flame}, 
volume = {80}, 
pages = {238--255},
year = {1990} 
}

@TechReport {Martin1996, 
author = {D. F. Martin and K. L. Cartwright}, 
title = {{Solving {P}oisson’s equation using adaptive mesh refinement}},
institution = {University of California, Berkeley},
number = {UCB/ERI M96/66},
year = {1996} 
}

@article{Martin2008,
title = {A cell-centered adaptive projection method for the incompressible {N}avier–{S}tokes equations in three dimensions},
author = {Martin, D. F. and Colella, P. and Graves, D.},
journal = JCP,
volume = {227},
number = {3},
pages = {1863-1886},
year = {2008},
issn = {0021-9991},
doi = {https://doi.org/10.1016/j.jcp.2007.09.032}
}

@unpublished {Martinez2012,
 author = {Martinez, D. and Tozzi, L. and Marchese, A. J.},
title = {reduced chemical kinetic mechanism for CFD simulations of high BMEP, lean burn, natural gas engines},
 month = {May},
 note = {Torino, Italy, ASME ICES2012-81109},
 year = {2012}
}

@techreport {Marxen2008,
author = {Marxen, O. and Iaccarino, G.},
title = {Numerical simulation of the effect of a roughness element on high-speed boundary-layer instability},
institution = {38th Fluid Dynamics Conference and Exhibit},
year = {2008},
type = {Paper},
number = {},
address = {Seattle, Washington},
month = {},
note = {}
}

@book{Masatsuka2013,
  title={I do like CFD, VOL.1, Second Edition},
  author={Masatsuka, K.},
  number={v. 1},
  isbn={9781304827937},
  year={2013},
  publisher={K. Masatsuka}
}

@article{Masri1992,
author = {Masri, A. R. and Dibble, R. W. and Barlow, R. S.},
title = {Raman-Rayleigh measurements in bluff-body stabilized flames of hydrocarbon fuels},
volume = {24},
year = {1992},
pages = {317--324},
journal = {Proc. Combust. Inst.},
note = {Formerly {\it Twenty-Fourth Symposium (International) on Combustion.}}
}

@article{Masri1994,
author = {Masri, A. R. and Dally, B. B. and Barlow, R. S.},
title = {The structure of the recirculation zone of a bluff-body combustor, in: 25th Symposium on Combustio},
volume = {25},
year = {1994},
pages = {1301--1308},
journal = {Proc. Combust. Inst.},
note = {Formerly {\it Twenty-Fifth Symposium (International) on Combustion.}}
}

@article {Matalon1982,
author = {Matalon, M. and Matkowsky, B. J.},
title = {Flames as gasdynamic discontinuities},
journal = {J. Fluid Mech.},
year = {1982},
volume = {124},
number = {},
pages = {239--259},
month = {},
note = {}
}

@article{Mathew2003,
  author =       {Mathew, J. and Lechner, R. and Holger, F. and Sesterhenn, J. and Friedrich R.},
  title =        {An explicit filtering method for large eddy simulation of compressible flows},
  journal =      PF,
  year =         {2003},
  volume =    {15},
  number =    {8},
  pages =     {2279--2289},
  month =     {August}
}

@article{Mathur1967,
  title={Thermal conductivity of binary, ternary and quaternary mixtures of rare gases},
  author={Mathur, S. and Tondon, P. K. and Saxena, S. C.},
  journal={Molecular Physics},
  volume={12},
  number={6},
  pages={569--579},
  year={1967},
  publisher={Taylor \& Francis}
}

@TechReport{Mattner2010,
author = {Mattner, T. W.},
title = {A refined stretched-vortex model for large-eddy simulation of turbulent mixing layers},
institution = {17th Australasian Fluid Mechanics Conference},
year = {2010},
type = {AFMC},
month = {December}
}

@article {Mattner2011,
author = {Mattner, T. W.},
title = {Large-eddy simulations of turbulent mixing layers using the stretched vortex model},
journal = JFM,
year = {2011},
volume = {671},
number = {},
pages = {507--534},
month = {},
note = {}
}

@article {Mazumder2006,
author = {Mazumder, S.},
title = {Critical assessment of the stability and convergence of the equations of multi-component diffusion},
journal = {J. Comput. Phys.},
year = {2006},
volume = {212},
number = {2},
pages = {383--392},
month = {},
note = {}
}

@inproceedings {McArdle2015,
author = {McArdle, P. and Williams, J. and Beavers, A. and and Gao, X.},
title = {A Numerical Model for the Determination of Biomass Ignition from a Hotspot},
booktitle = {Fall Meeting of the Western States Section of the Combustion Institute},
year = {2015},
editor = {},
pages = {},
organization = {},
publisher = {},
address = {},
month = {October},
note = {WSSCI 2015-134IE-0023}
}

@article {McCorquodale2001,
author = {McCorquodale, P. and Colella, P. and Johansen, H.},
title = {A {C}artesian grid embedded boundary method for the heat equation on irregular domains},
journal = JCP,
year = {2001},
volume = {173},
number = {},
pages = {620--635},
month = {},
note = {}
}

@article {McCorquodale2011,
author = {McCorquodale, P. and Colella, P.},
title = {A high-order finite-volume method for conservation laws on locally refined grids},
journal = {Comm.\ App.\ Math.\ Comput.\ Sci.},
year = {2011},
volume = {6},
number = {1},
pages = {1--25},
month = {},
note = {}
}

@article {McCorquodale2015,
author = {McCorquodale, P. and Dorr, M. R. and Hittinger, J. A. F. and Colella, P.},
title = {High-order finite-volume methods for hyperbolic conservation laws on mapped multiblock grids},
journal = JCP,
year = {2015},
month = {May},
number = {288},
pages = {181-195},
doi = {10.1016/j.jcp.2015.01.006}
}

@techreport{Mcbride1993,
  title={Coefficients for calculating thermodynamic and transport properties of individual species},
  author={McBride, Bonnie J and Gordon, Sanford and Reno, Martin A},
  year={1993},
  INSTITUTION = {NASA},
  TYPE={Reference Publication},
  NUMBER={4513}
}

@TECHREPORT{Mcbride1996,
    AUTHOR = {McBride, B. J. and Gordon, S.},
    TITLE = {Computer Program for Calculation of Complex Chemical Equilibrium 
             Compositions and Applications {II}. Users Manual and Program Description},
    INSTITUTION = {NASA},
    TYPE={Reference Publication},
    NUMBER={1311},
    YEAR = {1996}
    }

@PhdThesis{McCann2014,
author = {McCann, B. T.},
type = {{P}h.{D}. dissertation},
title = {A Wall Model for Large-Eddy Simulation of Compressible Channel Flows},
school = {University of Washington},
year = {2014}
}

@article {McEnally2000,
author = {C. S. Mc{E}nally and L. D. Pfefferle and A. M. Schaffer and M. B. Long and R. K. Mohammed and M. D. Smooke and M. B. Colket},
title = {Characterization of a coflowing methane/air non-premixed flame with computer modelling, {R}ayleigh-{R}aman imaging, and on-line mass spectrometry},
journal = {Proc. Combust. Inst.},
year = {2000},
volume = {28},
editor = {},
pages = {2063--2070},
month = {},
note = {}
}

@article {Menard2000,
author = {Menard, R. and Cohn, S. E. and Chang, L.-P. and Lyster, P. M.},
title = {Assimilation of stratospheric chemical tracer observations using a Kalman filter. Part I: Formulation},
journal = {Mon. Wea. Rev.},
year = {2000},
volume = {128},
editor = {},
pages = {2654--2671},
month = {},
note = {}
}

@InProceedings{Meng2010,
author={Meng, Q. and Luitjens, J. and Berzins, M.},
booktitle={2010 3rd Workshop on Many-Task Computing on Grids and Supercomputers},
title={Dynamic task scheduling for the {Uintah} framework},
year={2010},
volume={},
number={},
pages={1-10},
doi={10.1109/MTAGS.2010.5699431},
ISSN={2151-1683},
month={Nov}
}

@article {Menter1993,
author = {Menter, F. R.},
title = {Zonal two equation $k$-$\omega$ turbulence models for aerodynamic flows},
journal = {AIAA Paper 93-2906},
year = {1993},
volume = {},
editor = {},
pages = {},
month = {},
note = {}
}

@article {Merchant1967,
author = {Merchant, D. G. and Pope, R. L.},
title = {The scattering of bomblets by an aerodynamic method},
journal = {Technical Note HSA 126},
year = {1967},
month = {October},
note = {Australian Defence Scientific Service, Weapons Research Establishment, Confidential}
}

@article {Mercier2015,
author = {Mercier, R. and Moureau, V. and Veynante, D. and Fiorina, B.},
title = {{LES} of turbulent combustion: On the consistency between flame and flow filter scales},
journal = {Proceedings of the Combustion Institute},
year = {2015},
volume = {35},
number = {},
pages = {1359--1366},
month = {},
note = {}
}

@article {Mereb1994a,
author = {Mendiara, T. and Glarborg, P.},
title = {},
journal = {Combust. Flame},
year = {2009},
volume = {156},
number = {},
pages = {1937--1949},
month = {},
note = {}
}

@article {Mereb1994b,
author = {Mendiara, T. and Glarborg, P.},
title = {},
journal = {Energ.\ Fuels},
year = {2009},
volume = {23},
number = {},
pages = {3565--3572},
month = {},
note = {}
}

@article {Mereb1994,
author = {Mereb, J. B. and Wendt, J. O. L.},
title = {Air staging and reburning mechanisms for {NO}$_x$ abatement in a laboratory coal combustor},
journal = {Fuel},
year = {1994},
volume = {73},
number = {7},
pages = {1020--1026},
month = {},
note = {}
}

@article {Merlin2012,
author = {Merlin, C. and Domingo, P. and Vervisch, L.},
title = {Immersed boundaries in large eddy simulation of compressible flows},
journal = {Flow Turbul. Combust.},
year = {2012},
volume = {90},
number = {1},
pages = {29--68},
month = {},
note = {}
}

@article{Meshkov1969,
author="Meshkov, E. E.",
title="Instability of the interface of two gases accelerated by a shock wave",
journal="Fluid Dynamics",
year="1969",
volume="4",
number="5",
pages="101--104",
issn="1573-8507",
doi="10.1007/BF01015969",
url="http://dx.doi.org/10.1007/BF01015969"
}

@Misc{Metacomp,
  note =         {\url{http://www.metacomptech.com/}}
}

@article {Meyer1985,
author = {Meyer, C.},
title = {Ore Metals Through Geologic History},
journal = {Science},
year = {1985},
volume = {227},
number = {4693},
pages = {1421--1428},
month = {22 March},
note = {}
}

@article {Meyer2010,
author = {Meyer, M. and Hickel, S. and Adams, N.},
title = {Assessment of implicit large-eddy simulation with a conservative immersed interface method for turbulent cylinder flow},
journal = {Int. J. Heat Fluid Flow},
year = {2010},
volume = {31},
number = {3},
pages = {368--377},
month = {},
note = {}
}

@article{Michalark2009,
author = {Michalak, C. and Ollivier-Gooch, C.},
title = {Accuracy Preserving Limiter for the High-Order Accurate Solution of the Euler Equations},
year = {2009},
issue_date = {December, 2009},
publisher = {Academic Press Professional, Inc.},
address = {USA},
volume = {228},
number = {23},
issn = {0021-9991},
doi = {10.1016/j.jcp.2009.08.021},
journal = {J. Comput. Phys.},
month = {dec},
pages = {8693–8711},
numpages = {19},
keywords = {Compressible flow, High-order accurate, Limiter, Finite-volume method, Unstructured mesh}
}

@techreport {Miller1971,
author = {Miller, M. C.},
title = {An analysis of the dynamic and aerodynamic performance of a self-deploying articulated autorotor decelerator},
institution = {Edgewood Arsenal},
year = {1971},
type = {Technical Report},
number = {EASP 100-108},
address = {},
month = {October},
note = {}
}

@techreport {Miller1976,
author = {Miller, M. C.},
title = {A technique to measure the pressure distribution acting on the surface of a spinning body in a wind tunnel},
institution = {Edgewood Arsenal},
year = {1976},
type = {Technical Report},
number = {ED-TR-76070},
address = {},
month = {September},
note = {}
}

@misc {Miller,
	author = {J. A. Miller},
	title = {Chemical mechanism for methane combustion},
	howpublished = {privately distributed},
	month = {},
	year = {},
	note = {}
	}

@article {Miller2003,
author = {Miller, G.},
title = {Gateways Into Cells Usher in {N}obels},
journal = {Science},
year = {2003},
volume = {302},
number = {5644},
pages = {383--384},
month = {17 October},
note = {}
}

@ARTICLE{MillerTrebotich2012,
author = {G. H. Miller and D. Trebotich}, 
title  = {An Embedded Boundary Method for the Navier-Stokes Equations on a Time-Dependent Domain},
journal = {Communications in Applied Mathematics and Computational Science}, 
volume = 7,
pages = {1-31}, 
year = 2012, 
}

@article {MillerKee1977,
author = {Miller, J. A. and Kee, R. J.},
title = {Chemical Nonequilibrium Effects in Hydrogen-Air Laminar Jet Diffusion Flames},
journal = {J. Phys. Chem.},
year = {1977},
volume = {81},
number = {25},
pages = {2534--2541},
month = {},
note = {}
}

@article {Miller1983,
author = {Miller, J. A. and Smooke, M. D. and Green, R. M. and Kee, R. J.},
title = {Kinetic Modeling of the Oxidation of Ammonia in Flames},
journal = {Combust. Sci. Technol.},
year = {1983},
volume = {34},
number = {},
pages = {149--176},
month = {},
note = {}
}

@article {MillerBowman1989,
author = {Miller, J. A. and Bowman, C. T.},
title = {Mechanism and modeling of nitrogen chemistry in combustion},
journal = {Prog. Energy Combust. Sci.},
year = {1989},
volume = {15},
number = {4},
pages = {287--338},
}

@article {MillerGlarborg1999,
author = {Miller, J. A. and Glarborg},
title = {Modeling the Thermal De-{NO}$_x$ Process: Closing in on a Final Solution},
journal = {Int. J. Chem. Kinet.},
year = {1999},
volume = {31},
number = {},
pages = {757--765},
month = {},
note = {}
}

@article {Millevolte1966,
author = {Millevolte, P. L.},
title = {Dynamic stability of vortex gliders},
journal = {Master's Thesis, University of Minnesota},
year = {1966},
month = {July},
}

@book {Milnor1963,
author = {Milnor, J.},
title = {Morse Theory},
year = {1963},
publisher = {Princeton University Press},
address = {Princeton, NJ}
}

@article {Milton1984,
	author = {Milton, B.E. and Keck, J.C.},
	title = {Laminar burning velocities in stoichiometric hydrogen
 and hydrogen-hydrocarbon gas mixtures},
       journal = {Combust. Flame},
	year = {1984},
	volume = {58},
	number = {},
	pages = {13--22},
	month = {},
	note = {}
	}
@article {Mishra1994,
author = {M. K. Mishra and R. Yetter and Y. Reuvan and H. Rabitz and M. D. Smooke},
title = {},
journal = {Int. J. Chem. Kinet.},
year = {1994},
volume = {26},
number = {},
pages = {437--443},
month = {},
note = {}
}

@article{Misra1997,
author = {Misra, A. and Pullin, D. I.},
title = {A vortex-based subgrid stress model for large-eddy simulation},
journal = PF,
volume = {9},
number = {8},
pages = {2443--2454},
year = {1997},
month = {August}
}

@article{MitaniWilliams:1980,
author = {Mitani, T. and Williams, F. A.},
title = {Studies of Cellular Flames in Hydrogen-Oxygen-Nitrogen Mixtures},
journal = {Combust. Flame},
year = {1980},
volume = {39},
number = {},
pages = {169--190},
month = {},
note = {}
}

@article{Mittal2003,
author = {Mittal, S. and Kumar, B.},
title = {Flow past a rotating cylinder},
journal = {J. Fluid Mech.},
year = {2003},
volume = {476},
number = {},
pages = {303--334},
month = {},
note = {}
}

@article{Mittal2004,
author = {Mittal, S.},
title = {Three-dimensional instabilities in flow past a rotating cylinder},
journal = {Journal of Applied Mechanics},
year = {2004},
volume = {71},
number = {},
pages = {89--95},
month = {January},
note = {}
}

@article{Mittal2005,
author = {Mittal, R. and Iaccarino, G.},
title = {Immersed boundary methods},
journal = {Annu. Rev. Fluid Mech.},
year = {2005},
volume = {37},
number = {},
pages = {239--261},
month = {},
note = {}
}

@article {Mizobuchi2002,
author = {Mizobuchi, Y. and Tachibana, S. and Shinio, J. and Ogawa, S. and Takeno, T.},
title = {A Numerical Analysis of the Structure of a Turbulent Hydrogen Jet Lifted Flame},
journal = {Proc. Combust. Inst.},
year = {2002},
volume = {29},
number = {},
pages = {2009--2015},
month = {},
note = {}
}

@article {Mokhov1997, 
author = {Mokhov, A. V. and Levinsky, H. B. and van~der~Meij, C. E.}, 
title = {Temperature dependence of laser-induced fluorescence of nitric oxide in laminar premixed atmospheric-pressure flames},
journal = {Applied Optics}, 
year = {1997}, 
volume = {36}, 
number = {}, 
pages = {3233--3243},
month = {}, 
note = {} 
}

@article {Mohammed1998,
author = {R. H. Mohammed and M. A. Tanoff and M. D. Smooke and A. M. Schaffer},
title = {Computational and experimental study of a forced, time-varying, axisymmetric, laminar diffusion flame},
journal = {Proc. Combust. Inst.},
year = {1998},
volume = {27},
pages = {693--702}
}

@Unpublished{Mohan2019,
  author =       {Mohan, A. and Daniel, D. and Chertkov, M. and Livescu, D.},
  title =        {Compressed Convolutional LSTM: An Efficient Deep Learning Framework to Model High Fidelity 3D Turbulence},
  note =         {arXiv preprint arXiv:1903.00033.},
  OPTkey =       {},
  OPTmonth =     {},
  OPTyear =      {},
  OPTannote =    {}
}

@article {Moin1982,
author = {Moin, P. and Kim, J.},
title = {Numerical investigation of turbulent channel flow},
journal = {J. Fluid Mechanics},
year = {1982},
volume = {118},
pages = {341--377},
note = {}
}

@article {Mons2014,
author = {Mons, V. and Chassaing, J.-C. and Gomez, T. and Sagaut, P.},
title = {Is isotropic turbulence decay governed by asymptotic behavior of large scales? An eddy-damped quasi-normal Markovian-based data assimilation study},
journal = {Phys. Fluids},
year = {2014},
volume = {26},
pages = {115105},
note = {Published Online: http://aip.scitation.org/doi/10.1063/1.4901448}
}

@article {Mons2016,
author = {Mons, V. and Chassaing, J.-C. and Gomez, T. and Sagaut, P.},
title = {Reconstruction of unsteady viscous flows using data assimilation schemes},
journal = JCP,
year = {2016},
volume = {316},
pages = {255--280},
note = {}
}

@article {Moureau2009,
author = {Moureau, V. and Fiorina, B. and Pitsch, H.},
title = {A level set formulation for premixed combustion {LES} considering the turbulent flame structure},
journal = {Combust. Flame},
year = {2009},
volume = {156},
pages = {801--812},
note = {}
}

@TechReport{Moran1:1977,
  author =       {W. A. Moran},
  title =        {Giromill Wind Tunnel Test and Analysis, Volume 1---Executive Summary},
  institution =  {McDonnell Aircraft Company},
  year =         1977}

@TechReport{Moran2:1977,
  author =       {W. A. Moran},
  title =        {Giromill Wind Tunnel Test and Analysis, Volume 2---Technical Discussion},
  institution =  {McDonnell Aircraft Company},
  year =         1977}
  
@article{Morshed2013,
author = {Morshed, Khandakar Niaz and Venayagamoorthy, Subhas Karan and Dasi, Lakshmi Prasad},
title = {Intermittency and local dissipation scales under strong mean shear},
journal = PF,
year = {2013},
volume = {25},
number = {1}, 
}

@article{Motheau2017,
author = {Motheau, Emmanuel and Almgren, Ann and Bell, John B.},
title = {{N}avier-{S}tokes Characteristic Boundary Conditions Using Ghost Cells},
journal = {AIAA Journal},
volume = {55},
number = {10},
year = {2017}
}

@article{Moore2014,
author = {Moore B. and Dasi L.P.},
title = {Spatiotemporal complexity of the aortic sinus vortex},
journal = {Experiments in fluids},
volume = {55},
number = {},
pages = {1--12},
year = {2014}
}

@article{Moore2015,
author = {Moore B. and Dasi L.P.},
title = {Coronary Flow Impacts Aortic Leaflet Mechanics and Aortic Sinus Hemodynamics},
journal = {Annals of biomedical engineering},
volume = {43},
number = {},
pages = {2231--2241},
year = {2015}
}

@ARTICLE{Morzfeld2015,
AUTHOR = {M. Morzfeld and X. Tu and J. Wilkening and A. Chorin},
TITLE = {Parameter estimation by implicit sampling},
JOURNAL = {Commun. Appl. Math. Comput. Sci.},
  FJOURNAL = {CAMCOS},
    VOLUME = {10},
      YEAR = {2015},
     PAGES = {205--225}
}

@InProceedings{Moser2001,
  author =       {Moser, R. D. and Langford, J.A. and Volker, S.},
  title =        {A radical approach to large eddy simulation},
  booktitle =    {AIAA},
  year =         2001,
  number =       {98-2290}
}

@article {Most2002,
author = {Most, D. and Dinkelacker, F. and Leipertz, A.},
title = {Lifted reaction zones in premixed turbulent bluff-body stabilized flames},
journal = {Proc. Combust. Inst.},
year = {2002},
volume = {29},
number = {},
pages = {1801--1806},
month = {},
note = {}
}

@article{MuellerETAL:1998,
  author = {J. Mueller and  J.F. Driscoll and  D.L. Reuss and  M.C. Drake and
M.  Rosalik },
 title = {Vorticity generation and attenuation as vortices convect through a
premixed flame},
 journal = {Combust. Flame}, 
 volume = 112,
 year = 1998,
 pages = {342-358}
}

@article {Muller1981, 
author = {M\"uller-Dethlefs, K. and Peleat, M. and Taran, J.-P.}, 
title = {Temperature and Hydrogen Concentration Measurements by {CARS} in an Ethylene-Air-Bunsen Flame}, 
journal = {Ber. Bunsenges. Phys. Chem.}, 
year = {1981}, 
volume = {85}, 
number = {9}, 
pages = {803--807}, 
note = {}
}

@article {Mueller1995,
author = {Mueller, C. J. and Driscoll, J. F. and Sutkus, D. J. and Roberts, W. L. and Drake, M. C. and Smooke, M. D.},
title = {Effects of unsteady stretch rate on {OH} chemistry during a flame-vortex interaction: {T}o assess flamelet models},
journal = {Combust. Flame},
year = {1995},
volume = {100},
pages = {323--331},
}

@article{Mueller1996,
author = {Mueller, C. J. and Driscoll, J. F. and Reuss, D. L. and Drake, M. C.},
title = {Effect of unsteady stretch on the strength of a freely-propagating flame wrinkled by a vortex},
volume = {26},
year = {1996},
pages = {347--355},
journal = {Proc. Combust. Inst.}
}

@article {Mueller1998,
author = {Mueller, C. J. and Driscoll, J. F. and Reuss, D. L. and Drake, M. C. and Rosalik, M. E.},
title = {Vorticity generation and attenuation as vortices convect through a premixed flame},
journal = {Combust. Flame},
year = {1998},
volume = {112},
number = {3},
pages = {342--358}
}

@article{Muralidharan2016,
  author = {Muralidharan, B. and Menon, S.},
  title = {A high-order adaptive {C}artesian cut-cell method for simulation of compressible viscous flow over immersed bodies},
  journal = JCP,
  year = {2016},
  volume = {21},
  pages = {342--368}
}

@InProceedings{Murman2016,
author       = {Murman, S. M. and Diosady, L. T. and Garai, A. and Ceze, M.},
title        = {A Space-Time Discontinuous-Galerkin Approach for Separated Flows},
booktitle    = {54th AIAA Aerospace Sciences Meeting},
year         = {2016},
number       = {2016-1059},
organization = {AIAA SciTech Forum}
}

@article {Murphy2012,
author = {Murphy, A.},
title = {Transport coefficients of plasmas in mixtures of nitrogen and hydrogen},
journal = {Chemical Physics},
year = {2012},
volume = {},
number = {398},
pages = {64--72}
}

@article {Mukhopadhyay2003,
author = {Mukhopadhyay, A. and Puri, I. K.},
title = {An assessment of stretch effects on a flame tip using the thin flame and thick flame formulations},
journal = {Combust. Flame},
year = {2003},
volume = {133},
number = {},
pages = {499--502},
month = {},
note = {}
}

@article {Muzychka2010,
author = {Muzychka, Y.S. and Yovanovich, M.M.},
title = {Unsteady viscous flows and Stoke's first problem},
journal = {International Journal of Thermal Sciences},
year = {2010},
volume = {49},
number = {},
pages = {820--828},
month = {},
note = {}
}

   #    #
   ##   #
   # #  #
   #  # #
   #   ##
   #    #
   #    #

@article {Najafi-Yazdi2015,
author = {Najafi-Yazdi, A. and Najafi-Yazdi, M. and Mongeau, L.},
title = {A high resolution differential filter for large eddy simulation: Toward explicit filtering on unstructured grids},
journal = {J. Comput. Phys.},
year = {2015},
volume = {292},
number = {},
pages = {272--286},
month = {July},
note = {}
}

@article {NajmKnio1998,
author = {Najm, H. N. and Knio, O. M. and Paul, P. H. and Wyckoff, P. S.},
title = {A Study of Flame Observables in Premixed Methane-Air Flames},
journal = {Combust. Sci. Technol.},
year = {1998},
volume = {140},
number = {},
pages = {369--403},
month = {},
note = {}
}

@article {NajmPaul1998,
author = {Najm, H. N. and Paul, P. H. and Mueller, C. J. and Wyckoff, P. S.},
title = {On the Adequacy of Certain Experimental Observables as Measurements of Flame Burning Rate},
journal = {Combust. Flame},
year = {1998},
volume = {113},
number = {3},
pages = {312--332},
month = {},
note = {}
}

@techreport {NajmSchefer1998,
author = {Najm, H. N. and Schefer, R. W. and Milne, R. B. and Mueller, C. J. and Devine, K. D. and Kempka, S. N.},
title = {Numerical and experimental investigation of vortical flow--flame interaction},
institution = {Sandia National Laboratory},
number = {SAND98-8232},
month = feb,
year = {1998}
}

@article {NajmWyckoff1997,
author = {Najm, H. N. and Wyckoff, P. S.},
title = {Premixed Flame Response to Unsteady Strain Rate and Curvature},
journal = {Combust. Flame},
year = {1997},
volume = {110},
number = {1--2},
pages = {92--112},
month = {},
note = {}
}

@article {NajmWyckoff1998,
author = {H. N. Najm and P. S. Wyckoff and O. M. Knio},
title = {A semi-implicit numerical scheme for reacting flow. {I}. {S}tiff Chemistry},
journal = {J. Comput. Phys.},
volume = 143,
pages = {381--402},
year = {1998}
}

@article {Nakahara2009,
author = {M. Nakahara and T. Shirasuna and J. Hashimoto},
title = {Experimental study on local flame properties of hydrogen added hydrocarbon premixed turbulent flames},
journal = {J. Therm. Sci. Technol.},
volume = {4},
pages = {190--201},
year = {2009}
}

@article {Namazian1994, 
author = {Namazian, M. and Kelly, J. and Schefer, R.},
title = {Simultaneous {NO} and temperature imaging measurements in turbulent nonpremixed flames}, 
journal = {Proc. Combust. Inst.}, 
year = {1994}, 
volume = {25}, 
number = {}, 
pages = {1149--1157}, 
month = {}, 
note = {} 
}

@misc{blanco2014nanoflann,
  title        = {nanoflann: a {C}++ header-only fork of {FLANN}, a library for Nearest Neighbor ({NN}) with KD-trees},
  author       = {Blanco, Jose Luis and Rai, Pranjal Kumar},
  howpublished = {\url{https://github.com/jlblancoc/nanoflann}},
  year         = {2014}
}

@article {Nastac2017, 
author = {Nastac, G. and Labahn, W. and Magri, L. and Ihme, M.},
title = {Lyapunov exponent as a metric for assessing the dynamic content and predictability of large-eddy simulations}, 
journal = {Phys. Rev. Fluids}, 
year = {2017}, 
volume = {2}, 
number = {}, 
pages = {094606}, 
month = {}, 
note = {} 
}

@article {NguyenPaul1996,
author = {Nguyen, Q.-V. and Paul, P. H.},
title = {The Time Evolution of a Vortex-Flame Interaction Observed via Planar Imaging of {CH} and {OH}},
journal = {Proc. Combust. Inst.}, 
volume = {26},
year = {1996},
pages = {357--364}
}

@article {Nishioka1994,
author = {Nishioka, M. and Nakagawa, S. and Ishikawa, Y. and Takeno, T.},
title = {{NO} Emission Characteristics of Methane-Air Double Flame},
journal = {Combust. Flame},
year = {1994},
volume = {98},
number = {},
pages = {127--138},
month = {},
note = {}
}

@article {Nishioka1996,
author = {M. Nishioka and Y. Takemoto and H. Yamashita and T. Takeno},
title = {Effects of multi-dimensionality on a diffusion flame},
journal = {Proc. Combust. Inst.}, 
year = {1996},
volume = {26},
pages = {1071--1077}
}

@Book{Nocedal2006,
  author =    {Nocedal, J. and Wright, S. J.},
  ALTeditor =    {},
  title =        {Numerical Optimization},
  publisher =    {Springer},
  year =         {2006},
  OPTkey =       {},
  OPTvolume =    {},
  OPTnumber =    {},
  OPTseries =    {},
  OPTaddress =   {},
  OPTedition =   {},
  OPTmonth =     {},
  OPTnote =      {},
  OPTannote =    {}
}

@article {Noda2000,
author = {Noda, S. and Harano, A. and Hashimoto, M. and Sadakata, M.},
title = {Development of Selective Noncatalytic Reduction by Ammonia in the Presence of Phenol},
journal = {Combust. Flame},
year = {2000},
volume = {122},
number = {},
pages = {439--450},
month = {},
note = {}
}

@Manual{NPARC-VnV,
  title =        {Tutorial on CFD Verification and Validation},
  organization = {NPARC Alliance},
  url =          {https://www.grc.nasa.gov/WWW/wind/valid/tutorial/tutorial.html}}

@Manual{nvidia_k20,
  title =        {Telsa K20 GPU Accelerator},
  organization = {Nvidia},
  month =        {July},
  year =         2013,
  note =         {\url{http://www.nvidia.com/content/PDF/kepler/Tesla-K20-Passive-BD-06455-001-v07.pdf}}
}

   #   #
   #   #
   #   #
   #   #
   #   #
    ###

@techreport {Oberlack1997,
author = {Oberlack, M.},
title = {Invariant modeling in large-eddy simulation of turbulence},
year = {1997},
type = {Annual Research Briefs},
institution = {Center for Turbulence Research},
number = {},
address = {},
month = {},
note = {} 
}

@techreport {Ochs2009,
author = {Ochs, R.},
title = {Development of a next-generation burner for use in testing thermal acoustic insulation burnthrough resistance},
year = {2009},
type = {Technical Report},
number = {DOT/FAA/AR-TN09/23},
address = {},
month = {},
note = {} 
} 

@article {OConnaire2004,
author = {M. O'Connaire and H. J. Curran and J. M. Simmie and W. J. Pitz and C. K. Westbrook},
title = {A Comprehensive Modeling Study of Hydrogen Oxidation},
journal = {Int. J. Chem. Kinet.},
year = {2004},
volume = {36},
number = {},
pages = {603--622},
month = {},
note = {}
}

@article {Oijen2005,
author = {Oijen, J. A. van and Groot, G. R. A. and Bastiaans, R. J. M. and de Goey, L. P. H.},
title = {A Flamelet Analysis of the Burning Velocity of Premixed Turbulent Expanding Flames},
journal = {Proc. Combust. Inst.},
year = {2005},
volume = {30},
number = {1},
pages = {657--664}
}

@article {OijenGoey2000,
author = {Oijen, J. A. van and de Goey, L. P. H.},
title = {Modelling of Premixed Laminar Flames using Flamelet-Generated Manifolds},
journal = {Combust. Sci. Technol.},
year = {2000},
volume = {161},
number = {},
pages = {113--137},
month = {},
note = {}
}

@article {OijenGoey2002,
author = {Oijen, J. A. van and de Goey, L. P. H.},
title = {Modelling of premixed counterflow flames using the flamelet-generated manifold method},
journal = {Combust. Theory Model.},
year = {2002},
volume = {6},
number = {},
pages = {463--478},
month = {},
note = {}
}

@article {Oke2007,
author = {Oke, P. R. and Sakov, P. and Corney, S. P.},
title = {Impacts of localisation in the EnKF and EnOI: experiments with a small model},
journal = {Ocean Dynamics},
year = {2007},
volume = {57},
number = {},
pages = {32--45},
month = {},
note = {}
}

@InProceedings{Olschanowsky2014,
author =       {Olschanowsky, C. and Strout, M. M. and Guzik, S. and Loffeld, J. and Hittinger, J.},
title =        {A study on balancing parallelism, data locality, and recomputation in existing {PDE} solvers},
booktitle =    {Supercomputing},
year =         2014
}

@misc{OpenMP-4.0,
  Author = {OpenMP Architecture Review Board},
  Title = {{OpenMP} Application Program Interface, Version 4.0},
  Month = {July},
  Year = {2015},
  url = {http://www.openmp.org/mp-documents/OpenMP4.0.0.pdf}
}

@misc{OpenMP-4.5,
  author = {OpenMP Architecture Review Board},
  title = {{OpenMP} Application Program Interface, Version 4.5},
  month = {November},
  year = {2015},
  url = {http://www.openmp.org/wp-content/uploads/openmp-4.5.pdf}
}

@Book{Oran2005,
  author =       {Oran, E. and Boris, J.},
  title =        {Numerical Simulation of Reactive Flows},
  publisher =    {Cambridge University Press: Cambridge},
  year =         {2005} 
}

@article {Örley2015,
author = {Örley,  F. and Pasquariello, V. and Hickel, S. and Adams, N.},
title = {Cut-element based immersed boundary method for moving geometries in compressible liquid flows with cavitation},
journal = {J. Comput. Phys.},
year = {2015},
volume = {283},
number = {},
pages = {1--2},
month = {},
note = {}
}

@article{Overton2017,
  author =       {Overton, N. and Gao, X. and Guzik, S.},
  title =        {Spline Interpolation for A Fourth-Order Adaptive Mesh Refinement Algorithm on Arbitrary Mapped Grids},
  booktitle =    {23rd AIAA Computational Fluid Dynamics Conference},
  year =         {2017},
  number =       {3107},
  organization = {AIAA Aviation Forum},
  note =         {\url{https://doi.org/10.2514/6.2017-3107}}
}

@article{Overton2020,
  author = {Overton-Katz, N. and Gao, X. and Guzik, S.},
  title = {Applying High-Order, Adaptively-Refined, Finite-Volume Methods to Discrete Structured Representations of Arbitrary Geometry},
  booktitle = {2020 AIAA SciTech Forum},
  year = {2020},
  number = {1310},
  organization = {AIAA SciTech Forum},
  doi = {10.2514/6.2020-1310}
}

@unpublished{Overton2021a,
author = {Overton-Katz, N. and Johansen, H. and Gao, X. and Guzik, S. M.},
title = {Adaptive Clipping-and-Redistribution Algorithms for Bounded and Conservative High-Order Interpolations Applied to Discontinuous and Reactive Flows},
note = {Manuscript under revision},
journal = JCP,
year = {2021}
}

@unpublished{Overton2021b,
author = {Overton-Katz, N. and Gao, X. and Guzik, S. M.},
title = {Mapped Multi-Block Grids of Arbitrary Geometry for High-Order Finite-Volume Methods with Adaptive Mesh Refinement},
note = {Manuscript in progress for submission in Computers and Mathematics with Application},
year = {2021}
}

@article{Overton2022a,
author = {Overton-Katz, N. and Gao, X. and Guzik, S. M. and Antepara, O. and Graves, D. T. and Johansen, H.},
title = {Towards a High-Order Embedded Boundary Finite Volume Method for the Incompressible {N}avier-{S}tokes Equations with Complex Geometries},
booktitle = {AIAA SCITECH 2022 Forum},
chapter = {},
pages = {},
doi = {10.2514/6.2022-2202}
}

@article{Owen2015,
author = {Owen, L. D. and Guzik, S. M. and Gao, X.},
title = {High-Order {CFD} Modeling of Multispecies Flows},
booktitle = {Fall Meeting of the Western States Section of the Combustion Institute},
year = {2015},
editor = {},
pages = {},
organization = {},
publisher = {},
address = {},
month = {October},
note = {WSSCI 2015-134IE-0030}
}

@article{Owen2016,
author = {Owen, L. D. and Guzik, S. M. and Gao, X.},
title = {Fourth-Order Viscous Operator on Mapped Grids},
booktitle = {54th AIAA Aerospace Sciences Meeting},
year = {2016},
number={AIAA 2016-0604},
organization={AIAA SciTech Forum},
OPTurl = {https://doi.org/10.2514/6.2016-0604}
}

@article{Owen2017,
  author =       {Owen, L. and Guzik, S. and Gao, X.},
  title =        {A Fourth-Order Finite-Volume Algorithm for Compressible Flow with Chemical Reactions on Mapped Grids},
  booktitle =    {23rd AIAA Computational Fluid Dynamics Conference},
  year =         {2017},
  number =       {AIAA 2017-4498},
  organization = {AIAA Aviation Forum},
  doi = {10.2514/6.2017-4498},
  OPTurl = {https://doi.org/10.2514/6.2017-4498}
}

@article{Owen2018,
author = {Owen, L. D. and Guzik, S. M. and Gao, X.},
title = {A high-order adaptive algorithm for multispecies gaseous flows on mapped domains},
journal = {Comput. Fluids},
volume = {170},
pages = {249--260},
year = {2018},
issn = {0045-7930},
OPTdoi = {https://doi.org/10.1016/j.compfluid.2018.05.010},
OPTurl = {http://www.sciencedirect.com/science/article/pii/S0045793018302536},
keywords = {High-order finite-volume method, Nonlinear {PDE}s, Adaptive-mesh refinement, Compressible multispecies flows}
}

@PhdThesis{Owen2019a,
author = {Owen, L. D.},
type = {{P}h.{D}. dissertation},
title = {A Fourth-Order Solution-Adaptive Finite-Volume Algorithm for Compressible Reacting Flows on Mapped Domains},
school = {Colorado State University},
year = {2019}
}

@unpublished{Owen2019b,
author = {Owen, L. D. and Gao, X. and Guzik, S. M.},
title = {Stability techniques for a fourth-order finite-volume algorithm solving shocks and detonations},
note = {Accepted for publication in Journal of Computational Physics},
year = {2019} 
}

@unpublished{Owen2019c,
author = {Owen, L. D. and Gao, X. and Guzik, S. M.},
title = {Modeling oblique cellular detonation with an adaptive fourth-order finite-volume algorithm},
note = {Manuscript submitted for publication in Phys. Fluids},
year = {2019} 
}

@article{Owen2020,
  author =       {Owen, L. D. and Gao, X. and Guzik, S. M.},
  title =        {Techniques for improving monotonicity in a fourth-order finite-volume algorithm solving shocks and detonations},
  journal = JCP,
  year =         {2020},
  volume = {415}
}


   ####
   #   #
   #   #
   ####
   #
   #
   #


@article {Pallickara2012, 
author = {Pallickara, S. L. and Pallickara, S. and Zupanski, M.}, 
title = { Towards efficient data search and subsetting of large-scale atmospheric datasets}, 
journal = {Future Gener. Comp. Sy.}, 
year = {2012}, 
volume = {28}, 
number = {},
pages = {112--118}, 
month = {}, 
note = {} 
}

@article {Papageorgiou1991, 
author = {Papageorgiou, D. and Smyrlis, Y.}, 
title = {The Route to Chaos for the {K}uramoto-{S}ivashinsky Equation}, 
journal = {Theoret. Comput. Fluid Dynamics}, 
year = {1991}, 
volume = {3}, 
number = {},
pages = {15--42}, 
month = {}, 
note = {} 
}

@article {Pantano2002, 
author = {Pantano, C. and Sarkar, S.}, 
title = {A study of compressibility effect in the high-speed turbulent shear layer using direct simulation}, 
journal = {J. Fluid Mech.}, 
year = {2002}, 
volume = {451}, 
number = {},
pages = {329--371}, 
month = {}, 
note = {} 
}

@Book{Panton1996,
  author =       {Ronald L. Panton},
  title =        {Incompressible flow},
  publisher =    {John Wiley \& Sons, Inc.},
  year =         1996,
  address =      {New York},
  edition =      {2nd}
}

@article {Papadakis2008, 
author = {Papadakis, N. and M{\'e}min, E.}, 
title = {A Variational Technique for Time Consistent Tracking of Curves and Motion}, 
journal = {Journal of Mathematical Imaging and Vision}, 
year = {2008}, 
volume = {31}, 
number = {},
pages = {81--103}, 
month = {}, 
note = {} 
}

@article {Papadakis2010, 
author = {Papadakis, N. and M{\'e}min, E. and Cuzol, A. and Gengembre, N.}, 
title = {Data assimilation with the weighted ensemble Kalman filter}, 
journal = {Tellus A}, 
year = {2010}, 
volume = {62}, 
number = {},
pages = {673--697}, 
month = {}, 
note = {} 
}

@article {Park2015,
author = {Park, S. K. and Lim, S. and Zupanski, M.},
title = { Structure of forecast error covariance in coupled atmosphere-chemistry data assimilation},
journal = {Geoscientific Model Development},
year = {2015},
volume = {8},
number = {},
pages = {1315--1320},
month = {},
note = {}
}


@article {Parkinson1964,
author = {Parkinson, G. V.},
title = {On the performance of Lanchester's "aerial tourbillion"},
journal = {Journal of the Royal Aeronautical Society},
year = {1951},
volume = {68},
number = {644},
pages = {561-564},
month = {},
note = {}
}


@article {Parrish1992, 
author = {Parrish, D. F. and Derber, J. C.}, 
title = {The National Meteorological Center's Spectral Statistical Interpolation Analysis System}, 
journal = {Mon. Wea. Rev.}, 
year = {1992}, 
volume = {120}, 
number = {},
pages = {1747-1763}, 
month = {}, 
note = {} 
}


@InProceedings{Pascucci2007,
author =      {Pascucci, V. and Scorzelli, G. and Bremer, P.-T. and Mascarenhas, A.},
title =       {Robust on-line computation of reeb graphs: Simplicity and speed},
booktitle =   {ACM Transactions on graphics: ACM SIGGRAPH 2007 Papers},
year =        2007
}

@article {PaulGray1993, 
author = {Paul, P. H. and Gray, J. A. and Durant, Jr., J. L. and Thoman Jr., J. W.}, 
title = {A model for temperature-dependent collisional quenching of {NO} {A}$^2$ ${\Sigma}^+$}, 
journal = {Appl. Phys. B}, 
year = {1993}, 
volume = {57}, 
number = {},
pages = {249--259}, 
month = {}, 
note = {} 
}

@article {Paul1997, 
author = {Paul, P. H.}, 
title = {Calculation of transition frequencies and rotational line strengths in the $\gamma$-bands of nitric oxide},
journal = {J. Quant. Spectrosc. Radiat. Transfer}, 
year = {1997}, 
volume = {57}, 
number = {}, 
pages = {581--589}, 
month = {}, 
note = {} 
}

@article {Paul1998,
author = {Paul, P. H. and Warnatz, J.},
title = {A Re-Evaluation of the Means Used to Calculate Transport Properties of Reacting Flows},
journal = {Proc. Combust. Inst.},
year = {1998},
volume = {27},
number = {},
pages = {495--504},
month = {},
note = {}
}

@InProceedings   {Paxton2019,
author =         {Paxton, B. and Fugger, C. and Rankin, B. and Caswell, A.},
title =	         {Development and characterization of an experimental arrangement for studying bluff-body-stabilized turbulent premixed propane-air flames},
publisher =      {AIAA Scitech 2019 Forum},
number =         {AIAA 2019-0118},
month =	         Jan,
year =           {2019},
note =           {\url{https://doi.org/10.2514/6.2019-0118}}
}

@article {Phares2013,
author = {Phares, C. L. and Blanquart, G.},
title = {A proposed modification to Lundgren’s physical space velocity forcing method for isotropic turbulence},
journal = PF,
year = {2013},
volume = {25}
}

@article{Peer2008,
title = {A new fourth-order non-oscillatory central scheme for hyperbolic conservation laws},
journal = {Appl. Numer. Math.},
volume = {58},
number = {5},
pages = {674--688},
year = {2008},
issn = {0168-9274},
OPTdoi = {https://doi.org/10.1016/j.apnum.2007.02.004},
OPTurl = {http://www.sciencedirect.com/science/article/pii/S016892740700044X},
author = {Peer, A. A. I. and Gopaul, A. and Dauhoo, M. Z. and Bhuruth, M.},
}

@article {PemberHowell1998,
author = {Pember, R. B. and Howell, L. H. and Bell, J. B. and Colella, P. and Crutchfield, W. Y. and Fiveland, W. A. and Jessee, J. P.},
title = {An adaptive projection method for unsteady, low-{M}ach number combustion},
journal = {Combust. Sci. Technol.},
volume = {140},
pages = {123--168},
year = {1998}
}

@InProceedings {Pember1993,
author = {Pember, R. B. and Bell, J. B. and Colella, P. and Crutchfield, W. Y. and Welcome, M. W.},
title =	{Adaptive {C}artesian grid methods for representing geometry in inviscid compressible flow},
booktitle = {Proceedings of the Eleventh AIAA Computational Fluid Dynamics Conference},
pages =	{948--958},
publisher = {AIAA},
month =	jun,
year = {1993}
}

@article {Pember1995,
author = {Pember, R. B. and Bell, J. B. and Colella, P. and Crutchfield, W. Y. and Welcome, M. W.},
title =	{An adaptive {C}artesian grid method for unsteady compressible flow in irregular regions},
volume = {120},
year = {1995},
journal = JCP,
pages = {278--304}
}

@article{Peskin1977,
title = {Numerical analysis of blood flow in the heart},
journal = {Journal of Computational Physics},
volume = {25},
number = {3},
pages = {220-252},
year = {1977},
issn = {0021-9991},
doi = {https://doi.org/10.1016/0021-9991(77)90100-0},
author = {Peskin, C.},
}

@article {Peskin2002,
author = {Peskin, C.},
title = {The immersed boundary method},
volume = {},
year = {2002},
journal = {Acta Numerica},
pages = {479--527}
}

@article {Peters2009,
author = {Peters, N.},
title = {Multiscale combustion and turbulence},
volume = {32},
year = {2009},
journal = {Proc. Combust. Inst.},
pages = {1--25}
}

@article {Peters1986,
author = {Peters, N.},
title = {Laminar flamelet concepts in turbulent combustion},
volume = {21},
year = {1986},
journal = {Proc. Combust. Inst.},
pages = {1231--1250}
}

@article {Peters1999,
author = {Peters, N.},
title = {The turbulent burning velocity for large-scale and small-scale turbulence},
journal = {J. Fluid Mech.},
year = {1999},
volume = {384},
number = {},
pages = {107--132},
month = {},
note = {}
}


@Book{Peters2000,
author = {Peters, N.},
title = {Turbulent Combustion},
publisher = {Cambridge University Press},
address = {Cambridge},
edition = {},
year = {2000}
}

@article {PetersenEmmons1961,
author = {Petersen, R. E. and Emmons, H. W.},
title = {Stability of Laminar Flames},
journal = {Phys. Fluids},
year = {1961},
volume = {4},
number = {4},
pages = {456--464},
month = {},
note = {}
}

@article {Petersen2010,
author = {Petersen, M. R. and Livescu, D.},
title = {Forcing for statistically stationary compressible isotropic turbulence},
journal = PF,
year = {2010},
volume = {22},
number = {},
pages = {116101},
month = {},
note = {}
}

@PhdThesis{Petrie2008,
  author =       {Petrie, R. E.},
  title =        {Localization in the ensemble Kalman Filter},
  school =       {University of Reading},
  year =         {2008},
  address =   {Department of Meteorology},
  month =     {August}
}


@article {Petrov1995,
author = {Petrov, C. and Ghoniem, A.},
title = {The transient response of strained laminar-premixed flames},
journal = {Combust. Flame},
year = {1995},
volume = {102},
pages = {401--417}
}

@TechReport{petsc-user-ref,
  Author = {S. Balay and S. Abhyankar and M. F. Adams and J. Brown and P. Brune
            and K. Buschelman and L. Dalcin and V. Eijkhout and W. D. Gropp
            and D. Kaushik and M. G. Knepley and D. A. May and L. Curfman McInnes
            and R. T. Mills and T. Munson and K. Rupp and P. Sanan
            and B. F. Smith and S. Zampini and H. Zhang and H. Zhang},
  Title = {{PETS}c Users Manual},
  Number = {ANL-95/11 - Revision 3.9},
  Institution = {Argonne National Laboratory},
  Year = {2018}
}

@InProceedings{petsc-efficient,
  Author = {Balay, S. and Gropp, W. D. and Curfman McInnes, L.  and Smith, B. F.},
  Title = {Efficient Management of Parallelism in Object Oriented Numerical Software Libraries},
  Booktitle = {Modern Software Tools in Scientific Computing},
  Editor = {E. Arge and A. M. Bruaset and H. P. Langtangen},
  Pages = {163--202},
  Publisher = {Birkh{\"{a}}user Press},
  Year = {1997}
}

@Article{slepc,
   author  = "Hernandez, V. and Roman, J. and Vidal, V.",
   title   = "{SLEPc}: A scalable and flexible toolkit for the solution of eigenvalue problems",
   journal = "ACM Trans. Math. Software",
   volume  = "31",
   number  = "3",
   pages   = "351--362",
   year    = "2005"
} 

@article {Pfefferle1986,
author = {Pfefferle, L. D. and Churchill, S. W.},
title = {{NO$_x$ Production from the Combustion of Ethane Doped with Ammonia in a Thermally Stabilized Plug Flow Burner}},
journal = {Combust. Sci. Techn.},
volume = {49},
pages = {235--249},
year = {1986}
}

@article {Phenix1998,
author = {Phenix, B. D. and Dinaro, J. L. and Tatang, M. A. and Tester, J. W. and Howard, J. B. and Mcrae, G. J.},
title = {Incorporation of Parametric Uncertainty into Complex Kinetic Mechanisms: Application to Hydrogen Oxidation in Supercritical Water},
journal = {Combust. Flame},
year = {1998},
volume = {112},
number = {1--2},
pages = {132--146},
month = {},
note = {}
}

@article {Patnaik1989,
	author = {Patnaik, G. and Kailasanath, K. and Laskey, K. J. and Oran,
E. S.},
	title = {Detailed Numerical Simulations of Cellular Flames},
 journal = {Proc. Combust. Inst.},
	year = {1989},
	volume = {22},
	number = {},
	pages = {1517--1526},
	month = {},
	note = {}
	}

@book{Piegl1997,
 author = {Piegl, Les and Tiller, Wayne},
 title = {The NURBS Book (2Nd Ed.)},
 year = {1997},
 publisher = {Springer-Verlag New York, Inc.},
 address = {New York, NY, USA},
}

@article{Pilgrim2011,
author  = {Pilgrim, T. and Wenaweser, P. and Meuli, F. and Huber, C. and Stortecky, S. and Seiler, C. and Zbinden, S. and Meier, B. and Carrel, T. and Windecker, S.},
title   = {Clinical Outcome of High-Risk Patients with Severe Aortic Stenosis and Reduced Left Ventricular Ejection Fraction Undergoing Medical Treatment or TAVI},
journal = {PLoS ONE},
volume  = {6},
number  = {},
year    = {2011},
month   = {},
pages   = {}
}

@article{Pilgrim2012,
author = {Pilgrim, T. and Kalesan, B. and Wenaweser, P. and Huber, C. and Stortecky, S. and Buellesfeld, L. and Khattab, A.A. and Eberle, B. and Gloekler, S. and Gsponer, T. and Meier, B. and Juni, P. and Carrel, T. and Windecker, S.},
title = {Predictions of clinical outcomes in patients with severe aortic stenosis undergoing TAVI: a multistate analysis},
journal = {Circulation Cardiocascular interventions},
volume = {5},
number = {},
pages = {856-861},
year = {2012},
}

@article {Pitsch2002,
author = {Pitsch, H. and Duchamp De Lageneste, L.},
title = {Large-Eddy simulation of premixed turbulent combustion using a level-set approach},
journal = {Proc. Combust. Inst.},
year = {2002},
volume = {},
number = {},
pages = {2001--2008},
month = {},
note = {}
}
@article {Pitsch2005,
author = {Pitsch, H.},
title = {A consistent level set formulation for large-eddy simulation of premixed turbulent combustion},
journal = {Combust. Flame},
year = {2005},
volume = {143},
number = {4},
pages = {587--598},
month = {},
note = {}
}


@InCollection{Pitsch2014,
  author =       {Pitsch, H.},
  title =        {Modeling Turbulent Combustion},
  booktitle =    {{CEFRC} Combustion Summer School},
  OPTcrossref =  {},
  OPTkey =       {},
  OPTpublisher = {},
  year =      {2014},
  OPTeditor =    {},
  OPTvolume =    {},
  OPTnumber =    {},
  OPTseries =    {},
  OPTtype =      {},
  OPTchapter =   {},
  OPTpages =     {},
  OPTedition =   {},
  OPTmonth =     {},
  OPTaddress =   {},
  OPTnote =      {},
  OPTannote =    {}
}

@article {Platou1961,
author = {Platou, A. S.},
title = {The magnus force on a rotating cylinder in transonic cross flow},
journal = {BRL Report 1150},
year = {1961},
note = {Ballistic Research Laboratories}
}

@article {Pogorelov2015,
author = {Pogorelov, A.M.M. and Schröder, W.},
title = {Cut-cell method based large-eddy simulation of tip-leakage flow},
journal = {Phys. Fluids},
year = {2015},
volume = {27},
number = {},
pages = {},
month = {},
note = {}
}

@InProceedings{Polak2018,
  author =       {Polak, S. and Gao, X.},
  title =        {A Fourth-Order Finite-Volume Method with Adaptive Mesh Refinement for the Multifluid Plasma Model},
  booktitle = {2018 AIAA Aerospace Sciences Meeting},
  year =      2018,
  number =    {AIAA 2018-2195},
  organization = {AIAA SciTech Forum},
  note =      {\url{https://doi.org/10.2514/6.2018-2195}}
}

@article {Pope1990,
author = {Pope, S. B.},
title = {Computations of turbulent combustion: Progress and Challenges},
journal = {Proc. Combust. Inst.},
year = {1990},
volume = {},
number = {},
pages = {591--612},
month = {},
note = {}
}

@article {Pope2012,
author = {Pope, S. B.},
title = {Small scales, many species and the manifold challenges of turbulent combustion},
journal = {Proc. Combust. Inst.},
year = {2012},
volume = {34},
number = {},
pages = {1--31},
month = {},
note = {}
}

@article {Popov2014,
author = {Popov, P. P. and Pope, S. B.},
title = {Large Eddy Simulation/Probability Density Function Simulations of Bluff Body Stabilized Flames},
journal = {Combust. Flame},
year = {2014},
volume = {161},
number = {},
pages = {3100--3133},
month = {},
note = {}
}



@article {Poinsot1990,
author = {Poinsot, T. and Veynante, D. and Candel, S.},
title = {Diagrams of premixed turbulent combustion based on direct simulation},
journal = {Proc. Combust. Inst.},
year = {1990},
volume = {23},
number = {},
pages = {613--619},
month = {},
note = {}
}

@article {Poinsot1992,
author = {Poinsot, T. and Echekki, T. and Mungal, M. G.},
title = {A Study of the Laminar Flame Tip and Implications for Premixed Turbulent Combustion},
journal = {Combustion Science and Technology},
year = {1992},
volume = {81},
number = {},
pages = {45--73},
month = {},
note = {}
}

@article {Poinsot1992a,
author = {Poinsot, T.J. and Lele, S.K.},
title = {Boundary conditions for direct simulations of compressible viscous flow},
journal = JCP,
year = {1992},
volume = {101},
number = {1},
pages = {104--129},
month = {},
note = {}
}

@Article{Poinsot1995,
  author =       {Poinsot, T. and Candel, S. and Trouve, A.},
  title =        {Applications of direct numerical simulation to premixed turbulent combustion},
  journal =      {Prog. Energy Combust. Sci.},
  year =         {1995},
  volume =    {21},
  pages =     {531-576}
}

@article{Poinsot1996,
author = {Poinsot, T.},
title = {Using direct numerical simulations to understand premixed turbulent combustion},
volume = {26},
year = {1996},
pages = {219--232},
journal = {Proc. Combust. Inst.},
note = {Formerly {\it Twenty-Sixth Symposium (International) on Combustion.}}
}

@article{Poinsot1998,
author = {Poinsot, T.},
title = {Comments on ``{F}lame Stretch Interactions of Laminar Premixed Hydrogen Air Flames at Normal Temperature and Pressure'' by {K. T. A}ung, {M. J. H}assan, and {G. M. F}aeth},
volume = {113},
year = {1998},
pages = {279--281},
journal = {Combust. Flame},
}

@book {Poinsot2001,
author = {Poinsot, T. and Veynante, D.},
title = {Theoretical and Numerical Combustion},
year = {2001},
publisher = {R.\ T. Edwards, Inc.},
edition = {first},
address = {Philadelphia}
}

@book {Poinsot2005,
author = {Poinsot, T. and Veynante, D.},
title = {Theoretical and Numerical Combustion},
year = {2005},
publisher = {R.\ T. Edwards, Inc.},
edition = {Second},
address = {Philadelphia}
}

@article{Pope1985,
author = {Pope, S. B. },
title = {PDF methods for turbulent reactive flows},
journal = {Prog. Energy and Combustion Sci.},
volume = {11},
pages = {119--192},
year = {1985}
}

@article{Pope1988,
author = {Pope, S. B. },
title = {The evolution of surfaces in turbulence},
journal = {Int. J. Engng. sci.},
volume = {26},
pages = {445--469},
year = {1988}
}

@Article{Pope2004,
  author =       {Pope, S. B.},
  title =        {Ten questions concerning the large-eddy simulation of turbulent flows},
  journal =      {New Journal of Physics},
  year =         {2004},
  doi =          {10.1088/1367-2630/6/1/035},
  volume =       {6},
  pages =        {1--24}
}

@article{Pruett1995,
author = {Pruett, C.D. and Chang, C-L.},
title = {Spatial direct numerical simulation of high-speed boundary-layer flows Part II: Transition on a cone in Mach 8 flow},
journal = {Theoretical and Computational Fluid Dynamics},
volume = {7},
number = {},
pages = {397--424},
month = {},
year = {1995}
}

@InProceedings{Pruett1995a,
  author =       {Pruett, C. D.},
  title =        {Spatial Direct Numerical Simulation of Transitioning High-Speed Flows},
  booktitle =    {Transitional and Turbulent Compressible Flows},
  year =         1995,
  number =       {},
  organization = {ASME},
  pages = {63--70},
  volume = {224},
  editor = {Kral, L.D and Spina, E.F. and Arakawa, C.},
  note = {}
}

@InProceedings{Pruett1999,
  author =       {Pruett, C. D.},
  title =        {Eulerian Time-Domain Filtering for Spatial LES},
  booktitle =    {Recent Advances in DNS and LES: Proceedings of the Second AFOSR Conference held at Rutgers},
  year =         1999,
  number =       {},
  organization = {AFOSR},
  note =         {}
}

@article{Pruett2000,
author = {Pruett, C. D.},
title = {Eulerian Time-Domain Filtering for Spatial Large-Eddy Simulation},
journal = {AIAA Journal},
volume = {38},
number = {9},
pages = {1634--1642},
month = {September},
year = {2000}
}

@InProceedings{Pruett2001,
  author =       {Pruett, C. D.},
  title =        {Toward the De-Mystification of LES},
  booktitle =    {DNS/LES Progress and Challenges. Proceedings of the Third AFOSR International Conference on DNS/LES},
  year =         2001,
  number =       {},
  organization = {AFOSR},
  note =         {}
}

@article{Pruett2003,
author = {Pruett, C. D. and Gatski, T. B. and Grosch, C. E. and Thacker, W. D.},
title = {The temporally filtered {N}avier-{S}tokes equations: Properties of the residual stress},
journal = PF,
volume = {15},
number = {8},
pages = {2127--2140},
year = {2003}
}

@article{Pruett2006,
author = {Pruett, C. D. and Thomas, B. C. and Grosch, C. E. and Gatski, T. B.},
title = {A temporal approximate deconvolution model for large-eddy simulation},
journal = PF,
volume = {18},
number = {2},
pages = {028104},
year = {2006}
}

@book{Pulliam2014,
author={Pulliam, T. H. and Zingg, D. W.},
title={Fundamental Algorithms in Computational Fluid Dynamics},
series={Scientific Computation},
year={2014},
publisher={Spinger International Publishing},
edition={1},
address={New Delhi, India}
}

@article{Pullin1993,
author = {Pullin, D. I. and Saffman, P. G.},
title = {On the Lundgren-Townsend model of turbulent fine scales},
journal = PF,
volume = {5},
number = {1},
pages = {126--145},
year = {1993},
month = {January}
}

@article{Pullin1994a,
author = {Pullin, D. I. and Saffman, P. G.},
title = {Reynolds stresses and one-dimensional spectra for a vortex model of homogeneous anisotropic turbulence},
journal = PF,
volume = {6},
number = {5},
pages = {1787--1796},
year = {1994},
month = {May}
}

@article{Pullin1994b,
author = {Pullin, D. I. and Buntine, J. D. and Saffman, P. G.},
title = {On the spectrum of a stretched spiral vortex},
journal = PF,
volume = {6},
number = {9},
pages = {3010--3027},
year = {1994},
month = {September}
}

@article{Pullin1998,
author = {Pullin, D. I. and Saffman, P. G.},
title = {Vortex Dynamics in Turbulence},
journal = {Annual Review of Fluid Mechanics},
year = {1998},
volume = {30},
pages = {31--51}
}

@article{Pullin2000,
author = {Pullin, D. I.},
title = {A vortex-based model for the subgrid flux of a passive scalar},
journal = PF,
volume = {12},
number = {9},
pages = {2311--2319},
year = {2000},
month = {September}
}

@article{Pullin2001,
author = {Pullin, D. I. and Lundgren, T. S.},
title = {Axial motion and scalar transport in stretched spiral vortices},
journal = PF,
volume = {13},
number = {9},
pages = {2553--2563},
year = {2001},
month = {September}
}

@article{Pruett2008,
author = {Pruett, C. D.},
title = {Temporal large eddy simulation: theory and implementation},
journal = {Theoretical Computational Fluid Dynamics},
volume = {22},
pages = {275--304},
year = {2008}
}

@techreport{QUARK-UserGuide,
author      = {YarKhan, A. and Kurzak, J. and Dongarra, J.},
title       = {QUARK Users' Guide: QUeueing And Runtime for Kernels},
booktitle   = {University of Tennessee Innovative Computing Laboratory},
institution = {Innovative Computing Laboratory, University of Tennessee},
year        = {2011},
month       = {April},
number      = {ICL-UT-11-02}
}

@misc{QUARKWeb,
  author =    {University of Tennessee},
  title =     {QUARK},
  url =      {http://icl.cs.utk.edu/quark/software/index.html}
}

   ####
   #   #
   #   #
   ####
   # #
   #  #
   #   #

@article {Rabier2000,
author = {Rabier, F. and Jarvinen, H. and Klinker, E. and Mahfouf, J.-F. and Simmons, A.},
title = {The {ECMWF} operational implementation of four- dimensional variational assimilation. {I}: Experimental results with simplified physics},
journal = {Quart. J. Roy. Meteor. Soc.},
year = {2000},
volume = {126A},
number = {},
pages = {1143--1170},
month = {},
note = {}
}

@article {Ragab1989,
author = {Ragab, S. A. and Wu, J. L.},
title = {Linear instabilities in two-dimensional compressible mixing layers},
journal = {Phys. Fluids A},
year = {1989},
volume = {1},
number = {6},
pages = {957 -- 966},
month = {},
note = {}
}

@Manual{RAJA_web,
  title =        {RAJA},
  organization = {Lawrence Livermore National Laboratory},
  note =      {\url{http://llnl.github.io/RAJA/}}
}

@Manual{RAJA_webdoc,
  title =        {RAJA User Guide},
  organization = {Lawrence Livermore National Laboratory},
  note =      {\url{https://raja.readthedocs.io/en/master/index.html}}
}

@TechReport{RAJA_2014_TR,
  author =       {Hornung, R. D. and Keasler, J. A.},
  title =        {The RAJA Portability Layer: Overview and Status},
  institution =  {LLNL},
  year =         2014,
  number =       {LLNL-TR-661403},
  note =         {\url{https://e-reports-ext.llnl.gov/pdf/782261.pdf}}}

@article {Raman2019,
author = {Raman, V. and Hassanaly, M.},
title = {Emerging trends in numerical simulations of combustion systems},
journal = {Proceedings of the Combustion Institute},
year = {2019},
volume = {37},
number = {},
pages = {2073--2089},
note = {}
}

@article {Rao2005,
author = {Rao, A. D. and Samuelsen, G. S. and Yi, Y.},
title = {Gas turbine based high-efficiency ``{V}ision 21'' natural gas and coal central plants},
journal = {Proc. ImechE Part A: J. Power and Energy},
year = {2005},
volume = {219},
number = {},
pages = {127--136},
month = mar,
note = {}
}

@article {Rastigejev2006ctm,
	author = {Rastigejev, Y. and Matalon, M.},
	title = {Numerical simulation of flames as gas-dynamic discontinuities},
	journal = {Combust. Theory Model.},
	year = {2006},
	volume = {10},
	number = {3},
	pages = {459--481},
	month = jun,
	note = {}
	}
   
@article {Rastigejev2006jfm,
	author = {Rastigejev, Y. and Matalon, M.},
	title = {Nonlinear evolution of hydrodynamically unstable premixed flames},
	journal = {J. Fluid. Mech.},
	year = {2006},
	volume = {554},
	number = {},
	pages = {371--392},
	month = {},
	note = {}
	}
   
@article {Reagan2003,
author = {Reagan, M. T. and Najm, H. N. and Ghanem, R. G. and Knio, O. M.},
title = {Uncertainty quantification in reacting-flow simulations through non-intrusive spectral projection},
journal = {Combust. Flame},
year = {2003},
volume = {132},
number = {3},
pages = {545--555},
month = {},
note = {}
}
   
@article {Reagan2016,
author = {Reagan, A. J. and Dubief, Y. and Dodds, P. S. and Danforth, C. M.},
title = {Predicting Flow Reversals in a Computational Fluid Dynamics Simulated Thermosyphon Using Data Assimilation},
journal = {PLoS ONE},
year = {2016},
volume = {11},
number = {2},
pages = {},
month = {},
note = {}
}


@article {Rehm2009,
author = {Rehm, R. G. and McDermott, R. J.},
title = {Fire front propagation using the level-set method},
journal = {NIST, Technical Report},
volume = {1611},
year = {2009}
}

@article {RehmBaum1978,
author = {Rehm, R. G. and Baum, H. R.},
title = {The equations of motion for thermally driven buoyant flows},
journal = {N. B. S. J. Res.},
volume = {83},
pages = {297--308},
year = {1978}
}

@Book{Reich2015,
  author =    {Reich, S. and Cotter, C.},
  title =        {Probabilistic Forecasting and Bayesian Data Assimilation},
  publisher =    {Cambridge University Press},
  year =         {2015},
  OPTkey =       {},
  OPTvolume =    {},
  OPTnumber =    {},
  OPTseries =    {},
  OPTaddress =   {},
  OPTedition =   {},
  OPTmonth =     {},
  OPTnote =      {},
  OPTannote =    {}
}

@article {Ren2001,
author = {Ren, J. Y. and Qin, W. and Egolfopoulos, F. N. and Tsotsis, T. T.},
title = {Strain-rate effects on hydrogen-enhanced lean premixed combustion},
journal = {Combust. Flame},
year = {2001},
volume = {124},
number = {},
pages = {717--720},
month = {},
note = {}
}

@article {Ren2002,
author = {Ren, J.-Y. and Egolfopoulos, F. N. and Tsotsis, T. T.},
title = {{$\rm NO_x$} emission control of lean methane--air combustion with addition of methane reforming products},
journal = {Combust. Sci. and Tech.},
year = {2002},
volume = {174},
number = {},
pages = {181--205},
month = {},
note = {}
}

@article {Renard2000,
author = {Renard, P.-H. and Th\'evenin, D. and Rolon, J. C. and Candel, S.},
title = {Dynamics of flame/vortex interactions},
journal = {Prog. Energy Combust. Sci.},
year = {2000},
volume = {26},
number = {},
pages = {225--282},
month = {},
note = {}
}

@article {Reynolds1895,
author = {Reynolds, O.},
title = {On the Dynamical Theory of Incompressible Viscous Fluids and the Determination of the Criterion},
journal = {Philosophical Transactions of the Royal Society of London},
year = {1895},
volume = {186},
number = {},
pages = {123--164},
month = {},
note = {}
}

@book {Rezaiyan2005,
author = {Rezaiyan, J. and Cheremisinoff, N. P.},
title = {Gasification Technologies: A Primer for Engineers and Scientists},
year = {2005},
publisher = {Taylor and Francis},
edition = {},
address = {Boca Raton}
}

@article {Richards2001,
author = {Richards, G. A. and McMillian, M. M. and Gemmen, R. S. and Rogers, W. A. and Cully, S. R.},
title = {Issues for low-emission, fuel-flexible power systems},
journal = {Prog. Energy Combust. Sci.},
year = {2001},
volume = {27},
number = {2},
pages = {141--169},
month = {},
note = {}
}

@misc{Richards2021,
author = {Richards, K.J. and Senecal, P.K. and Pomraning, E.},
title = {CONVERGE 3.0*},
howpublished = {Convergent Science, Madison, WI},
year = {2021}
}

@article {Richtmyer1960,
author = {Richtmyer, R. D.},
title = {Taylor instability in shock acceleration of compressible fluids},
journal = CPAM,
volume = {13},
number = {2},
publisher = {Wiley Subscription Services, Inc., A Wiley Company},
issn = {1097-0312},
OPTurl = {http://dx.doi.org/10.1002/cpa.3160130207},
OPTdoi = {10.1002/cpa.3160130207},
pages = {297--319},
year = {1960}
}


@TechReport{Riley2016,
author = {Riley, J. R. and Gao, X. and Olschanowsky, C. and Guzik, S. M},
title = {Enabling Performance Optimization of {CFD} Applications with Source-to-Source Compiler Technology},
institution = {54th AIAA Aerospace Sciences Meeting},
year = {2016},
type = {AIAA},
number = {2016-1812}
}

@article {Roberts1991,
author = {Roberts, W. L. and Driscoll, J. F.},
title = {A laminar vortex interacting with a premixed flame: Measured formation of pockets of reactants},
journal = {Combust. Flame},
year = {1991},
volume = {87},
pages = {245--256}
}

@article {Roberts1992,
author = {Roberts, W. L. and Driscoll, J. F. and Drake, M. C. and Ratcliffe, J. W.},
title = {{OH} fluorescence images of the quenching of a premixed flame during an interaction with a vortex},
volume = {24},
year = {1992},
pages = {169--176},
journal = {Proc. Combust. Inst.},
}

@article {Roberts1993,
author = {Roberts, W. L. and Driscoll, J. F. and Drake, M. C. and Goss, L. P.},
title = {Images of the quenching of a flame by a vortex --- {T}o quantify regimes of turbulent combustion},
journal = {Combust. Flame},
year = {1993},
volume = {98},
pages = {58--69}
}

@article {Rochette2018,
author = {Rochette, B. and Collin-Bastiani, F. and Gicquel, L. and Vermorel, O. and Veynante, D. and Poinsot, T.},
title = {Influence of chemical schemes, numerical method and dynamic turbulent combustion modeling on LES of premixed turbulent flames},
journal = {Combust. Flame},
year = {2018},
volume = {191},
pages = {417--430}
}

@article {Rogg1988,
author = {Rogg, B.},
title = {Response and flamelet structure of stretched premixed methane-air flames},
journal = {Combust. Flame},
year = {1988},
volume = {73},
pages = {45--46}
}

@article {RojelJenson2000,
author = {R{\o}jel, H. and Jensen, A. and Glarborg, P. and Dam-Johansen, K.},
title = {Mixing Effects in the Selective Noncatalytic Reduction of {NO}},
journal = {Ind. Eng. Chem. Res.},
year = {2000},
volume = {39},
number = {},
pages = {3221-3232},
month = {},
note = {}
}

@article {Rolon1995,
author = {Rolon, J. C. and Aguerre, F. and Candel, S.},
title = {Experiments on the interaction between a vortex and a strained diffusion flame},
journal = {Combust. Flame},
year = {1995},
volume = {100},
number = {3},
pages = {422--429}
}

@InBook{Rood2010,
  author =    {Rood, R. B.},
  editor =    {Lahoz, W. and Khattatov, B. ‎and Menard, R.},
  title =        {Data Assimilation},
  chapter =      {The Role of the Model in the Data Assimilation System},
  publisher =    {Springer-Verlag Berlin Heidelberg },
  year =         {2010}
}

@article {Rook2003,
author = {Rook, R. and de Goey, L. P. H.},
title = {The acoustic response of burner-stabilized flat flames: a two-dimensional numerical analysis},
journal = {Combust. Flame},
year = {2003},
volume = {133},
number = {},
pages = {119--132},
month = {},
note = {}
}

@article {Roper1977,
author = {Roper, F. G.},
title = {The Prediction of Laminar Jet Diffusion Flame Sizes: Part {I}.\ Theoretical Model},
journal = {Combust. Flame},
year = {1977},
volume = {29},
number = {},
pages = {219--226},
month = {},
note = {}
}

@article {RoperSmith1977,
author = {Roper, F. G. and Smith, C. and Cunningham, A. C.},
title = {The Prediction of Laminar Jet Diffusion Flame Sizes: Part {II}.\ Experimental Verification},
journal = {Combust. Flame},
year = {1977},
volume = {29},
number = {},
pages = {227--234},
month = {},
note = {}
}

@InProceedings {Rortvett2002,
author = {Rortvett, G. and Zepter, K. and Skreiberg, O. and Fossum, M. and Hustad, J.},
title =	{A comparison of low-NO$_x$ burners for combustion of methane and hydrogen mixtures},
booktitle = {Proceedings of the Combustion Institute},
pages =	{1123--1129},
publisher = {},
month =	{},
year = {2002}
}

@article {Rosales2005,
author = {Rosales, C. and Meneveau, C.},
title = {Linear forcing in numerical simulations of isotropic turbulence: Physical space implementations and convergence properties},
journal = PF,
year = {2005},
volume = {17},
pages = {095106}
}


@Misc{ROSEweb,
  key =          {ROSE},
  title =        {{ROSE} compiler infrastructure},
  note =         {\url{http://www.rosecompiler.org}}
}

@TechReport{ROSEmanual2015,
  author =       {Quinlan, D. and Liao, C. and Panas, T. and Matzke, R. and Schordan, M. and Vuduc, R. and Yi, Q.},
  title =        {{ROSE} User Manual: A Tool for Building Source-to-Source Translators},
  institution =  {Lawrence Livermore National Laboratory},
  year =         2015
}

@article {Roshko1961,
author = {Roshko, A.},
title = {Experiments on the flow past a circular cylinder at very high Reynolds number},
journal = JFM,
year = {1961},
volume = {10},
number = {3},
pages = {345--356},
month = {May},
note = {}
}

@article {Rosner2000,
author = {Rosner, D. E. and Israel, R. S. and La Mantia, B.},
title = {``{H}eavy'' Species {L}udwig-{S}oret Transport Effects in Air-Breathing Combustion},
journal = {Combust. Flame},
year = {2000},
volume = {123},
number = {},
pages = {547--560},
month = {},
note = {}
}

@TechReport{Rothermel1972,
  author =       {Rothermel, R. C.},
  title =        {A mathematical model for predicting fire spread in wildland fuels},
  institution =  {USDA Forest Service, Research Paper INT-115, Intermountain Forest and Range Experiment Ogden},
  year =         {1972},
}

@article {RutlandTrouve1993,
author = {Rutland, C. J. and Trouv\'e, A.},
title = {Direct simulations of premixed turbulent flames with non-unit {L}ewis numbers},
journal = {Combust. Flame},
year = {1993},
volume = {94},
number = {},
pages = {41--57},
month = {},
note = {}
}

    ###
   #   #
   #
    ###
       #
   #   #
    ###

@article{Saffman1994,
author = {Saffman, P. G. and Pullin, D. I.},
title = {Anisotropy of the Lundgren-Townsend model of fine-scale turbulence},
journal = PF,
volume = {6},
number = {2},
pages = {802--807},
year = {1994},
month = {February}
}

@BOOK{Sagaut1998,
  AUTHOR = 	 {Sagaut, P.},
  TITLE = 	 {Large Eddy Simulation for Incompressible Flows: An Introduction},
  PUBLISHER = 	 {Springer-Verlag},
  YEAR = 	 {1998},
  EDITION = 	 {3rd}
}
@BOOK{Garnier2009,
  AUTHOR = 	 {Garnier, E. and Adams, N. and Sagaut, P.},
  TITLE = 	 {Large Eddy Simulation for Compressible Flows},
  PUBLISHER = 	 {Springer},
  YEAR = 	 {2009},
  EDITION = 	 {1st}
}
@article {Sakov2012,
author = {Sakov, P. and Oliver, D. S. and Bertino, L.},
title = {An iterative EnKF for strongly nonlinear systems},
journal = {Mon. Wea. Rev.},
volume = {140},
number = {},
pages = {1988--2004},
year = {2012}
}

@article{Saye2017,
title = {Implicit mesh discontinuous Galerkin methods and interfacial gauge methods for high-order accurate interface dynamics, with applications to surface tension dynamics, rigid body fluid–structure interaction, and free surface flow: Part I},
journal = {Journal of Computational Physics},
volume = {344},
pages = {647-682},
year = {2017},
issn = {0021-9991},
doi = {https://doi.org/10.1016/j.jcp.2017.04.076},
author = {Saye, R.}
}

@techreport {Salari2000,
author = {Salari, K. and Knupp, P.},
title = {Code Verification by the Method of Manufactured Solutions},
institution = {Sandia National Laboratories},
year = {2000},
type = {Technical Report},
number = {SAND2000-1444},
address = {},
month = {June}
}

@incollection {Samaniego1993,
author = {Samaniego, J.-M.},
title = {Stretch-induced quenching in flame-vortex interactions},
booktitle = {1993 Annual Research Briefs},
year = {},
editor = {},
pages = {205},
organization = {},
publisher = {Center for Turbulence Research},
address = {Stanford University},
month = {},
}

@inproceedings {Sankaran2007,
	author = {R. Sankaran and E. R. Hawkes and C. Y. Yoo and J. H. Chen and T. Lu and C. K. Law},
	title = {Direct numerical simuation of stationary lean premixed methane-air flames under intense turbulence},
	booktitle = {Proceedings of the 5$^{\rm th}$ US Combustion Meeting
(CD-ROM)},
	year = {2007},
	editor = {},
	pages = {},
	organization = {},
	publisher = {Western States Section of the Combustion Institute},
	address = {},
	month = mar,
	note = {Paper B09}
	}

@article {Saric2002,
author = {Saric, W.S. and Reed, H.L and Kerschen, E.J.},
title = {Boundary-layer receptivity to freestream disturbance},
journal = {Annual Review of Fluid Mechanics},
volume = {34},
number = {},
pages = {291--319},
year = {2002}
}

@article {Sarofim1975,
author = {A. F. Sarofim and G. C. Williams and M. Modell and S. M. Slater},
title = {Conversion of Fuel Nitrogen to Nitric Oxide in Premixed and Diffusion Flames},
journal = {AIChE Symp. Ser.},
volume = {71},
number = {148},
pages = {51--61},
year = {1975}
}

@article {Sarghini2003,
author = {Sarghini, F. and De Felice, G. and Santini, S.},
title = {Neural networks based subgrid scale modeling in large-eddy simulations},
journal = {Computers and Fluids},
volume = {32},
number = {1},
pages = {97--108},
year = {2003}
}

@article {Sarv1989,
author = {Sarv, H. and Cernansky, N. P.},
title = {{NO}$_x$ Formation from the Combustion of Monodisperse $n$-Heptane Sprays Doped with Fuel-Nitrogen Additives},
journal = {Combust. Flame},
year = {1989},
volume = {76},
number = {},
pages = {265--283},
month = {},
note = {}
}

@article {Sattler2002,
author = {Sattler, S. S. and Knaus, D. A. and Gouldin, F. C.},
title = {Determination of three-dimensional flamelet orientation distributions in turbulent {V}-flames from two-dimensional image data},
journal = {Proc. Combust. Inst.},
year = {2002},
volume = {29},
number = {},
pages = {1785--1795},
month = {},
note = {}
}

@article{Savard2014,
title = {An a priori model for the effective species Lewis numbers in premixed turbulent flames},
author = {Savard, B. and Blanquart, G.},
journal = {Combust. Flame},
volume = {161},
number = {6},
pages = {1547 - 1557},
year = {2014},
issn = {0010-2180},
publisher = {Elsevier},
doi = {https://doi.org/10.1016/j.combustflame.2013.12.014},
url = {http://www.sciencedirect.com/science/article/pii/S0010218013004628},
}

@article{Schive2012,
author = {Hsi-Yu Schive and Ui-Han Zhang and Tzihong Chiueh},
title ={Directionally unsplit hydrodynamic schemes with hybrid {MPI}/{OpenMP}/{GPU} parallelization in {AMR}},
journal = {The International Journal of High Performance Computing Applications},
volume = {26},
number = {4},
pages = {367-377},
year = {2012},
URL = {https://doi.org/10.1177/1094342011428146}
}

@BOOK{schlichting:1979,
    AUTHOR={H. Schlichting},
    TITLE={Boundary-Layer Theory},
    EDITION={7th},
    PUBLISHER={McGraw-Hill},
    ADDRESS={Toronto},
    YEAR={1979}   }

@article {Schmidt2001,
author = {Schmidt, C. C. and Bowman, C. T.},
title = {Flow Reactor Study of the Effect of Pressure on the Thermal De-{NO}x Process
},
journal = {Combust. Flame},
year = {2001},
volume = {127},
number = {},
pages = {1958--1970},
month = {},
note = {}
}

@article{Schmitt2010,
  title={Large-eddy simulation of supercritical-pressure round jets},
  author={Schmitt, T. and Selle, L. and Ruiz, A. and Cuenot, B.},
  journal={AIAA Journal},
  volume={48},
  number={9},
  pages={2133--2144},
  year={2010}
}

@article {Schneider2008,
author = {Schneider, S.P.},
title = {Summary of hypersonic boundary-layer transition experiments on blunt bodies with roughness},
journal = {Journal of Spacecraft and Rockets},
year = {2008},
volume = {45},
number = {},
pages = {1090--1112},
month = {},
note = {}
}

@article {Schneiders2012,
author = {Schneiders, L. and Hartmann, D. and Meinke, M. and Schröder, W.},
title = {An accurate moving boundary formulation in cut-cell methods},
journal = {J. Comput. Phys.},
year = {2012},
volume = {235},
number = {},
pages = {786--809},
month = {},
note = {}
}

@article {Schuller2003,
author = {Schuller, T. and Durox, D. and Candel, S.},
title = {A unified model for the prediction of laminar flame transfer functions: comparisons between conical and {V}-flame dynamics},
journal = {Combust. Flame},
year = {2003},
volume = {134},
number = {},
pages = {21--34},
month = {},
note = {}
}

@article {Schulz1999,
author = {Schulz, C. and Sick, V. and Meier, U. and Heinze, J. and Stricker, W.},
title = {Quantification of {NO} {A}-{X}(0,2) {LIF}:Investigation of calibration and collisional influences in high-pressure flames},
journal = {Applied Optics},
year = {1999},
volume = {38},
pages = {1434--1443}
}

@article {Schur1911,
author = {Schur, I.},
title = {Bemerkungen zur Theorie der beschr{\"a}nkten Bilinearformen mit unendlich vielen Ver{\"a}nderlichen},
journal = {J. reine angew. Math},
year = {1911},
volume = {140},
pages = {1--28}
}

@article{Schwartz2015,
author = {Schwartz, P. and Percelay, J. and Ligocki, T. and Johansen, H. and Graves, D. and Devendran, D. and Colella, P and Ateljevich, E.},
title = {{High-accuracy embedded boundary grid generation using the divergence theorem}},
volume = {10},
journal = {Communications in Applied Mathematics and Computational Science},
number = {1},
publisher = {MSP},
pages = {83 -- 96},
keywords = {{C}artesian grid embedded boundaries, finite volume methods, grid generation},
year = {2015},
doi = {10.2140/camcos.2015.10.83},
}


@article {Searby1990,
author = {Searby, G. and Quinard, J.},
title = {Direct and Indirect Measurements of Markstein Numbers of Premixed Flames},
journal = {Combust. Flame},
year = {1990},
volume = {82},
number = {},
pages = {298--311},
month = {},
note = {}
}

@article {Seo2011,
author = {Seo, J. and Mittal, R.},
title = {A sharp interface immersed boundary method with improved mass conservation and reduced spurious pressure oscillations},
journal = {J. Comput. Phys.},
year = {2011},
volume = {230},
number = {},
pages = {7347--7363},
month = {},
note = {}
}

@article {SeshadriPeters2001,
author = {Seshadri, K. and Peters, N. and Oijen, J. A. van and de Goey, L. P. H.},
title = {The asymptotic structure of weakly strained moderately rich methane-air flames},
journal = {Combust. Theory Model.},
year = {2001},
volume = {5},
number = {},
pages = {201--215},
month = {},
note = {}
}

@incollection {Seybold2015,
author = {Seybold, H. and Ravela, S. and Tagade, P.},
title = {Ensemble learning in jon-Gaussian data assimilation},
booktitle = {Dynamic Data-Driven Environmental Systems Science},
year = {2015},
editor = {Ravela, S. and Sandu, A.},
pages = {227--238},
organization = {},
publisher = {Springer},
address = {},
month = {},
note = {}
}

@techreport {Shadow1972,
author = {Shadow, T. O. and Gomillion, G. R.},
title = {Transonic aerodynamic characteristics of bomblet munition models used in the evaluation of the roll-through-zero aerodynamic dispersion technique},
institution = {USAF AEDC},
year = {1972},
type = {Technical Report},
number = {AEDC-TR-72-106, AFATL-TR-72-138},
address = {},
month = {July},
note = {}
}

@article {Shanbhogue2009,
author = {Shanbhogue, S. J. and Husain, S. and Lieuwen, T.},
title = {Lean blowoff of bluff body stabilized flames: Scaling and dynamics},
journal = {Progress in Energy and Combustion Science},
year = {2009},
volume = {35},
number = {},
pages = {98--120},
month = {},
note = {}
}

@Book{Shannon1949,
  author =    {Shannon, C. E. and Weaver, W.},
  title =        {The mathematical theory of communication},
  publisher =    {University of Illinois Press: Urbana},
  year =         {1949}
}

@article {Shaw2006,
author = {Shaw, J.},
title = {{Fueling Our Future}},
journal = {Harvard Magazine},
year = {2006},
volume = {},
number = {},
pages = {40--48},
month = {May-June},
note = {}
}

@article {Shu1998,
author = {Shu, C.-W.},
title = {Essentially non-oscillatory and weighted essentially non-oscillatory schemes for hyperbolic conservation laws},
journal = {Advanced numerical approximation of nonlinear hyperbolic equations (eds B. Cockburn, C. Johnson, C.-W. Shu, E. Tadmor, A. Quarteroni)},
year = {1998},
volume = {1697},
number = {},
pages = {325--432},
month = {},
note = {}
}

@article {Schefer2002,
author = {Schefer,R.W. and Wicksall, D.M. and Agrawal, A. K.},
title = {Combustion of hydrogen-enriched methane in a lean premixed swirl-stablized burner},
year = {2002},
volume = {},
number = {},
pages = {843--852},
month = {},
note = {\ 29$^{th}$ Symposium (International) on Combustion.}}
}

@article {Shefer2003,
author = {Shefer, R. W.},
title = {Hydrogen enrichment for improved lean flame stability},
journal = {Int. J. Hydrogen Energ.},
year = {2003},
volume = {28},
number = {},
pages = {1131--1141},
month = {},
note = {}
}

@incollection {Shepherd1992,
author = {Shepherd, I. G. and Hertzberg and J. R. and Talbot, L.},
editor = {Hussaini, M. Y. and Kumar, A. and Voigt, R. G.},
booktitle = {Major Research Topics in Combustion},
year = {1992},
publisher = {Springer-Verlag},
address = {New York}
}

@article {Shepherd1996,
author = {Shepherd, I. G.},
title = {Flame Surface Density and Burning Rate in Premixed Turbulent Flames},
journal = {Proc. Combust. Inst.},
year = {1996},
volume = {22},
pages = {373--379}
}

@article {Shepherd2002,
author = {Shepherd, I. G. and Cheng, R. K. and Plessing, T. and Kortschik, C. and Peters, N.},
title = {Premixed flame front structure in intense turbulence},
journal = {Proc. Combust. Inst.},
year = {2002},
volume = {29},
number = {},
pages = {1833--1840},
month = {},
note = {}
}

@Book{Sherman1991,
  author =    {Sherman, F.},
  editor =    {},
  title =        {Viscous Flows},
  publisher =    {McGraw-Hill},
  year =         {1991},
  OPTkey =       {},
  OPTvolume =    {},
  OPTnumber =    {},
  OPTseries =    {},
  OPTaddress =   {New York, NY},
  OPTedition =   {},
  OPTmonth =     {},
  note =      {pp. 335--336},
  OPTannote =    {}
}

@article {Shetty2013,
author = {Shetty, D. A. and Frankel, S. H.},
title = {Assessment of stretched vortex subgrid-scale models for LES of incompressible inhomogeneous turbulent flows},
journal = {Int. J. Numer. Meth. Fluids},
year = {2013},
volume = {73},
pages = {152--171}
}

@Article{Sheu2000,
  author =       {Tony W. H. Sheu and S. K. Wang and R. K. Lin},
  title =        {An Implicit Scheme for Solving the Convection-Diffusion-Reaction Equation in Two Dimensions},
  journal =      JCP,
  year =         {2000},
  OPTkey =       {},
  volume =    {164},
  OPTnumber =    {},
  pages =     {123-142},
  month =     {},
  note =      {}
  }

@article {Sick1998,
author = {Sick, V. and Hildenbrand, F. and Lindstedt, P.},
title = {Quantitative Laser-based measurement and detailed chemical kinetic modeling of nitric oxide concentrations in methane-air counterflow diffusion flames},
journal = {Proc. Combust. Inst.},
year = {1998}, 
volume = {27}, 
number = {}, 
pages = {1401--1409},
month = {}, 
note = {} 
}

@article {Silver1983,
author = {Silver, J. A.},
title = {The Effect of Sulfur on the Thermal De{NO}$_x$ Process},
journal = {Combust. Flame},
year = {1983},
volume = {53},
number = {},
pages = {17--21},
month = {},
note = {}
}



@Article{Simon2009,
  author =   {E. Simon and L. Bertino},
  title =    {Application of the Gaussian anamorphosis to assimilation in a 3-D coupled physical-ecosystem model of the North Atlantic with the EnKF: A twin experiment.},
  journal =  {Ocean Sci.},
  year =     {2009},
  volume =    {5},
  pages =     {495–510},
  note =      {doi:10.5194/os-5-495-2009}
}


@article {Simmons2006,
	author = {Simmons, S. F. and Brown, K. L.},
	title = {Gold in Magmatic Hydrothermal Solutions and the Rapid Formation
of a Giant Ore Deposit},
	journal = {Science},
	year = {2006},
	volume = {314},
	number = {5797},
	pages = {288--291},
	month = {13 October},
	note = {}
	}

@article {Singh2012,
	author = {Singh, G. and S. Chander and A. Ray},
	title = {Heat transfer characteristics of natural gas/air swirling flame impinging on a flat surface},
	journal = {Exp. Thermal Fluid Science},
	year = {in press, 2012},
	volume = {},
	number = {},
	pages = {},
	month = {},
	note = {}
	}


@article {Skinner1979,
author = {Skinner, B. J.},
title = {Earth resources},
journal = {Proc. Natl. Acad. Sci. USA},
year = {1979},
volume = {76},
number = {9},
pages = {4212--4217},
month = sep,
note = {}
}
 
@article {Sinibaldi1998,
author = {Sinibaldi, J. O. and Mueller, C. J. and Driscoll, J. F.},
title = {Local flame propagation speeds along wrinkled, unsteady, stretched premixed flames},
journal = {Proc. Combust. Inst.},
year = {1998},
volume = {27},
number = {},
pages = {827--832},
month = {},
note = {}
}

@article {Sinibaldi2003,
author = {Sinibaldi, J. O. and Driscoll, J. F. and Mueller, C. J. and Donbar, J. M. and Carter, C. D.},
title = {Propagation speeds and stretch rates measured along wrinkled flames to assess the theory of flame stretch},
journal = {Combust. Flame},
year = {2003},
volume = {133},
number = {3},
pages = {323--334},
month = {},
note = {}
}

@article {Sivashinsky1977a,
author = {Sivashinsky, G. I.},
title = {Diffusional-Thermal Theory of Cellular Flames},
journal = {Combust. Sci. Technol.},
year = {1977},
volume = {15},
number = {3},
pages = {137--146},
month = {},
note = {}
}

@article {Sivashinsky1977b,
author = {Sivashinsky, G. I.},
title = {Nonlinear analysis of hydrodynamic instability in laminar flames--I. Derivation of basic equations},
journal = {Acta Astronomica},
year = {1977},
volume = {4},
number = {},
pages = {1177--1206},
month = {},
note = {}
}

@article {Sivashinsky1980a,
author = {Sivashinsky, G. I.},
title = {On Flame Propagation Under Conditions of Stoichiometry},
journal = {SIAM J. Appl. Math},
year = {1980},
volume = {39},
number = {1},
pages = {},
month = {},
note = {}
}

@article {Sivashinsky1980b,
author = {Sivashinsky, G. I.},
title = {On irregular wavy flow of a liquid down a vertical plane},
journal = {Progr. Theoret. Phys.},
year = {1980},
volume = {63},
number = {},
pages = {2112-2114},
month = {},
note = {}
}

@article {Sivashinsky1983,
author = {Sivashinsky, G. I.},
title = {Instabilities, Pattern Formation, and Turbulence in Flames},
journal = {Annual Review of Fluid Mechanics},
year = {1983},
volume = {15},
number = {},
pages = {179--200},
month = {},
note = {}
}

@article {Skreiberg2004,
author = {Skreiberg, O. and Kilpinen, P. and Glarborg, P.},
title = {Ammonia Chemistry below 1400 {K} at Fuel-Rich Conditions in a Flow
Reactor},
journal = {Combust. Flame},
year = {2004},
volume = {136},
number = {},
pages = {501--518},
month = {},
note = {}
}

@unpublished {SmithGolden,
 author = {Smith et al., G. P.},
 title = {{GRI}-{M}ech 3.0},
 note = {Available at \url{http://www.me.berkeley.edu/gri_mech}},
 month = {},
 year = {}
}

{Smith, G. P. and Golden, D. M. and Frenklach, M. and Moriarty, N. W. and Eiteneer, B. and Goldenberg, M. and Bowman, C. T. and Hanson, R. K. and Song, S. and Gardiner Jr., W. C. and Lissianski, V. V. and Qin, Z.}

@incollection {Smith2015,
author = {Smith, B. and Tu, X.},
title = {Domain Decomposition},
booktitle = {Encyclopedia of Applied and Computational Mathematics},
year = {2015},
editor = {},
pages = {375--381},
organization = {},
publisher = {Springer},
address = {},
month = {},
note = {}
}

@article {Smith2004,
author = {Smith, R.},
title = {After Long Taking Its Lumps, Coal is Suddenly Hot Again},
journal = {Wall Street Journal},
year = {2004},
volume = {CCXLIII},
number = {64},
pages = {A1, A6},
month = {April 1},
note = {}
}

@techreport {Smith1995,
author = {Smith, T. S. and Caton, J. A.},
title = {Reductions and Conversions of Nitrogen Compounds Using Ammonia in a
Selective Non-Catalytic Process for Exhaust Streams for Pressures up
to 515 k{P}a},
institution = {Joint Western States and Central States and Mexican National Section of the Combustion Institute},
year = {1995},
type = {Paper},
number = {95S-016},
address = {},
month = {},
note = {}
}

@article {Smith1982,
author = {Smith, T. Shen, Z. and Friedman, J.},
title = {Evaluation of coefficients for weighted sum of gray gasses model},
journal = {J. Heat Transfer},
year = {1982},
volume = {104},
number = {},
pages = {602--608},
month = {},
note = {}
}

@InProceedings{Smits2009,
  author = {Smits, A. J. and Martin, M. P. and Girimaji, S.},
  title = {Current Status of Basic Research in Hypersonic Turbulence},
  booktitle = {39th AIAA Fluid Dynamics Conference and Exhibit},
  year = {2009},
  number = {AIAA 2009-151},
  organization = {AIAA}
}

@TechReport{Slotnick2014,
  author =       {Slotnick, J. and Khodadoust, A. and Alonso, J. and Darmofal, D and Gropp, W and Lurie, E. and Mavriplis, D},
  title =        {CFD Vision 2030 Study: A Path to
Revolutionary Computational Aerosciences},
  institution =  {NASA/CR},
  year =         {2014},
  OPTkey =       {},
  OPTtype =      {},
  number =    {218178},
  OPTaddress =   {},
  OPTmonth =     {},
  OPTnote =      {},
  OPTannote =    {}
}

@incollection {Smooke1982,
	author = {Smooke, M. D. and Miller, J. A. and Kee, R. J.},
	title = {On the use of Adaptive Grids in Numerically Calculating Adiabatic Flame Speeds},
	booktitle = {\rm \cite {WarnatzPeters1982}},
	year = {1982},
	editor = {},
	pages = {},
	organization = {},
	publisher = {},
	address = {},
	month = {},
	note = {}
	}

@article {Smooke1988,
author = {M. D. Smooke and H. Rabitz and Y. Reuven and F. L. Dryer},
title = {},
journal = {Combust. Sci. Technol.},
year = {1988},
volume = {59},
number = {},
pages = {295--319},
month = {},
note = {}
}

@article {SmookeErn1996,
author = {Smooke, M. D. and Ern, A. and Tanoff, M. A. and Valdati, B. A. and Mohammed, R. K. and Marran, D. F. and Long, M. B.},
title = {Computational and Experimental Study of {NO} in an Axisymmetric Laminar Diffusion Flame},
journal = {Proc. Combust. Inst.},
year = {1996},
volume = {26},
number = {},
pages = {2161--2170},
month = {},
note = {}
}

@article {SmookeLin1990,
author = {Smooke, M. D. and Lin, P. and Lam, J. K. and Long, M. B.},
title = {Computational and experimental study of a laminar axisymmetric methane-air diffusion flame},
journal = {Proc. Combust. Inst.},
year = {1990},
volume = {23},
pages = {575--582},
note = {}
}

@article {SmookeMcEnally1999,
author = {Smooke, M. D. and Mc{E}nally, C. S. and Pfefferle, L. D. and
Hall, R. J. and Colket, M. B.},
title = {Computational and experimental study of soot formation in a coflow, laminar diffusion flame},
journal = {Combust. Flame},
year = {1999},
volume = {117},
number = {},
pages = {117--139},
month = {},
note = {}
}

@article {SmookeMitchell1989,
author = {Smooke, M. D. and Mitchell, R. E. and Keyes, D. E.},
title = {Numerical Solution of Two-Dimensional Axisymmetric Laminar Diffusion Flames},
journal = {Combust. Sci. Technol.},
year = {1989},
volume = {67},
number = {},
pages = {85--122},
month = {},
note = {}
}

@inproceedings {SmookeTurnbull1988,
author = {M. D. Smooke A. A. Turnbull and and R. E. Mitchell and D. E. Keyes},
title = {Solution of Two-Dimensional Axisymmetric Laminar Diffusion Flames by Adaptive Boundary Value Methods},
booktitle = {Mathematical Modeling in Combustion and Related Topics},
pages = {261--300},
year = {1988}
}

@inproceedings {SmookeZurn1992,
author = {M. D. Smooke and Y. Xu and R. M. Zurn and P. Lin and J. H. Frank and M. B. Long},
title = {Computational and experimental study of {OH} and {CH} radicals in axisymmetric laminar diffusion flames},
booktitle = {Proc. Combust. Inst.},
volume = {24},
year = {1992},
pages = {813--821}
}

@article {Smyth1996,
author = {Smyth, K. C.},
title = {{NO} Production and Destruction in a Methane/Air Diffusion Flame},
journal = {Combust. Sci. Technol.},
year = {1996},
volume = {115},
number = {},
pages = {151--176},
month = {},
note = {}
}

@phdthesis {Somers1994,
	author = {Somers, L. M. T.},
	title = {The Simultation of Flat Flames with Detailed and Reduced Chemical Models},
	school = {Eindhoven University of Technology},
	year = {1994},
	address = {},
	month = {},
	note = {Available at \url {http://yp.wtb.tue.nl/pdfs/1684.pdf}}
	}

@article {Spalart1994,
author = {Spalart, P. R. and Allmaras, S. R.},
title = {A One-Equation Turbulence Model for Aerodynamic Flows},
journal = {Recherche Aerospatiale},
year = {1994},
volume = {},
number = {1},
pages = {5--21},
month = {},
note = {}
}

@article {Spalart1997,
author = {Spalart, P. R. and Jou, W-H and Allmaras, S. R.},
title = {Comments on the feasibility of LES for wings, and on a hybrid RANS/LES approach},
journal = {Advances in DNS/LES},
year = {1997},
volume = {},
number = {},
pages = {137-147},
month = {},
note = {}
}

@article{Spalart2007,
  author =       {Spalart, P. and Rumsey, C.},
  title =        {Effective Inflow Conditions for Turbulence Models in Aerodynamic Calculations},
  journal =      {AIAA J.},
  year =         {2007},
  OPTkey =       {},
  volume =    {45},
  number =    {10},
  OPTpages =     {},
  OPTmonth =     {},
  OPTnote =      {},
  OPTannote =    {}
}

@article {Spalart2014,
author = {Spalart, P. R. and Garbaruk, A. and Strelets, M.},
title = {RANS Solutions in Couette flow with streamwise vortices},
journal = {International Journal of Heat and Fluid Flow},
year = {2014},
volume = {49},
number = {},
pages = {128--134},
month = {},
note = {}
}

@techreport {Speth2005,
author = {Speth, R.L. and Ghoniem, A.F. and Marzouk, Y.M.},
title = {Impact of hydrogen addition on flame response to stretch and curvature},
institution = {AIAA},
year = {2005},
type = {Paper},
number = {AIAA 2005-143},
address = {},
month = {},
note = {}
}

@article {Speziale1979,
author = {Speziale, C. G.},
title = {Invariance of turbulent closure models},
journal = PF,
year = {1979},
volume = {22},
number = {6},
pages = {1033--1037},
month = {June},
note = {}
}

@article {Speziale1983,
author = {Speziale, C. G.},
title = {On the Nonlinear Stability of Rotating Newtonian and Non-Newtonian Fluids},
journal = {Acta Mechanica},
year = {1983},
volume = {49},
number = {},
pages = {263--273},
month = {},
note = {}
}

@article {Speziale1985a,
author = {Speziale, C. G.},
title = {Galilean invariance of subgrid-scale stress models in the large-eddy simulation of turbulence},
journal = {J. Fluid Mech.},
year = {1985},
volume = {156},
number = {},
pages = {55--62},
month = {},
note = {}
}

@TechReport{Speziale1985b,
author = {Speziale, C. G.},
title = {Second-order Closure Models for Rotating Turbulent Flows},
institution = {Institute for Computer Applications in Science and Engineering},
year = {1985},
type = {ICASE},
number = {NASA-CR-178005}
}

@article {Speziale1985c,
author = {Speziale, C. G.},
title = {Subgrid Scale Stress Models for the Large-Eddy Simulation of Rotating Turbulent Flows},
journal = {Geophys. Astrophys. Fluid Dynamics},
year = {1985},
volume = {33},
number = {},
pages = {199--222},
month = {},
note = {}
}

@TechReport{Spotts2013,
author = {Spotts, N. and Guzik, S. M. and and Gao, X.},
title = {A CFD Analysis of Compressible Flow through Convergent-Conical Nozzles},
institution = {49th AIAA Joint Propulsion Conference & Exhibit},
year = {2013},
type = {AIAA},
number = {2013-3734}
}

@MastersThesis{Spotts2015,
  author =       {Spotts, N.},
  title =        {Unsteady Reynolds-Averaged {N}avier-{S}tokes simulations of inlet flow distortion in the fan system of a gas-turbine aero-engine},
  school =       {Colorado State University},
  year =         2015,
  note =         {\url{http://hdl.handle.net/10217/170387}}
}

@TechReport{Spotts2016,
author = {Spotts, N. and Gao, X.},
title = {A Comparative Study of Turbulence Models for RANS Simulations of Rotor 67},
institution = {54th AIAA Aerospace Sciences Meeting},
year = {2016},
type = {AIAA},
number = {2016-0608}
}

@TechReport{ Steinthorsson1994,
author = { Steinthorsson, Erlendur and Modiano, D. and Colella, P.},
title = { Computations of unsteady viscous compressible flows using adaptive mesh refinement in curvilinear body-fitted grid systems},
institution = { 25th AIAA Fluid Dynamics Conference},
year = { 1994 }
}

@article {Steward2012,
author = {Steward, J. L. and Navon, I. M. and Zupanski, M. and Karmitsa, N.},
title = {Impact of Non-Smooth Observation Operators on Variational and Sequential Data Assimilation for a Limited-Area Shallow-Water Equation Model},
journal = {Quart. J. Roy. Meteor. Soc.},
year = {2012},
volume = {138},
number = {},
pages = {323--339},
month = {},
note = {}
}

@article {Stilley1967,
author = {Stilley, G. D.},
title = {Unified stability criteria for autorotating glide bomblets},
journal = {Proceedings of Conference on Dynamics and Aerodyamics of Bomblets, Technical Report AFATL-TR-67-195},
year = {1967},
volume = {1},
number = {},
pages = {},
month = {},
note = {}
}

@article {Stojkovic2003,
author = {Stojkovic, D. and Sch{\"o}n, P. and Breuer, M. and Durst, F.},
title = {On the new vortex shedding mode past a rotating circular cylinder},
journal = PF,
year = {2003},
volume = {15},
number = {5},
pages = {1257--1260},
month = {May},
note = {}
}

@article{Stolz1999,
  author =       {Stolz, S. and Adams, A.},
  title =        {An approximate deconvolution procedure for large-eddy simulation},
  journal =      PF,
  year =         {1999},
  volume =    {11},
  number =    {7},
  pages =     {1699--1701},
  month =     {July}
}

@techreport {Strickland1979,
author = {Strickland, J. H. and Webster, B. T. and Nguyen, T.},
title = {A vortex model of the Darrieus turbine: an analytical and experimental study},
institution = {Sandia Laboratories},
year = {1979},
type = {Technical Report},
number = {},
address = {},
month = {},
note = {}
}

@techreport {Strickland1975,
author = {Strickland, J. H.},
title = {The Darrieus turbine: a performance prediction model using multiple streamtubes},
institution = {Sandia Laboratories},
year = {1975},
type = {Technical Report},
number = {SAND75-0431},
address = {},
month = {October},
note = {}
}

@article {SullivanJensen2002,
author = {Sullivan, N. and Jensen, A. and Glarborg, P. and Day, M. S. and Grcar, J. F. and Bell, J. B. and Pope, C. and Kee, R. J.},
title = {Ammonia Conversion and {NO}$_x$ Formation in Laminar Coflowing Nonpremixed Methane-Air Flames},
journal = {Combust. Flame},
year = {2002},
volume = {131},
number = {},
pages = {285--298},
month = {},
note = {}
}

@article {Sun2007,
author = {Sun, Y and Wang, ZJ and Liu, Y},
title = {High-order multidomain spectral difference method for the {N}avier–{S}tokes equations on unstructured hexahedral grids},
journal = {Commun. Comput.},
year = {2007},
volume = {2},
number = {},
pages = {310--333},
month = {},
OPTurl = {http://www.global-sci.com/issue/abstract/readabs.php?vol=2&page=310&year=2007&issue=2&ppage=333/}
}

@article {Suzuki2012,
author = {Suzuki, T.},
title = {Reduced-order {K}alman-filtered hybrid simulation combining particle tracking velocimetry and direct numerical simulation},
journal = {J. Fluid Mech},
year = {2012},
volume = {709},
number = {},
pages = {249--288},
month = {},
note = {}
}

@article {Suzuki2015,
author = {Suzuki, T. and Yamamoto, F.},
title = {Hierarchy of hybrid unsteady-flow simulations integrating time-resolved {PTV} with {DNS} and their data-assimilation capabilities},
journal = {Fluid Dynamics Research},
year = {2015},
volume = {47},
number = {5},
pages = {051407},
month = {},
note = {doi:10.1088/0169-5983/47/5/051407}
}

@article {Stewartson1951,
author = {Stewartson, K.},
title = {On the impulsive motion of a flat plate in a viscous fluid},
journal = {Q J Mechanics Appl Math},
year = {1951},
volume = {4},
number = {2},
pages = {182--198},
month = {},
note = {}
}

@article {Swart2006,
author = {Swart, J. A. M. de and Groot, G. R. A. and Oijen, J. A. van and ten Thije Boonkkamp, J. H. M. and de Goey, L. P. H.},
title = {Detailed analysis of the mass burning rate of stratched flames including preferential diffusion effects},
journal = {Combust. Flame},
year = {2006},
volume = {145},
number = {1--2},
pages = {245--258},
month = {},
note = {}
}

@TechReport{Steger1978,
  author =       {Joseph L. Steger},
  title =        {Implicit Finite Difference Simulation of Flow about Arbitrary Two-Dimensional Geometries},
  OPTinstitution = {},
  year =         {1978},
  OPTkey =       {},
  type =         {AIAA},
  number =       {77-665},
  OPTaddress =   {},
  OPTmonth =     {},
  OPTnote =      {},
  OPTannote =    {}
}

@article {Su2016,
author = {Su, C. and Tu, X.},
title = {Sequential implicit sampling methods for Bayesian Inverse Problems},
journal = {SIAM/ASA J. Uncertain. Quantif. },
year = {2016},
volume = {},
number = {},
pages = {},
month = {},
note = {Under revision}
}

   #####
     #
     #
     #
     #
     #
     #

@article {Taatjes2005,
	author = {Taatjes, C. A. and Hansen, N. and McIlroy, A. and  Miller, J.
A. and Senosiain, J. P. and Klippenstein, S. J. and Qi, F. and 
Sheng, L. and Zhang, Y. and Cool, T. A. and Wang, J. and Westmoreland,
P. R. and Law, M. E. and Kasper, T. and Kohse-Hinghaus, K.},
	title = {Enols Are Common Intermediates in Hydrocarbon Oxidation},
	journal = {Science},
	year = {2005},
	volume = {308},
	number = {5730},
	pages = {1887--1889},
	month = {24 June},
	note = {A large photograph of a low pressure flame stabilized and flattened by a sintered metal burner appears on the cover of this issue.}
	}

@misc {Taatjes2005supp,
	author = {Taatjes, C. A. and et al.},
	title = {Supporting Online Material},
	howpublished = {World wide web supplement to \cite {Taatjes2005}},
	month = {},
	year = {2005},
	note = {}
	}

@article {Takagi1994,
author = {Takagi, T. and Xu, Z.},
title = {Numerical Analysis of Laminar Diffusion Flames --- Effects of Preferential Diffusion of Heat and Species},
journal = {Combust. Flame},
year = {1994},
volume = {96},
number = {},
pages = {50--59},
month = {},
note = {}
}

@techreport {Takita2006,
author = {Takita, K. and Ju. Y.},
title = {Effect of radical addition on extinction limits of H$_2$ and CH$_4$ flames},
institution = {AIAA},
year = {2006},
type = {Paper},
number = {AIAA-2006-1029},
address = {},
month = {},
note = {}
}

@article {Talagrand1987,
author = {Talagrand, O. and Courtier, P.},
title = {Variational assimilation of meteorological observations with the adjoint vorticity equation. I: Theory.},
journal = {Journal of the Meteorological Society},
volume = {113},
year = {1987},
pages = {1311-1328}
}
@article {Talagrand1997,
author = {Talagrand, O.},
title = {Assimilation of observations-An introduction},
journal = {Journal of the Meteorological Society of Japan},
volume = {75},
year = {1997},
pages = {191--209}
}


@article {Tamura1998, 
author = {Tamura, M. and Luque, J. and Harrington, J. E. and Berg, P. A. and Smith, G. P. and Jeffries, J. B. and Crosley, D. R.}, 
title = {Laser-induced fluorescence of seeded nitric oxide as a flame thermometer},
journal = {Appl. Phys. B},
year = {1998}, 
volume = {66}, 
number = {}, 
pages = {503--510},
month = {}, 
note = {} 
}

@article {Tanoff1996,
author = {Tanoff, M. A. and Smooke, M. D. and Osborne, R. J. and Brown, T. M. and Pitz, R. W.},
title = {},
journal = {Proc. Combust. Inst.},
year = {1996},
volume = {26},
number = {},
pages = {1121--1128},
month = {},
note = {}
}

@article {Tanahashi2000,
author = {Tanahashi, M. and Fujimura, M. and Miyauchi, T.},
title = {Coherent fine scale eddies in turbulent premixed flames},
journal = {Proc. Combust. Inst.},
volume = {28},
year = {2000},
pages = {529--535}
}

@article{Tanahashi2002,
author = {Tanahashi, M. and Nada, Y. and Ito, Y. and Miyauchi, T.},
title = {Local flame structure in the well-stirred reactor regime},
volume = {29},
year = {2002},
journal = {Proc. Combust. Inst.},
pages = {2041--2049}
}


@Book{Tao2003,
  author =    {Tao, G.},
  title =        {Adaptive Control Design and Analysis},
  publisher =    {Wiley-IEEE Press},
  year =         {2003},
}

@article {Tatebe2012,
author = {Tatebe, H. and Ishii, M. and Mochizuki, T. and Chikamoto, Y. and Sakamoto, T. T. and Komuro, Y. and Mori, M. and Yasunaka, S. and Watanabe, M. and Ogochi, K. and Suzuki, T. and Nishimura, T. and Kimoto, M.},
title = {The Initialization of the {MIROC} Climate Models with Hydrographic data assimilation for decadal prediction},
journal = {Journal of the Meteorological Society of Japan},
year = {2012},
volume = {90A},
number = {},
pages = {275--294},
month = {},
note = {}
}

@article {tenThijeBoonkkamp,
author = {ten Thije Boonkkamp, J. H. M. and de Goey, L. P. H.},
title = {A flamelet model for premixed stretched flames},
journal = {Combustion Science and Technology},
year = {1999},
volume = {149},
number = {},
pages = {183--200},
month = {},
note = {}
}

@article{Terashima2012,
title = {Approach for simulating gas--liquid-like flows under supercritical pressures using a high-order central differencing scheme},
author = {Terashima, H. and Koshi, M.},
journal = JCP,
volume = {231},
number = {20},
pages = {6907--6923},
year = {2012},
issn = {0021-9991},
OPTdoi = {https://doi.org/10.1016/j.jcp.2012.06.021},
OPTurl = {http://www.sciencedirect.com/science/article/pii/S0021999112003361}
}

@article {Thevenin2005,
author = {Th$\acute{e}$venin, D.},
title = {Three-dimensional direct simulations and structure of expanding turbulent methane flames},
volume = {30},
year = {2005},
journal = {Proc. Combust. Inst.},
pages = {629--637}
}


@article {Thomsen2001,
author = {Thomsen, D. D. and Laurendeau, N. M.},
title = {{LIF} measurements and modeling of nitric oxide concentration in atmospheric counterflow premixed flames},
journal = {Combust. Flame},
year = {2001},
volume = {124},
number = {},
pages = {350--369},
month = {},
note = {}
}

@article {Timmes1992,
author = {Timmes, F. X. and Woosley, S. E.},
title = {The Conductive Propagation of Nuclear Flames {I}. Degenerate {C}+{O} and {O}+{Ne}+{Mg} White Dwarfs},
journal = {Astrophys. J.},
year = {1992},
volume = {396},
pages = {649--667}
}

@article {Timmes1994,
author = {Timmes, F. X. and Woosley, S. E. and Taam, R. E.},
title = {The Conductive Propagation of Nuclear Flames {II}. Flames in {C}+{O} and {O}+{Ne}+{Mg} Cores},
journal = {Astrophys. J.},
year = {1994},
volume = {420},
pages = {348--363}
}

@unpublished {tinseth2010,
author = {Tinseth, Randy},
title = {Current Market Outlook 2010},
note = {{\ttfamily http://www.boeing.com/cmo}},
month = {July},
year = {2010}
}

@article {Titi1990,
author = {Titi, E. S.},
title = {On approximate {I}nertial {M}anifolds to the {N}avier-{S}tokes equations},
journal = {Journal of Mathematical Analysis and Applications},
year = {1990},
volume = {149},
pages = {540--557}
}

@article {Todling1994,
author = {Todling, R.and Cohn, S. E.},
title = {Suboptimal schemes for atmosheric data assimilation based on the Kalman filter},
journal = {Mon. Wea. Rev.},
year = {1994},
volume = {122},
pages = {2530--2557}
}

@book{Toro2009,
author = {Toro, E. F.},
title = {Riemann Solvers and Numerical Methods for Fluid Dynamics},
publisher = {Springer-Verlag Berlin Heidelberg},
year = {2009},
edition = {3}
}


@Article{Toth1993,
  author =       {Toth, Z. and E. Kalnay},
  title =        { Ensemble forecasting at NCEP: The generation of perturbations},
  journal =      {Bull. Amer. Meteor. Soc.},
  year =         {1993},
  OPTkey =       {},
  OPTvolume =    {},
  number =    {74},
  pages =     {2317-2330},
  OPTmonth =     {},
  OPTnote =      {},
  OPTannote =    {}
}

@inproceedings {Towery2014,
author={Towery, C. A. Z. and Poludnenko, A. Y. and Urzay, J. and Ihme, M. and Hamlington, P. E.},
title={Spectral energy dynamics in premixed flames},
booktitle = {Proceedings of the Summer Program},
year={2014}
}

@article{Towery2016,
title = {Spectral kinetic energy transfer in turbulent premixed reacting flows},
author = {Towery, C. A. Z. and Poludnenko, A. Y. and Urzay, J. and O'Brien, J. and Ihme, M. and Hamlington, P. E.},
journal = {Phys. Rev. E},
volume = {93},
issue = {5},
pages = {053115},
numpages = {11},
year = {2016},
month = {May},
publisher = {American Physical Society},
doi = {10.1103/PhysRevE.93.053115},
url = {https://link.aps.org/doi/10.1103/PhysRevE.93.053115}
}

@article {Tran2014,
author = {Tran, A. P. and Vanclooster, M. and Zupanski, M. and Lambot, S.},
title = {Joint estimation of soil moisture profile and hydraulic parameters by ground-penetrating radar data assimilation
with maximum likelihood ensemble filter},
journal = {Water Resources Research},
year = {2014},
volume = {50},
pages = {},
note = {doi:10.1002/2013WR014583}
}

@book{Trebotich2008,
	Address = {},
	Author = {Trebotich, D. and Van Straalen, B. and Graves, D. and Colella, P.},
	Month = {July},
	Publisher = {Institute of Physics Publishing},
	Series = {Journal of Physics Conference Series 2008},
	Title = {Performance of Embedded Boundary Methods for CFD with Complex Geometry},
	Volume = {125},
	Year = {2008}}
        
@Article{Trebotich2015,
  author =       {Trebotich, D. and Graves, D. T.},
  title =        {An adaptive finite volume method for the incompressible {N}avier-{S}tokes equations in complex geometries},
  journal =      {Comm. App. Math. and Comp. Sci.},
  year =         2015,
  volume =       10,
  number =       1,
  pages =        {43--82}
}

@article {Trouve1994,
author = {Trouv\'e, A. and Poinsot, T. J.},
title = {The evolution equation for the flame surface density in turbulent premixed combustion},
journal = {J. Fluid Mech.},
volume= 278,
pages = {1--31},
year = {1994}
}

@article {Truffaut1999,
author = {Truffaut, J.-M. and Searby, G.},
title = {Experimental Study of the {D}arrieus-{L}andau instability on an inverted-`{V}' flame, and measurement of the {M}arkstein number},
journal = {Combustion Science and Technology},
year = {1999},
volume = {149},
number = {},
pages = {35--52},
month = {},
note = {}
}

@article {Tse2000,
author = {S. D. Tse and D. L. Zhu and C. K. Law},
title = {Morphology and burning rates of expanding spherical flames in $\rm {H}_2$/$\rm {O}_2$/Inert Mixtures up to 60 Atmospheres},
journal = {Proc. Combust. Inst.},
year = {2000},
volume = {28},
number = {},
pages = {1793--1800},
month = {},
note = {}
}

@article {Tseng1993,
author = {Tseng, L.-K. and Ismail, M. A. and Faeth, G. M.},
title = {Laminar Burning Velocities and {M}arkstein Numbers of Hydrocarbon / Air Flames},
journal = {Combust. Flame},
year = {1993},
volume = {95},
number = {},
pages = {410--425},
month = {},
note = {}
}

@article {Tseng2003,
author = {Tseng, T. and Freziger, J.},
title = {A ghost-cell immersed boundary method for flow in complex geometry},
journal = {J. Comput. Phys.},
year = {2003},
volume = {192},
number = {},
pages = {593--623},
month = {},
note = {}
}

@article {Tsuboi2002,
author = {Tsuboi, N. and Katoh, S. and Hayashi, A. K.},
title = {Three-dimensional numerical simulations for hydrogen/air detonation: rectangular and diagonal structures},
journal = {Proc. Combust. Inst.},
year = {2003},
volume = {29},
number = {},
pages = {2783--2788},
month = {},
note = {}
}

@article {Tu2013,
author = {Tu, X. and Li, J.},
title = {A unified dual-primal finite element tearing and interconnecting approach for incompressible {S}tokes equations},
journal = {Int. J. Numer. Meth. Fluids},
year = {2013},
volume = {94},
number = {2},
pages = {128--149},
month = {},
note = {}
}

@article {Tu2015,
author = {Tu, X. and Li, J.},
title = {A {FETI}-{DP} type domain decomposition algorithm for three-dimensional incompressible {S}tokes equations},
journal = {SIAM J. Numer. Anal.},
year = {2015},
volume = {53},
number = {2},
pages = {720--742},
month = {},
note = {}
}

@article {Tu2016,
author = {Tu, X. and Wang, B.},
title = {A {BDDC} algorithm for second-order elliptic problems with hybridizable discontinuous Galerkin discretizations},
journal = {Electronic Transactions on Numerical Analysis},
year = {2016},
volume = {45},
number = {},
pages = {354--370},
month = {},
note = {}
}

@inproceedings {Tuncer2007,
title={Dynamics, NO$_x$ and Flashback Characteristics of Confined Pre-Mixed Hydrogen Enriched Methane Flames},
booktitle = {Proceedings of the ASME Turbo Expo},
author = {O. Tuncer and S. Acharya and J.-H. Uhm},
year = {2007},
editor = {},
pages = {857--868},
address = {Montreal, Canada},
note = {GT2007-28158}
}

@article {Turns1995,
author = {Turns, S. R.},
title = {Understanding {NO}$_x$ formation in nonpremixed flames: experiments and modeling},
journal = {Prog. Energy Combust. Sci.},
year = {1995},
volume = {21},
number = {},
pages = {361--385},
month = {},
note = {}
}

@book {Turns2000,
author = {Turns, S. R.},
title = {An Introduction to Combustion},
year = {2000},
publisher = {McGraw-Hill},
edition = {second},
address = {New York}
}

   #   #
   #   #
   #   #
   #   #
   #   #
    # #


@article {Udaykumar1996,
author = {Udaykumar, H. and Shyy, W. and Rao, M.},
title = {A mixed {E}ulerian–{L}agrangian method for fluid flows with complex and moving boundaries},
journal = {Int. J. Numer. Methods},
year = {1996},
volume = {22},
number = {},
pages = {691--705},
month = {},
note = {}
}

@article {Udaykumar1999,
author = {Udaykumar, H. and Mittal, R. and Shyy, W.},
title = {Computation of solid–liquid phase fronts in the sharp interface limit on fixed grids},
journal = JCP,
year = {1999},
volume = {153},
number = {},
pages = {662--709},
month = {},
note = {}
}

@article {Udaykumar2001,
author = {Udaykumar, H. and Mittal, R. and Rampunggoon, P. and Khanna, A.},
title = {A sharp interface {C}artesian grid method for simulating flows with complex moving boundaries},
journal = JCP,
year = {2001},
volume = {174},
number = {},
pages = {345--380},
month = {},
note = {}
}

@article {Udin2014,
author = {Udin, H. and Kramer, R. and Pantano, C.},
title = {A {C}artesian-based embedded geometry technique with adaptive high-order finite differences for compressible flow around complex geometries},
journal = {J. Comput. Phys.},
year = {2014},
volume = {262},
number = {},
pages = {379--407},
month = {},
note = {}
}

@article {Uykur2001,
author = {Uykur, C. and Henshaw, P.F. and Ting, D.S.K. and Barron, R.M.},
title = {Effects of addition of electrolysis products on methane/air laminar combustion},
journal = {Int. J. of Hydrogen Energy},
year = {2001},
volume = {26},
number = {},
pages = {265--273},
month = {},
note = {}
}


   #   #
   #   #
   #   #
   #   #
   #   #
    # #
     #

@article {Vagelopoulos1994,
author = {Vagelopoulos, C.M. and Egolfopoulos, F.N. and Law, C.K.},
title = {Further Considerations on the Determination of Laminar Flame Speeds with the Counterflow Twin-Flame Technique},
journal = {Proc. Combust. Inst.},
year = {1994},
volume = {25},
number = {},
pages = {1341},
month = {},
note = {}
}

@article {Vagelopoulos1998,
author = {Vagelopoulos, C. M. and Egolfopoulos, F. N.},
title = {Direct experimental determination of laminar flame speeds},
journal = {Proc. Combust. Inst.},
year = {1998},
volume = {27},
number = {},
pages = {513--519},
month = {},
note = {Formerly {\it Twenty-Seventh Symposium (International) on Combustion.}}
}

@article {VandenAbeele2008,
author = {Van den Abeele, K and Lacor, C and Wang, ZJ},
title = {On the stability and accuracy of the spectral difference method},
journal = {J. Sci. Comput.},
year = {1995},
volume = {7},
number = {5},
pages = {1171--1172},
month = {},
OPTdoi = {10.1007/s10915-008-9201-0}
}

@article {vanderBoon2012,
author = {van der Boon, R. M. and Nuis, R. J. and Van Mieghem, N. M. and Benitez, L. M. and van Geuns, R. J. and Galema, T. W. and van Domburg, R. T. and Geleijnse, M. L. and Dager, A. and de Jaegere, P. P., C and Wang, ZJ},
title = {Clinical outcome following Transcatheter Aortic Valve Implantation in patients with impaired left ventricular systolic function},
journal = {Catheterization and cardiovascular interventions: official journal of the Society for Cardiac Angiography \& Interventions},
year = {2012},
volume = {79},
number = {},
pages = {702--710},
month = {},
OPTdoi = {}
}

@article {VanderVen1995,
author = {van der Ven, H.},
title = {A family of large eddy simulation {LES} filters with nonuniform filter widths},
journal = {Phys. Fluids},
year = {2008},
volume = {37},
number = {},
pages = {162--188},
month = {},
}

@article{VanLeer1977,
author = {{Van Leer}, B.},
title = {Towards the ultimate conservative difference scheme. {IV}. {A} new approach to numerical convection},
journal = JCP,
volume = {23},
number = {3},
pages = {276-299},
year = {1977},
issn = {0021-9991},
}

@article {VanLeeuwen2009,
author = {VanLeeuwen, P. J.},
title = {Particle Filtering in Geophysical System},
journal = {Mon. Wea. Rev.},
year = {2009},
volume = {2137},
number = {},
pages = {4089--4114},
month = {},
note = {}
}

@article {VanLeeuwen2010, 
author = {van Leeuwen, P. J.}, 
title = {Nonlinear data assimilation in geosciences: an extremely efficient particle filter},
journal = {Quarterly Journal of Royal Meteorological Society}, 
year = {2010}, 
volume = {136}, 
number = {}, 
pages = {1991-1999}, 
month = {}, 
note = {} 
}

@article {vanRees2011, 
author = {van Rees, W. M. and Leonard, A. and Pullin, D. I. and Koumoutsakos, P.}, 
title = {A comparison of vortex and pseudo-spectral methods for the simulation of periodic vortical flows at high Reynolds numbers},
journal = {J. Comput. Phys.}, 
year = {2011}, 
volume = {230}, 
number = {8}, 
pages = {2794-2805}, 
month = {April}, 
note = {} 
}

@InProceedings {VanStraalen2011,
author = {B. {Van Straalen} and P. Colella and D. T. Graves and N. Keen},
title = {Petascale Block-Structured {AMR} Applications Without Distributed Meta-data},
booktitle = {Proceedings, Part II. Lecture Notes in Computer Science},
year = {2011},
organization = {Euro-Par 2011 Parallel Processing -- 17th International Conference},
publisher = {Springer},
note = {{ISBN 978-3-642-23396-8}}
}

@article {Vasilyev1998, 
author = {Vasilyev, O. and Lund, T. S. and Moin, P.}, 
title = {A general class of commutative filters for {LES} in complex geometries},
journal = {J. Comput. Phys.}, 
year = {1998}, 
volume = {146}, 
number = {}, 
pages = {82--104}, 
note = {} 
}

@article {Vassberg2010, 
author = {Vassberg, J and Tinoco, E and Mani, M and Rider, B and Zickuhr, T and Levy, D and Brodersen, O and Eisfeld, B and Crippa, S and Wahls, R and Morrison, J and Mavriplis, D and Murayama, M}, 
title = {Summary of the Fourth AIAA CFD Drag Prediction Workshop},
journal = {28th AIAA Applied Aerodynamics Conf., Chicago, IL, 28 June-1 July}, 
year = {2010}, 
volume = {}, 
number = {}, 
pages = {}, 
note = {} 
}

@Article{Vervisch1998,
  author =       {Vervisch, L. and Poinsot, T.},
  title =        {Direct numerical simulation of non-premixed turbulent flames},
  journal =      {Annu. Rev. Fluid Mech.},
  year =         {1998},
  volume =    {30},
  pages =     {655-691}
}


@article {Vervisch2004,
author = {Vervisch, L. and Hauguel, R. and Domingo, P. and Rullaud, M.},
title = {Three facets of turbulent combustion modelling: {DNS} of premixed {V}-flame, {LES} of lifted nonpremixed flame and {RANS} of jet-flame},
journal = {J. Turbulence},
year = {2004},
volume = {5},
number = {},
pages = {1--36},
month = {},
note = {}
}

@article {Veynante2002,
author = {Veynante, D. and Vervisch, L.},
title = {Turbulent combustion modeling},
journal = {Prog. Energy Combust. Sci.},
year = {2002},
volume = {28},
number = {},
pages = {193--266},
month = {},
note = {}
}


@InCollection{Veynante2009,
  author =       {Veynante, D.},
  title =        {Large Eddy Simulations of Turbulent Combustion},
  booktitle =    {Turbulence and Interactions},
  publisher = {Springer, Berlin, Heidelberg},
  year =      {2009},
  editor =    {Deville M. and L$\^e$ TH., Sagaut P.},
  volume =    {105},
  note =      {Notes on Numerical Fluid Mechanics and Multidisciplinary Design}
  }
 

@article {Veynante2001,
author = {Veynante, D. and Duclos, J. M. and Piana, J.},
title = {Experimental analysis of flamelet meodels for premixed turbulent combustion},
journal = {Proc. Combust. Inst.},
year = {1994},
volume = {25},
number = {},
pages = {1249--1256},
month = {},
note = {}
}

@misc{visit,
  author =    {VisIt},
  title =     {Software that delivers parallel interactive visualization},
  howpublished = {https://wci.llnl.gov/codes/visit/},
  month =     {},
  year =      {2000},
  note =      {Lawrence Livermore National Laboratory},
  
}

@misc{crd,
  author =    {DOE},
  title =     {Co-Designing Exascale Architectures and Algorithms for Real-World Combustion Simulations},
  howpublished = {http://crd.lbl.gov/news-and-publications/news/2011/co-designing-exascale-architectures-and-algorithms-for-real-world-combustion-simulations/},
  month =     {},
  year =      {2011},
  note =      {Lawrence Berkeley National Laboratory},
  
}



http://crd.lbl.gov/news-and-publications/news/2011/co-designing-exascale-architectures-and-algorithms-for-real-world-combustion-simulations/

@techreport {Hasselbrink1996,
author = {Hasselbrink, E. F. and Mungal, M. G.},
title = {An analysis of the time-averaged properties of the far field of the transverse jet},
institution = {AIAA},
year = {1996},
type = {Paper},
number = {AIAA 96-0201},
address = {},
month = {},
note = {}
}

@article {Vreman1994, 
author = {Vreman, B. and Geurts, B. and Kuerten, H.}, 
title = {On the formulation of the dynamic mixed subgrid-scale model},
journal = PF,
year = {1994}, 
volume = {6}, 
number = {12}, 
pages = {4057--4059}, 
month = {}, 
note = {} 
}

@article {Vyrodov1995a, 
author = {Vyrodov, A. O. and Heinze, J. and Dillmann, M. and Meier, U. E. and Stricker, W.}, 
title = {Laser-induced fluorescence thermometry and concentration measurements on {NO} {A}-{X} $(0,0)$ transitions in the exhaust gas of high pressure {CH}$_4$/air flames},
journal = {Appl. Phys. B}, 
year = {1995}, 
volume = {61}, 
number = {}, 
pages = {409--414}, 
month = {}, 
note = {} 
}

@techreport {Vijaykant2005, 
author = {Vijaykant, S. and Agrawal, A.K.},
title = {Numerical investigation of swirl stablized combustion of lean premixed methane and hydrogen enriched methane},
institution = {AIAA},
year = {2005},
type = {Paper},
number = {AIAA 2005-167},
address = {},
month = {},
note = {}
}

@article {Visbal2002, 
author = {Visbal, MR and Gaitonde, DV}, 
title = {On the use of higher-order finite-difference schemes on curvilinear and deforming meshes},
journal = {J. Comput. Phys.}, 
year = {2002}, 
volume = {181}, 
number = {}, 
pages = {155--185}, 
month = {}, 
note = {} 
}

@article {Viskanta1993, 
author = {Viskanta, R.}, 
title = {Heat transfer to impinging isothermal and flame jets},
journal = {Exp. Thermal and Fluid Sci.}, 
year = {1993}, 
volume = {6}, 
number = {}, 
pages = {111--134}, 
month = {}, 
note = {} 
}

@article {Viskanta1987, 
author = {Viskanta, R. and Menguc, M.}, 
title = {Radiation heat transfer in combustion systems},
journal = {Prog. Energy Combustion Sci.}, 
year = {1987}, 
volume = {13}, 
number = {}, 
pages = {97--160}, 
month = {}, 
note = {} 
}

@PhdThesis{Viswanath1998,
author = {Viswanath, D.},
type = {{P}h.{D}. dissertation},
title = {Lyapunov exponents from random Fibonacci sequences to the Lorenz equations},
school = {Cornell University},
year = {1998}
}

@article{Voelkl2000,
author = {Voelkl, T. and Pullin, D. I. and Chan, D. C.},
title = {A physical-space version of the stretched-vortex subgrid-stress model for large-eddy simulation},
journal = PF,
volume = {12},
number = {7},
pages = {1810--1825},
year = {2000},
month = {July}
}

   #     #
   #     #
   #     #
   #     #
   #  #  #
   # # # #
    #   #

@article {WSJ2004,
author = {},
title = {},
journal = {Wall Street Journal},
year = {April 1, 2004},
volume = {},
number = {},
pages = {1},
month = {},
note = {}
}

@article{Waksman2014,
author  = {Waksman, R. and Minha, S.},
title   = {Stroke after Aortic Valve Replacement: The Known and Unknown},
journal = {Circulation},
volume  = {},
number  = {},
year    = {2014},
month   = {},
pages   = {}
}

@InProceedings{Walters2017,
  author = {Walters, S. and Gao, X. and Guzik, S.},
  title = {Computational Predictions of Forces on Autorotors at High {R}eynolds Numbers},
  booktitle = {23rd AIAA Computational Fluid Dynamics Conference},
  year = {2017},
  number = {AIAA 2017-4116},
  organization = {AIAA Aviation Forum},
  note = {\url{https://doi.org/10.2514/6.2017-4116}}
}

@InProceedings{Walters2018,
  author = {Walters, S. and Guzik, S. and Gao, X.},
  title = {Favre-Averaged Spatiotemporal-Filtered Large Eddy Simulation},
  booktitle = {2018 AIAA Aerospace Sciences Meeting},
  year = {2018},
  number = {AIAA 2018-0373},
  organization = {AIAA SciTech Forum},
  note = {\url{https://doi.org/10.2514/6.2018-0373}}
}

@InProceedings{Walters2019a,
  author = {Walters, S. and Guzik, S. and Gao, X.},
  title = {Evaluation of the Stretched-Vortex Subgrid-Scale Model for Large-Eddy Simulation with a Fourth-Order Finite Volume Algorithm},
  booktitle = {2019 AIAA SciTech Forum},
  year = {2019},
  number = {AIAA 2019-1886},
  OPTorganization = {AIAA SciTech Forum},
  note = {\url{https://doi.org/10.2514/6.2019-1886}}
}

@Unpublished{Walters2019b,
  author =       {Walters, S. and Gao, X. and Johansen, H. and Guzik, S.},
  title =        {Assessing Stretched-Vortex Subgrid-Scale Models in Finite Volume Methods for Unbounded Turbulent Flows},
  note =         {Accepted for the Journal of Flow,Turbulence and Combustion},
  OPTkey =       {},
  OPTmonth =     {},
  year =      {2019},
  OPTannote =    {}
}
@InProceedings{Walters2020,
  author = {Walters, S. and Gao, X. and Guzik, S.},
  title = {ELarge-Eddy Simulations of Wall-Bounded Flows Using High-Order Finite Volume Methods with Adaptive Mesh Refinement},
  booktitle = {2020 AIAA SciTech Forum},
  year = {2020},
  number = { },
  OPTorganization = {AIAA SciTech Forum},
  note = {}
}

@article {Wang2006,
author = {Wang, P. and Wehrmeyer, J. A. and Pitz, R. W.},
title = {Stretch rate of tubular premixed flames},
journal = {Combust. Flame},
volume = {145},
pages = {401--414},
year = {2006}
}

@article {Wang2007,
author = {Wang, ZJ},
title = {High-order methods for the {E}uler and {N}avier-{S}tokes equations on unstructured grids},
journal = {Prog. Aerosp. Sci.},
volume = {43},
pages = {1--41},
year = {2007}
}

@article {Wang2008,
author = {Wang, X. and Barker, D. M. and Snyder, C. and Hamill, T. M.},
title = {A hybrid {ETKF-3DVAR} data assimilation scheme for the WRF model. Part I: Observation system simulation experiment},
journal = {Mon. Wea. Rev.},
volume = {136},
pages = {5116--5131},
year = {2008}
}

@article{Wang2013,
author = {Wang, Z. J. and Fidkowski, K. and Abgrall, R. and Bassi, F. and Caraeni, D. and Cary, A. and Deconinck, H. and Hartmann, R. and Hillewaert, K. and Huynh, H. T. and Kroll, N. and May, G. and Persson, P.-O. and van Leer, B. and Visbal, M.},
title = {High-order {CFD} methods: current status and perspective},
journal = {Int. J. Numer. Methods Fluids},
volume = {72},
number = {8},
issn = {1097-0363},
OPTurl = {http://dx.doi.org/10.1002/fld.3767},
OPTdoi = {10.1002/fld.3767},
pages = {811--845},
keywords = {High-order methods, CFD},
year = {2013}
}

@article{Wang2014,
author = {Wang, Z. J.},
title = {High-order computational fluid dynamics tools for aircraft design},
journal = {Phil. Trans. R. Soc. A},
volume = {372},
number = {2022},
issn = {1364-503X},
OPTurl = {https://royalsocietypublishing.org/doi/10.1098/rsta.2013.0318},
OPTdoi = {10.1098/rsta.2013.0318},
pages = {},
keywords = {High-order, CFD},
year = {2014}
}

@Unpublished{Wang2019,
  author =       {Wang, Y. and Guzik, S. and Zupanski, M. and Tu, X. and Gao, X.},
  title =        {Improving Uncertainty Estimation in Turbulence Modeling With Maximum Likelihood Ensemble Filter},
  note =         {Manuscript in preparation for Journal of Computational Physics},
  OPTkey =       {},
  OPTmonth =     {},
  year =      {2019},
  OPTannote =    {}
}

@InProceedings{Wang2020,
  author = {Wang, Y. and Walters, S. and Guzik, S. and Gao, X.},
  title = {Data-Assimilated Large Eddy Simulation of Bluff-Body Stabilized Premixed Flames},
  booktitle = {2020 AIAA SciTech Forum},
  year = {2020},
  number = { },
  OPTorganization = {AIAA SciTech Forum},
  note = {}
}

@PhdThesis{Wang2022,
author = {Wang, Y.},
type = {{P}h.{D}. dissertation},
title = {Bayesian Data Assimilation for {CFD} Modeling of Turbulent Combustion},
school = {Colorado State University},
year = {2022}
}

@article{Wangard2001,
  title={ A numerically stable method for integration of the multi-component species diffusion equations},
  author={Wangard, W and Dandy, D. and Miller, B.},
  journal={J. Comput. Phys.},
  volume={174},
  number={},
  pages={460--472},
  year={2001},
  publisher={Elsevier}
}

@article {WangTrouve2004,
author = {Wang, Y. and Trouv\'e, A.},
title = {Artificial acoustic stiffness reduction in fully compressible, direct numerical simulation of combustion},
journal = {Combust. Theory Model.},
year = {2004},
volume = {8},
number = {},
pages = {633--660},
month = {},
note = {}
}

@book {WarnatzPeters1982,
author = {},
editor = {Peters, N. and Warnatz, J.},
title = {Numerical Methods in Laminar Flame Propagation},
publisher = {Vieweg-Verlag},
year = {1982},
volume = {6},
series = {Notes on numerical fluid mechanics},
address = {Braunschweig},
edition = {},
month = {},
note = {Proceedings of a GAMM workshop held at Aachen on October 12-14, 1981.}
}

@article {Warnatz1978,
author = {Warnatz, J.},
title = {Calculation of the Structure of Laminar Flat Flames {II}: Flame Velocity of Freely Propagating Hydrogen-Air and Hydrogen-Oxygen Flames},
journal = {Ber. Bunsenges. Phys. Chem.},
year = {1978},
volume = {82},
number = {},
pages = {643--649},
month = {},
note = {}
}

@incollection {Warnatz1982,
author = {Warnatz, J.},
title = {Influence of transport models and boundary conditions on flame structure},
booktitle = {Numerical Methods in Laminar Flame Propagation},
editor = {Peters, N. and Warnatz, J.},
publisher = {Vieweg-Verlag},
address = {Braunschweig},
pages = {87--111},
year = {1982}
}

@incollection {Warnatz1984,
author = {Warnatz, J.},
title = {Rate Coefficients in the {C}/{H}/{O} System},
booktitle = {Combustion Chemistry},
year = {1984},
editor = {Gardiner Jr., W. C.},
pages = {197--360},
organization = {},
publisher = {Springer-Verlag},
address = {New York},
month = {},
note = {}
}

@book {Warnatz2001,
author = {Warnatz, J. and Maas, U. and Dibble, R. W.},
title = {Combustion},
year = {2001},
publisher = {Springer-Verlag},
edition = {3rd},
address = {Berlin}
}

@InProceedings{Weinmeister2017,
  author =       {Weinmeister, J. and Xie, N. and Gao, X. and Prasad, A. K. and Roy, S.},
  title =        {Combining a Reduced Polynomial Chaos Expansion Approach with Universal {K}riging for Uncertainty Quantification},
  booktitle = {8th AIAA Theoretical Fluid Mechanics Conference},
  year =      2017,
  number =    {AIAA 2017-3481},
  organization = {AIAA Aviation Forum},
  note =      {\url{https://doi.org/10.2514/6.2017-3481}}
}

@InProceedings{Weinmeister2018,
  author =       {Weinmeister, J. and Xie, N. and Gao, X. and Prasad, A. K. and Roy, S.},
  title =        {Analysis of a Polynomial Chaos-{K}riging Metamodel for Uncertainty Quantification in Aerospace Applications},
  booktitle = {2018 AIAA/ASCE/AHS/ASC Structures, Structural Dynamics, and Materials Conference},
  year =      2018,
  number =    {AIAA 2018-0911},
  organization = {AIAA SciTech Forum},
  note =      {\url{https://doi.org/10.2514/6.2018-0911}}
}

@article {Wendt1974, 
author = {J. O. L. Wendt and C. V. Sternling}, 
title = {Effect of Ammonia in Gaseous Fuels on {NO}x Emissions}, 
journal = {J. Air Poll. Control Ass.}, 
volume = {24}, 
pages = {1055--1058}, 
year = {1974}
}

@inproceedings {Wernet1999,
author = {Wernet, M. P.},
title = {Fuzzy logic enhanced digital PIV processing software},
year = {1999},
booktitle = {Proceedings of the 18th International Congress on Instrumentation for Aerospace
Simulation Facilities},
note = {Toulouse, France}
}

@article {Westbrook1981,
author = {Westbrook, C. K. and Dryer, F. L.},
title = {Simplified reaction mechanisms for the oxidation of hydrocarbon fuels in flames},
journal = {Combust. Sci. Technol.},
year = {1981},
volume = {27},
number = {},
pages = {31--43},
month = {},
note = {}
}

@Article{Westbrook2005,
  author =       {Westbrook, C .K. and Mizobuchi, Y. and Poinsot, T. J. and Smith, P. J. and Warantz, J.},
  title =        {Computational Combustion},
  journal =      {Proc. Combust. Inst.},
  year =         {2005},
  volume =    {30},
  number=     {1},
  pages =     {125-157}
}

@article{Westbrook2009,
  author = {Westbrook, C., Pitz and W.J., Herbinet and O. and Curran, H. J. and Silke,  E. J.},
 title = {A comprehensive detailed chemical kinetic reaction mechanism for combustion of n-alkane hydrocarbons from n-octane to n-hexadecane},
 journal = {Combust. Flame}, 
 volume = {156},
 year = {2009},
 pages = {181-199}
}

@InProceedings{Wheatley2017,
  author =       {Wheatley, B. B. and Donahue, T. H. and Catton, K.},
  title =        {An Active Learning Environment to Improve First-Year Mechanical Engineering Retention Rates and Software Skills},
  year =         {2017},
  number =       {18212},
  organization = {American Society for Engineering Education},
}

@article{Whitaker1998,
  author = {Whitaker, J. S. and Loughe, A. F.},
 title = {The Relationship between Ensemble Spread and Ensemble Mean Skill.},
 journal = {Mon. Wea. Rev.}, 
 volume = {126},
 year = {1998},
 pages = {3292--3302}
}



@article{Whitaker2002,
  author = {Whitaker, J. S. and Hamill, T. M.},
 title = {Ensemble data assimilation without perturbed observations},
 journal = {Mon. Wea. Rev.}, 
 volume = {130},
 year = {2002},
 pages = {1913--1924}
}




@Book{White1991,
  author =    {White, F. M.},
  editor =    {},
  title =        {Viscous Fluid Flow},
  publisher =    {McGraw-Hill},
  year =         {1991},
  OPTkey =       {},
  OPTvolume =    {},
  OPTnumber =    {},
  OPTseries =    {},
  OPTaddress =   {New York, NY},
  OPTedition =   {},
  OPTmonth =     {},
  note =      {pp. 132--143},
  OPTannote =    {}
}

@Book{White2011,
  author =    {White, F. M.},
  editor =    {},
  title =        {Fluid Mechanics},
  publisher =    {McGraw-Hill},
  year =         {2011},
  OPTkey =       {},
  OPTvolume =    {},
  OPTnumber =    {},
  OPTseries =    {},
  OPTaddress =   {New York, NY},
  OPTedition =   {7th},
  OPTmonth =     {},
  note =      {},
  OPTannote =    {}
}

@TechReport{Wiart2016,
  author =       {Carton de Wiart, C. and Murman, S. M.},
  title =        {Extending the dynamic slip boundary condition to
variational multi-scale methods
},
  institution =  {Center for Turbulence Research},
  year =         {2016},
  OPTkey =       {},
  OPTtype =      {},
  OPTnumber =    {},
  OPTaddress =   {},
  OPTmonth =     {},
  note =      {Proceedings of the Summer Program},
  OPTannote =    {}
}

@article {Wicksall2005,
author = {Wicksall, D.W. and Agrawal, A.K. and Shefer, R.W. and Kelley, J.O.},
title = {Influence of hydrogen addition on flow structure in confined swirling methane flame},
journal = {J. of Propulsion and Power},
year = {2005},
volume = {21},
number = {},
pages = {16--24},
month = {},
note = {}
}

@article {Wiegmann1998,
author = {Wiegmann, A. and Bube, K.P.},
title = {The explicit-jump immersed interface method: finite difference methods for {PDE}s with piecewise smooth solutions},
journal = {SIAM Journal on Numerical Analysis},
year = {1998},
volume = {37},
number = {},
pages = {827--862},
month = {},
note = {}
}

@article {Wiegmann2000,
author = {Wiegmann, A. and Bube, K.P.},
title = {The explicit-jump immersed interface method: finite difference methods for {PDE}s with piecewise smooth solutions},
journal = {SIAM Journal on Numerical Analysis},
year = {2000},
volume = {37},
number = {},
pages = {827--862},
month = {},
note = {}
}

@article {Wilcox2006,
author = {Wilcox, D. C.},
title = {Formulation of the k-omega turbulence model revisited},
journal = {AIAA Journal},
year = {2008},
volume = {46},
number = {11},
pages = {2823--2838},
month = {},
note = {}
}




@article {Williams1958,
	author = {Williams, F. A.},
	title = {Elementary Derivation of the Multicomponent Diffusion Equation},
	journal = {Amer. J. Phys.},
	year = {1958},
	volume = {26},
	number = {},
	pages = {467--469},
	month = {},
	note = {}
	}

@article {Williams1994,
author = {Williams, B. A. and Fleming, J. W.},
title = {Comparative Species Concentrations in {CH}$_4$/{O}$_2$/{A}r Flames Doped with {N}$_2${O}, {NO}, and {NO}$_2$},
journal = {Combust. Flame},
volume = {98},
pages = {93--106},
year = {1994}
}

@article {Williams2000a,
author = {Williams, F. A.},
title = {},
journal = {Prog. Energy Combust. Sci.},
year = {2000},
volume = {26},
number = {},
pages = {65},
month = {},
note = {}
}

@article {Williams2001,
author = {Williams, B. A.},
title = {Sensitivity of Calculated Extinction Strain Rate to Molecular Transport Formulation in Nonpremixed Counterflow Flames},
journal = {Combust. Flame},
year = {2001},
volume = {124},
number = {1--2},
pages = {330--333},
month = {},
note = {}
}

@article {WilliamsGrcar2008,
author = {Williams, F. A. and Grcar, J. F.},
title = {A hypothetical burning-velocity formula for very lean hydrogen-air mixtures},
journal = {Proc. Combust. Inst.},
year = {2008},
volume = {32},
number = {},
pages = {},
month = {},
note = {Accepted for oral presentation.  Also appears as technical report LBNL-XXXXX.}
}



@book {Williams2000,
author = {Williams, A. and Pourkashanian, M. and Jones, J. M. and Skorupska, N.},
title = {Combustion and Gassification of Coal},
year = {2000},
publisher = {Taylor and Francis},
edition = {},
address = {New York}
}


@Misc{WilliamsRoofline,
  author =       {Williams},
  title =        {Roofline Performance Model},
  howpublished = {Website},
  note = {\url{https://crd.lbl.gov/departments/computer-science/PAR/research/roofline/}}}

@techreport {Wilson1974,
author = {Wilson, R. E. and Lissaman, P. B. S.},
title = {Applied aerodynamics of wind power machines},
institution = {NSF},
year = {1974},
type = {Technical Report},
number = {NSF-RA-N-74-113},
address = {},
month = {July},
note = {}
}

@techreport {Wilson1976,
author = {Wilson, R. E. and Lissaman, P. B. S. and Walker, S. N.},
title = {Aerodynamic performance of wind turbines},
institution = {NSF},
year = {1976},
type = {Technical Report},
number = {NSF-RA-760228},
address = {},
month = {June},
note = {}
}

@techreport {Wilson1980,
author = {Wilson, R. E. and Walker, S. N.},
title = {Fixed wake analysis of the Darrieus rotor},
institution = {Sandia National Laboratories},
year = {1980},
type = {Technical Report},
number = {SAND-81-7026},
address = {},
month = {November},
note = {}
}

@book {Wolfram2003,
	author = {Wolfram, S.},
	editor = {},
	title = {The Mathematica Book},
	publisher = {Wolfram Media},
	year = {2003},
	volume = {},
	series = {},
	address = {Champaign},
	edition = {fifth},
	month = {},
	note = {}
	}

@incollection {Wolfrum2000,
author = {Wolfrum, J. and Dreier, T. and Ebert, V. and Schulz, C.},
title = {Laser-based Combustion Diagnostics},
booktitle = {Encyclopedia of Analytic Chemistry},
year = {2000},
volume = {},
number = {},
series = {},
type = {},
edition = {},
editor = {Meyers, R. A.},
pages = {2118--2148},
organization = {},
publisher = {John Wiley \& Sons},
address = {Chichester},
note = {}
}

@Inbook{Woodward1986,
author={Woodward, P. R.},
OPTeditor={Winkler, Karl-Heiz A. and Norman, Michael L.},
title={Piecewise-Parabolic Methods for Astrophysical Fluid Dynamics},
bookTitle={Astrophysical Radiation Hydrodynamics},
year={1986},
publisher={Springer Netherlands},
address={Dordrecht},
pages={245--326},
isbn={978-94-009-4754-2},
OPTdoi={10.1007/978-94-009-4754-2_8},
OPTurl={https://doi.org/10.1007/978-94-009-4754-2_8}
}

@article {Wooster2005,
author = {Wooster, M. J. and Roberts, G. and Perry, G. and Kaufman Y. J.},
title = {Retrieval of biomass combustion rates and totals from fire radiative power observations: FRP derivation and calibration relationship between biomass consumption and fire radiative energy release},
journal = {Journal of Geophysical Research},
year = {2005},
volume = {110},
number = {},
pages = {},
month = {},
note = {D24311}
}

@article {Wu2008,
author = {Wu, X. and Moin, P.},
title = {A direct numerical simulation study on the mean velocity characteristics in turbulent pipe flow},
journal = {J. Fluid Mech.},
volume = {608},
pages = {81--112},
year = {2008}
}

@article {Wu2016,
author = {Wu, J. and Wang, J. and Xiao, H.},
title = {A Bayesian Calibration–Prediction Method for Reducing Model-Form Uncertainties with Application in RANS Simulations},
journal = {Flow, Turbulence and Combustion},
volume = {97},
pages = {761--786},
year = {2016}
}

@inproceedings {Wu2017,
author = {Wu, X. and Moin, P. and Wallace, J. M. and Skarda, J. and Lozano-Duran, A. and Hickey, J-P.},
title = {Transitional-Turbulent Spots and Turbulent-Turbulent Spots in Boundary Layers},
booktitle = {Proceedings of National Academy of Sciences},
year = {2017},
editor = {},
volume = {},
pages = {},
organization = {},
publisher = {},
address = {},
month = {},
note = {}
}

@article {Wu2019,
author = {Wu, J. and Xiao, H. and Sun, R. and Wang, Q.},
title = {Reynolds-averaged {N}avier–{S}tokes equations with explicit data-driven Reynolds stress closure can be ill-conditioned},
journal = {J. Fluid Mech.},
volume = {869},
pages = {553--586},
year = {2019}
}

@article {WuRonney1999,
author = {Wu, M.-S. and Ronney, P. D. and Colantonio, R. O. and VanZandt, D. M.},
title = {Detailed Numerical Simulation of Flame Ball Structure and Dynamics},
journal = {Combust. Flame},
year = {1999},
volume = {116},
number = {},
pages = {387--397},
month = {},
note = {}
}

@article {Xu1993,
author = {Xu, Y. and Smooke, M. D. and Lin, P. and Long, M. B.},
title = {Primitive Variable Modeling of Multidimensional Laminar Flames},
journal = {Combust. Sci. Technol.},
year = {1993},
volume = {90},
number = {},
pages = {289},
month = {},
note = {}
}

@Misc{Xu2018,
  OPTkey =       {},
  author =    {Xu, R. and Wang, H.},
  title =     {A skeletal model for methane oxygen combustion in rocket engines},
  howpublished = {Stanford University},
  OPTmonth =     {},
  year =      {2018},
  OPTnote =      {},
  OPTannote =    {}
}

@article {Xue2003,
author = {Xue, H. S. and Aggarwal, S. K.},
title = {},
journal = {Combust. Flame},
year = {2003},
volume = {132},
number = {},
pages = {723--741},
month = {},
note = {}
}

 
 #         #
  #       #
   #     #
    #   #
     # #
      #
      #
      #
      #
      #

@article {Yang2000,
author = {Yang, G. and Causon, D. and Ingram, D.},
title = {Calculation of compressible flows about complex moving geometries using a three-dimensional {C}artesian cut cell method},
journal = {Int. J. Numer. Methods Fluids},
volume = {33},
pages = {1121--1151},
year = {2000}
}

@article {Yang2014,
author = {Zhiyin Yang},
title = {Large-eddy simulation: Past, present and the future},
journal = {Chinese Journal of Aeronautics},
volume = {28(1)},
pages = {11-24},
year = {2015}
}

@techreport {Yang2016,
author = {Yang, X. I. A. and Bose, S. T. and Moin, P.},
title = {A physics-based interpretation of the slip-wall {LES} model},
institution = {Center for Turbulence Research},
year = {2016},
type = {Annual Research Briefs 2016},
number = {},
address = {},
month = {},
note = {}
}

@article{Yankelson,
author = {Yankelson, L. and Steinvil, A. and Gershovitz, L. and Leshem-Rybinow, E. and Rurer, A and Viskin, S. and Kerern, G. and Banai, S. and Finkelson, A.},
title = {Atrial Fibrillation, Stroke, and Mortatity Rates After Transcatheter Aortic Valce Implantation},
journal = {American Journal of Cardiology},
volume = {114},
number = {},
pages = {1861-1866},
year = {},
}

@article{Ye1999,
author = {Ye, T. and Mittal, R. and Udaykumar, H. and Shyy, W.},
title = {An accurate {C}artesian grid method for viscous incompressible flows with complex immersed boundaries},
journal = {J. Comput. Phys.},
year = {1999},
volume = {156},
number = {},
pages = {209--240},
month = {},
note = {}
}

@article {Yelmgren1966,
author = {Yelmgren, K.},
title = {The autorotation of magnus rotors},
journal = {Department of Aerospace Engineering Report},
year = {1966},
note = {University of Notre Dame}
}

@InProceedings{Yin2018,
  author =       {Yin, S. and Guzik, S. and Gao, X.},
  title =        {A Fourth-Order Finite-Volume Method with Adaptive Mesh Refinement for Large-Eddy Simulation: Wall-Layer Models},
  booktitle = {2018 AIAA Aerospace Sciences Meeting},
  year =      2018,
  number =    {AIAA 2018-1304},
  organization = {AIAA SciTech Forum},
  note =      {\url{https://doi.org/10.2514/6.2018-1304}}
}

@article {Yokomori2003,
author = {Yokomori, T. and Mizomoto, M.},
title = {Flame temperatures along a laminar premixed flame with a non-uniform stretch rate},
journal = {Combust. Flame},
year = {2003},
volume = {135},
number = {4},
pages = {489--502},
month = {},
note = {}
}

@article {Yu1986,
author = {Yu, G. and Law, C. K. and Wu, C. K.},
title = {Laminar flame speed of Hydrogen + air mixtures with Hydrogen Addition},
journal = {Combust. Flame},
year = {1986},
volume = {63},
number = {},
pages = {339--347},
month = {},
note = {}
}

   #####
       #
      #
     #
    #
   #
   #####


@article {Zampini2016,
author = {Zampini, S. and Tu, X.},
title = {Addaptive multilevel {BDDC} deluxe algorithms for flow in porous media},
journal = {J. Sci. Comput.},
year = {2016},
volume = {},
number = {},
pages = {},
month = {},
note = {under revision}
}

@article {Zang1993, 
author = {Zang, Y. and Street, R. L. and Koseff, J. R.}, 
title = {A dynamic mixed subgrid-scale model and its application to turbulent recirculating flows},
journal = {Phys. Fluids}, 
year = {1993}, 
volume = {5}, 
number = {12}, 
pages = {3186--3196}, 
month = {July}, 
note = {} 
}

@book {Zeldovich1944,
author = {Zeldovich, Y. B.},
editor = {},
title = {Theory of Combustion and Detonation in Gases (in Russian)},
publisher = {Acad. Sci. USSR},
year = {1944},
volume = {},
series = {},
address = {},
edition = {},
month = {},
note = {}
}

@article {Zettervall2017,
author = {Zettervall, N. and Nordin-Bates, K. and Nilsson, E. J. K. and Fureby, C.}, 
title = {Large Eddy Simulation of a premixed bluff body stabilized flame using global and skeletal reaction mechanisms},
journal = {Combust. Flame},
year = {2017},
volume = {179}, 
pages = {1--22}
}

@article {Zsely2011,
author = {Zsely, I.G. and Nagy, T. and Simmie, J.M. and Curran, H. J. and Rutland, C. J.},
title = {Reduction of a detailed kinetic model for the ignition of methane/propane mixtures at gas turbine conditions using simulation error minimization methods},
journal = {Combust. Flame},
volume = {158},
pages = {1469--1479},
year = {2011}
}

@article {Zwietering1959,
author = {Zwietering, T. N.},
title = {The degree of mixing in continuous flow systems},
journal = {Chem. Eng. Sci.},
year = {1959},
volume = {11},
number = {},
pages = {1--15},
month = {},
note = {}
}

@article {Zhang2013,
author = {Zhang, M. and Zupanski, M. and Kim, M. and Knaff, J.},
title = {Assimilating AMSU-A Radiances in TC Core Area with NOAA Operational HWRF (2011) and a Hybrid Data Assimilation System: Danielle (2010)},
journal = {Mon. Wea. Rev.},
volume = {141},
pages = {3889--3907},
year = {2013}
}

@article {Zhang2012a,
author = {Zhang, Q. and Johansen, H. and Colella, P.},
title = {A fourth-order accurate finite-volume method with structured adaptive mesh refinement for solving the advection-diffusion equation},
journal = {SIAM J. Sci. Comput.},
volume = {34},
pages = {B179--B201},
year = {2012}
}

@Article{Zhang2003,
  author =       {Zhang, S. and Anderson, J. L.},
  title =        {Impact of spatially and temporally varying estimates of error covariance on assimilation in a simple atmospheric model},
  journal =      {Tellus A},
  year =         {2003},
  pages = {126--147},
  volume =    {55}
}

@Article{Zhang2012b,
  author =       {Zhang, S. and Liu, Z. and Rosati, A. and Delworth, T.},
  title =        {A study of enhancive parameter correction with coupled data assimilation for climate estimation and prediction using a simple coupled model},
  journal =      {Tellus A},
  year =         {2012},
  volume =    {64}
}


@article {Zhang1995,
author = {Zhang, S. and Rutland, C. J.},
title = {Premixed flame effects on turbulence and pressure-related terms},
journal = {Combust. Flame},
volume = {102},
pages = {447--461},
year = {1995}
}

@InProceedings{Zhao2018,
  author =       {Zhao, T. and Williams, S. and Hall, M. and Johansen, H.},
  title =        {Delivering Performance Portable Stencil Computations on CPUs and GPUs Using Bricks},
  booktitle =    {International Workshop on Performance, Portability and Productivity in HPC (P3HPC)},
  year =         2018
}

@article {Zhong1998,
author = {Zhong, X.},
title = {High-order finite-difference schemes for numerical simulation of hypersonic boundary-layer transition},
journal = JCP,
year = {1998},
volume = {144},
pages = {662--709}
}

@article {Zhong2001,
author = {Zhong, X.},
title = {Leading-edge receptivity to free stream disturbance waves for hypersonic flow over a parabola},
journal = {Journal of Fluid Mechanics},
year = {2001},
volume = {441},
pages = {315--367}
}

@inproceedings {Zhou1997,
author = {Zhou, J. and Masutani, S. M. and Ishimura, D. M. and Turn, S. Q. and Kinoshita, C. M.},
title = {},
booktitle = {IECEC-97, Proc. 32nd Int. Energy Conv. Eng. Conf.},
year = {1997},
editor = {},
volume = {4},
pages = {1785--1790},
organization = {},
publisher = {},
address = {},
month = {},
note = {}
}

@article {ZhuNishioka1998,
author = {X. L. Zhu and M. Nishioka and T. Takeno},
title = {{NO} emission characteristics of methane-air coflow partially premixed flame},
journal = {Proc. Combust. Inst.},
year = {1998},
volume = {27},
pages = {1369--1376}
}

@article {Zimont1969,
author = {Zimont, V. L. and Trushin, Y. M.},
title = {Total combustion kinetics of hydrocarbon fuels},
journal = {Comb. Expl. Shock Wave},
year = {1969},
volume = {5},
number = {},
pages = {391--194},
month = {},
note = {}
}

@techreport {Zipfel1970,
author = {Zipfel, P. H.},
title = {On flight dynamics of magnus rotors},
institution = {Department of the Army},
year = {1970},
type = {Technical Report},
number = {117},
address = {},
month = {November},
note = {}
}

@article {Zuckerman2006,
author = {Zuckerman, N. and Lior, N.},
title = {Jet impingement heat transfer, physics, correlations and numerical modeling},
journal = {Adv. Heat Transfer},
year = {2006},
volume = {39},
number = {},
pages = {565--631},
month = {},
note = {}
}
@article {Zupanski1993,
author = {Zupanski, M.},
title = {Regional Four-Dimensional Variational Data Assimilation in a Quasi-Operational Forecasting Environment},
journal = {Monthly Weather Review},
year = {1993},
volume = {121},
number = {},
pages = {2396-2408},
month = {},
note = {}
}
@article {Zupanski1997,
author = {Zupanski, D. and Zupanski, M.},
title = {Model Error Estimation Employing an Ensemble Data Assimilation Approach},
journal = {Monthly Weather Review},
year = {1997},
volume = {134},
number = {},
pages = {1337--1354},
month = {},
note = {}
}

@article {Zupanski2005,
author = {Zupanski, M.},
title = {Maximum Likelihood Ensemble Filter: Theoretical aspects},
journal = {Mon. Wea. Rev.},
year = {2005},
volume = {133},
number = {},
pages = {1710--1726},
month = {},
note = {}
}

@article {Zupanski2007,
author = {Zupanski, D. and Hou, A. Y. and Zhang, S. Q. and Zupanski, M. and Kummerow, C. D. and Cheung, S. H.},
title = {Application of information theory in ensemble data assimilation},
journal = {Q. J. R. Meteorol. Soc.},
year = {2007},
volume = {133},
number = {},
pages = {1533--1545},
month = {},
note = {}
}

@article {Zupanski2008a,
author = {Zupanski, M. and Lokupitiya, R. S. and Denning, A. S. and Kawa, S. R. and Gurney, K. R.},
title = {Estimation of global $CO_{2}$ fluxes at regional scale using the maximum likelihood ensemble filter},
journal = {Q. J. R. Meteorol. Soc.},
year = {2008},
volume = {134},
number = {},
pages = {1039--1050},
month = {},
note = {}
}


@article {Zupanski2008b,
author = {Zupanski, M. and Navon, I. M. and Zupanski, D},
title = {The Maximum Likelihood Ensemble Filter as a non-differentiable minimization algorithm},
journal = {Q. J. R. Meteorol. Soc.},
year = {2008},
volume = {113},
number = {D20110},
pages = {},
month = {},
note = {}
}

@article {Zupanski2008c,
author = {Zupanski, M. and Navon, I. M. and Zupanski, D.},
title = {The Maximum Likelihood Ensemble Filter as a non-differentiable minimization algorithm},
journal = {Q. J. R. Meteorol. Soc.},
year = {2008},
volume = {134},
number = {},
pages = {1039--1050},
month = {},
note = {}
}

@incollection {Zupanski2013,
author = {Zupanski, M.},
title = {All-sky satellite radiance data assimilation: Methodology and Challenges},
booktitle = {Data Assimilation for Atmospheric, Oceanic, and Hydrologic Applications},
year = {2013},
volume = {II},
number = {},
series = {},
type = {},
edition = {},
editor = {Park, S. K. and Xu, L.},
pages = {465--488},
organization = {},
publisher = {Springer},
address = {}
}

@article {Zupanski2016a,
author = {Zupanski, M.},
title = {Reduced rank static error covariance for high-dimensional applications},
journal = {Int. J. Numer. Meth. Fluids},
year = {2016},
volume = {},
number = {},
pages = {},
month = {},
note = {In print. doi: 10.1002/fld.4264}
}

@incollection {Zupanski2016b,
author = {Zupanski, M.},
title = {Data assimilation for coupled modeling systems},
booktitle = {Data Assimilation for Atmospheric, Oceanic, and Hydrologic Applications},
year = {2016},
volume = {III},
number = {},
series = {},
type = {},
edition = {},
editor = {Park, S. K. and Xu, L.},
pages = {},
organization = {},
publisher = {Springer},
address = {},
note = {In print}
}




@article{YamamotoETAL:2008,
	author = {K. Yamamoto and M. Ozeki and N. Hayashi and H. Yamashita},
	title = {Burning velocity and OH concentration in premixed combustion},
	journal = {Proc. Combust. Inst.},
	volume = 32,
	year = 2009,
	pages = {1227-1235}
}

	
@Misc{bluffbody,
  OPTkey =       {},
  OPTauthor =    {},
  OPTtitle =     {},
  OPThowpublished = {},
  OPTmonth =     {},
  OPTyear =      {},
  note =      {BLUFF-BODY FLOWS AND FLAMES},
  annote =    {http://sydney.edu.au/engineering/aeromech/thermofluids/bluff.htm}
}

@Misc{WebsiteB,
  OPTkey =       {},
  OPTauthor =    {},
  OPTtitle =     {},
  OPThowpublished = {},
  OPTmonth =     {},
  OPTyear =      {},
  note =      {TNF Workshop Abstract},
  annote =    {http://www.sandia.gov/TNF/abstract.html}
}

@ARTICLE{Ar2,
AUTHOR="Arulampalam, M. S. and  Maskell, S. and Gordon, N. and Clapp, T.",
TITLE="A tutorial on particle filters for online nonlinear/nongaussian
{B}ayesia tracking",
JOURNAL="IEEE Trans. Sig. Proc.",
 YEAR=2002,
VOLUME=50,
PAGES="174--188"
}

@article {StuartInverse,
    AUTHOR = {Stuart, A. M.},
     TITLE = {Inverse problems: a {B}ayesian perspective},
   JOURNAL = {Acta Numer.},
  FJOURNAL = {Acta Numerica},
    VOLUME = {19},
      YEAR = {2010},
     PAGES = {451--559},
      ISSN = {0962-4929},
   MRCLASS = {65J22 (35R25 35R30 62C10 65J20)},
  MRNUMBER = {2652785 (2011i:65093)},
MRREVIEWER = {Ruben D. Spies},
}

@PhdThesis{Yuen2009,
  author =       {Frank T.C. Yuen},
  title =        {Experimental Investigation of the Dynamics and Structure of Lean-Premixed Turbulent Combustion },
  school =       {University of Toronto Institute for Aerospace Studies},
  year =         {2009} 
}


@BOOK{Do2,
 AUTHOR="Doucet, A  and de Freitas, N.  and  Gordon, N.",
 TITLE = "Sequential {M}onte {C}arlo Methods in Practice",
 PUBLISHER = "Springer, New York",
 YEAR = 2001
}


@ARTICLE{Smagorinsky1963,
AUTHOR="J. Smagorinsky",
TITLE="General circulation experiments with the primitive equation",
JOURNAL="Mon. Wea. Rev.",
 YEAR=1963,
VOLUME=91,
PAGES="99--152"
}


@ARTICLE{Sny,
AUTHOR="Snyder, C. and Bengtsson, T.  and Bickel, P. and Anderson, J.",
TITLE="Obstacles to high-dimensional particle filtering",
JOURNAL=" Mon. Wea. Rev.",
 YEAR=2008,
VOLUME=136,
PAGES="4629--4640"
}

@article{Chopard2015,
author = {Chopard, R. and Teiger, E. and Meneveau, N. and Chocron, S. and Gilard, M. and Laskar, M. and Eltchaninoff, H. and Lung, B. and Leprince, P. and Chevreul, K. and Prat, A. and Lievre, M. and Leguerrier, A. and Donzeau-Geuge, P. and Fajadet, J. and Mouillet, G. and Shcielle, F.},
title = {Baseline Characteristics and Prognostic Implications of Pre-Existing and New-Onset Atrial Fibrillation After Transcatheter Aoritic Valve Implantations: Results From the FRANCE-2 Registry},
journal = {JACC Cardiovastular interventions},
volume = {8},
number = {},
pages = {1346-1355},
year = {2015},
}

@ARTICLE{CT1,
AUTHOR="Chorin, A. J.  and  Tu, X.",
TITLE="Implicit sampling for particle filters",
JOURNAL="Proc. Nat. Acad. Sc. USA",
YEAR=2009,
VOLUME=106,
PAGES="17249--17254 "
}

@ARTICLE{CMT,
AUTHOR="Chorin, A. J.  and Morzfeld, M.  and Tu, X.",
TITLE="Implicit Particle Filters for data assimilation",
JOURNAL = {Commun. Appl. Math. Comput. Sci.},
FJOURNAL = {Communications in Applied Mathematics and Computational
 Science},
VOLUME = {5},
YEAR = {2010},
PAGES = {221--240}
}

@article{Morzfeld2012, 
title = "A random map implementation of implicit filters",
journal = JCP,
volume = "231",
number = "4",
pages = "2049-2066",
year = "2012",
 AUTHOR = "Morzfeld, M. and Tu, X. and Atkins, E. and
              Chorin, A.",
}


@Article{Xie2012,
  author =       {Xie, C.},
  title =        {Interactive Heat Transfer Simulations for Everyone},
  journal =      {The Physics Teacher},
  year =         {2012},
  volume =    {50},
  number =    {4},
  pages =     {237--240}
}
@Misc{tbb,
  OPTkey =       {},
  OPTauthor =    {},
  OPTtitle =     {},
  howpublished = {https://en.wikipedia.org/wiki/Threading Building Blocks},
  OPTmonth =     {},
  OPTyear =      {},
  OPTnote =      {},
  OPTannote =    {}
}
@Misc{computing,
  OPTkey =       {},
  OPTauthor =    {},
  OPTtitle =     {},
  howpublished = {https://en.wikipedia.org/wiki/WomeninComputing},
  OPTmonth =     {},
  OPTyear =      {},
  OPTnote =      {},
  OPTannote =    {}
}
@Misc{standards,
  OPTkey =       {},
  OPTauthor =    {},
  OPTtitle =     {},
  howpublished = {https://www.cde.state.co.us/coscience/statestandards},
  OPTmonth =     {},
  OPTyear =      {},
  OPTnote =      {},
  OPTannote =    {}
}
@Article{Lesieur1996,
  author =       {Lesieur, M. and Metais, O.},
  title =        {New trends in large eddy simulations of turbulence},
  journal =      {Annu Rev Fluid Mech},
  year =         {1996},
  volume =       {28},
  number =       {1},
  pages =        {45-82}
}
@Article{Piomelli1999,
  author =       {Piomelli, U.},
  title =        {Large-eddy simulation: achievements and challenges},
  journal =      {Prog Aerosp Sci},
  year =         {1999},
  volume =       {35},
  number =       {4},
  pages =        {335--362}
}



@Article{Pitsch2006,
  author =       {Pitsch, H.},
  title =        {Large-eddy simulation of turbulent combustion},
  journal =      {Annu Rev Fluid Mech},
  year =         {2006},
  volume =       {38},
  pages =        {453--482}
}

@Article{Pitsch2008,
  author =       {Pitsch, H. and Desjardins, O. and Balarac, G. and Ihme, M.},
  title =        {Large-eddy simulation of turbulent reacting flows},
  journal =      {Prog Aerosp Sci},
  year =         {2008},
  volume =       {44},
  number =       {6},
  pages =        {466-478}
}
@Article{Guermond2004,
  author =       {Guermond, J. L. and Oden, J. T. and Prudhomme, S.},
  title =        {Mathematical perspectives on large eddy simulation models for turbulent flows},
  journal =      {J Math Fluid Mech },
  year =         {2004},
  volume =       {6},
  number =       {2},
  pages =        {194-248}
}
@Article{Boudier2009,
  author =       {Boudier, G. and Lamarque, N. and Staffelbach, G. and Gicquel, L. Y. M. and Poinsot, T.},
  title =        {Thermo-acoustic stability of a helicopter gas turbine combustor using large-eddy simulations},
  journal =      {Int J Aeroacoustics},
  year =         {2009},
  volume =       {8},
  number =       {1},
  pages =        {69-94}
}

@Article{Staffelbach2009,
  author =       {Staffelback, G. and Gicquel, L. Y. M. and Boudier, G. and Poinsot, T.},
  title =        {Large eddy simulation of self-excited azimuthal modes in annular combustors},
  journal =      {Proc Combust Inst},
  year =         {2009},
  volume =       {32},
  number =       {2},
  pages =        {2909--2916}
}
@Article{Wolf2009,
  author =       {Wolf, P. and Staffelbach, G. and Roux, A. and Gicquel, L. Y. M. and Poinsot, T. and Moureau, V.},
  title =        {Massively parallel LES of azimuthal thermo-acoustic instabilities in annular gas turbines},
  journal =      {C R Acad Sci M\'{e}c},
  year =         {2009},
  volume =       {337},
  pages =        {385--394}
}

@Article{Wolf2012,
  author =       {Wolf, P. and Balakrishnan, R. and Staffelbach, G. and Gicquel, L. Y. M. and Poinsot, T.},
  title =        {Using {LES} to study reacting flows and instabilities in annular combustion chambers},
  journal =      {Flow Turbul Combust},
  year =         {2012},
  volume =       {88},
  number =       {1-2},
  pages =        {191--206}
}

@InProceedings{Chapuis2010,
  author =       {Chapuis, M. and Fureby, C. and Fedina, E. and Alin, N. and Tegn$\acute{e}$r, J.},
  title =        {{LES} modeling of combustion applications using OpenFOAM},
  booktitle =    {Proceedings of V European conference on computational dynamics},
  year =         {2010},
  editor =       {Pereira, J. and Sequeira, A.},
  pages =        {1--20},
  month =        {June},
  address =      {Lisbon, Portugal}
}

@Article{Eggenspiele2004,
  author =       {Eggenspieler G. and Menon S. },
  title =        {Large-eddy simulation of pollutant emission in a
DOE-HAT combustor},
  journal =      {J. Propuls. Power},
  year =         {2004},
  volume =       {20},
  number =       {6},
  pages =        {1076--1085}
}
@Article{DiMare2004,
  author =       {Di Mare F. and Jones W. and Menzies K.},
  title =        {Large eddy simulation of a model gas turbine
combustor},
  journal =      {Combust. Flame},
  year =         {2004},
  volume =       {137},
  number =       {3},
  pages =        {278--294}
}
@Article{Selle2004,
  author =       {Selle L. and Lartigue G. and Poinsot T. and Koch R and Schildmacher K.},
  title =        {Compressible  large  eddy  simulation  of  turbulent  combustion  in  complex  geometry on unstructured meshes},
  journal =      {Combust. Flame},
  year =         {2004},
  volume =       {137},
  number =       {4},
  pages =        {489--505}
}
@Article{Stone2003,
  author =       {Stone C. and Menon S.},
  title =        {Open-loop control of combustion instabilities in a model
gas turbine combustor},
  journal =      {J. Turbul. },
  year =         {2003},
  volume =       {4},
  number =       {},
  pages =        {20}
}
@Article{Sommerer2004,
  author =       {Sommerer Y. and Galley D. and Poinsot T. and  Ducruix S. and Lacas F. and Veynante D.},
  title =        {Large eddy
simulation and experimental study of flashback and blow-off in a lean partially
premixed swirled burner},
  journal =      {J. Turbul. },
  year =         {2004},
  volume =       {4},
  number =       {},
  pages =        {037}
}
 

@TechReport{Wall2005,
  author =       {Wall C.T. and Moin P.},
  title =        {Numerical methods for large eddy simulation of acoustic
combustion instabilities},
  institution =  {Stanford, CA: Stanford Univ},
  year =         {2005},
  OPTkey =       {},
  OPTtype =      {},
  OPTnumber =    {},
  OPTaddress =   {},
  OPTmonth =     {},
  OPTnote =      {},
  OPTannote =    {}
}
@TechReport{You2008,
  author =       {You, D. and Ham, F. and Moin, P.},
  title =        {Large-eddy simulation analysis of turbulent
combustion in a gas turbine engine combustor},
  institution =  {Stanford, CA: Stanford Univ},
  year =         {2008},
  OPTkey =       {},
  OPTtype =      {},
  OPTnumber =    {},
  OPTaddress =   {},
  OPTmonth =     {},
  OPTnote =      {},
  OPTannote =    {}
}
@Article{Shinjo2003,
  author =       {Shinjo J. and Mizobuchi Y. and Ogawa S.},
  title =        {LES of unstable combustion in a gas turbine
combustor },
  journal =      {High Perform. Comput.},
  year =         {2003},
  volume =       {},
  number =       {2858},
  pages =        {234--244}
}

@Article{Angelberger2000,
  author =       {Angelberger C. and Veynante D. and Egolfopoulos F.},
  title =        {{LES} of chemical and acoustic
forcing of a premixed dump combustor},
  journal =      {Flow Turbul. Combust.},
  year =         {2000},
  volume =       {65},
  number =       {2},
  pages =        {205--222}
}
@Article{Gicquel2012,
  author =       {Gicquel, L. and  Staffelbach, G. and  Poinsot, T.},
  title =        {Large  Eddy Simulations  of  gaseous  flames  in  gas  turbine  combustion  chambers},
  journal =      {Progress in Energy and Combustion Science},
  year =         {2012},
  volume =       {38},
  number =       {6},
  pages =        {782--817}
}
@Article{Oefelein2006,
  author =       {Oefelein, J.C. and Schefer, R.W. and Barlow, R.S.},
  title =        {Toward Validation of Large Eddy Simulation for Turbulent Combustion},
  journal =      {AIAA Journal},
  year =         {2006},
  volume =       {44},
  number =       {3},
  pages =        {418--433}
}


@Article{Lim2015,
  author =       {Lim, S. J. and Park, S. K. and Zupanski, M.},
  title =        {Ensemble Data Assimilation of Total Column Ozone Using a Coupled Meteorology-Chemistry Model and Its Impact on the Structure of Typhoon Nabi (2005)},
  journal =      {Atmospheric Chemistry and Physics},
  year =         {2015},
  volume =    {15},
  pages =     {10019--10031} 
}
 
@article {ZhangSQ2013,
author = {Zhang, S. Q. and Zupanski, M. and Hou, A. Y. and Lin, X. and Cheung, S. H.},
title = {Assimilation of Precipitation-Affected Radiances in a Cloud-Resolving WRF Ensemble Data Assimilation System},
journal = {Mon. Wea. Rev.},
year = {2013},
volume = {141},
number = {},
pages = { 754--772},
month = {},
note = {}
}
@article {Courtier1994,
author = {Courtier, P. and Thepaut, J-N. and Hollingsworth, A.},
title = {A Strategy for Operational Implementation of 4D-Var, Using an Incremental Approach},
journal = {Quart. J. Roy. Meteor. Soc.},
volume = {120},
pages = {1367--1387},
year = {1994}
}

@article {Courtier1997,
author = {Courtier, P.},
title = {Dual formulation of four-dimensional variational assimilation},
journal = {Quart. J. Roy. Meteor. Soc.},
volume = {123},
pages = {2449--2461},
year = {1997}
}



@article {GaoXue2008,
author = {Gao, J. and Xue, M.},
title = {An Efficient Dual-Resolution Approach for Ensemble Data Assimilation and Tests with Simulated Doppler Radar Data},
journal = {Mon. Wea. Rev.},
year = {2008},
volume = {136},
number = {},
pages = {945-963},
month = {},
note = {}
}

@article {Batten2004,
author = {Batten, P. and Goldberg, U. and Chakravarthy, S.},
title = {Interfacing Statistical Turbulence Closures with Large-Eddy Simulation},
journal = {AIAA Journal},
year = {2004},
volume = {42},
number = {3},
pages = {485-492},
month = {},
note = {}
}

@article {Piomelli2003,
author = {Piomelli, U. and Balaras, E. and Pasinato, H. and Squires, K. and Spalart, P.},
title = {The Inner-Outer Layer Interface in Large-Eddy Simulations with Wall-Layer Models},
journal = {International Journal of heat and fluid flow},
year = {2003},
volume = {24},
number = {4},
pages = {538-550},
month = {},
note = {}
}
 
@PhdThesis{Xun2015,
  author =       {Xun, Q.},
  title =        { A Novel Dynamic Forcing Scheme Incorporating Backscatter for Hybrid RANS/LES},
  school =       {University of Manitoba},
  year =         {2015} 
}

@article {Xun2016,
author = {Xun, Q. and Wang, B.},
title = {Hybrid RANS/LES of Turbulent Flow in a Rotating Rib-Roughened Channel},
journal = PF,
year = {2016},
volume = {28},
number = {7},
pages = {},
month = {},
note = {}
}
@inproceedings {Wabel2016a,
author = {Timothy M. Wabel and Aaron W. Skiba and Jacob E. Temme and James F. Driscoll},
title = {Measurements to Determine the Regimes of Premixed Flames in Extreme Turbulence},
booktitle = {36th Intl Symposium on Combustion},
year = {2016},
volume = {},
number = {},
pages = {},
month = {Aug},
note = {}
}
@inproceedings {Wabel2016b,
author = {Timothy M. Wabel and Aaron W. Skiba and James F. Driscoll},
title = {Turbulent Burning Velocity Measurements: Extended to Extreme Levels of Turbulence},
booktitle = {36th Intl Symposium on Combustion},
year = {2016},
volume = {},
number = {},
pages = {},
month = {Aug},
note = {}
}
@Article{Davidson2005,
  author =       {Davidson, L. and Dahlstr\"{o}m, S.},
  title =        {Hybrid LES-RANS: An Approach to Make LES Applicable at
High Reynolds Number},
  journal =      {International Journal of Computational Fluid Dynamics},
  year =         {2005},
  volume =    {19},
  number =    {6},
  pages =     {415–427}
 }
@Article{Davidson2006,
  author =       {Davidson, L. and Billson, M.},
  title =        {Hybrid LES-RANS Using Synthesized Turbulent Fluctuations for
Forcing in the Interface Region},
  journal =      {International Journal of Heat and Fluid Flow},
  year =         {2006},
  volume =    {27},
  number =    {6},
  pages =     {1028–1042}
  }
  @article{Laney06vis,
	Author = {D. Laney and P.-T. Bremer and A. Mascarenhas and P. Miller and V. Pascucci},
	Date-Added = {2012-09-19 20:32:21 -0700},
	Date-Modified = {2012-09-19 20:32:21 -0700},
	Journal = {IEEE Trans. Visualization and Computer Graphics (TVCG) / Proc.of IEEE Visualization},
	Number = {5},
	Organization = {IEEE},
	Pages = {1052-1060},
	Title = {Understanding the Structure of the Turbulent Mixing Layer in Hydrodynamic Instabilities},
	Volume = {12},
	Year = {2006}}

@inproceedings{Gyulassy12ipdps,
	Address = {Shanghai, China},
	Author = {A. Gyulassy and T. Peterka and V. Pascucci and R. Ross},
	Booktitle = {Proceedings of IPDPS '12},
	Date-Added = {2012-09-19 20:32:10 -0700},
	Date-Modified = {2012-09-19 20:32:10 -0700},
	Title = {Characterizing the Parallel Computation of Morse-Smale Complexes},
	Year = {2012}}

@article{Bennett11tvcg,
	Author = {J. Bennett and V. Krishnamurthy and S. Liu and V. Pascucci and R. Grout and J. Chen and P.-T. Bremer},
	Date-Added = {2012-09-19 20:32:00 -0700},
	Date-Modified = {2012-09-19 20:32:00 -0700},
	Journal = {{IEEE} Trans. Vis. Comp. Graph.},
	Number = {12},
	Pages = {1822-1831},
	Title = {Feature-Based Statistical Analysis of Combustion Simulation Data},
	Volume = {17},
	Year = {2011}}

@article{Bremer10tvcg,
	Author = {P.-T. Bremer and G. Weber and J. Tierny and V. Pascucci and M. Day and J. B. Bell},
	Date-Added = {2012-09-19 20:31:46 -0700},
	Date-Modified = {2012-09-19 20:31:46 -0700},
	Journal = {IEEE Trans. on Visualization and Computer Graphics},
	Number = {9},
	Pages = {1307-1324},
	Title = {Interactive Exploration and Analysis of Large Scale Simulations Using Topology-based Data Segmentation},
	Volume = {17},
	Year = {2011}}

@article{Day09,
	Author = {M. Day and J. Bell and P.-T. Bremer and V. Pascucci and V. Beckner and M. Lijewski},
	Date-Added = {2012-09-19 20:31:39 -0700},
	Date-Modified = {2012-09-19 20:31:39 -0700},
	Journal = {Combust. Flame},
	Pages = {1035-1045},
	Title = {Turbulence effects on cellular burning structures in lean premixed hydrogen flames},
	Volume = {156},
	Year = {2009}}

@inbook{Mascarenhas09,
	Author = {A. Mascarenhas and R. W. Grout and P.-T. Bremer and E. R. Hawkes and V. Pascucci and J.H. Chen},
	Booktitle = {Proceedings of the 3rd TopoInVis Workshop},
	Date-Added = {2012-09-19 20:31:32 -0700},
	Date-Modified = {2012-09-19 20:31:32 -0700},
	Pages = {229-240},
	Publisher = {Springer},
	Rating = {0},
	Series = {Mathematics and Visualization},
	Title = {Topological feature extraction for comparison of terascale combustion simulation data},
	Year = {2011}}

@article{Bremer09tvcg,
	Author = {P.-T. Bremer and G. Weber and V. Pascucci and M. Day and J. Bell},
	Date-Added = {2012-09-19 20:30:14 -0700},
	Date-Modified = {2012-09-19 20:30:14 -0700},
	Journal = {{IEEE} Transactions on Visualization and Computer Graphics},
	Number = {2},
	Pages = {248-260},
	Title = {Analyzing and Tracking Burning Structures in Lean Premixed Hydrogen Flames},
	Volume = {16},
	Year = {2010}}

@article{Gyulassy08tvcg,
	Author = {A. Gyulassy and P.-T. Bremer and V. Pascucci and B. Hamann},
	Date-Added = {2012-09-19 20:28:40 -0700},
	Date-Modified = {2012-09-19 20:28:40 -0700},
	Journal = {{IEEE} Transactions on Visualization and Computer Graphics},
	Number = {6},
	Pages = {1619-1626},
	Title = {A Practical Approach to {M}orse-{S}male Complex Computation: Scalability and Generality},
	Volume = {14},
	Year = {2008}}

@article{Gyulassy07btvcg,
	Author = {A. Gyulassy and M. Duchaineau and V. Natarajan and V. Pascucci and E.Bringa and A. Higginbotham and B. Hamann},
	Date-Added = {2012-09-19 20:28:40 -0700},
	Date-Modified = {2012-09-19 20:28:40 -0700},
	Journal = {IEEE Transactions on Computer Graphics and Visualization (TVCG)},
	Number = {6},
	Pages = {1432--1439},
	Title = {Topologically Clean Distance Fields},
	Volume = {13},
	Year = {2007}}

@article{Gerber10,
	Author = {S. Gerber and P.-T. Bremer and V. Pascucci and R. Whitaker},
	Date-Added = {2012-09-19 20:28:23 -0700},
	Date-Modified = {2012-09-19 20:28:23 -0700},
	Journal = {{IEEE} Transactions on Visualization and Computer Graphics},
	Number = {6},
	Pages = {1271-1280},
	Title = {Visual Exploration of High Dimensional Scalar Functions},
	Volume = {16},
	Year = {2010}}

@conference{Bennett12sc,
	Author = {J. Bennett and H. Abbasi and P.-T. Bremer and R. Grout and A. Gyulassy and T. Jin and S. Klasky and H. Kolla and M. Parashar and V. Pascucci and P. Pebay and D. Thompson and H. Yu and F. Zhang and J. Chen},
	Booktitle = {Proc. {ACM/IEEE} Conference on Supercomputing (SC12)},
	Date-Added = {2012-09-19 20:27:51 -0700},
	Date-Modified = {2012-09-19 20:27:51 -0700},
	Title = {Combining In-situ and In-transit Processing to Enable Extreme-Scale Scientific Analysis},
	Year = {2012}}

@article{Gyulassy12tvcg,
	Author = {A. Gyulassy and P.-T. Bremer and V. Pascucci},
	Date-Added = {2012-09-19 20:27:51 -0700},
	Date-Modified = {2012-09-19 20:27:51 -0700},
	Journal = {{IEEE} Transactions on Visualization and Computer Graphics},
	Title = {Computing {M}orse-{S}male Complexes with Accurate Geometry},
	Volume = {to appear},
	Year = {2012}}

@ARTICLE{woodwardColella:1984,
author = {Woodward, P. R. and Colella, P.},
title = {The numerical simulation of two-dimensional fluid flow with strong
shocks},
journal= JCP,
volume = {54},
number={1},
year = {1984},
pages = {115--173},
issn = {0021-9991},
OPTdoi = {https://doi.org/10.1016/0021-9991(84)90142-6},
OPTurl = {http://www.sciencedirect.com/science/article/pii/0021999184901426}
}


@Misc{BoxLib,
 author = {},
 title = {BoxLib Codes},
 note = {https://boxlib-codes.github.io/},
 month = {},
 year = {}
}
@Misc{SAMRAI,
 author = {},
 title = {SAMRAI: Structured Adaptive Mesh Refinement Application Infrastructure},
 note = {https://computation.llnl.gov/projects/samrai},
 month = {},
 year = {}
}
@Misc{AMReX,
 author = {},
 title = {AMReX: Software Framework for Block Structured AMR},
 note = {https://amrex-codes.github.io/amrex/},
 month = {},
 year = {}
}
@Misc{p4est,
 author = {},
 title = {p4est: Parallel AMR on Forests of Octrees},
 note = {http://www.p4est.org/},
 month = {},
 year = {}
}
@Misc{hwloc,
 author = {},
 title = {Portable Hardware Locality (hwloc)},
 note = {https://www.open-mpi.org/projects/hwloc/},
 month = {},
 year = {}
}

@Misc{NASALRC,
 author = {},
 title = {NASA Langley Research Center turbulence modeling resource},
 note = {https://turbmodels.larc.nasa.gov/flatplate.html},
 month = {},
 year = {}
}

@Misc{FluentSAModel,
 author = {},
 title = {ANSYS Fluent Spalart-Allmaras Model},
 note = {http://www.afs.enea.it/project/neptunius/docs/fluent/html/th/node48.htm},
 month = {},
 year = {}
}
@Misc{doeGov,
 author = {},
 title = {Advanced Scientific Computing Research},
 note = {https://www.energy.gov/science/ascr/advanced-scientific-computing-research},
 month = {},
 year = {}
}
@Misc{AerospaceAmerica,
 author = {Keith Button},
 title = {Decoding the boundary layer at hypersonic speeds},
 note = {https://aerospaceamerica.aiaa.org/departments/decoding-the-boundary-layer-at-hypersonic-speeds/},
 month = {October},
 year = {2019}
}

@Misc{Cart3D,
 author = {},
 title = { },
 note = {https://www.nas.nasa.gov/publications/software/docs/cart3d/pages/cart3Dhome.html},
 month = {},
 year = {}
}

@Misc{IBAMR,
 author = {},
 title = { },
 note = {https://github.com/IBAMR/IBAMR},
 month = {},
 year = {}
}

@Misc{Pointwise,
 author = {},
 title = {},
 note = {https://www.pointwise.com/index.html},
 month = {},
 year = {}
}

@Misc{Chord,
 author = {},
 title = {},
 note = {https://cfd-repo.engr.colostate.edu/},
 month = {},
 year = {}
}
 
@TechReport{Voke1990,
  author =       {Voke, P.R.},
  title =        {Multiple mesh simulation of turbulent flow},
  institution =  {Queen Mary and Westfield College, University of London, London, U.K.},
  year =         {1990},
  OPTkey =       {},
  OPTtype =      {},
  number =    {QMW EP-1082},
  OPTaddress =   {},
  OPTmonth =     {},
  OPTnote =      {},
  OPTannote =    {}
}

@Article{Tziperman1993,
  author =       {Tziperman, E. and Yavneh, I. and Ta'asan, S.},
  title =        {Multilevel turbulence simulations},
  journal =      {Europhys. Lett.},
  year =         {1993},
  OPTkey =       {},
  volume =    {24},
  number =    {4},
  pages =     {239-244},
  OPTmonth =     {},
  OPTnote =      {},
  OPTannote =    {}
}

@Article{Liu1994,
  author =       {Liu, C. and Liu, Z.},
  title =        {Fourth order finite difference and multigrid methods for modeling instabilities in flat plat boundary layers - 2D and 3D approaches},
  journal =      {Computers Fluids},
  year =         {1994},
  OPTkey =       {},
  volume =    {23},
  number =    {7},
  pages =     {955-982},
  OPTmonth =     {},
  OPTnote =      {},
  OPTannote =    {}
}

@Article{Liu1995,
  author =       {Liu, C. and Liu, Z.},
  title =        {Multigrid mapping in box relaxation for simulation of the whole process of flow transition in 3D boundary layers},
  journal =      {J. Comput. Phys.},
  year =         {1995},
  OPTkey =       {},
  volume =    {119},
  OPTnumber =    {},
  pages =     {325-341},
  OPTmonth =     {},
  OPTnote =      {},
  OPTannote =    {}
}

@Article{Sagaut2000,
  author =       {Sagaut, P. and Labourasse, E. and Qu\'{e}m\'{e}r\'{e}, P. and Terracol, M.},
  title =        {Multiscale approaches for unsteady simulation of turbulent flows},
  journal =      {Int. J. Nonlinear Sciences and Numerical Simulation},
  year =         {200},
  OPTkey =       {},
  volume =    {1},
  number =    {4},
  OPTpages =     {},
  OPTmonth =     {},
  OPTnote =      {},
  OPTannote =    {}
}

@Article{Terracol2003,
  author =       {Terracol, M. and Sagaut, P. and Basdevant, C.},
  title =        {A time self-adaptive multi-level algorithm for large-eddy simulation of turbulent compressible flows},
  journal =      {J. Comput. Phys.},
  year =         {},
  OPTkey =       {},
  volume =    {184},
  OPTnumber =    {},
  pages =     {339-365},
  OPTmonth =     {},
  OPTnote =      {},
  OPTannote =    {}
}

